### 2014-04-25 tex/ms.tex
start paper

\documentclass[12pt, preprint]{aastex}

\input{vc}

\begin{document}

Hello World!
This version of the paper was generated
  from a git repository available at \url{http://github.com/bd-j/something/}
  with git hash \texttt{\githash} (\gitdate).

\end{document}

### 2014-04-25 tex/ms.tex

@@
 
+\title{Combining information from photometric and spectroscopic data:
+  Don't waste your time in spectral calibration!}
+\author{BDJ, DRW, DFM, DWH, CC, others}
+
+\begin{abstract}
 Hello World!
+\end{abstract}
+
+\keywords{
+  greetings
+  ---
+  whole world
+}
+
+All the code used in this project is available under an open-source license
+  from \url{http://github.com/bd-j/something/}.
 This version of the paper was generated
-  from a git repository available at \url{http://github.com/bd-j/something/}
+  from a git repository available at \url{http://github.com/bd-j/speccal/}
   with git hash \texttt{\githash} (\gitdate).

### 2014-04-25 tex/ms.tex
asdfasd
asdfs
abstractStart

@@
 \begin{abstract}
-Hello World!
+In a typical spectral-fitting project,
+  there tend to be a small number of bands of well-calibrated photometry
+  and thousands of poorly calibrated spectroscopic pixels.
+Good spectroscopic calibration is both expensive and difficult,
+  but naive weighted least-square fitting will weight
+  the thousands of spectroscopic pixels far higher overall
+  than the few photometric bands.
 \end{abstract}
@@
 
+\acknowledgements
+Thanks in advance to X. for bringing us beer.
+
 \end{document}

### 2014-04-25 tex/ms.tex
abstract and shit

@@
-\documentclass[12pt, preprint]{aastex}
+\documentclass[iop,numberedappendix]{emulateapj}
+\usepackage{apjfonts}
+\bibliographystyle{apj}
 
@@
 
-\title{Combining information from photometric and spectroscopic data:
+\title{Combining information from photometric and spectroscopic data:\\
   Don't waste your time in spectral calibration!}
 \author{BDJ, DRW, DFM, DWH, CC, others}
+\affil{foo}
 
@@
   than the few photometric bands.
+Here we present a flexible and general spectroscopic calibration model,
+  which can be fit simultaneously along with whatever spectral parameters.
+The model involves a polynommial calibration vector to capture large-scale calibration issues
+  and a Gaussian Process to capture small-scale wiggles.
+We show that, in this framework, the quality of some kinds of spectral parameter fits
+  is not a strong function of the quality of the spectroscopic calibration;
+  that is, for many scientific goals there is no scientific reason
+  to obtain good spectrophotometric calibration.
+In particular, for stellar population fitting, high signal-to-noise data,
+  and good photometry,
+  we show that raw counts are just as good as calibrated counts for measuring the
+  parameters of interest.
 \end{abstract}
@@
 }
+
+\section{fuck}
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+blah blah blah blah blah blah blah blah blah blah blah blah blah blah
 

### 2014-04-25 tex/ms.tex
sectionstructure

@@
 
-\section{fuck}
+\section{Spectral calibration is a bitch}
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+Hello World.
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+\section{Model generalities}
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+Hello World.
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+\section{Experiments and results}
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+Hello World.
 
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
-blah blah blah blah blah blah blah blah blah blah blah blah blah blah
+\section{Discussion}
 
@@
 \acknowledgements
-Thanks in advance to X. for bringing us beer.
+Thanks to X. for bringing us beer.
 

### 2014-04-26 tex/ms.tex
intro text

@@
 
-\section{Spectral calibration is a bitch}
+\section{Spectral calibration}
 
-Hello World.
+In probabilistic inference, all information flows from the data to the
+parameters of interest by means of a likelihood function, or an
+expression for the probability of the data conditioned on the
+parameters.
+If there are $N$ independent sources of data, for each of which there
+is a likelihood function, the full-data likelihood is the product of
+the $N$ individual likelihoods (or the log-likelihood is a sum of the
+$N$ individual log-likelihoods).
+There is no bespoke ``weighting'' of the data that is justifiable in
+this framework.
+This creates some apparent paradoxes!
+One is the following:
+
+Imagine you have three photometric bands through which you have
+observed some object (independently, say), and also a 2500-pixel
+spectrum, where the pixels are defined such that they are precisely or
+approximately independent measurements.
+For these purposes, two spectral pixels are very close to independent
+measurements if they are derived from disjoint sets of detector pixels
+in the spectrograph detector plane.
+Each photometric band and each spectroscopic pixel has a
+log-likelihood function, and these 2503 log-likelihood functions must
+be (by the Rules of Righteousness) coadded equally into one full-data
+log-likelihood.
+The log-likelihood is therefore fully dominated by the spectral
+pixels!
+This despite the fact that in almost all astronomical investigations,
+the photometry is far more reliable, per measurement, than the
+spectra.
+That is, if the spectral pixels tend to prefer one model, or one set
+of parameters, and the photometry another, the spectra will almost
+always ``win'' just by their overwhelming force.
+
+What is a Righteous Probabilistic Investigator (RPI) to do?
+One option---fully unjustified---is to ``down-weight'' the
+log-likelihoods of the spectral pixels relative to the photometric
+measurements.
+This is equivalent to taking the likelihoods to some power, which has
+no justification in inference (though it is sometimes used in
+optimization and sampling as an ``annealing'' move).
+This down-weighting is not justified, but there is even more
+ad-hockery than this, because there is no principled way to choose the
+unprincipled weights.
+
+The Right Thing To Do (RTTD) is to express the \emph{reason} that the
+RPI believes the spectroscopic data to be less reliable \emph{within}
+the likelihood function.
+That is, the RPI must add nuisance parameters to parameterize the
+unreliability of the spectroscopy, and infer those along with the
+parameters of interest.
+If this parameterization is good, the information in the spectroscopy
+data will not flow entirely to the parameters of interest; instead,
+some will flow to the nuisance parameters.
+This will reduce the importance of the spectroscopy relative to the
+photometry and the RPI will be well pleased with the dominance of the
+photometric data in the final inferences of the parameters of
+interest.
+In this what follows, we provide an example of this kind of
+parameterization and inference.
+
+Our example involves instantiating a ``calibration adjustment'' model,
+which has a polynomial component and a non-parametric component.
+The parameters of the calibration adjustment are nuisances, from a
+scientific standpoint.
+However, because the calibration adjustment is inferred along with the
+parameters of interest, the probabilistic inference that provides
+parameter estimates \emph{also} provides a spectrophotometric
+calibration of the spectral data.
+That is, the method we present has the potential to \emph{obviate
+spectrophotometric calibration}.
 

### 2014-04-26 tex/ms.tex
more intro words

@@
 Our example involves instantiating a ``calibration adjustment'' model,
-which has a polynomial component and a non-parametric component.
+which itself has both a polynomial component and a non-parametric
+component.
 The parameters of the calibration adjustment are nuisances, from a
@@
 spectrophotometric calibration}.
+We find that this potential is realized.
 

### 2014-04-26 tex/ms.tex
tweak

@@
 \title{Combining information from photometric and spectroscopic data:\\
-  Don't waste your time in spectral calibration!}
+  Don't waste your time in spectrophotometric calibration!}
 \author{BDJ, DRW, DFM, DWH, CC, others}
@@
   that is, for many scientific goals there is no scientific reason
-  to obtain good spectrophotometric calibration.
+  to obtain good---or really any---spectrophotometric calibration.
 In particular, for stellar population fitting, high signal-to-noise data,

### 2014-04-26 tex/ms.tex
equations, notes to self

@@
-\documentclass[iop,numberedappendix]{emulateapj}
-\usepackage{apjfonts}
+% \documentclass[iop,numberedappendix]{emulateapj}
+% \usepackage{apjfonts}
+\documentclass[12pt, letterpaper, preprint]{aastex}
 \bibliographystyle{apj}
@@
 \input{vc}
+\newcommand{\transpose}[1]{{#1}^{\!\mathsf T}}
+\newcommand{\given}{\,|\,}
 
@@
 
-Hello World.
+THIS SECTION NEEDS WORK; THIS IS JUST AN EQUATION DUMP.
+
+The standard chi-squared or log-Gaussian log-likelihood is
+\begin{eqnarray}
+\ln p(d\given\theta) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{\sigma_n^2} + \ln(2\,\pi\,\sigma_n^2) \right]
+\quad ,
+\end{eqnarray}
+where $\theta$ is a blob of parameters of interest,
+$d$ is the full set (in the form of a column vector) of data,
+made up of $N$ values $d_n$,
+$\mu(\theta)$ is the the column-vector mean prediction (expectation value) of the model,
+made up of $N$ values $\mu_n(\theta)$,
+the $\sigma_n^2$ are the observational noise variances.
+We have included the $\ln(\sigma_n^2)$ term in the likelihood because
+in what follows we are going to be modifying the noise model.
+
+The calibration-vector and Gaussian-Process modified log-likelihood is
+\begin{eqnarray}
+\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\,\pi]^N\,\det{C}) \right]
+\\
+\Delta &\equiv& d - f(\alpha)\ast\mu(\theta)
+\\
+C_{nn'} &\equiv& \sigma_n^2\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_n')
+\quad ,
+\end{eqnarray}
+where $\alpha$ is a blob of nuisance parameters
+(which determine the calibration vector and the kernel function),
+$\Delta$ is a residual column vector,
+$f(\alpha)$ is a calibration column vector,
+the $\ast$ operator is the pixel-wise multiplication operator,
+$C$ is the Gaussian Process covariance matrix,
+made up of $N^2$ values $C_{nn'}$,
+$K_\alpha$ is a kernel function,
+and each $\lambda_n$ is the wavelength of spectral pixel $n$.
+and $a^2$ and $\ell^2$ are parameters of the kernel function (and hence elements of $\alpha$).
+The calibration vector $f(\alpha)$ takes care of the large-scale
+calibration residual; the Gaussian process is going to pick up
+smaller-scale residuals away from \emph{that}.
+
+In detail, we are going to choose a $M$th-order polynomial form for
+the calibration vector $f(\alpha)$ and a bell-shape (Gaussian) for the
+kernel function $K_\alpha(\cdot)$:
+\begin{eqnarray}
+f(\alpha) &=& \sum_{m=1}^M c_m\,x^m
+\\
+x &\equiv& \frac{\lambda}{\lambda_0} - 1
+\\
+K_\alpha(x) &=& a^2\,\exp(-\frac{x^2}{2\,\ell^2})
+\\
+\transpose{\alpha} &\equiv& \left[ \{c_m\}_{m=0}^M, a^2, \ell^2 \right]
+\quad ,
+\end{eqnarray}
+where $\lambda$ is a column vector made up of the wavelengths $\lambda_m$
+and $x$ is a scaled and shifted version of the same,
+scaled by a fiducial wavelength $\lambda_0$.
+Nuisance parameters $a^2$ and $\ell^2$ set the variance and
+correlation length of the covariant calibration noise, respectively.
 
@@
 
-Hello World.
+BDJ INSERT WORDS HERE.
 
 \section{Discussion}
+
+BDJ INSERT WORDS HERE.
+
+HOGG COMPUTE TOTAL ANNUAL COST OF SPECTROPHOTOMETRY (to astronomical community).
 

### 2014-04-26 tex/ms.tex
tweaks

@@
 \begin{eqnarray}
-\ln p(d\given\theta) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{\sigma_n^2} + \ln(2\,\pi\,\sigma_n^2) \right]
+\ln p(d\given\theta) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{\sigma_n^2} + \ln(2\pi\,\sigma_n^2) \right]
 \quad ,
@@
 \begin{eqnarray}
-\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\,\pi]^N\,\det{C}) \right]
+\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
 \\
@@
 \\
-C_{nn'} &\equiv& \sigma_n^2\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_n')
+C_{nn'} &\equiv& \sigma_n^2\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_{n'})
 \quad ,
@@
 $f(\alpha)$ is a calibration column vector,
-the $\ast$ operator is the pixel-wise multiplication operator,
+the ``$\ast$'' operator is the pixel-wise multiplication operator,
 $C$ is the Gaussian Process covariance matrix,
@@
 and each $\lambda_n$ is the wavelength of spectral pixel $n$.
-and $a^2$ and $\ell^2$ are parameters of the kernel function (and hence elements of $\alpha$).
-The calibration vector $f(\alpha)$ takes care of the large-scale
-calibration residual; the Gaussian process is going to pick up
-smaller-scale residuals away from \emph{that}.
+The calibration vector $f(\alpha)$ is going to take care of the
+large-scale calibration residual; the Gaussian process is going to
+pick up smaller-scale residuals away from \emph{that}.
 
@@
 scaled by a fiducial wavelength $\lambda_0$.
-Nuisance parameters $a^2$ and $\ell^2$ set the variance and
-correlation length of the covariant calibration noise, respectively.
+Nuisance parameters $c_m$ set the shape of the large-scale calibration
+issues, while $a^2$ and $\ell^2$ set the variance and correlation
+length of the remaining covariant calibration noise.
 
@@
   from a git repository available at \url{http://github.com/bd-j/speccal/}
-  with git hash \texttt{\githash} (\gitdate).
+  with git hash \texttt{\githash\,(\gitdate)}.
 

### 2014-04-26 tex/ms.tex
introduction text, notes to self, copyright

@@
+% This file is part of the speccal project.
+% Copyright 2014 the authors.
+
+% ## style notes:
+% - all equations in `eqnarray` environments
+% - parameters are `inferred`; `measurement` is reserved for data
+
 % \documentclass[iop,numberedappendix]{emulateapj}
@@
 
+\newcommand{\lick}{1}
+\newcommand{\ccpp}{2}
+\newcommand{\cds}{3}
+\newcommand{\mpia}{4}
+
 \begin{document}
@@
   Don't waste your time in spectrophotometric calibration!}
-\author{BDJ, DRW, DFM, DWH, CC, others}
-\affil{foo}
+\author{
+  BDJ\altaffilmark{\lick},
+  DRW\altaffilmark{\lick},
+  DFM\altaffilmark{\ccpp},
+  DWH\altaffilmark{\ccpp, \cds, \mpia},
+  CC\altaffilmark{\lick},
+  others}
+\altaffiltext{\lick}{University of California Lick Observatory}
+\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
+\altaffiltext{\cds}{Center for Data Science, New York University}
+\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}
 
@@
   and good photometry,
-  we show that raw counts are just as good as calibrated counts for measuring the
+  we show that raw counts are just as good as calibrated counts for making inferences about the
   parameters of interest.
+This obviation of calibration overheads will pay all yall \emph{mad cheddar},
+  at least if all yall employ full cost accounting.
 \end{abstract}
@@
 
-\section{Spectral calibration}
+\section{Introduction}
 
@@
 spectrophotometric calibration}.
-We find that this potential is realized.
+
+We find that this potential---obviation of calibration---is realized.
+That is, if the procedures demonstrated below become widely adopted,
+some or perhaps most astronomical spectroscopic projects could
+potentially drop or dramatically reduce their spectrophotometric
+calibration programs.
+This would reduce telescope overheads and data-analysis time and
+complexity, delivering economic and sanity benefits to the whole
+community.
 
@@
 THIS SECTION NEEDS WORK; THIS IS JUST AN EQUATION DUMP.
+
+HOGG: A model is a parameterized likelihood function, with prior PDFs on the nuisance parameters (at least)...
+
+HOGG: There is a likelihood for the photometry and for the spectroscopy...
+
+HOGG: Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...
 

### 2014-04-26 tex/ms.tex
comments
tweaks

@@
-% This file is part of the speccal project.
+% This file is part of the `speccal` project.
 % Copyright 2014 the authors.
+% All rights reserved.
 
@@
 % - parameters are `inferred`; `measurement` is reserved for data
+% - use emulateapj or aastex, as you like, but watch for equation-wrapping in the former
 
-% \documentclass[iop,numberedappendix]{emulateapj}
-% \usepackage{apjfonts}
-\documentclass[12pt, letterpaper, preprint]{aastex}
+% ---- Hogg (aastex) mode ----
+% \documentclass[12pt, letterpaper, preprint]{aastex}
+% ----
+
+% ---- Charlie (emulateapj) mode ----
+\documentclass[iop,numberedappendix]{emulateapj}
+\usepackage{apjfonts}
+% ----
+
 \bibliographystyle{apj}
+\input{vc}
 
-\input{vc}
+% math shih
 \newcommand{\transpose}[1]{{#1}^{\!\mathsf T}}
@@
 
+% affiliation marks; edit with care
 \newcommand{\lick}{1}
@@
 
-\begin{document}
-
+\begin{document}\sloppy\sloppypar
 \title{Combining information from photometric and spectroscopic data:\\
   Don't waste your time in spectrophotometric calibration!}
+\shorttitle{don't waste your time in calibration!}
 \author{
@@
   others}
+\shortauthors{bdj et al}
 \altaffiltext{\lick}{University of California Lick Observatory}
@@
   parameters of interest.
-This obviation of calibration overheads will pay all yall \emph{mad cheddar},
-  at least if all yall employ full cost accounting.
+This obviation of calibration overheads will pay \emph{all yall mad cheddar},
+  at least if yall employ full cost accounting.
 \end{abstract}
@@
 
-The Right Thing To Do (RTTD) is to express the \emph{reason} that the
-RPI believes the spectroscopic data to be less reliable \emph{within}
-the likelihood function.
+The Right Thing To Do is to express the \emph{reason} that the RPI
+believes the spectroscopic data to be less reliable \emph{within} the
+likelihood function.
 That is, the RPI must add nuisance parameters to parameterize the
@@
 In detail, we are going to choose a $M$th-order polynomial form for
-the calibration vector $f(\alpha)$ and a bell-shape (Gaussian) for the
+the calibration vector $f(\alpha)$ and a bell shape (Gaussian) for the
 kernel function $K_\alpha(\cdot)$:

### 2014-04-27 tex/ms.tex
starting on experiments section

@@
 
+As a demonstration and test of the methodology for spectrophotometric
+calibration described above, we will apply it to an \emph{actual,
+  real} optical spectrum of a stellar cluster in M31.  Spectra of star
+clusters provide a good test case, as they are less complex than
+galaxy spectra (for which it is necessary to model the star formation
+history) but are by no means trivial. In this way the key features of the
+calibration model and methodology are not obscured, but the influence
+of the .
+
+We model the stellar cluster as a single age SSP. The physical
+parameters $\theta$ which affect the spectrum of a star
+cluster include the age, metallicity, stellar mass, attenuation by dust,
+velocity dispersion, redshift, and uncertain
+aspects of the stellar population synthesis models, including the
+intial mass function.
+
+The model for the spectrum is then 
+\begin{eqnarray}
+F(\lambda_o, \theta) = G(\sigma_v) \ast m_* S(\lambda_e/(1+z), Z, t,
+imf [, {\rm etc}]) e^ {-k_\lambda \tau_V}
+\end{eqnarray}
+
 BDJ INSERT WORDS HERE.

### 2014-04-27 tex/ms.tex
more ex
bdj changes to model generalities

@@
 % - all equations in `eqnarray` environments
+% - use `\,` as the multiply operator!
 % - parameters are `inferred`; `measurement` is reserved for data
@@
 % ---- Hogg (aastex) mode ----
-% \documentclass[12pt, letterpaper, preprint]{aastex}
+\documentclass[12pt, letterpaper, preprint]{aastex}
 % ----
@@
 % ---- Charlie (emulateapj) mode ----
-\documentclass[iop,numberedappendix]{emulateapj}
-\usepackage{apjfonts}
+% \documentclass[iop,numberedappendix]{emulateapj}
+% \usepackage{apjfonts}
 % ----
@@
 \newcommand{\given}{\,|\,}
+\renewcommand{\det}[1]{||{#1}||}
 
@@
 
+If you don't believe the reported data noise variances $\sigma_n^2$,
+it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
+This is a trivial modification of the chi-squared log-likelihood:
+\begin{eqnarray}\label{eq:photometricLF}
+\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{[\sigma_n^2 + s^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
+\quad .
+\end{eqnarray}
+This modification shows the necessity of including the log-variance
+term.
+This---equation~(\ref{eq:photometricLF})---is in fact the log-likelihood
+function we are going to use for the photometric measurements (BDJ: IS
+THIS TRUE?) in what follows.
+In this formulation, if $\theta$ are the parameters of interest, the
+jitter variance $s^2$ is a nuisance noise-model parameter.
+The Gaussian Process will be a generalization of this modification.
+
 The calibration-vector and Gaussian-Process modified log-likelihood is
-\begin{eqnarray}
+\begin{eqnarray}\label{eq:spectroscopicLF}
 \ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
@@
 \\
-C_{nn'} &\equiv& \sigma_n^2\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_{n'})
+C_{nn'} &\equiv& [\sigma_n^2 + s^2]\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_{n'})
 \quad ,
@@
 where $\alpha$ is a blob of nuisance parameters
-(which determine the calibration vector and the kernel function),
+(which determine the jitter, the calibration vector and the kernel function),
 $\Delta$ is a residual column vector,
@@
 pick up smaller-scale residuals away from \emph{that}.
+This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
+are going to use for the spectroscopic data in what follows.
 
@@
 kernel function $K_\alpha(\cdot)$:
-\begin{eqnarray}
-f(\alpha) &=& \sum_{m=1}^M c_m\,x^m
+\begin{eqnarray}\displaystyle
+f(\alpha) &=& c_0\,[1 + \sum_{m=1}^M c_m\,x^m]
 \\
@@
 \\
-K_\alpha(x) &=& a^2\,\exp(-\frac{x^2}{2\,\ell^2})
+K_\alpha(\lambda_n - \lambda_{n'}) &=& a^2\,\exp(-\frac{[\lambda_n - \lambda_{n'}]^2}{2\,\ell^2})
 \\
-\transpose{\alpha} &\equiv& \left[ \{c_m\}_{m=0}^M, a^2, \ell^2 \right]
+\transpose{\alpha} &\equiv& \left[ \{c_m\}_{m=0}^M, s^2, a^2, \ell^2 \right]
 \quad ,
@@
 \section{Experiments and results}
+
+We are now left to demonstrate that it is possible to infer the
+parameters of interest $\theta$ while marginalizing over the
+calibration parameters $\alpha$.
 

### 2014-04-28 tex/ms.tex
cleaning up mean model definition

@@
 function we are going to use for the photometric measurements (BDJ: IS
-THIS TRUE?) in what follows.
+THIS TRUE?  DWH, Currently I'm not using a jitter term, but I can and will) in what follows.
 In this formulation, if $\theta$ are the parameters of interest, the
@@
 parameters of interest $\theta$ while marginalizing over the
-calibration parameters $\alpha$.
-
-As a demonstration and test of the methodology for spectrophotometric
-calibration described above, we will apply it to an \emph{actual,
+calibration parameters $\alpha$.  We will apply the methodology for
+spectrophotometric calibration described above to an \emph{actual,
 real} optical spectrum of a stellar cluster in M31.  Spectra of star
@@
 galaxy spectra (for which it is necessary to model the star formation
-history) but are by no means trivial. In this way the key features of the
-calibration model and methodology are not obscured, but the influence
-of the .
+history) but are by no means trivial. In this way the key features of
+the calibration model and methodology are not obscured.
 
-We model the stellar cluster as a single age SSP. The physical
-parameters $\theta$ which affect the spectrum of a star
-cluster include the age, metallicity, stellar mass, attenuation by dust,
-velocity dispersion, redshift, and uncertain
-aspects of the stellar population synthesis models, including the
-intial mass function.
+We model the stellar cluster as a single age SSP. The spectrum of a
+star cluster under this assumption is given by
+\begin{eqnarray}\label{eq:MeanModel} 
+\mu(\theta, \lambda(1+z)) & = &
+\frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
+S(\lambda, t, Z [, \beta]) e^ {-k_\lambda\tau_V} 
+\\ 
+\theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
+\quad ,
+\end{eqnarray} where the parameters $\theta$ include include the age
+$t$, metallicity $Z$, stellar mass $m_*$, dust attenuation effective
+$V$-band optical depth $\tau_V$, velocity dispersion $\sigma_v$,
+luminosity distance $d_L$ and redshift $z$.  The spectrum of one solar
+mass of stars that formed at time $t$ with metallicity $Z$ is given by
+$S(\lambda, t, Z [, \beta])$ where the additional parameters $\beta$
+may include details of the population synthesis, such as the IMF slope
+and adjustments to the stellar spectra or stellar evolutionary tracks
+\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
+purposes of this exercise, with no loss of generality (DO WE WANT TO
+VARY IMF SLOPE?).  We will also fix the shape of the attenuation
+curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ and assume that $d_L$ is
+known to high accuracy from independent methods.
 
-The model for the spectrum is then 
-\begin{eqnarray}
-F(\lambda_o, \theta) = G(\sigma_v) \ast m_* S(\lambda_e/(1+z), Z, t,
-imf [, {\rm etc}]) e^ {-k_\lambda \tau_V}
-\end{eqnarray}
+To model the photometry we simply project the observed frame mean
+model spectrum $\mu(\theta, \lambda(1+z))$ onto the filters of
+interest.  Note that we do \emph{not} include the calibration vector
+$f(\alpha)$ in this projection.
 
-BDJ INSERT WORDS HERE.
+BDJ/DRW WORDS ABOUT DATA
+
+To demonstrate the effectiveness of our spectrophotometric calibration
+strategy we will infer the parameters $\theta$ from the spectrum both
+\emph{before} and \emph{after} it has been spectrophotometrically
+calibrated using typical techniques and ancillary spectrophotometric
+calibration data. (PROBABLY NEED WORDS FROM NELSON HERE, OR CITE HIS
+PAPER IF DETAILED ENOUGH)
 
@@
 BDJ INSERT WORDS HERE.
+BDJ random issues, collected here in case we want to address them and
+to keep me from cluttering up the main text: effective aperture
+corrections (i.e. we're implicitly assuming photometry and
+spectroscopy sample the same population).  Sky subtraction residuals.
+Model resolution and instrument resolution.  Method only useful when
+you have a model for the mean spectrum?  How to interpret GP
+residuals, as a fn of S/N?  Photometric upper limits?
 

### 2014-04-30 tex/ms.tex
start on sampling description, move some text in results around

@@
 
+To demonstrate the effectiveness of our spectrophotometric calibration
+strategy we will infer the parameters $\theta$ from the spectrum both
+\emph{before} and \emph{after} it has been spectrophotometrically
+calibrated using typical techniques and ancillary spectrophotometric
+calibration data. ( CITE NC)
+
 We model the stellar cluster as a single age SSP. The spectrum of a
@@
 \citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
-purposes of this exercise, with no loss of generality (DO WE WANT TO
-VARY IMF SLOPE?).  We will also fix the shape of the attenuation
-curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ and assume that $d_L$ is
-known to high accuracy from independent methods.
+purposes of this exercise, with no loss of generality (KEEPING IMF
+SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
+attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
+way average of \citet{CCM89} and assume that $d_L$ is known to high
+accuracy from independent methods.
 
@@
 
+BDJ WORDS ABOUT FSPS.
+
 BDJ/DRW WORDS ABOUT DATA
 
-To demonstrate the effectiveness of our spectrophotometric calibration
-strategy we will infer the parameters $\theta$ from the spectrum both
-\emph{before} and \emph{after} it has been spectrophotometrically
-calibrated using typical techniques and ancillary spectrophotometric
-calibration data. (PROBABLY NEED WORDS FROM NELSON HERE, OR CITE HIS
-PAPER IF DETAILED ENOUGH)
+Our sampling of the posterior is accomplished using \texttt{emcee}
+\cite{dfm} after an intial round of minimization.
 

### 2014-04-30 tex/ms.tex
redshift notation change
more sampling text, start on results desc

@@
   which can be fit simultaneously along with whatever spectral parameters.
-The model involves a polynommial calibration vector to capture large-scale calibration issues
+The model involves a polynomial calibration vector to capture large-scale calibration issues
   and a Gaussian Process to capture small-scale wiggles.
@@
 To demonstrate the effectiveness of our spectrophotometric calibration
-strategy we will infer the parameters $\theta$ from the spectrum both
+strategy we will infer the parameters $\theta$ from a spectrum both
 \emph{before} and \emph{after} it has been spectrophotometrically
@@
 \begin{eqnarray}\label{eq:MeanModel} 
-\mu(\theta, \lambda(1+z)) & = &
+\mu(\theta, \lambda_o) & = &
 \frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
@@
 \\ 
+\lambda_o & = & (1+z)\lambda 
+\\
 \theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
 \quad ,
-\end{eqnarray} where the parameters $\theta$ include include the age
-$t$, metallicity $Z$, stellar mass $m_*$, dust attenuation effective
-$V$-band optical depth $\tau_V$, velocity dispersion $\sigma_v$,
-luminosity distance $d_L$ and redshift $z$.  The spectrum of one solar
-mass of stars that formed at time $t$ with metallicity $Z$ is given by
-$S(\lambda, t, Z [, \beta])$ where the additional parameters $\beta$
-may include details of the population synthesis, such as the IMF slope
-and adjustments to the stellar spectra or stellar evolutionary tracks
+\end{eqnarray} where the parameters $\theta$ include the stellar mass
+$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
+velocity dispersion $\sigma_v$, luminosity distance $d_L$ and redshift
+$z$.  The spectrum of one solar mass of stars that formed at time $t$
+with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$ where
+the additional parameters $\beta$ may include details of the
+population synthesis model, such as the IMF slope and adjustments to
+the stellar spectra or stellar evolutionary tracks
 \citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
@@
 way average of \citet{CCM89} and assume that $d_L$ is known to high
-accuracy from independent methods.
+precision from independent methods.
 
 To model the photometry we simply project the observed frame mean
-model spectrum $\mu(\theta, \lambda(1+z))$ onto the filters of
+model spectrum (equation \ref{eq:MeanModel}) onto the filters of
 interest.  Note that we do \emph{not} include the calibration vector
@@
 
-BDJ WORDS ABOUT FSPS.
+We calculate $\mu$ using the Flexible Stellar Population Synthesis
+code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
+\citep{Padova} and high-resolution theoretical stellar spectra
+\citep{CKC14} which allow us to probe super-solar metallicities at
+early ages.  NEBULAR EMISSION - MASK OR INFER?
 
@@
 
-Our sampling of the posterior is accomplished using \texttt{emcee}
-\cite{dfm} after an intial round of minimization.
+We estimate the posterior through MCMC sampling. Our sampling of the
+posterior is accomplished using \texttt{emcee} \cite{dfm} after an
+intial round of minimization.  \texttt{emcee} is an implementation of
+the affine-invariant ensemble sampler of \citet{GW}, and unlike
+typical Metropolis-Hastings MCMC sampling does not require the
+specification of step sizes in each dimension.  Our prior
+distributions are in all cases top-hat functions, though more
+informative priors distributions may be used.  Informative priors may
+be especially appropriate for the calibration parameters $\alpha$ if
+additional information about the instrument is available or for the
+parameters of interest $\theta$, for example in the case where there
+is knowledge of the metallicity distribution of the population from
+which a given cluster is drawn.
+
+NEEDS MASSIVE REWORDING.
+In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
+from draws of the parameters $[\theta,alpha]$ from the posterior
+distribution.  This figure also shows the calibrated spectrum on which
+the priors were conditioned, and individual components of the model
+constructed from each draw.   In Figure \ref{fig:calibrated_residuals}
+we show the residuals between the data and the draws from the
+posterior, for the spectra and the photometry.
+
+In Figure \ref{fig:calibrated_triangle} we show the marginalized and
+joint-pdfs for the parameters.
 
@@
 you have a model for the mean spectrum?  How to interpret GP
-residuals, as a fn of S/N?  Photometric upper limits?
+residuals, as a fn of S/N?  Photometric upper limits? Infer the
+wavelength solution as well - stellar population (and telluric lines) as your arc.
 
@@
 All the code used in this project is available under an open-source license
-  from \url{http://github.com/bd-j/something/}.
+  from \url{http://github.com/bd-j/bsfh/}.
 This version of the paper was generated

### 2014-04-30 tex/ms.tex
equation formatting

@@
 % ---- Hogg (aastex) mode ----
-\documentclass[12pt, letterpaper, preprint]{aastex}
+%\documentclass[12pt, letterpaper, preprint]{aastex}
 % ----
@@
 % ---- Charlie (emulateapj) mode ----
-% \documentclass[iop,numberedappendix]{emulateapj}
-% \usepackage{apjfonts}
+ \documentclass[iop,numberedappendix]{emulateapj}
+ \usepackage{apjfonts}
 % ----
@@
 star cluster under this assumption is given by
-\begin{eqnarray}\label{eq:MeanModel} 
+\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
 \mu(\theta, \lambda_o) & = &
-\frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
-S(\lambda, t, Z [, \beta]) e^ {-k_\lambda\tau_V} 
+\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
+S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
 \\ 
-\lambda_o & = & (1+z)\lambda 
+\lambda_o & = & (1+z)\,\lambda 
 \\
-\theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
+\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
 \quad ,
@@
 $m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
-velocity dispersion $\sigma_v$, luminosity distance $d_L$ and redshift
-$z$.  The spectrum of one solar mass of stars that formed at time $t$
-with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$ where
-the additional parameters $\beta$ may include details of the
+velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
+redshift $z$.  The spectrum of one solar mass of stars that formed at
+time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
+where the additional parameters $\beta$ may include details of the
 population synthesis model, such as the IMF slope and adjustments to
@@
 way average of \citet{CCM89} and assume that $d_L$ is known to high
-precision from independent methods.
+precision from independent methods. (BDJ NOTE TO SELF - do not use $k$
+for the attenuation curve shape - will confuse people used to
+reddening curves)
 
@@
 posterior is accomplished using \texttt{emcee} \cite{dfm} after an
-intial round of minimization.  \texttt{emcee} is an implementation of
-the affine-invariant ensemble sampler of \citet{GW}, and unlike
-typical Metropolis-Hastings MCMC sampling does not require the
-specification of step sizes in each dimension.  Our prior
-distributions are in all cases top-hat functions, though more
+intial round of optimization using Powell's method.  \texttt{emcee} is
+an implementation of the affine-invariant ensemble sampler of
+\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
+not require the specification of step sizes in each dimension.  Our
+prior distributions are in all cases top-hat functions, though more
 informative priors distributions may be used.  Informative priors may
@@
 In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
-from draws of the parameters $[\theta,alpha]$ from the posterior
+from draws of the parameters $[\theta,\alpha]$ from the posterior
 distribution.  This figure also shows the calibrated spectrum on which

### 2014-04-30 tex/ms.tex
subsections, revert to emulateapj

@@
 
+\subsection{Data}
+BDJ/DRW WORDS ABOUT DATA
+
+\subsection{Star Cluster Model}
 We model the stellar cluster as a single age SSP. The spectrum of a
@@
 redshift $z$.  The spectrum of one solar mass of stars that formed at
-time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
-where the additional parameters $\beta$ may include details of the
-population synthesis model, such as the IMF slope and adjustments to
-the stellar spectra or stellar evolutionary tracks
+lookback time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [,
+\beta])$ where the additional parameters $\beta$ may include details
+of the population synthesis model, such as the IMF slope and
+adjustments to the stellar spectra or stellar evolutionary tracks
 \citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
@@
 attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
-way average of \citet{CCM89} and assume that $d_L$ is known to high
-precision from independent methods. (BDJ NOTE TO SELF - do not use $k$
-for the attenuation curve shape - will confuse people used to
-reddening curves)
+way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
+known to high precision from independent methods. (BDJ NOTE TO SELF -
+do not use $k$ for the attenuation curve shape - will confuse people
+used to reddening curves.  Even though it's super handy.)
 
@@
 
-We calculate $\mu$ using the Flexible Stellar Population Synthesis
-code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
+We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
+Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
 \citep{Padova} and high-resolution theoretical stellar spectra
 \citep{CKC14} which allow us to probe super-solar metallicities at
-early ages.  NEBULAR EMISSION - MASK OR INFER?
+early ages.  NEBULAR EMISSION - MASK OR INFER?  The model spectra are
+smoothed by convolution with a Gaussian in velocity space, and are
+interpolated to the wavelength points of the of the observed spectrum
+taking into account the redshift.
 
-BDJ/DRW WORDS ABOUT DATA
-
+\subsection{Sampling and Priors}
 We estimate the posterior through MCMC sampling. Our sampling of the

### 2014-05-16 tex/ms.tex
updating model description for nebular lines

@@
 
-\section{Experiments and results}
+\section{Experiments and Results}
 
@@
 
-\subsection{Data}
-BDJ/DRW WORDS ABOUT DATA
+\subsection{Test Data}
+The data we use to test our method consists of MMT Hectospec
+spectroscopy of XX stellar clusters in M31 for which YY-band HST
+photometric data exist.  The optical spectra were obtained by
+\citet{caldwell}.  The wavelength range of the spectra is $3700-7200
+\AA$. The instrumental resolution is $\sim 5\AA$ across the optical
+range \citep{fabricant13}.  Sky subtraction happened.  We got data
+which were uncalibrated and data which had been approximately
+spectrophotometrically calibrated using an average for the night (MORE
+HERE).
+
+DRW/BDJ WORDS ABOUT DATA
 
@@
 \mu(\theta, \lambda_o) & = &
-\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
-S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
+\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
+S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  +
+\sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-(\lambda - \lambda_i)^2/(2\sigma_e^2)}
 \\ 
@@
 \\
-\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
+\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
+  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
 \quad ,
-\end{eqnarray} where the parameters $\theta$ include the stellar mass
-$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
-velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
-redshift $z$.  The spectrum of one solar mass of stars that formed at
-lookback time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [,
-\beta])$ where the additional parameters $\beta$ may include details
-of the population synthesis model, such as the IMF slope and
-adjustments to the stellar spectra or stellar evolutionary tracks
+\end{eqnarray} where the parameters $\theta$ include 
+the stellar mass $m_*$, 
+effective optical depth to dust in the $V$-band $\tau_V$,
+velocity dispersion or instrumental resolution $\sigma$, 
+luminosity distance $d_L$, 
+and redshift $z$.  
+The spectrum of one solar mass of stars that formed at lookback time
+$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
+where the additional parameters $\beta$ may include details of the
+population synthesis model, such as the IMF slope and adjustments to
+the stellar spectra or stellar evolutionary tracks
 \citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
@@
 way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
-known to high precision from independent methods. (BDJ NOTE TO SELF -
-do not use $k$ for the attenuation curve shape - will confuse people
-used to reddening curves.  Even though it's super handy.)
+known to high precision from independent methods.
+
+Nebular emission lines (which may arise from HII regions around the
+clusters or from a diffuse ionized gas) and interstellar absorption is
+modeled as a sum of Gaussians of unknown amplitude $a_i$, all of the
+same width $\sigma_e$ (which need not be the same as stellar
+broadening $\sigma$) and with known central wavelengths $\lambda_i$.
+For emission lines the amplitudes are constrained to be positive,
+while for interstellar absorption (e.g. Na D and Ca K) the amplitudes
+are constrained to be negative. This framework can be easily extended
+to include more complex models for the nebular emission, such as
+allowing line dependent widths.
 
@@
 Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
-\citep{Padova} and high-resolution theoretical stellar spectra
-\citep{CKC14} which allow us to probe super-solar metallicities at
-early ages.  NEBULAR EMISSION - MASK OR INFER?  The model spectra are
-smoothed by convolution with a Gaussian in velocity space, and are
-interpolated to the wavelength points of the of the observed spectrum
-taking into account the redshift.
+\citep{Padova} and the MILES stellar spectral library.  The model
+spectra are smoothed by convolution with a Gaussian in wavelength
+space (to model the MMT line-spread function) and are interpolated to
+the wavelength points of the of the observed spectrum while taking
+into account the redshift.
 
 \subsection{Sampling and Priors}
+
 We estimate the posterior through MCMC sampling. Our sampling of the
@@
 \citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
-not require the specification of step sizes in each dimension.  Our
-prior distributions are in all cases top-hat functions, though more
-informative priors distributions may be used.  Informative priors may
-be especially appropriate for the calibration parameters $\alpha$ if
-additional information about the instrument is available or for the
+not require the specification of step sizes in each dimension.
+
+Our prior distributions are in all cases top-hat functions, though
+more informative prior distributions may be used.  Informative priors
+may be especially appropriate for the calibration parameters $\alpha$
+if additional information about the instrument is available or for the
 parameters of interest $\theta$, for example in the case where there
@@
 which a given cluster is drawn.
+
+\subsection{Results}
 
@@
 In Figure \ref{fig:calibrated_triangle} we show the marginalized and
-joint-pdfs for the parameters.
+joint PDFs for the parameters.
+
+Apparently we get really nice redshift/velocity constraints.
 
@@
 residuals, as a fn of S/N?  Photometric upper limits? Infer the
-wavelength solution as well - stellar population (and telluric lines) as your arc.
+wavelength solution as well - stellar population (and telluric lines)
+as your arc. Combinations of broadening in velocity space (physical)
+and in wavelength space (instrumental)
 

### 2014-05-16 tex/ms.tex
tweaks to new model equation and text

@@
 interest.
-In this what follows, we provide an example of this kind of
+In what follows, we provide an example of this kind of
 parameterization and inference.
@@
 calibrated using typical techniques and ancillary spectrophotometric
-calibration data. ( CITE NC)
+calibration data.
 
 \subsection{Test Data}
-The data we use to test our method consists of MMT Hectospec
-spectroscopy of XX stellar clusters in M31 for which YY-band HST
-photometric data exist.  The optical spectra were obtained by
-\citet{caldwell}.  The wavelength range of the spectra is $3700-7200
-\AA$. The instrumental resolution is $\sim 5\AA$ across the optical
-range \citep{fabricant13}.  Sky subtraction happened.  We got data
-which were uncalibrated and data which had been approximately
-spectrophotometrically calibrated using an average for the night (MORE
-HERE).
 
 DRW/BDJ WORDS ABOUT DATA
+
+The data we use to test our method consists of optical spectroscopy of
+XX stellar clusters in M31 for which YY-band HST photometric data
+exist.  The optical spectra were obtained using the fiber-fed
+Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
+of the spectra is $3700-7200 \AA$. The instrumental resolution is
+$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
+subtraction happened.  We got data which were uncalibrated and data
+which had been approximately spectrophotometrically calibrated using
+an average for the night (MORE HERE).  Show figure of calibrated and
+uncalibrated data.  Discuss S/N, sky subtraction, calibration.
 
@@
 \frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
-S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  +
-\sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-(\lambda - \lambda_i)^2/(2\sigma_e^2)}
-\\ 
+S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  + \\
+& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
+\nonumber \\ 
 \lambda_o & = & (1+z)\,\lambda 
@@
 luminosity distance $d_L$, 
-and redshift $z$.  
+and redshift $z$,
+and amplitudes of the $N_l$ nebular and interstellar emission lines
+$a_i$.
+
 The spectrum of one solar mass of stars that formed at lookback time
@@
 Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
-\citep{Padova} and the MILES stellar spectral library.  The model
+\citep{Padova} and the MILES stellar spectral library \citep{MILES}.  The model
 spectra are smoothed by convolution with a Gaussian in wavelength
@@
 
+We first infer the parameters of interest $\theta$ for a calibrated
+spectrum of one of the clusters, using the full YY-band photometry.
+
 NEEDS MASSIVE REWORDING.
@@
 
-Apparently we get really nice redshift/velocity constraints.
+Apparently we get really nice redshift/velocity constraints for free.
 

### 2014-05-16 tex/ms.tex
working on results section

@@
 % ---- Hogg (aastex) mode ----
-%\documentclass[12pt, letterpaper, preprint]{aastex}
+\documentclass[12pt, letterpaper, preprint]{aastex}
 % ----
@@
 % ---- Charlie (emulateapj) mode ----
- \documentclass[iop,numberedappendix]{emulateapj}
- \usepackage{apjfonts}
+% \documentclass[iop,numberedappendix]{emulateapj}
+% \usepackage{apjfonts}
 % ----
@@
 \frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
-S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  + \\
+S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
 & & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
@@
 We first infer the parameters of interest $\theta$ for a calibrated
-spectrum of one of the clusters, using the full YY-band photometry.
-
-NEEDS MASSIVE REWORDING.
-In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
+spectrum of one of the clusters, using the full YY-band photometry. In
+Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
 from draws of the parameters $[\theta,\alpha]$ from the posterior
 distribution.  This figure also shows the calibrated spectrum on which
-the priors were conditioned, and individual components of the model
-constructed from each draw.   In Figure \ref{fig:calibrated_residuals}
-we show the residuals between the data and the draws from the
-posterior, for the spectra and the photometry.
+the priors were conditioned, and several of the individual components
+of the model constructed from each draw.  In Figure
+\ref{fig:calibrated_residuals} we show the residuals between the data
+and the draws from the posterior, for both the spectra and the
+photometry. In Figure \ref{fig:calibrated_triangle} we show the
+marginalized and joint PDFs for the parameters.
 
-In Figure \ref{fig:calibrated_triangle} we show the marginalized and
-joint PDFs for the parameters.
+Discuss degeneracies, etc.  Apparently we get really nice
+redshift/velocity constraints for free.
 
-Apparently we get really nice redshift/velocity constraints for free.
+Next, we infer the parameters of the spectrum of the same cluster
+\emph{without} spectrophotometric calibration.
 

### 2014-05-16 tex/ms.tex
tweaking

@@
 which had been approximately spectrophotometrically calibrated using
-an average for the night (MORE HERE).  Show figure of calibrated and
-uncalibrated data.  Discuss S/N, sky subtraction, calibration.
+an average for the night (MORE HERE). Figure \ref{fig:data} shows the
+calibrated and uncalibratred spectra for each cluster.  Discuss S/N,
+sky subtraction, calibration.
 
@@
 \theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
-  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
+  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
 \quad ,
@@
 
-We estimate the posterior through MCMC sampling. Our sampling of the
-posterior is accomplished using \texttt{emcee} \cite{dfm} after an
-intial round of optimization using Powell's method.  \texttt{emcee} is
-an implementation of the affine-invariant ensemble sampler of
-\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
-not require the specification of step sizes in each dimension.
+We estimate the posterior through MCMC sampling after an initial round
+of optimization using Powell's method.  The specific sampling
+algorithm we use is the affine-invariant ensemble sampling scheme of
+\citet{GW}, as implemented in the \texttt{emcee} package \cite{dfm}
+Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
+sampler does not require the specification of step sizes in each
+dimension.  ASSESSING SAMPLER CONVERGENCE
 
@@
 if additional information about the instrument is available or for the
-parameters of interest $\theta$, for example in the case where there
+parameters of interest $\theta$, for example in the case that there
 is knowledge of the metallicity distribution of the population from
@@
 \emph{without} spectrophotometric calibration.
+
+Then, we show select marginalized or joint PDFs for each cluster
+calibrated/uncalibrated, to assess consistency.
+
+Finally, we have fun playing with the number of photometric bands and the S/N.
 

### 2014-05-22 tex/ms.tex
better figures for older cluster

@@
 $\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
-subtraction happened.  We got data which were uncalibrated and data
-which had been approximately spectrophotometrically calibrated using
-an average for the night (MORE HERE). Figure \ref{fig:data} shows the
-calibrated and uncalibratred spectra for each cluster.  Discuss S/N,
-sky subtraction, calibration.
+subtraction happened. The data were approximately
+spectrophotometrically calibrated using an average calibration vector
+the night constructed from.... (MORE HERE). Figure \ref{fig:data}
+shows the spectra before and after calibration for each cluster.
+Discuss S/N, sky subtraction.
 
@@
 S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
-& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
+& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2})
 \nonumber \\ 
@@
 luminosity distance $d_L$, 
-and redshift $z$,
+redshift $z$,
 and amplitudes of the $N_l$ nebular and interstellar emission lines
@@
 
-Discuss degeneracies, etc.  Apparently we get really nice
+BDJ: Discuss degeneracies, etc.  Apparently we get really nice
 redshift/velocity constraints for free.
 
-Next, we infer the parameters of the spectrum of the same cluster
+BDJ: Next, we infer the parameters of the spectrum of the same cluster
 \emph{without} spectrophotometric calibration.
 
-Then, we show select marginalized or joint PDFs for each cluster
+BDJ: Then, we show select marginalized or joint PDFs for each cluster
 calibrated/uncalibrated, to assess consistency.
 
-Finally, we have fun playing with the number of photometric bands and the S/N.
+BDJ: Finally, we have fun playing with the number of photometric bands
+and the S/N.
 

### 2014-07-07 tex/ms.tex
split up mean model definitions for clarity

@@
 of the spectra is $3700-7200 \AA$. The instrumental resolution is
-$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
-subtraction happened. The data were approximately
-spectrophotometrically calibrated using an average calibration vector
-the night constructed from.... (MORE HERE). Figure \ref{fig:data}
-shows the spectra before and after calibration for each cluster.
-Discuss S/N, sky subtraction.
+$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
+calibration happened. Sky subtraction happened. The data were
+approximately spectrophotometrically calibrated using an average
+calibration vector the night constructed from.... (MORE HERE). Figure
+\ref{fig:data} shows the spectra before and after calibration for each
+cluster.  Discuss S/N, sky subtraction.
 
@@
 star cluster under this assumption is given by
-\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
-\mu(\theta, \lambda_o) & = &
-\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
-S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
-& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2})
+\begin{eqnarray}\displaystyle
+F_{\theta^\prime}(\lambda_o) & = &
+\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
 \nonumber \\ 
@@
 \\
-\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
-  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
+\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta, \right]
 \quad ,
-\end{eqnarray} where the parameters $\theta$ include 
-the stellar mass $m_*$, 
-effective optical depth to dust in the $V$-band $\tau_V$,
-velocity dispersion or instrumental resolution $\sigma$, 
-luminosity distance $d_L$, 
-redshift $z$,
-and amplitudes of the $N_l$ nebular and interstellar emission lines
-$a_i$.
+\end{eqnarray} where the
+parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
+depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
+and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
+related to the restframe wavelengths $\lambda$ in the usual way.
 
 The spectrum of one solar mass of stars that formed at lookback time
-$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
-where the additional parameters $\beta$ may include details of the
+$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
+Here the additional parameters $\beta$ may include details of the
 population synthesis model, such as the IMF slope and adjustments to
@@
 SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
-attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
+attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$, to the Milky
 way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
@@
 
+BDJ Discuss broadening here.  The instrumental resolution is given by $\sigma$,
+
 Nebular emission lines (which may arise from HII regions around the
-clusters or from a diffuse ionized gas) and interstellar absorption is
-modeled as a sum of Gaussians of unknown amplitude $a_i$, all of the
-same width $\sigma_e$ (which need not be the same as stellar
-broadening $\sigma$) and with known central wavelengths $\lambda_i$.
-For emission lines the amplitudes are constrained to be positive,
-while for interstellar absorption (e.g. Na D and Ca K) the amplitudes
-are constrained to be negative. This framework can be easily extended
-to include more complex models for the nebular emission, such as
-allowing line dependent widths.
+clusters or from diffuse ionized gas) and interstellar absorption
+lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
+all of the same width $\sigma_e$ (which need not be the same as
+stellar broadening $\sigma$) and with known central wavelengths
+$\lambda_\ell$.  For emission lines the amplitudes are constrained to be
+positive, while for interstellar absorption (e.g. Na D and Ca K) the
+amplitudes are constrained to be negative. This framework can be
+easily extended to include more complex models for the nebular
+emission, such as allowing line dependent widths and velocities.
+
+The final mean model is then given by 
+\begin{eqnarray}\label{eq:MeanModel} 
+\mu(\theta, \lambda_o) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
+\sum_{\ell=0}^{N_\ell} S_\ell \\
+S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
+ \lambda_\ell)^2}{2\sigma_e^2})\\
+\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
+  \sigma_e \right]
+\quad ,
+\end{eqnarray}
+where $G$ represents a Gaussian of unit area, $\otimes$ indicates
+convolution, and the full parameter set $\theta$ now includes the
+amplitudes of the $N_l$ nebular and interstellar emission lines
+$A_\ell$.  We again implicitly include the conversion from restframe
+to observed frame spectra.
 

### 2014-07-07 tex/ms.tex
more model notation tweaks

@@
 \\
-\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta, \right]
+\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
 \quad ,
@@
 \begin{eqnarray}\label{eq:MeanModel} 
-\mu(\theta, \lambda_o) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
+\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
 \sum_{\ell=0}^{N_\ell} S_\ell \\
@@
 \end{eqnarray}
-where $G$ represents a Gaussian of unit area, $\otimes$ indicates
-convolution, and the full parameter set $\theta$ now includes the
-amplitudes of the $N_l$ nebular and interstellar emission lines
-$A_\ell$.  We again implicitly include the conversion from restframe
-to observed frame spectra.
+where $G_\sigma$ represents a Gaussian of unit area and standard
+deviation $\sigma$, $\otimes$ indicates convolution, and the full
+parameter set $\theta$ now includes the dispersion $\sigma_e$ and
+amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
+lines.
 

### 2014-07-07 tex/ms.tex
moving some model description text around
more about the mean model

@@
 term.
-This---equation~(\ref{eq:photometricLF})---is in fact the log-likelihood
-function we are going to use for the photometric measurements (BDJ: IS
-THIS TRUE?  DWH, Currently I'm not using a jitter term, but I can and will) in what follows.
-In this formulation, if $\theta$ are the parameters of interest, the
-jitter variance $s^2$ is a nuisance noise-model parameter.
-The Gaussian Process will be a generalization of this modification.
+This---equation~(\ref{eq:photometricLF})---is in fact the
+log-likelihood function we are going to use for the photometric
+measurements (BDJ: IS THIS TRUE?  DWH, Currently I'm not using a
+jitter term, but I can and will) in what follows.  In this
+formulation, if $\theta$ are the parameters of interest, the jitter
+variance $s^2$ is a nuisance noise-model parameter.  The Gaussian
+Process will be a generalization of this modification.
 
@@
 approximately spectrophotometrically calibrated using an average
-calibration vector the night constructed from.... (MORE HERE). Figure
+calibration vector for the night constructed from.... (MORE HERE). Figure
 \ref{fig:data} shows the spectra before and after calibration for each
@@
 \end{eqnarray} where the
-parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
-depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
-and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
-related to the restframe wavelengths $\lambda$ in the usual way.
+parameters $\theta^\prime$ include 
+the stellar mass $m_*$, 
+effective optical depth to dust in the $V$-band $\tau_V$, 
+luminosity distance $d_L$,
+and redshift $z$.  
+The observed frame wavelengths $\lambda_o$ are related to the restframe
+wavelengths $\lambda$ in the usual way.
 
@@
 population synthesis model, such as the IMF slope and adjustments to
-the stellar spectra or stellar evolutionary tracks
-\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
-purposes of this exercise, with no loss of generality (KEEPING IMF
-SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
-attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$, to the Milky
-way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
-known to high precision from independent methods.
+the stellar spectra or stellar evolutionary tracks. We will assume
+$\beta$ to be fixed for the purposes of this exercise, with no loss of
+generality (KEEPING IMF SLOPE CONSTANT FOR NOW).  We will also fix the
+shape of the attenuation curve, $k_\lambda \equiv
+\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
+$R_V=3.1$ and assume that $d_L$ is known to high precision from
+independent methods and can therefore be treated as fixed.  In
+practice, $d_L$ is completely degenerate with $m_*$. We calculate
+$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
+code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
+\citep{Padova} and the MILES stellar spectral library \citep{MILES}.
 
-BDJ Discuss broadening here.  The instrumental resolution is given by $\sigma$,
+BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
+by convolution with a Gaussian in wavelength space (to model the MMT
+line-spread function) and are interpolated to the wavelength points of
+the of the observed spectrum while taking into account the
+redshift. The instrumental resolution is given by $\sigma$.
 
@@
 \end{eqnarray}
-where $G_\sigma$ represents a Gaussian of unit area and standard
-deviation $\sigma$, $\otimes$ indicates convolution, and the full
-parameter set $\theta$ now includes the dispersion $\sigma_e$ and
+where $G_\sigma$ represents a Gaussian of unit area 
+and standard deviation $\sigma$, 
+$\otimes$ indicates convolution, 
+and the full parameter set $\theta$ now includes 
+the dispersion $\sigma_e$ and
 amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
@@
 $f(\alpha)$ in this projection.
-
-We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
-Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
-\citep{Padova} and the MILES stellar spectral library \citep{MILES}.  The model
-spectra are smoothed by convolution with a Gaussian in wavelength
-space (to model the MMT line-spread function) and are interpolated to
-the wavelength points of the of the observed spectrum while taking
-into account the redshift.
 

### 2014-07-07 tex/ms.tex
outline required figures and tables

@@
 of parameters, and the photometry another, the spectra will almost
-always ``win'' just by their overwhelming force.
+always ``win'' just by their overwhelming numbers.
 
@@
 calibration parameters $\alpha$.  We will apply the methodology for
-spectrophotometric calibration described above to an \emph{actual,
-real} optical spectrum of a stellar cluster in M31.  Spectra of star
+spectrophotometric calibration described above to \emph{actual,
+real} optical spectra of a stellar clusters in M31.  Spectra of star
 clusters provide a good test case, as they are less complex than
@@
 
-To demonstrate the effectiveness of our spectrophotometric calibration
-strategy we will infer the parameters $\theta$ from a spectrum both
-\emph{before} and \emph{after} it has been spectrophotometrically
-calibrated using typical techniques and ancillary spectrophotometric
-calibration data.
+To demonstrate the effectiveness of our strategy for combining
+spectroscopic and photometric information we will infer the parameters
+$\theta$ from a spectrum both \emph{before} and \emph{after} it has
+been spectrophotometrically calibrated using typical techniques and
+ancillary spectrophotometric calibration data.
 
@@
 approximately spectrophotometrically calibrated using an average
-calibration vector for the night constructed from.... (MORE HERE). Figure
-\ref{fig:data} shows the spectra before and after calibration for each
-cluster.  Discuss S/N, sky subtraction.
+calibration vector for the night constructed from.... (MORE
+HERE). Figure \ref{fig:data} shows the spectra before and after
+calibration (SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?).  Discuss
+S/N, sky subtraction.
+
+\begin{figure}[h!]
+\caption{Shows the calibrated and uncalibrated spectrum for one
+  cluster, along with the uncertainty spectrum and (maybe) the
+  calibration vector. \label{fig:data}}
+\end{figure}
+
+\begin{table}[h!]
+\caption{List all the clusters, and individual exposures.}
+\end{table}
 
@@
 
+\begin{table}[h!]
+\caption{List the parameters and  their allowed ranges.}
+\end{table}
+
 \subsection{Results}
@@
 of the model constructed from each draw.  In Figure
-\ref{fig:calibrated_residuals} we show the residuals between the data
+\ref{fig:calibrated_spectrum} we also show the residuals between the data
 and the draws from the posterior, for both the spectra and the
@@
 BDJ: Then, we show select marginalized or joint PDFs for each cluster
-calibrated/uncalibrated, to assess consistency.
+calibrated/uncalibrated, to assess consistency.  They are very consistent.
 
@@
 and the S/N.
+
+\begin{figure}[h!]
+\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
+  the posterior for the model, and residuals}
+\end{figure}
+
+\begin{figure}[h!]
+\caption{Show the observed photometric SED and draws from the
+  posterior, for one cluster.}
+\end{figure}
+
+\begin{figure}[h!]
+\caption{Show a corner plot of selected relevant parameters, for one cluster.}
+\end{figure}
+
+\begin{figure}[h!]
+\caption{Money plot.  Show the difference between the parameters
+  inferred from the calibrated and uncalibrated spectra, for each cluster.}
+\end{figure}
 

### 2014-07-07 tex/ms.tex
add some discussion text, fleshing out broadening text

@@
 the of the observed spectrum while taking into account the
-redshift. The instrumental resolution is given by $\sigma$.
+redshift. The instrumental resolution is given by $\sigma$.  Discuss
+Intrinsic resolution of model spectra (MILES), whether instrumentasl
+resolution is larger, smaller, or comparable to intrinsic velocity
+broadening.
 
@@
 and the full parameter set $\theta$ now includes
-the dispersion $\sigma_e$ and
+the instrumental wavelength broadening $\sigma$, 
+and the dispersion $\sigma_e$ and
 amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
@@
 spectrum of one of the clusters, using the full YY-band photometry. In
-Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
+Figure \ref{fig:inferred_spectrum} we show the spectrum resulting
 from draws of the parameters $[\theta,\alpha]$ from the posterior
@@
 of the model constructed from each draw.  In Figure
-\ref{fig:calibrated_spectrum} we also show the residuals between the data
+\ref{fig:inferred_spectrum} we also show the residuals between the data
 and the draws from the posterior, for both the spectra and the
-photometry. In Figure \ref{fig:calibrated_triangle} we show the
+photometry. In Figure \ref{fig:inferred_params} we show the
 marginalized and joint PDFs for the parameters.
@@
 \caption{Show, for one cluster, the (un)calibrated spectral data, draws from
-  the posterior for the model, and residuals}
+  the posterior for the model, and residuals \label{fig:inferred_spectrum}}
 \end{figure}
@@
 \caption{Show the observed photometric SED and draws from the
-  posterior, for one cluster.}
+  posterior, for one cluster.\label{fig:inferred_sed}}
 \end{figure}
@@
 \begin{figure}[h!]
-\caption{Show a corner plot of selected relevant parameters, for one cluster.}
+\caption{Show a corner plot of selected relevant parameters, for one
+cluster. \label{fig:inferred_params}}
 \end{figure}
@@
 \caption{Money plot.  Show the difference between the parameters
-  inferred from the calibrated and uncalibrated spectra, for each cluster.}
+  inferred from the calibrated and uncalibrated spectra, for each
+  cluster.\label{fig:boom}}
 \end{figure}
@@
 
-BDJ INSERT WORDS HERE.
-BDJ random issues, collected here in case we want to address them and
+BDJ INSERT WORDS HERE.  We have shown that we can combine photometric
+and spectroscopic data in a principled way to infer physical
+properties.  We do not resort to an arbitrary down-weighting or
+up-weighting of certain data. Instead, we explicitly model our
+uncertainty in the spectral calibration.  This combination of
+spectroscopy and photometry reduces the need for spectrophotometric
+calibration for a number of applications.  Furthermore, our strategy
+easily extensible to more complicated models, which include for
+example night sky line emission in the spectroscopy, wavelength
+calibration.
+
+BDJ misc issues, collected here in case we want to address them and
 to keep me from cluttering up the main text: effective aperture

### 2014-07-08 tex/ms.tex
more discussion text and figure list

@@
 lines. 
+This is the mean model which appears in equation
+\ref{eq:SpectroscopicLF}.
 
@@
 \begin{figure}[h!]
+\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
+\end{figure}
+
+\begin{figure}[h!]
 \caption{Money plot.  Show the difference between the parameters
@@
 
-BDJ INSERT WORDS HERE.  We have shown that we can combine photometric
-and spectroscopic data in a principled way to infer physical
-properties.  We do not resort to an arbitrary down-weighting or
-up-weighting of certain data. Instead, we explicitly model our
-uncertainty in the spectral calibration.  This combination of
-spectroscopy and photometry reduces the need for spectrophotometric
-calibration for a number of applications.  Furthermore, our strategy
+BDJ INSERT WORDS HERE.  We have demonstrated that we can combine
+photometric and spectroscopic data in a principled way to infer
+physical properties.  We do not resort to an arbitrary down-weighting
+or up-weighting of certain data. Instead, we explicitly model our
+uncertain knowledge of the spectral calibration.  For a number of
+applications this combination of spectroscopy and photometry reduces
+the need for spectrophotometric calibration.  Calibration information,
+if it exists, can be used to generate informative priors on the
+calibration parameters of our model. Furthermore, our strategy is
 easily extensible to more complicated models, which include for
@@
 calibration.
+
+In a heirarchical model it should be possible to use the inferred
+calibration parameters, along with additional information about the
+observations (e.g. airmass, instrument temperature), to in turn infer
+the parameters of a generative model for the calibration.
+
+Limitations.  The strategy we have outlined here has several
+limitations.  First, it requires a generative model for the spectrum of
+the object of interest, and is thus ill-suited to discovery projects.
 

### 2014-07-16 tex/ms.tex
note that gaussian for absorption lines is not a very good model

@@
 redshift. The instrumental resolution is given by $\sigma$.  Discuss
-Intrinsic resolution of model spectra (MILES), whether instrumentasl
-resolution is larger, smaller, or comparable to intrinsic velocity
-broadening.
+intrinsic resolution of model spectra (MILES), what to do in
+situations where instrumental resolution is higher, lower or
+comparable (ouch) to intrinsic velocity broadening.
 
@@
 stellar broadening $\sigma$) and with known central wavelengths
-$\lambda_\ell$.  For emission lines the amplitudes are constrained to be
-positive, while for interstellar absorption (e.g. Na D and Ca K) the
-amplitudes are constrained to be negative. This framework can be
+$\lambda_\ell$.  For emission lines the amplitudes are constrained to
+be positive, while for interstellar absorption (e.g. Na D and Ca K)
+the amplitudes are constrained to be negative. This framework can be
 easily extended to include more complex models for the nebular
-emission, such as allowing line dependent widths and velocities.
+emission, such as allowing line dependent widths and velocities, and
+using Voight profiles for the line shapes.  NB GAUSSIANS ARE A NOT
+GREAT APPROXIMATION FOR ABSORPTION LINE SHAPES (GAUSSIAN IN OPTICAL
+DEPTH, NOT $\Delta F$)
 
@@
 
-BDJ INSERT WORDS HERE.  We have demonstrated that we can combine
-photometric and spectroscopic data in a principled way to infer
-physical properties.  We do not resort to an arbitrary down-weighting
-or up-weighting of certain data. Instead, we explicitly model our
-uncertain knowledge of the spectral calibration.  For a number of
-applications this combination of spectroscopy and photometry reduces
-the need for spectrophotometric calibration.  Calibration information,
-if it exists, can be used to generate informative priors on the
-calibration parameters of our model. Furthermore, our strategy is
-easily extensible to more complicated models, which include for
-example night sky line emission in the spectroscopy, wavelength
-calibration.
+BDJ INSERT WORDS HERE.  We have demonstrated, using a sample of
+stellar clusters in M31, that we can combine photometric and
+spectroscopic data in a principled way to infer physical properties.
+We do not resort to an arbitrary down-weighting or up-weighting of
+certain data. Instead, we explicitly model our uncertain knowledge of
+the spectral calibration and infer it along with the physical
+properties. For a number of applications this combination of
+spectroscopy and photometry reduces the need for spectrophotometric
+calibration.  Calibration information, if it exists, can be
+incorporated into informative priors on the calibration parameters of
+our model.
 
-In a heirarchical model it should be possible to use the inferred
-calibration parameters, along with additional information about the
-observations (e.g. airmass, instrument temperature), to in turn infer
-the parameters of a generative model for the calibration.
+Our strategy is easily extensible to more complicated models, which
+include for example night sky line emission in the spectroscopy,
+wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
+MULTIPLE KERNELS, etc.  MODEL CHECKING.
 
-Limitations.  The strategy we have outlined here has several
-limitations.  First, it requires a generative model for the spectrum of
-the object of interest, and is thus ill-suited to discovery projects.
+In a heirarchical modelling context it should be possible to use the
+inferred calibration parameters, along with additional information
+about the observations (e.g. airmass, instrument temperature), to in
+turn infer the parameters of a generative model for the
+calibration. This generative model can then be used in the
+(probabilistic) calibration of objects where the spectra are difficult
+to model explicitly.
+
+Limitations.  The strategy we have advocated has several limitations.
+First, it requires a generative model for the spectrum of the object
+of interest, and is thus ill-suited to discovery projects.  Second,
+care must be taken to avoid absorbing interesting model deficiencies
+into the calibration model.  Third, we have made the assumption that
+the spectrscopy and the photometry are sampling the same populations.
+In practice, differences between spectroscopic and photometric
+apertures mean that the photometry and the spectroscopy are sampling
+slightly different physical regions.  The correct response to this
+situation is to explicitly model the differences, incorporating prior
+information about the spatial variation of physical properties.
+Finally, this method is computationally intensive and expensive, since
+we are constantly inverting largish matrices.
 

### 2014-07-24 tex/ms.tex
figure making script

@@
 In practice, differences between spectroscopic and photometric
-apertures mean that the photometry and the spectroscopy are sampling
+apertures often mean that the photometry and the spectroscopy are sampling
 slightly different physical regions.  The correct response to this

### 2014-07-24 figs/make_figures.py

@@ -1,0 +1,212 @@
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib import gridspec
+
+import diagnostics
+
+import sps_basis
+sps = sps_basis.StellarPopBasis(smooth_velocity=False)
+
+
+def data_figure(results_list, layout = None, shaded = False, **kwargs):
+    fig = pl.figure()
+
+    #get the panel geometry if not given
+    nobj = len(results_list)
+    if layout is None:
+        nx = int(np.floor(np.sqrt(nobj)))
+        ny = int(np.ceil(nobj*1.0/nx))
+        layout = [ny,nx]
+    print(ny, nx)
+    gs = gridspec.GridSpec(layout[0], layout[1])
+    for i, res in enumerate(results_list):
+        obs = res['obs']
+
+        if shaded:
+            ax = pl.Subplot(fig, gs[i])
+            ax = one_data_figure_shaded(obs, ax, color = 'blue', facecolor = 'grey')
+            fig.add_subplot(ax)
+
+        else:
+            fig, gs = one_data_figure_sep(obs, fig, subplot_spec = gs[i], **kwargs)
+    #pl.tight_layout(fig)
+    return fig
+        
+def one_data_figure_shaded(obs, axobj, color='Blue', facecolor='Blue',
+                           **kwargs):
+    """
+    Plot the spectrum on one panel with shading to show the uncertainty.
+    """
+    
+    x, y, e = obs['wavelength'], obs['spectrum'], obs['unc']
+    axobj.fill_between(x, y-e, y+e, facecolor='grey', alpha=0.3)
+    axobj.plot(x, y, color = color, linewidth = 0.5,**kwargs)
+
+    return axobj
+
+def one_data_figure_sep(obs, fig, subplot_spec=None, **kwargs):
+    """
+    Plot the spectrum and uncertainties in different panels
+    """
+    if subplot_spec is None:
+        gs = gridspec.GridSpec(2,1,height_ratios = [3,1], hspace=0)
+    else:
+        gs = gridspec.GridSpecFromSubplotSpec(2, 1, hspace=0,
+                                              subplot_spec=subplot_spec,
+                                              height_ratios = [3,1])
+    
+    
+    spec = pl.Subplot(fig, gs[0,0])
+    spec.plot(obs['wavelength'], obs['spectrum'], **kwargs)
[…]

### 2014-07-28 tex/ms.tex
adding figures and captions to ms

@@
 \newcommand{\mpia}{4}
+
+%figures
+\usepackage{graphicx}
+\DeclareGraphicsExtensions{.png,.pdf}
+\newcommand{\excluster}{B192-G242}
 
@@
 
-We are now left to demonstrate that it is possible to infer the
-parameters of interest $\theta$ while marginalizing over the
-calibration parameters $\alpha$.  We will apply the methodology for
-spectrophotometric calibration described above to \emph{actual,
-real} optical spectra of a stellar clusters in M31.  Spectra of star
-clusters provide a good test case, as they are less complex than
-galaxy spectra (for which it is necessary to model the star formation
-history) but are by no means trivial. In this way the key features of
-the calibration model and methodology are not obscured.
+We are now left to demonstrate that, by including photometry as well
+as spectroscopy, it is possible to infer the parameters of interest
+$\theta$ while marginalizing over the calibration parameters $\alpha$.
+We will apply the methodology for spectrophotometric calibration
+described above to \emph{actual, real} optical spectra of a stellar
+clusters in M31.  Spectra of star clusters provide a good test case,
+as they are less complex than galaxy spectra (for which it is
+necessary to model the star formation history) but are by no means
+trivial. In this way the key features of the calibration model and
+methodology are not obscured.
 
@@
 \begin{figure}[h!]
-\caption{Shows the calibrated and uncalibrated spectrum for one
-  cluster, along with the uncertainty spectrum and (maybe) the
-  calibration vector. \label{fig:data}}
+\includegraphics[width = \textwidth]{figures/dfig_b192-g242_020.png}
+\caption{The calibrated (left) and uncalibrated (right) spectrum for
+  \excluster, along with the uncertainties (bottom panel). The
+  spectra are not normalized. \label{fig:data}}
 \end{figure}
@@
 \begin{table}[h!]
-\caption{List all the clusters, and individual exposures.}
+\caption{List all the clusters, RA, Dec, photometry and individual exposures.}
 \end{table}
@@
 emission, such as allowing line dependent widths and velocities, and
-using Voight profiles for the line shapes.  NB GAUSSIANS ARE A NOT
-GREAT APPROXIMATION FOR ABSORPTION LINE SHAPES (GAUSSIAN IN OPTICAL
-DEPTH, NOT $\Delta F$)
+using Voight profiles for the line shapes.
 
@@
 and the full parameter set $\theta$ now includes
-the instrumental wavelength broadening $\sigma$, 
+the instrumental wavelength broadening $\sigma$ 
 and the dispersion $\sigma_e$ and
-amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
-lines. 
+amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
+absorption lines.
 This is the mean model which appears in equation
@@
 of the model constructed from each draw.  In Figure
-\ref{fig:inferred_spectrum} we also show the residuals between the data
+\ref{fig:inferred_sed} we also show the residuals between the data
 and the draws from the posterior, for both the spectra and the
@@
 \begin{figure}[h!]
-\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
-  the posterior for the model, and residuals \label{fig:inferred_spectrum}}
+\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
+\caption{Spectra resulting from draws from the posterior parameter
+space conditioned on the calibrated \excluster~ spectrum and
+photometry.  Left: For each of 5 draws from the posterior we show from
+top to bottom, three components of the model: the mean cluster
+spectrum, the calibration vector, and the mean prediction of the
+Gaussian process.  Right: From top to bottom, the full model ({\it
+cyan}) compared to the observed, calibrated spectrum ({\it magenta}),
+the ratio of the observed to the modeled spectrum, and the difference
+between the observed spectrum and the modeled spectrum normalized by
+the uncertainty.
+\label{fig:inferred_spectrum}}
 \end{figure}
@@
 \begin{figure}[h!]
-\caption{Show the observed photometric SED and draws from the
-  posterior, for one cluster.\label{fig:inferred_sed}}
+\includegraphics[width=\textwidth]{figures/pfig_b192-g242_020_cal.png}
+\caption{The photometric SED resulting \label{fig:inferred_sed}}
 \end{figure}
@@
 \begin{figure}[h!]
+\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
 \caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
@@
 
+\subsection{Dependence on Photometric Data}
+In this section we examine how the constraints on physical (and
+calibration) parameters vary as a function of the number and type of
+photometric points available.
+
 \section{Discussion}
@@
 certain data. Instead, we explicitly model our uncertain knowledge of
-the spectral calibration and infer it along with the physical
+the spectral calibration and infer this calibration jointly with the physical
 properties. For a number of applications this combination of
@@
 calibration.  Calibration information, if it exists, can be
-incorporated into informative priors on the calibration parameters of
-our model.
+incorporated into informative priors on the calibration parameters of the model.
 
 Our strategy is easily extensible to more complicated models, which
-include for example night sky line emission in the spectroscopy,
+include for example night sky-line emission in the spectroscopy (or
+residuals from an intial sky-line subtraction), and uncertainties in
 wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
@@
 into the calibration model.  Third, we have made the assumption that
-the spectrscopy and the photometry are sampling the same populations.
+the spectroscopy and the photometry are sampling the same populations.
 In practice, differences between spectroscopic and photometric
@@
 
-BDJ misc issues, collected here in case we want to address them and
-to keep me from cluttering up the main text: effective aperture
-corrections (i.e. we're implicitly assuming photometry and
-spectroscopy sample the same population).  Sky subtraction residuals.
-Model resolution and instrument resolution.  Method only useful when
-you have a model for the mean spectrum?  How to interpret GP
-residuals, as a fn of S/N?  Photometric upper limits? Infer the
-wavelength solution as well - stellar population (and telluric lines)
-as your arc. Combinations of broadening in velocity space (physical)
-and in wavelength space (instrumental)
+BDJ misc issues, collected here in case we want to address them and to
+keep me from cluttering up the main text: Model resolution and
+instrument resolution.  How to interpret GP residuals, as a fn of S/N?
+Photometric upper limits? Infer the wavelength solution as well -
+stellar population (and telluric lines) as your arc. Combinations of
+broadening in velocity space (physical) and in wavelength space
+(instrumental)
 

### 2014-07-28 tex/figures/make_figures.py

@@ -263,29 +263,29 @@ if __name__ == '__main__':
         sf, mf = r+'_mcmc', r+'_model'
         result, pr, model = diagnostics.read_pickles(sf, model_file = mf)
         of = result['run_params']['outfile'].split('/')[-1]
-        
+        of = of.replace('.','_')
         ns = result['chain'].shape[0] * result['chain'].shape[1]
         sample = [int(s * ns) for s in samples]
     
-        #sfig = spec_figure(result, samples=sample,
-        #                linewidth = 0.5, xlim = (3650, 7300))
-        #sfig.suptitle(name[i])
-        #sfig.savefig('sfig.'+ of + figext)
-        #pl.close(sfig)
+        sfig = spec_figure(result, samples=sample,
+                        linewidth = 0.5, xlim = (3650, 7300))
+        sfig.suptitle(name[i])
+        sfig.savefig('sfig_'+ of + figext)
+        pl.close(sfig)
         
-        #pfig = phot_figure(result, samples=sample)
-        #pfig.suptitle(name[i])
-        #pfig.savefig('pfig.' + of + figext)
-        #pl.close(pfig)
+        pfig = phot_figure(result, samples=sample)
+        pfig.suptitle(name[i])
+        pfig.savefig('pfig_' + of + figext)
+        pl.close(pfig)
 
         tfig = corner_plot(result, showpars = showpars_phys)
         tfig.suptitle(name[i])
-        tfig.savefig('ptri.' + of + figext)
+        tfig.savefig('ptri_' + of + figext)
         pl.close(tfig)
 
         tfig = corner_plot(result, showpars = showpars_cal)
         tfig.suptitle(name[i])
-        tfig.savefig('ctri.' + of + figext)
+        tfig.savefig('ctri_' + of + figext)
         pl.close(tfig)
 
                
@@ -294,11 +294,11 @@ if __name__ == '__main__':
     dfig = data_figure(results,
                        color='b', linewidth=0.5)
     [dfig.axes[i*2].set_title(name[i]) for i in range(len(name))]
-    dfig.savefig('data_fig.'+ '.'.join(of.split('.')[0:2]) + figext)
+    dfig.savefig('dfig_'+ '_'.join(of.split('_')[0:2]) + figext)
 
     cfig = calibration_figure(*results, samples =sample)
[…]

### 2014-07-28 tex/ms.tex
comments in color, and more figure captions, many small changes

@@
 % ---- Charlie (emulateapj) mode ----
-% \documentclass[iop,numberedappendix]{emulateapj}
-% \usepackage{apjfonts}
+ \documentclass[iop,numberedappendix]{emulateapj}
+ \usepackage{apjfonts}
 % ----
-
+\usepackage{color}
 \bibliographystyle{apj}
@@
 log-likelihood function we are going to use for the photometric
-measurements (BDJ: IS THIS TRUE?  DWH, Currently I'm not using a
-jitter term, but I can and will) in what follows.  In this
+measurements ({\color{blue} BDJ: IS THIS TRUE?} {\color{red} DWH,
+Currently I'm not using a jitter term, but I can and will.  Update:
+having difficulty with a jitter term}) in what follows.  In this
 formulation, if $\theta$ are the parameters of interest, the jitter
@@
 
-DRW/BDJ WORDS ABOUT DATA
-
-The data we use to test our method consists of optical spectroscopy of
+The data we use to test our method consist of optical spectroscopy of
 XX stellar clusters in M31 for which YY-band HST photometric data
@@
 Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
-of the spectra is $3700-7200 \AA$. The instrumental resolution is
-$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
-calibration happened. Sky subtraction happened. The data were
+of the spectra is $3700-9100 \AA$. The instrumental resolution is
+$\sim 5\AA$ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
+calibration happened. Sky subtraction happened.} The data were
 approximately spectrophotometrically calibrated using an average
-calibration vector for the night constructed from.... (MORE
-HERE). Figure \ref{fig:data} shows the spectra before and after
-calibration (SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?).  Discuss
-S/N, sky subtraction.
+calibration vector for the night constructed from {\color{blue} MORE
+HERE}. Figure \ref{fig:data} shows the spectra before and after
+calibration {\color{blue} SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.  Discuss
+S/N, sky subtraction.}
 
-\begin{figure}[h!]
+{\color{red} Specify order of calibration polynomial here?}
+
+\begin{figure*}[h!]
 \includegraphics[width = \textwidth]{figures/dfig_b192-g242_020.png}
@@
   spectra are not normalized. \label{fig:data}}
-\end{figure}
+\end{figure*}
 
@@
 $\beta$ to be fixed for the purposes of this exercise, with no loss of
-generality (KEEPING IMF SLOPE CONSTANT FOR NOW).  We will also fix the
+generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also fix the
 shape of the attenuation curve, $k_\lambda \equiv
@@
 
-BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
-by convolution with a Gaussian in wavelength space (to model the MMT
+The model spectra $F_{\theta^\prime}$ are smoothed by convolution
+with a Gaussian in wavelength space (in this case to model the MMT
 line-spread function) and are interpolated to the wavelength points of
 the of the observed spectrum while taking into account the
-redshift. The instrumental resolution is given by $\sigma$.  Discuss
-intrinsic resolution of model spectra (MILES), what to do in
-situations where instrumental resolution is higher, lower or
-comparable (ouch) to intrinsic velocity broadening.
+redshift. The instrumental resolution is given by the parameter
+$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
+(MILES), what to do in situations where instrumental resolution is
+higher, lower or comparable (ouch) to intrinsic velocity broadening.}
 
@@
 sampler does not require the specification of step sizes in each
-dimension.  ASSESSING SAMPLER CONVERGENCE
+dimension.  {\color{blue}ASSESSING SAMPLER CONVERGENCE}
 
@@
 may be especially appropriate for the calibration parameters $\alpha$
-if additional information about the instrument is available or for the
+if additional information about the instrument is available; or for the
 parameters of interest $\theta$, for example in the case that there
@@
 
-\begin{table}[h!]
-\caption{List the parameters and  their allowed ranges.}
-\end{table}
-
+\input{tables/priors.tbl}
 \subsection{Results}
@@
 We first infer the parameters of interest $\theta$ for a calibrated
-spectrum of one of the clusters, using the full YY-band photometry. In
-Figure \ref{fig:inferred_spectrum} we show the spectrum resulting
-from draws of the parameters $[\theta,\alpha]$ from the posterior
-distribution.  This figure also shows the calibrated spectrum on which
-the priors were conditioned, and several of the individual components
-of the model constructed from each draw.  In Figure
-\ref{fig:inferred_sed} we also show the residuals between the data
-and the draws from the posterior, for both the spectra and the
-photometry. In Figure \ref{fig:inferred_params} we show the
-marginalized and joint PDFs for the parameters.
+spectrum of one of the clusters, \excluster, using the full YY-band
+photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
+that result from draws of the parameters $[\theta,\alpha]$ from the
+posterior distribution, as well as several of the individual
+components of the model constructed from each draw.  This figure also
+shows the calibrated spectrum on which the priors were conditioned,
+and residuals between the posterior models and the observed data.  In
+Figure \ref{fig:inferred_sed} we also show the residuals between the
+data and the draws from the posterior for the spectra. In Figure
+\ref{fig:inferred_params} we show the marginalized and joint PDFs for
+a subset of the full model parameters.
 
@@
 
-BDJ: Finally, we have fun playing with the number of photometric bands
-and the S/N.
-
-\begin{figure}[h!]
+\begin{figure*}[h!]
 \includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
@@
 top to bottom, three components of the model: the mean cluster
-spectrum, the calibration vector, and the mean prediction of the
-Gaussian process.  Right: From top to bottom, the full model ({\it
-cyan}) compared to the observed, calibrated spectrum ({\it magenta}),
-the ratio of the observed to the modeled spectrum, and the difference
-between the observed spectrum and the modeled spectrum normalized by
-the uncertainty.
+spectrum, the calibration vector, and the mean prediction of $\Delta$
+for the Gaussian process.  Right: From top to bottom, the full model
+({\it cyan}) compared to the observed, calibrated spectrum ({\it
+magenta}), the ratio of the observed to the modeled spectrum, and the
+difference between the observed spectrum and the modeled spectrum
+normalized by the uncertainty.
 \label{fig:inferred_spectrum}}
-\end{figure}
+\end{figure*}
 
 \begin{figure}[h!]
-\includegraphics[width=\textwidth]{figures/pfig_b192-g242_020_cal.png}
-\caption{The photometric SED resulting \label{fig:inferred_sed}}
+\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_020_cal.png}
+\caption{Model SEDs.  Top: The model photometric SED resulting from draws from the posterior
+  parameter space conditioned ({\it cyan}) on the observed photometry
+  ({\it magenta})  and spectra.  Bottom: uncertainty normalized
+  residuals of the models from the observations. 
+ . \label{fig:inferred_sed}}
 \end{figure}
@@
 
-\begin{figure}[h!]
+\begin{figure*}[h!]
 \includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
 \caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
-\end{figure}
+\end{figure*}
 
@@
 calibration) parameters vary as a function of the number and type of
-photometric points available.
+photometric points available. {\color{red} BDJ DO THIS TEST.}
 
@@
 
-BDJ INSERT WORDS HERE.  We have demonstrated, using a sample of
-stellar clusters in M31, that we can combine photometric and
-spectroscopic data in a principled way to infer physical properties.
-We do not resort to an arbitrary down-weighting or up-weighting of
-certain data. Instead, we explicitly model our uncertain knowledge of
-the spectral calibration and infer this calibration jointly with the physical
-properties. For a number of applications this combination of
-spectroscopy and photometry reduces the need for spectrophotometric
-calibration.  Calibration information, if it exists, can be
-incorporated into informative priors on the calibration parameters of the model.
+We have demonstrated, using a sample of stellar clusters in M31, that
+we can combine photometric and spectroscopic data in a principled way
+to infer physical properties.  We do not resort to an arbitrary
+down-weighting or up-weighting of certain data. Instead, we explicitly
+model our uncertain knowledge of the spectral calibration and infer
+this calibration jointly with the physical properties. For a number of
+applications this combination of spectroscopy and photometry reduces
+the need for spectrophotometric calibration.  Calibration information,
+if it exists, can be incorporated into informative priors on the
+calibration parameters of the model.
 
@@
 residuals from an intial sky-line subtraction), and uncertainties in
-wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
-MULTIPLE KERNELS, etc.  MODEL CHECKING.
+wavelength calibration. {\color{blue} DISCUSS MORE COMPLICATED
+COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL CHECKING.}
 

### 2014-07-28 tex/ms.tex
more figures and more text tweaks

@@
 
+\begin{figure}[h!]
+\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
+\caption{The calibrated (left) and uncalibrated (right) spectrum for
+\excluster, along with the uncertainties (bottom panel). The spectra
+have been renormalized to avoid floating point errors. {\color{blue}
+SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.}\label{fig:data}}
+\end{figure}
+
 \subsection{Test Data}
@@
 calibration vector for the night constructed from {\color{blue} MORE
-HERE}. Figure \ref{fig:data} shows the spectra before and after
-calibration {\color{blue} SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.  Discuss
-S/N, sky subtraction.}
+HERE. Discuss S/N, sky subtraction.}
 
-{\color{red} Specify order of calibration polynomial here?}
-
-\begin{figure*}[h!]
-\includegraphics[width = \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{The calibrated (left) and uncalibrated (right) spectrum for
-  \excluster, along with the uncertainties (bottom panel). The
-  spectra are not normalized. \label{fig:data}}
-\end{figure*}
+An example spectrum, both after and before spectrophotometric
+calibration, is shown in Figure \ref{fig:data}.  When fitting the
+spectra we mask the region around the bright OI5577 sky line, and we
+fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
+S/N edges and, on the red side, imperfect sky line subtraction in a
+region of the spectrum that has a paucity of informative spectral
+lines.Furthermore, the MILES empirical spectra (see
+\S\ref{sec:cluster_model}) are only available for $\lambda < 7500$\AA
+{\color{red} Specify/Justify order of calibration polynomial here?}.
 
@@
 
-Our prior distributions are in all cases top-hat functions, though
-more informative prior distributions may be used.  Informative priors
-may be especially appropriate for the calibration parameters $\alpha$
-if additional information about the instrument is available; or for the
-parameters of interest $\theta$, for example in the case that there
-is knowledge of the metallicity distribution of the population from
-which a given cluster is drawn.
+Our prior distributions are in all cases top-hat functions, described
+in Table \ref{tbl:priors}, though more informative prior distributions
+may be used.  Informative priors may be especially appropriate for the
+calibration parameters $\alpha$ if additional information about the
+instrument is available; or for the parameters of interest $\theta$,
+for example in the case that there is knowledge of the metallicity
+distribution of the population from which a given cluster is drawn.
 
 \input{tables/priors.tbl}
+
+\begin{figure*}[h!]
+\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
+\caption{Spectra resulting from draws from the posterior parameter
+space conditioned on the calibrated \excluster~ spectrum and
+photometry.  Left: For each of 5 draws from the posterior we show from
+top to bottom, three components of the model: the mean cluster
+spectrum, the calibration vector, and the mean prediction of $\Delta$
+for the Gaussian process.  Right: From top to bottom, the full model
+({\it cyan}) compared to the observed, calibrated spectrum ({\it
+magenta}), the ratio of the observed to the modeled spectrum, and the
+difference between the observed spectrum and the modeled spectrum
+normalized by the uncertainty.
+\label{fig:inferred_spectrum}}
+\end{figure*}
+
 \subsection{Results}
@@
 
-\begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
-\caption{Spectra resulting from draws from the posterior parameter
-space conditioned on the calibrated \excluster~ spectrum and
-photometry.  Left: For each of 5 draws from the posterior we show from
-top to bottom, three components of the model: the mean cluster
-spectrum, the calibration vector, and the mean prediction of $\Delta$
-for the Gaussian process.  Right: From top to bottom, the full model
-({\it cyan}) compared to the observed, calibrated spectrum ({\it
-magenta}), the ratio of the observed to the modeled spectrum, and the
-difference between the observed spectrum and the modeled spectrum
-normalized by the uncertainty.
-\label{fig:inferred_spectrum}}
-\end{figure*}
-
 \begin{figure}[h!]
@@
 \begin{figure}[h!]
-\caption{Show a corner plot of selected relevant parameters, for one
-cluster. \label{fig:inferred_params}}
+\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
+\caption{ Marginalized and joint PDFs of  subset of the physical
+  parameters $\theta$ inferred from the spectophotometrically
+  calibrated spectrum of \excluster. \label{fig:inferred_params}}
 \end{figure}
@@
 Thanks to X. for bringing us beer.
+DRW is supported by NASA through Hubble Fellowship grant
+  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
+BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
+CC is supported by Packard and Sloan Foundation Fellowships. 
+This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
+In large part, analysis and plots presented in this paper utilized
+  iPython and packages from NumPy, SciPy, and Matplotlib
+  \citep[][]{hunter2007, oliphant2007, perez2007, astropy2013} as well
+  as python-FSPS  (http:://github.com/dfm/python-fsps) .
 

### 2014-07-28 tex/figures/make_figures.py

@@ -278,12 +278,12 @@ if __name__ == '__main__':
         pfig.savefig('pfig_' + of + figext)
         pl.close(pfig)
 
-        tfig = corner_plot(result, showpars = showpars_phys)
+        tfig = corner_plot(result, showpars = showpars_phys, start=-250)
         tfig.suptitle(name[i])
         tfig.savefig('ptri_' + of + figext)
         pl.close(tfig)
 
-        tfig = corner_plot(result, showpars = showpars_cal)
+        tfig = corner_plot(result, showpars = showpars_cal, start=-250)
         tfig.suptitle(name[i])
         tfig.savefig('ctri_' + of + figext)
         pl.close(tfig)

### 2014-07-28 tex/ms.tex
more results text, and figure captions

@@
 region of the spectrum that has a paucity of informative spectral
-lines.Furthermore, the MILES empirical spectra (see
-\S\ref{sec:cluster_model}) are only available for $\lambda < 7500$\AA
+lines. Furthermore, the MILES spectral library (see
+\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
 {\color{red} Specify/Justify order of calibration polynomial here?}.
+
+{\color{blue} DRW words about photometry}
 
@@
 posterior distribution, as well as several of the individual
-components of the model constructed from each draw.  This figure also
-shows the calibrated spectrum on which the priors were conditioned,
-and residuals between the posterior models and the observed data.  In
-Figure \ref{fig:inferred_sed} we also show the residuals between the
-data and the draws from the posterior for the spectra. In Figure
-\ref{fig:inferred_params} we show the marginalized and joint PDFs for
-a subset of the full model parameters.
+components of the model constructed from each draw. Figure
+\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
+which the priors were conditioned, and residuals between the posterior
+models and the observed data.  The agreement is quite good, though
+some lines are not accurately predicted.  For example, the observed
+Mg$b$ absorption appears stronger than the modeled absorption.
 
-BDJ: Discuss degeneracies, etc.  Apparently we get really nice
-redshift/velocity constraints for free.
-
-BDJ: Next, we infer the parameters of the spectrum of the same cluster
-\emph{without} spectrophotometric calibration.
-
-BDJ: Then, we show select marginalized or joint PDFs for each cluster
-calibrated/uncalibrated, to assess consistency.  They are very consistent.
+In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
+posterior parameter draws, compared to the observed SED. Finally, In
+Figure \ref{fig:inferred_params} we show the marginalized and joint
+PDFs for a subset of the full model parameters.
 
@@
   parameters $\theta$ inferred from the spectophotometrically
-  calibrated spectrum of \excluster. \label{fig:inferred_params}}
+  calibrated spectrum of \excluster. The blue lines indicate the
+  parameter values that resulted from the powell minimization. \label{fig:inferred_params}}
 \end{figure}
+
+The physical model parameters that we infer indicate that \excluster~
+has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
+extinction, and a stellar mass of $\sim 1e5$ M$_{sun}$ {\color{blue}
+check that this is current mass, not initial mass}.  We find a spectral
+broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
+quadrature with the intrinsic resolution of the MILES library, 2.5\AA
+FWHM \citep{beifiori11}, reproduces the typical line-spread function
+of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
+We obtain strong constraints on the systemic velocity.
+
+For the calibration model, we obtain a calibration vector $f(\alpha)$
+that is nearly linear in wavelength {\color{red} WHY IS IT NOT A
+CONSTANT?  Need longer burn-in?  Is this the same issue as the SED
+residuals?}.  The length scale of the Gaussian process is $\sim
+60$\AA.  It is possible to reconstruct the inferred total
+multiplicative calibration vector for each draw of the model
+parameters.  Rearranging equation \ref{eq:spectroscopicLF} yields
+\begin{eqnarray} 
+\frac{d}{\mu(\theta)} & = & f(\alpha) +
+\frac{\tilde{\Delta}}{\mu(\theta)}
+\quad ,
+\end{eqnarray}
+for the total effective multiplicative calibration, where
+$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
+residual between the data and the model. The inverse of this ratio is
+shown in the left panel of Figure \ref{fig:inferred_calib} as our
+inferred total multiplicative calibration function; if the
+spectrophotometric calibration were perfect and we had correctly
+inferred it, then we would expect this vector to be constant as a
+function of wavelength.
 
@@
 \includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
-\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
+\caption{Left: Samples of the effective multiplicative calibration
+  vector for the spectrophotometrically calibrated spectrum of
+  \excluster~ ({\it cyan}) compared to that obtained from ancillary
+  photometric data ({\it magenta}).  Right:  The same, but for the
+  uncalibrated data. 
+ \label{fig:inferred_calib}}
 \end{figure*}
 
+BDJ: Next, we infer the parameters of the spectrum of the same cluster
+\emph{without} spectrophotometric calibration.  How many/which figures
+to show?
+
+BDJ: Then, we show select marginalized or joint PDFs for each cluster
+calibrated/uncalibrated, to assess consistency.  Or we just show
+comparisons of confidence intervals.
+
 \begin{figure}[h!]
+\includegraphics[width =0.5\textwidth]{figures/B192_020_cratio.pdf}
 \caption{Money plot.  Show the difference between the parameters
   inferred from the calibrated and uncalibrated spectra, for each
-  cluster.\label{fig:boom}}
+  cluster. Tjis is a placeholder, since it only shows B192 for fixed
+  GP parameters. \label{fig:boom}}
 \end{figure}

### 2014-07-28 tex/ms.tex
minor tweak

@@
 has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
-extinction, and a stellar mass of $\sim 1e5$ M$_{sun}$ {\color{blue}
+extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
 check that this is current mass, not initial mass}.  We find a spectral
@@
 
-For the calibration model, we obtain a calibration vector $f(\alpha)$
+For the calibration model, we obtain a vector $f(\alpha)$
 that is nearly linear in wavelength {\color{red} WHY IS IT NOT A

### 2014-07-29 tex/ms.tex
add note about SED tension
adding references

@@
 % ----
-\usepackage{color}
+\usepackage{color, hyperref}
 \bibliographystyle{apj}
@@
 \newcommand{\excluster}{B192-G242}
+
+%references
+\newcommand{\foreign}[1]{\emph{#1}}
+\newcommand{\etal}{\foreign{et\,al.}}
 
@@
 Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
-of the spectra is $3700-9100 \AA$. The instrumental resolution is
-$\sim 5\AA$ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
+of the spectra is $3700-9100$\AA. The instrumental resolution is
+$\sim 5$\AA~ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
 calibration happened. Sky subtraction happened.} The data were
@@
 spectra we mask the region around the bright OI5577 sky line, and we
-fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
+fit only to the spectrum with $3750 < \lambda < 7200$\AA~ to avoid the low
 S/N edges and, on the red side, imperfect sky line subtraction in a
@@
 $\beta$ to be fixed for the purposes of this exercise, with no loss of
-generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also fix the
-shape of the attenuation curve, $k_\lambda \equiv
+generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also
+fix the shape of the attenuation curve, $k_\lambda \equiv
 \tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
@@
 $S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
-code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
-\citep{Padova} and the MILES stellar spectral library \citep{MILES}.
+code \citep[FSPS][]{fsps}.  We use the Padova 2007 isochrones
+\citep{girardi00, bertilli94, marigo07} and the MILES stellar spectral
+library \citep{miles_I, miles_II, miles_III}.
 
@@
 This is the mean model which appears in equation
-\ref{eq:SpectroscopicLF}.
+\ref{eq:spectroscopicLF}.
 
@@
 algorithm we use is the affine-invariant ensemble sampling scheme of
-\citet{GW}, as implemented in the \texttt{emcee} package \cite{dfm}
+\citet{goodman}, as implemented in the \texttt{emcee} package \citep{emcee}
 Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
@@
 In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
-posterior parameter draws, compared to the observed SED. Finally, In
-Figure \ref{fig:inferred_params} we show the marginalized and joint
-PDFs for a subset of the full model parameters.
+posterior parameter draws, compared to the observed SED. There is some
+tension between the modeled and observed SEDs, I'm not quite sure
+why. Finally, In Figure \ref{fig:inferred_params} we show the
+marginalized and joint PDFs for a subset of the full model parameters.
 
@@
 check that this is current mass, not initial mass}.  We find a spectral
-broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
-quadrature with the intrinsic resolution of the MILES library, 2.5\AA
+broadening of $\sim 1.75$\AA~ (4.1\AA~ FWHM), which when combined in
+quadrature with the intrinsic resolution of the MILES library, 2.5\AA~
 FWHM \citep{beifiori11}, reproduces the typical line-spread function
-of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
+of the MMT Hectospec instrument, $\sim 5$\AA~ \citep{fabricant13}.
 We obtain strong constraints on the systemic velocity.
@@
   iPython and packages from NumPy, SciPy, and Matplotlib
-  \citep[][]{hunter2007, oliphant2007, perez2007, astropy2013} as well
-  as python-FSPS  (http:://github.com/dfm/python-fsps) .
+  \citep[][]{hunter2007, oliphant2007, perez2007} as well
+  as python-FSPS  (\url{http:://github.com/dfm/python-fsps}) .
+
+\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
+\begin{thebibliography}{}\raggedright
+
+\bibitem[Beifiori \etal(2011)]{beifiori11} 
+Beifiori, A., Maraston, C., Thomas, D., \& Johansson, J.\ 2011, \aap, 531, A109
+
+\bibitem[Bertelli et al.(1994)]{bertelli94} Bertelli, G., Bressan, A., Chiosi, C., Fagotto, F., \& Nasi, E.\ 1994, \aaps, 106, 275
+
+\bibitem[Cardelli \etal(1989)]{CCM89} 
+Cardelli, J.~A., Clayton, G.~C., \& Mathis, J.~S.\ 1989, \apj, 345, 245
+
+\bibitem[Cenarro \etal(2007)]{miles_II} 
+Cenarro, A.~J., Peletier, R.~F., S{\'a}nchez-Bl{\'a}zquez, P., et al.\ 2007, \mnras, 374, 
+664
+
+\bibitem[Conroy \etal(2009)]{fsps} 
+Conroy, C., Gunn, J.~E., \& White, M.\ 2009, \apj, 699, 486
+
+\bibitem[Conroy \& Gunn(2010)]{fsps_cal} 
+Conroy, C., \& Gunn, J.~E.\ 2010, \apj, 712, 833
+
+\bibitem[Fabricant \etal(2013)]{fabricant13} 
+Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362
+
+\bibitem[Falc{\'o}n-Barroso \etal(2011)]{miles_III} 
+Falc{\'o}n-Barroso, J., S{\'a}nchez-Bl{\'a}zquez, P., Vazdekis, A., et al.\ 2011, \aap, 532, A95
+
+\bibitem[Foreman-Mackey \etal(2012)]{emcee}
+Foreman-Mackey, D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2013, \pasp, 125,
+306 (\arxiv{1202.3665})
+
+\bibitem[Girardi et al.(2000)]{girardi00} 
+Girardi, L., Bressan, A., Bertelli, G., \& Chiosi, C.\ 2000, \aaps, 141, 371
+
+\bibitem[Goodman~\&\ Weare(2010)]{goodman}
+Goodman,~J. \& Weare,\ J., 2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
+
+\bibitem[Marigo \& Girardi(2007)]{marigo07} 
+Marigo, P., \& Girardi, L.\ 2007, \aap, 469, 239
+
+\bibitem[S{\'a}nchez-Bl{\'a}zquez \etal(2006)]{miles_I} 
+S{\'a}nchez-Bl{\'a}zquez, P., Peletier, R.~F., Jim{\'e}nez-Vicente,
+J., et  al.\ 2006, \mnras, 371, 703
+
+\end{thebibliography}
 

### 2014-07-29 tex/figures/make_figures.py
fix corner plot figure labels

@@ -1,12 +1,27 @@
+import sys
 import numpy as np
 import matplotlib.pyplot as pl
 from matplotlib import gridspec
 import triangle
 
 import diagnostics
-
 import sps_basis
 sps = sps_basis.StellarPopBasis(smooth_velocity=False)
+
+pardict = {}
+pardict['mass']=r'$m_*$ (M$_\odot$)'
+pardict['tage']=r'$t$ (Gyr)'
+pardict['zmet']=r'$\log Z/Z_\odot$'
+pardict['dust2']=r'$A_V$'
+pardict['sigma_smooth']=r'$\sigma \, (\AA)$'
+pardict['zred']=r'$z$'
+pardict['gp_jitter']=r'$s$'
+pardict['gp_amplitude']=r'$a$'
+pardict['gp_length']=r'$l \, (\AA)$'
+pardict['poly_coeffs1']=r'$c_1$'
+pardict['poly_coeffs2']=r'$c_2$'
+pardict['spec_norm']=r'$c_0$'
+pardict['emission_disp']= r'$\sigma_e \, (\AA)$'
 
 def data_figure(results_list, layout = None, shaded = False, **kwargs):
     fig = pl.figure(figsize=(10, 5))
@@ -235,8 +250,8 @@ def corner_plot(results, showpars=None, start=0, thin=1):
         flatchain = flatchain[:,ind_show]
         truths = truths[ind_show]
         parnames= parnames[ind_show]
-        
-    fig = triangle.corner(flatchain, labels = parnames,
+        parlabels = [pardict[p] for p in parnames]
+    fig = triangle.corner(flatchain, labels = parlabels,
                           quantiles=[0.16, 0.5, 0.84], verbose=False,
                           truths = truths)
 
@@ -290,7 +305,8 @@ if __name__ == '__main__':
 
                
         results += [result]
-        
+
+    sys.exit()
     dfig = data_figure(results,
                        color='b', linewidth=0.5)
     [dfig.axes[i*2].set_title(name[i]) for i in range(len(name))]

### 2014-08-04 tex/ms.tex
fix corner plot figure labels
alternative \Delta formulation

@@
 
+XXX Alternative XXX.
+Because the model  of equation \ref{eq:spectroscopicLF} includes an
+additive term in the form of the residual column vector $\Delta$,
+sharp spectral features can be diluted. To mitigate this we try a
+model where the residual column vector is taken to be the residual
+\emph{from the calibration vector $f(\alpha)$}.  That is, 
+\begin{eqnarray}\label{eq:spectroscopicLFalt}
+\Delta &\equiv& \frac{d}{\mu(\theta)} - f(\alpha)
+\quad ,
+\end{eqnarray}
+
 In detail, we are going to choose a $M$th-order polynomial form for
@@
 some lines are not accurately predicted.  For example, the observed
-Mg$b$ absorption appears stronger than the modeled absorption.
+Mg$b$ absorption appears stronger than the modeled
+absorption. {\color{blue} Should I show blowups of selected regions/lines?}
 

### 2014-08-04 tex/ms.tex
alternative GP formulation rewrite, cal figures for this alternative

--- 2014-07-29 tex/ms.tex
@@
 
+XXX Alternative XXX.
+Because the residual column vector $\Delta$ of equation
+\ref{eq:spectroscopicLF} is additive with respect to the mean model
+$\mu$, sharp spectral features in the mean model (such as absorption
+lines) can be artificially
+diluted or enhanced, affecting the derived parameters. To mitigate this we construct a
+model where the residual column vector is taken to be the residual
+\emph{from the calibration vector $f(\alpha)$} and is multiplicative
+with respect to the mean model $\mu$.  That is,
+\begin{eqnarray}\label{eq:spectroscopicLFalt} \Delta &\equiv&
+\frac{d}{\mu(\theta)} - f(\alpha) \quad ,
+\end{eqnarray}
+where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before.
+
 In detail, we are going to choose a $M$th-order polynomial form for

### 2014-08-04 tex/figures/make_figures.py

@@ -262,7 +262,7 @@ def phot_figure(results, alpha=0.3, samples = [-1],
     
 
 def calibration_figure(cal_result, nocal_result, samples = [-1],
-                       start=0, thin=1,
+                       start=0, thin=1, multiplicative=False,
                        alpha = 0.3):
     #plot the calibration vector and the reconstruction of it
     # from the f(alpha) and GP, for cal and uncal.
@@ -287,7 +287,10 @@ def calibration_figure(cal_result, nocal_result, samples = [-1],
             comps = diagnostics.model_components(theta, result, result['obs'],
                                              sps, photflag=0)
             spec, gp, cal, mask, stars = comps
-            full_cal = cal[mask] + gp/stars[mask]
+            if multiplicative:
+                full_cal = (cal[mask] + gp)
+            else:
+                full_cal = cal[mask] + gp/stars[mask]
             mwave = result['obs']['wavelength'][mask]
             ax.plot(mwave, 1/full_cal, label = label,
                           color = 'cyan', alpha = alpha)

### 2014-08-06 tex/ms.tex
figure code updates
text and plotting code fro the log model

@@
 \begin{eqnarray}\label{eq:spectroscopicLFalt} \Delta &\equiv&
-\frac{d}{\mu(\theta)} - f(\alpha) \quad ,
+\frac{d}{\mu(\theta)} - f(\alpha) \\
+\sigma_{n} & = & \sigma'_n / \mu(\theta)
+\quad ,
 \end{eqnarray}
-where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before.
+where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
+$\sigma'_{n}$ are now the observational uncertainties
+
+XXX Alternative 2 XXX.
+Because the residual column vector $\Delta$ of equation
+\ref{eq:spectroscopicLF} is additive with respect to the mean model
+$\mu$, sharp spectral features in the mean model (such as absorption
+lines) can be artificially diluted or enhanced, affecting the derived
+parameters. To mitigate this we construct a noise model where the
+residual column vector is taken to be additive in the log and is
+therefore multiplicative with respect to the mean model $\mu$.  That
+is,
+\begin{eqnarray}\label{eq:spectroscopicLFalt2} 
+\Delta &\equiv&
+\ln d - \ln \mu(\theta) - f(\alpha) \\
+\sigma_{n} & = & \sigma'_n / d
+\quad ,
+\end{eqnarray}
+where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
+$\sigma'_{n}$ are now the observational uncertainties. In this
+formulation the the mean model $\mu$ will be effectively multiplied by
+$\e ^{f(\alpha)}$ which, given our quadratic form for $f(\alpha)$, is
+equivalent to a large scale Gaussian ({\color{red} could we just add
+this to the covariance matrix with a single long quadratic ?}).  This
+logarithmic formulation requires that $d$ be everywhere positive, and
+the uncertainties will be truncated to only allow positive values and
+incorrect in detail.  However, at high signal to noise they should be
+approximately correct. {color{\red} As I understand it, additional
+`bad lines' in the mean model could be accounted for using narrow
+quadratics in the covariance matrix, though their interpretation would
+be hellish.}
 

### 2014-08-06 tex/figures/make_figures.py

@@ -5,6 +5,8 @@ from matplotlib import gridspec
 import triangle
 
 import diagnostics
+from diagnostics import model_comp as mcomp
+
 import sps_basis
 sps = sps_basis.StellarPopBasis(smooth_velocity=False)
 
@@ -23,6 +25,284 @@ pardict['poly_coeffs2']=r'$c_2$'
 pardict['spec_norm']=r'$c_0$'
 pardict['emission_disp']= r'$\sigma_e \, (\AA)$'
 pardict['phot_jitter']=r'$s_{{phot}}$'
+
+
+def comp_samples(thetas, model, inlog=True, photflag=0):
+    specvecs =[]
+    obs, _, marker = obsdict(model.obs, photflag)
+    wave, ospec, mask = obs['wavelength'], obs['spectrum'], obs['mask']
+    mwave, mospec = wave[mask], ospec[mask]
+    mounc = obs['unc'][mask]
+    if inlog and (photflag == 0):
+         mospec = np.exp(mospec)
+         mounc *= mospec
+
+    for theta in thetas:
+        mu, cal, delta, mask, wave = mcomp(theta, model, sps,
+                                           inlog=True, photflag=photflag)
+        
+        if inlog & (photflag == 0):
+            full_cal = np.exp(cal + delta)
+            mod = np.exp(mu + cal + delta)
+            mu = np.exp(mu)
+            cal = np.exp(cal)
+            
+        elif photflag == 0:
+            full_cal = cal + delta/mu
+            mod = (mu*cal + delta)
+
+        else:
+            mod = mu
+
+        specvecs += [ [mu, cal, delta, mod,
+                       mospec/mod, (mospec-mod) / mounc] ]
+            
+    return wave, mospec, mounc, specvecs
+
+
+def spec_figure(results, alpha=0.3, samples=[-1],
+                start=0, thin=1, inlog=True,
+                subplot_spec=None, xlim=None, **kwargs):
+    """
+    plot stars+dust+neb, then the calibration vector, then the GP
+    predicitions, then data and full model, then residuals
+    """
+    
+    fig = pl.figure(figsize = (10,6))
+    gs = gridspec.GridSpec(3, 2, height_ratios=[3,1,1], hspace=0, wspace=0.05)
+    
+    # Axis variables
+    ylabels = [r'$\mu$',r'$f(\alpha)$', r'$\tilde{\Delta}$ (GP)', #r'$\delta[f(\alpha)\mu]$ (GP)',
[…]

### 2014-08-06 tex/ms.tex
bugs in tex equations and better figure labeling

@@
 formulation the the mean model $\mu$ will be effectively multiplied by
-$\e ^{f(\alpha)}$ which, given our quadratic form for $f(\alpha)$, is
+$e ^{f(\alpha)}$ which, given our quadratic form for $f(\alpha)$, is
 equivalent to a large scale Gaussian ({\color{red} could we just add
@@
 incorrect in detail.  However, at high signal to noise they should be
-approximately correct. {color{\red} As I understand it, additional
+approximately correct. {\color{red} As I understand it, additional
 `bad lines' in the mean model could be accounted for using narrow

### 2014-08-06 tex/figures/make_figures.py

@@ -72,8 +72,8 @@ def spec_figure(results, alpha=0.3, samples=[-1],
     gs = gridspec.GridSpec(3, 2, height_ratios=[3,1,1], hspace=0, wspace=0.05)
     
     # Axis variables
-    ylabels = [r'$\mu$',r'$f(\alpha)$', r'$\tilde{\Delta}$ (GP)', #r'$\delta[f(\alpha)\mu]$ (GP)',
-               r'$\mu\,f(\alpha) \, e^{\tilde{\Delta}}$','o/m', r'(o-m)/$\sigma$']
+    ylabels = [r'$\mu$',r'$e^{f(\alpha)}$', r'$\tilde{\Delta}$ (GP)', #r'$\delta[f(\alpha)\mu]$ (GP)',
+               r'$\mu \, e^{f(\alpha) + \tilde{\Delta}}$','o/m', r'$\chi$']
     color = ['blue', 'green', 'red', 'magenta', 'orange','orange']
     row = [0,1,2,0,1,2]
     col = [0,0,0,1,1,1]
@@ -163,7 +163,7 @@ def one_specregion_figure(wave, obs, specs, reg,
     pl.setp(sfig.get_xticklabels(), visible = False)
 
     rfig = pl.Subplot(fig, gs[1,0])
-    rfig.set_ylabel(r'(o-m)$/\sigma$')
+    rfig.set_ylabel(r'$\chi$')
     rfig.set_xlabel(r'$\lambda (\AA)$')
     inreg = (wave > reg[0]) & (wave < reg[1])
     print(inreg.sum())
@@ -189,7 +189,7 @@ def phot_figure(results, alpha=0.3, samples = [-1],
     gs = gridspec.GridSpec(2,1, height_ratios=[3,1])
     gs.update(hspace=0)
     phot, res = pl.Subplot(fig, gs[0]), pl.Subplot(fig, gs[1])
-    res.set_ylabel( r'(obs-model)/$\sigma$')
+    res.set_ylabel( r'$\chi$')
     phot.set_ylabel('maggies')
     
     # posterior draws
@@ -365,6 +365,44 @@ def one_data_figure_sep(obs, fig, subplot_spec=None, **kwargs):
     return fig, gs
 
 
+def gp_figure(result, start=0, thin=1,
+              inlog=True, samples=[-1]):
+    fig = pl.figure(figsize = (10,6))
[…]

### 2014-08-06 tex/ms.tex
better wording

@@
 lines) can be artificially
-diluted or enhanced, affecting the derived parameters. To mitigate this we construct a
+diluted or enhanced, affecting the inferred physical parameters. To mitigate this we construct a
 model where the residual column vector is taken to be the residual
@@
 $\mu$, sharp spectral features in the mean model (such as absorption
-lines) can be artificially diluted or enhanced, affecting the derived
-parameters. To mitigate this we construct a noise model where the
+lines) can be artificially diluted or enhanced, affecting the inferred
+physical parameters. To mitigate this we construct a noise model where the
 residual column vector is taken to be additive in the log and is

### 2014-08-06 tex/figures/make_figures.py

@@ -434,8 +434,9 @@ if __name__ == '__main__':
         sample = [int(s * ns) for s in samples]
 
         gfig = gp_figure(result, samples=sample, inlog=inlog)
+        gfig.axes[0].set_yscale('log')
         gfig.savefig('gp_figure.png')
-        sys.exit()
+        
         
         sfig = spec_figure(result, samples=sample,
                         linewidth = 0.5, xlim = (3650, 7300),
@@ -444,6 +445,7 @@ if __name__ == '__main__':
         sfig.suptitle(name[i])
         sfig.savefig('sfig_'+ of + figext)
         pl.close(sfig)
+        sys.exit()
         
         pfig = phot_figure(result, samples=sample)
         pfig.suptitle(name[i])

### 2014-08-07 tex/ms.tex
add lee 2011 (xray analysis) to ref list
better wording

@@
 formulation the the mean model $\mu$ will be effectively multiplied by
-$e ^{f(\alpha)}$ which, given our quadratic form for $f(\alpha)$, is
-equivalent to a large scale Gaussian ({\color{red} could we just add
+$e ^{f(\alpha)}$ ({\color{red} could we just add
 this to the covariance matrix with a single long quadratic ?}).  This
@@
 
+\bibitem[Lee et al.(2011)]{xray_calunc} Lee, H., Kashyap, V.~L., 
+van Dyk, D.~A., et al.\ 2011, \apj, 731, 126
+
 \bibitem[Marigo \& Girardi(2007)]{marigo07} 

### 2014-08-07 tex/ms.tex
update figures for multiplicative models, add zoom in figure and add discussion text

@@
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
+\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
 \caption{Spectra resulting from draws from the posterior parameter
@@
 \label{fig:inferred_spectrum}}
+\end{figure*}
+
+\begin{figure*}[h!]
+\includegraphics[width=\textwidth]{figures/zfig_b192-g242_225_cal.png}
+\caption{Zoom-in on selected regions of the observed spectrum, showing
+also draws from the posterior model for the spectra in these regions
+and residulas of these draws from the observations.
+\label{fig:zoom_spectrum}}
 \end{figure*}
@@
 Mg$b$ absorption appears stronger than the modeled
-absorption. {\color{blue} Should I show blowups of selected regions/lines?}
+absorption. {\color{blue} Should I show blowups of selected
+regions/lines?}
 
@@
 \begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_020_cal.png}
-\caption{Model SEDs.  Top: The model photometric SED resulting from draws from the posterior
-  parameter space conditioned ({\it cyan}) on the observed photometry
-  ({\it magenta})  and spectra.  Bottom: uncertainty normalized
-  residuals of the models from the observations. 
- . \label{fig:inferred_sed}}
+\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
+\caption{ Model SEDs.  Top: The model photometric SED resulting from
+draws from the posterior parameter space conditioned ({\it cyan}) on
+the observed photometry ({\it magenta}) and spectra.  Bottom:
+uncertainty normalized residuals of the models from the observations.
+\label{fig:inferred_sed}}
 \end{figure}
@@
 \begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
+\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
 \caption{ Marginalized and joint PDFs of subset of the physical
-  parameters $\theta$ inferred from the spectophotometrically
-  calibrated spectrum of \excluster. The blue lines indicate the
-  parameter values that resulted from the powell minimization. \label{fig:inferred_params}}
+parameters $\theta$ inferred from the spectophotometrically calibrated
+spectrum of \excluster. The blue lines indicate the parameter values
+that resulted from the powell minimization.
+\label{fig:inferred_params}}
 \end{figure}
@@
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
+\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
 \caption{Left: Samples of the effective multiplicative calibration
@@
 \excluster~ ({\it cyan}) compared to that obtained from ancillary
-  photometric data ({\it magenta}).  Right:  The same, but for the
-  uncalibrated data. 
+photometric data ({\it magenta}).  
+%Right: The same, but for the uncalibrated data.
  \label{fig:inferred_calib}}
@@
 applications this combination of spectroscopy and photometry reduces
-the need for spectrophotometric calibration.  Calibration information,
-if it exists, can be incorporated into informative priors on the
-calibration parameters of the model.
+the need for spectrophotometric calibration, such that the less
+expensive photometry is sufficient.  Additional calibration
+information, if it exists, can be incorporated into informative priors
+on the calibration parameters of the model, or inform the construction
+of the calibration model.
 
@@
 residuals from an intial sky-line subtraction), and uncertainties in
-wavelength calibration. {\color{blue} DISCUSS MORE COMPLICATED
-COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL CHECKING.}
+wavelength calibration. Furthermore, more complex physical models may
+be considered for the mean object model, for example including SFH
+parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
+COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
+CHECKING.}
 
@@
 about the observations (e.g. airmass, instrument temperature), to in
-turn infer the parameters of a generative model for the
-calibration. This generative model can then be used in the
-(probabilistic) calibration of objects where the spectra are difficult
-to model explicitly.
+turn infer the parameters of a generative model for the calibration
+\citep[e.g.][]{spectrophot}. This generative model can then be used in
+the (probabilistic) calibration of objects where the spectra are
+difficult to model explicitly.
 
@@
 care must be taken to avoid absorbing interesting model deficiencies
-into the calibration model.  Third, we have made the assumption that
-the spectroscopy and the photometry are sampling the same populations.
-In practice, differences between spectroscopic and photometric
-apertures often mean that the photometry and the spectroscopy are sampling
+into the calibration model. For example, in the model we have
+described, it is possible that broad shallow features (for example due
+to molecular bands or absorption line complexes) will be absorbed into
+the Gaussian process. Third, we have made the assumption that the
+spectroscopy and the photometry are sampling the same populations.  In
+practice, differences between spectroscopic and photometric apertures
+often mean that the photometry and the spectroscopy are sampling
 slightly different physical regions.  The correct response to this
@@
 we are constantly inverting largish matrices.
+
+Fundamentally, calibration involves observing a `known' or `truth'
+with an instrument, and using the observation to infer the effects of
+the instrument.  However, we do not have knowledge of a single truth
+for any object, only relative probabilities for what might be true.
+In this sense, one should never use a single point estimate of the
+calibration, the full distribution of the possible calibrations should
+be inferred from our probabilistic knowledge of the calibration object
+and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
+only distinction between 'calibration' objects and targets of interest
+is the complexity of the model for the object and the level of
+uncertainty in the calibration object spectrum.  If one is interested
+in inferring parameters of interest of spectral models of
+astrophysical objects, then there is no reason not to use those
+objects themselves as calibration objects.
 

### 2014-08-07 tex/ms.tex
comment out craqzy calibration text in discussion

@@
 
-Fundamentally, calibration involves observing a `known' or `truth'
-with an instrument, and using the observation to infer the effects of
-the instrument.  However, we do not have knowledge of a single truth
-for any object, only relative probabilities for what might be true.
-In this sense, one should never use a single point estimate of the
-calibration, the full distribution of the possible calibrations should
-be inferred from our probabilistic knowledge of the calibration object
-and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
-only distinction between 'calibration' objects and targets of interest
-is the complexity of the model for the object and the level of
-uncertainty in the calibration object spectrum.  If one is interested
-in inferring parameters of interest of spectral models of
-astrophysical objects, then there is no reason not to use those
-objects themselves as calibration objects.
+% Fundamentally, calibration involves observing a `known' or `truth'
+% with an instrument, and using the observation to infer the effects of
+% the instrument.  However, we do not have knowledge of a single truth
+% for any object, only relative probabilities for what might be true.
+% In this sense, one should never use a single point estimate of the
+% calibration, the full distribution of the possible calibrations should
+% be inferred from our probabilistic knowledge of the calibration object
+% and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
+% only distinction between 'calibration' objects and targets of interest
+% is the complexity of the model for the object and the level of
+% uncertainty in the calibration object spectrum.  If one is interested
+% in inferring parameters of interest of spectral models of
+% astrophysical objects, then there is no reason not to use those
+% objects themselves as calibration objects.
 

### 2014-08-07 tex/ms.tex
small wording changes in discussion

@@
 applications this combination of spectroscopy and photometry reduces
-the need for spectrophotometric calibration, such that the less
+the need for spectrophotometric calibration entirely, such that the less
 expensive photometry is sufficient.  Additional calibration
 information, if it exists, can be incorporated into informative priors
-on the calibration parameters of the model, or inform the construction
-of the calibration model.
+on the calibration parameters of the model, to inform the construction
+of the calibration model, or to approximately remove gross features
+that are difficult to model parameterically or as a sum of Gaussians.
 

### 2014-08-07 tex/ms.tex
add a Tests subsection with some things to do.  cleanup figure captions for new color scheme

@@
 for the Gaussian process.  Right: From top to bottom, the full model
-({\it cyan}) compared to the observed, calibrated spectrum ({\it
-magenta}), the ratio of the observed to the modeled spectrum, and the
+({\it magenta}) compared to the observed, calibrated spectrum ({\it
+grey}), the ratio of the observed to the modeled spectrum, and the
 difference between the observed spectrum and the modeled spectrum
@@
 
+\subsection{Tests}
+
 BDJ: Next, we infer the parameters of the spectrum of the same cluster
@@
 to show?
+
+BDJ: Then, we infer the parameters of the calibrated spectrum without
+including the noise model!  What changed, what did we get wrong
+without the noise model?
+
+BDJ: We should also test on fake data
 

### 2014-08-21 tex/ms.tex
remove old model equations from sec2, add a list of tests, comment out figures from the old model

@@
 log-likelihood function we are going to use for the photometric
-measurements ({\color{blue} BDJ: IS THIS TRUE?} {\color{red} DWH,
-Currently I'm not using a jitter term, but I can and will.  Update:
-having difficulty with a jitter term}) in what follows.  In this
-formulation, if $\theta$ are the parameters of interest, the jitter
-variance $s^2$ is a nuisance noise-model parameter.  The Gaussian
-Process will be a generalization of this modification.
+measurements ({\color{blue} BDJ: IS THIS TRUE?} {\color{red} Jitter
+will be added now with correct sign as I test increases in model
+complexity }) in what follows.  
+In this formulation, if $\theta$ are the parameters of interest, the
+jitter variance $s^2$ is a nuisance noise-model parameter.  The
+Gaussian Process will be a generalization of this modification.
 
@@
 \\
-\Delta &\equiv& d - f(\alpha)\ast\mu(\theta)
+\Delta &\equiv& \ln d - \ln \mu(\theta) - f(\alpha) 
 \\
-C_{nn'} &\equiv& [\sigma_n^2 + s^2]\,\delta_{nn'} + K_\alpha(\lambda_n - \lambda_{n'})
+C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
+K_\alpha(\lambda_n - \lambda_{n'})
+\\
+\hat{\sigma_n} & = &\sigma_n/d
 \quad ,
@@
 $K_\alpha$ is a kernel function,
+$\hat{\sigma}_n$ are the fractional uncertainties of the data,
 and each $\lambda_n$ is the wavelength of spectral pixel $n$.
@@
 pick up smaller-scale residuals away from \emph{that}.
+The residual column vector is defined in terms of the logarithmic
+difference between the data and the mean model $\mu$ since we are
+taking the calibration vector to be multiplicative with respect to
+the mean model $\mu$.
 This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
@@
 
-XXX Alternative XXX.
-Because the residual column vector $\Delta$ of equation
-\ref{eq:spectroscopicLF} is additive with respect to the mean model
-$\mu$, sharp spectral features in the mean model (such as absorption
-lines) can be artificially
-diluted or enhanced, affecting the inferred physical parameters. To mitigate this we construct a
-model where the residual column vector is taken to be the residual
-\emph{from the calibration vector $f(\alpha)$} and is multiplicative
-with respect to the mean model $\mu$.  That is,
-\begin{eqnarray}\label{eq:spectroscopicLFalt} \Delta &\equiv&
-\frac{d}{\mu(\theta)} - f(\alpha) \\
-\sigma_{n} & = & \sigma'_n / \mu(\theta)
-\quad ,
-\end{eqnarray}
-where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
-$\sigma'_{n}$ are now the observational uncertainties
-
-XXX Alternative 2 XXX.
-Because the residual column vector $\Delta$ of equation
-\ref{eq:spectroscopicLF} is additive with respect to the mean model
-$\mu$, sharp spectral features in the mean model (such as absorption
-lines) can be artificially diluted or enhanced, affecting the inferred
-physical parameters. To mitigate this we construct a noise model where the
-residual column vector is taken to be additive in the log and is
-therefore multiplicative with respect to the mean model $\mu$.  That
-is,
-\begin{eqnarray}\label{eq:spectroscopicLFalt2} 
-\Delta &\equiv&
-\ln d - \ln \mu(\theta) - f(\alpha) \\
-\sigma_{n} & = & \sigma'_n / d
-\quad ,
-\end{eqnarray}
-where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before, and
-$\sigma'_{n}$ are now the observational uncertainties. In this
-formulation the the mean model $\mu$ will be effectively multiplied by
-$e ^{f(\alpha)}$ ({\color{red} could we just add
-this to the covariance matrix with a single long quadratic ?}).  This
+In this formulation the the mean model $\mu$ will be effectively
+multiplied by $e ^{f(\alpha)}$ ({\color{red} could we just add this to
+the covariance matrix with a single long quadratic ?}).  This
 logarithmic formulation requires that $d$ be everywhere positive, and
 the uncertainties will be truncated to only allow positive values and
-incorrect in detail.  However, at high signal to noise they should be
-approximately correct. {\color{red} As I understand it, additional
-`bad lines' in the mean model could be accounted for using narrow
-quadratics in the covariance matrix, though their interpretation would
-be hellish.}
+are therefore incorrect in detail.  However, at high signal to noise
+the results should be unaffected. {\color{red} As I understand it,
+additional `bad lines' in the mean model could be accounted for using
+narrow quadratics in the covariance matrix, though their
+interpretation would be hellish. The best way is probably to explictly
+model them in the mean model}
 
@@
 \end{figure}
+
+\subsection{List of Tests}
+
+\begin{enumerate}
+
+\item We should test on fake data, with known squiggly
+  calibration applied, to demonstrate that we can infer the
+  calibration vector and the physical parameters with no bias.
+
+\item We infer the parameters of the spectrum of a real cluster that
+  has been photometrically calibrated.
+
+\item Next, we infer the parameters of the spectrum of the same
+cluster \emph{without} spectrophotometric calibration, to see if we
+infer physical parameters consistent with the calibrated case.  How
+many/which figures to show?
+
+\item  Then, we show select marginalized or joint PDFs for many
+clusters calibrated/uncalibrated, to assess consistency.  Or we just
+show comparisons of confidence intervals for the parameters of a
+number of clusters.
+
+\item We infer the parameters of the calibrated spectrum without
+including the noise model, or presumably the photometry (since
+reconciling photometry and spectroscopy is done by our noise model).
+What changed, what did we get wrong without the noise model?
+{\color{blue} Should we keep the $f(\alpha)$ and the photometry?  This
+just has the potential to show shortcomings in the spectrophotometric
+calibration calibration}
+
+\item Finally, we change the number of photometric bands and see what
+happens to the inferred parameters, using the full model.
+
+\end{enumerate}
 
@@
 Mg$b$ absorption appears stronger than the modeled
-absorption. {\color{blue} Should I show blowups of selected
-regions/lines?}
+absorption.
 
@@
 \begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
+%\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
 \caption{ Model SEDs.  Top: The model photometric SED resulting from
@@
 \begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
+%\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
 \caption{ Marginalized and joint PDFs of subset of the physical
@@
 
-For the calibration model, we obtain a vector $f(\alpha)$
-that is nearly linear in wavelength {\color{red} WHY IS IT NOT A
-CONSTANT?  Need longer burn-in?  Is this the same issue as the SED
-residuals?}.  The length scale of the Gaussian process is $\sim
-60$\AA.  It is possible to reconstruct the inferred total
-multiplicative calibration vector for each draw of the model
-parameters.  Rearranging equation \ref{eq:spectroscopicLF} yields
+It is possible to reconstruct the inferred total multiplicative
+calibration vector for each draw of the model parameters.  Rearranging
+equation \ref{eq:spectroscopicLF} yields
 \begin{eqnarray} 
-\frac{d}{\mu(\theta)} & = & f(\alpha) +
-\frac{\tilde{\Delta}}{\mu(\theta)}
+\frac{d}{\mu(\theta)} & = & exp(f(\alpha) + \tilde{\Delta})
 \quad ,
@@
 $\tilde{\Delta}$ is now the Gaussian process mean prediction for the
-residual between the data and the model. The inverse of this ratio is
-shown in the left panel of Figure \ref{fig:inferred_calib} as our
-inferred total multiplicative calibration function; if the
-spectrophotometric calibration were perfect and we had correctly
-inferred it, then we would expect this vector to be constant as a
-function of wavelength.
+logarithmic residual between the data and the model. The inverse of
+this ratio is shown in the left panel of Figure
+\ref{fig:inferred_calib} as our inferred total multiplicative
+calibration function; if the spectrophotometric calibration were
+perfect and we had correctly inferred it, then we would expect this
+vector to be constant as a function of wavelength.
 
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
+%\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
 \caption{Left: Samples of the effective multiplicative calibration
@@
 
-\subsection{Tests}
-
-BDJ: Next, we infer the parameters of the spectrum of the same cluster
-\emph{without} spectrophotometric calibration.  How many/which figures
-to show?
-
-BDJ: Then, we infer the parameters of the calibrated spectrum without
-including the noise model!  What changed, what did we get wrong
-without the noise model?
-
-BDJ: We should also test on fake data
-
-BDJ: Then, we show select marginalized or joint PDFs for each cluster
-calibrated/uncalibrated, to assess consistency.  Or we just show
-comparisons of confidence intervals.
-
 \begin{figure}[h!]
-\includegraphics[width =0.5\textwidth]{figures/B192_020_cratio.pdf}
+%\includegraphics[width =0.5\textwidth]{figures/B192_020_cratio.pdf}
 \caption{Money plot.  Show the difference between the parameters
@@
 the need for spectrophotometric calibration entirely, such that the less
-expensive photometry is sufficient.  Additional calibration
+expensive photometric calibration is sufficient.  Additional calibration
 information, if it exists, can be incorporated into informative priors
-on the calibration parameters of the model, to inform the construction
-of the calibration model, or to approximately remove gross features
+on the calibration parameters of the model, inform the construction
+of the calibration model, or approximately remove gross features
 that are difficult to model parameterically or as a sum of Gaussians.
+
+{\color{blue} BDJ words about the gains that might be made by
+including photometry over a large range in wavelngth with spectroscopy
+over relatively small ranges.}
 
@@
 
-% Fundamentally, calibration involves observing a `known' or `truth'
-% with an instrument, and using the observation to infer the effects of
-% the instrument.  However, we do not have knowledge of a single truth
-% for any object, only relative probabilities for what might be true.
-% In this sense, one should never use a single point estimate of the
-% calibration, the full distribution of the possible calibrations should
-% be inferred from our probabilistic knowledge of the calibration object
-% and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
-% only distinction between 'calibration' objects and targets of interest
-% is the complexity of the model for the object and the level of
-% uncertainty in the calibration object spectrum.  If one is interested
-% in inferring parameters of interest of spectral models of
-% astrophysical objects, then there is no reason not to use those
-% objects themselves as calibration objects.
+{\color{blue} BDJ - This paragraph is probably too calibration
+focused. We want to focus more on spec + phot combinations.  At least,
+this paragraph should not be in the discussion section.}
+Fundamentally, calibration involves observing a `known' or `truth'
+with an instrument, and using the observation to infer the effects of
+the instrument.  However, we do not have knowledge of a single truth
+for any object, only relative probabilities for what might be true.
+In this sense, one should never use a single point estimate of the
+calibration, the full distribution of the possible calibrations should
+be inferred from our probabilistic knowledge of the calibration object
+and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
+only distinction between 'calibration' objects and targets of interest
+is the complexity of the model for the object and the level of
+uncertainty in the calibration object spectrum.  If one is interested
+in inferring parameters of interest of spectral models of
+astrophysical objects, then there is no reason not to use those
+objects themselves as calibration objects.
 

### 2014-08-31 tex/figures/make_figures.py
figure for new model including gp_length

@@ -166,7 +166,7 @@ def one_specregion_figure(wave, obs, specs, reg,
     rfig.set_ylabel(r'$\chi$')
     rfig.set_xlabel(r'$\lambda (\AA)$')
     inreg = (wave > reg[0]) & (wave < reg[1])
-    print(inreg.sum())
+    #print(inreg.sum())
 
     for s in specs:
         sfig.plot(wave[inreg], s[3][inreg], alpha=0.3, color = 'magenta')
@@ -198,7 +198,7 @@ def phot_figure(results, alpha=0.3, samples = [-1],
                                   flatchain.shape[2])
     thetas = [flatchain[s,:] for s in samples]
     mwave, mospec, mounc, specvecs = comp_samples(thetas, results['model'], photflag=1)
-    print(mwave, mospec)
+    #print(mwave, mospec)
     for vecs in specvecs:
         vv = vecs[0], vecs[-1]
         [ax.plot(mwave, v, color='magenta', alpha=alpha, marker='o', **kwargs)
@@ -413,13 +413,16 @@ if __name__ == '__main__':
     samples = np.random.uniform(0, 1, size=nsample)
     showpars_phys = ['mass', 'tage', 'zmet', 'dust2', 'sigma_smooth']
     showpars_cal = ['dust2', 'spec_norm','poly_coeffs1', 'poly_coeffs2', 'gp_length', 'gp_amplitude', 'gp_jitter']
-    zoom_regions = [[3920,4150.], [6500, 6600.], [5850, 5950], [5000, 5400]]
+    zoom_regions = [[3750,4100.], [6500, 6600.], [5850, 5950], [5000, 5400]]
     
     results = []
     rdir = '/Users/bjohnson/Projects/cetus/results/'
     #res = [rdir+'b192-g242.020.cal_1405648278.sampler01',
     #       rdir+'b192-g242.020.nocal_1405677518.sampler01']
-    res = [rdir+'b192-g242.225.cal_1407376313.sampler01']
+    #res = [rdir+'b192-g242.225.cal_1407376313.sampler01']
+    #res = [rdir+'b192-g242.225.cal_1407608570.sampler01']
+    #res = [rdir+'b192-g242.225.cal_1409443437.sampler01']
+    res = [rdir+'b192-g242.225.cal_1409477803.sampler01']
     inlog = True
 
     name = ['B192 cal.', 'B192 no cal.']

### 2014-09-03 tex/ms.tex
put relevant figures back
figure for new model including gp_length
fixing for issue #6

@@
 
+We take the calibration-vector that modifies the mean model to produce
+the observed spectrum as multiplicative with respect to the mean
+model.  In this case we define the residual of the data from the model
+in terms of the logarithmic differences.  This logarithmic formulation
+requires that $d$ be everywhere positive, and distorts the
+uncertainties, especially at low S/N ratio.  The advantages of
+defining the residual in this way are that the model remains linear
+(and therefore fast) and the calibration vector is forced to be
+positive everywhere.  However, at high signal to noise the distortion
+of the uncertainties will be minimal.
+
 The calibration-vector and Gaussian-Process modified log-likelihood is
@@
 $f(\alpha)$ is a calibration column vector,
-the ``$\ast$'' operator is the pixel-wise multiplication operator,
 $C$ is the Gaussian Process covariance matrix,
 made up of $N^2$ values $C_{nn'}$,
-$K_\alpha$ is a kernel function,
+$K_\alpha$ is a kernel function that sets the wavelengths scale and
+amplitude of the residual calibration issues,
 $\hat{\sigma}_n$ are the fractional uncertainties of the data,
@@
 taking the calibration vector to be multiplicative with respect to
-the mean model $\mu$.
+the mean model $\mu$. In this formulation the the mean model $\mu$ will be effectively
+multiplied by $e ^{f(\alpha)}$ 
 This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
 are going to use for the spectroscopic data in what follows.
-
-In this formulation the the mean model $\mu$ will be effectively
-multiplied by $e ^{f(\alpha)}$ ({\color{red} could we just add this to
-the covariance matrix with a single long quadratic ?}).  This
-logarithmic formulation requires that $d$ be everywhere positive, and
-the uncertainties will be truncated to only allow positive values and
-are therefore incorrect in detail.  However, at high signal to noise
-the results should be unaffected. {\color{red} As I understand it,
-additional `bad lines' in the mean model could be accounted for using
-narrow quadratics in the covariance matrix, though their
-interpretation would be hellish. The best way is probably to explictly
-model them in the mean model}
 
@@
   calibration applied, to demonstrate that we can infer the
-  calibration vector and the physical parameters with no bias.
+  calibration vector and the physical parameters with no bias.  We
+  should use the squiggly calibration derived from one of Nelson's
+  calibrated/uncalibrated spectra.  We should also do this for
+  differnt S/N to find where the logarithmic residual formulation
+  breaks down.
 
 \item We infer the parameters of the spectrum of a real cluster that
-  has been photometrically calibrated.
-
-\item Next, we infer the parameters of the spectrum of the same
-cluster \emph{without} spectrophotometric calibration, to see if we
-infer physical parameters consistent with the calibrated case.  How
-many/which figures to show?
+has been photometrically calibrated. Then, we infer the parameters of
+the spectrum of the same cluster \emph{without} spectrophotometric
+calibration, to see if we infer physical parameters consistent with
+the calibrated case.  How many/which figures to show?
 
@@
 show comparisons of confidence intervals for the parameters of a
-number of clusters.
+number of clusters, calibrated/uncalibrated.
 
@@
 just has the potential to show shortcomings in the spectrophotometric
-calibration calibration}
+calibration}
 
@@
 \mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
-\sum_{\ell=0}^{N_\ell} S_\ell \\
-S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
+\sum_{\ell=0}^{N_\ell} S_\ell(\lambda) \\
+S_\ell (\lambda) & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
  \lambda_\ell)^2}{2\sigma_e^2})\\
@@
 \begin{figure}[h!]
-%\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
+\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
 \caption{ Model SEDs.  Top: The model photometric SED resulting from
@@
 \begin{figure}[h!]
-%\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
+\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
 \caption{ Marginalized and joint PDFs of subset of the physical
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
+\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
 \caption{Left: Samples of the effective multiplicative calibration
@@
 COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
-CHECKING.}
+CHECKING. As I understand it, additional `bad lines' in the mean model
+could be accounted for using narrow quadratics in the covariance
+matrix, though their interpretation would be hellish. The best way is
+probably to explictly model them in the mean model}
 
@@
 information about the spatial variation of physical properties.
-Finally, this method is computationally intensive and expensive, since
-we are constantly inverting largish matrices.
+Fourth, the method will break down at very low S/N due to the
+logarithmic formulation of the residual in
+equation~(\ref{eq:spectroscopicLF}).  Finally, this method is
+computationally intensive and expensive, since we are constantly
+inverting largish matrices.
 
@@
 Fundamentally, calibration involves observing a `known' or `truth'
-with an instrument, and using the observation to infer the effects of
+with an instrument, and using that observation to infer the effects of
 the instrument.  However, we do not have knowledge of a single truth
@@
 be inferred from our probabilistic knowledge of the calibration object
-and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
+and forward propogated \citep[e.g.][]{lee11}. Once this is done, the
 only distinction between 'calibration' objects and targets of interest
@@
 in inferring parameters of interest of spectral models of
-astrophysical objects, then there is no reason not to use those
+astrophysical objects, then there is often no reason not to use those
 objects themselves as calibration objects.

### 2014-09-04 tex/ms.tex
fixing for issue #6

@@
 made up of $N^2$ values $C_{nn'}$,
-$K_\alpha$ is a kernel function that sets the wavelengths scale and
+$K_\alpha$ is a kernel function that sets the wavelength scale and
 amplitude of the residual calibration issues,

### 2015-04-17 tex/ms.tex
tex updates for GGC data

@@
 \bibliographystyle{apj}
-\input{vc}
+%\input{vc}
 
@@
 interest.
+This amounts to propogating the uncertainties in the
+spectrophotometric calibration (or alternatively in the continuum
+normalization).
 In what follows, we provide an example of this kind of
@@
 \begin{eqnarray}\label{eq:photometricLF}
-\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{[\sigma_n^2 + s^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
+\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N
+                             \left[\frac{[d_n -
+                             \mu_n(\theta)]^2}{[\sigma_n^2 + (s\, \mu_n(\theta))^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
 \quad .
@@
 log-likelihood function we are going to use for the photometric
-measurements ({\color{blue} BDJ: IS THIS TRUE?} {\color{red} Jitter
-will be added now with correct sign as I test increases in model
-complexity }) in what follows.  
+measurements in what follows.  
 In this formulation, if $\theta$ are the parameters of interest, the
-jitter variance $s^2$ is a nuisance noise-model parameter.  The
+jitter variance $s^2$ is a nuisance noise-model parameter representing
+additonal fractional uncertainty in the flux.  The
 Gaussian Process will be a generalization of this modification.
@@
 (and therefore fast) and the calibration vector is forced to be
-positive everywhere.  However, at high signal to noise the distortion
+positive everywhere.  Additionally, at high signal to noise the distortion
 of the uncertainties will be minimal.
@@
 
+XXX Alternative XXX
+To avoid making the logarithmic transform described above, which
+distorts the errors, we can formulate the problem in a different way,
+modifying Equation \label{eq:spectroscopicLF} above as 
+\begin{eqnarray}\label{eq:spectroscopicLF_v2}
+\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
+\\
+\Delta &\equiv& d - \mu(\theta) * f(\alpha) 
+\\
+C_{nn'} &\equiv& [\sigma_n^2 + (s * \mu)^2]\,\delta_{nn'} +
+\transpose{\mu} \, K_\alpha(\lambda_n - \lambda_{n'}) \, \mu
+\quad ,
+\end{eqnarray}
+where the multiplication of $s$ and $K_\alpha$ by $\mu$ in the
+construction of $C_{nn'}$ means that they are defined in
+\emph{fractional} terms, and the uncertainties remain Gaussian in
+linear flux space.  It remains to be seen whether this actually works.
+
 \section{Experiments and Results}
@@
 We will apply the methodology for spectrophotometric calibration
-described above to \emph{actual, real} optical spectra of a stellar
-clusters in M31.  Spectra of star clusters provide a good test case,
+described above to both \emph{mock} and \emph{real} optical spectra of
+Galactic globular clusters.  Spectra of globular clusters provide a good test case,
 as they are less complex than galaxy spectra (for which it is
@@
 trivial. In this way the key features of the calibration model and
-methodology are not obscured.
+methodology are not obscured.  Additionally, information
+about the physical parameters of the cluster is available from
+resolved stellar CMDs, providing an important check on our inference methodology
+and especially our population synthesis models.
+
+The separate treatment of mock and real data allows us to address two
+separate issues.  The inference from mock data (with a realistic
+calibration vector applied) provides a test of the methodology and the
+effect of calibration uncertainties on the inferred parameters in the
+case of a perfect mean model $mu(\theta)$.  The inference from real
+data tests a combination of our methodology and the ability of the
+population synthesis models to recover parameters inferred from
+resolved star CMDs (i.e. some estimate of ground truth)
 
@@
 $\theta$ from a spectrum both \emph{before} and \emph{after} it has
-been spectrophotometrically calibrated using typical techniques and
+been spectrophotometrically calibrated using and
 ancillary spectrophotometric calibration data.
@@
 \begin{figure}[h!]
-\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{The calibrated (left) and uncalibrated (right) spectrum for
-\excluster, along with the uncertainties (bottom panel). The spectra
-have been renormalized to avoid floating point errors. {\color{blue}
-SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.}\label{fig:data}}
+%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
+\caption{The calibrated spectrum for \excluster, along with the
+uncertainties (bottom panel).The right panel shows the
+spectrophotometric calibration vector determined by
+\citet{schiavon05}. \label{fig:data}}
 \end{figure}
@@
 
-\item We should test on fake data, with known squiggly
-  calibration applied, to demonstrate that we can infer the
-  calibration vector and the physical parameters with no bias.  We
-  should use the squiggly calibration derived from one of Nelson's
-  calibrated/uncalibrated spectra.  We should also do this for
-  differnt S/N to find where the logarithmic residual formulation
-  breaks down.
+\item Mock perfectly calibrated data: inference using spectroscopy and one
+  photometric band, with both full calibration model and assuming no
+  calibration uncertainty.
 
-\item We infer the parameters of the spectrum of a real cluster that
-has been photometrically calibrated. Then, we infer the parameters of
-the spectrum of the same cluster \emph{without} spectrophotometric
-calibration, to see if we infer physical parameters consistent with
-the calibrated case.  How many/which figures to show?
+\item Mock uncalibrated data:  inference using spectroscopy and one
+  photometric band, with full calibration model
 
-\item  Then, we show select marginalized or joint PDFs for many
-clusters calibrated/uncalibrated, to assess consistency.  Or we just
-show comparisons of confidence intervals for the parameters of a
-number of clusters, calibrated/uncalibrated.
+\item Mock data: inference using photometry only, full spectroscopic model
 
-\item We infer the parameters of the calibrated spectrum without
-including the noise model, or presumably the photometry (since
-reconciling photometry and spectroscopy is done by our noise model).
-What changed, what did we get wrong without the noise model?
-{\color{blue} Should we keep the $f(\alpha)$ and the photometry?  This
-just has the potential to show shortcomings in the spectrophotometric
-calibration}
+\item Mock uncalibrated data: inference using spectroscopy and all
+  photometry, full calibration model.
 
-\item Finally, we change the number of photometric bands and see what
-happens to the inferred parameters, using the full model.
+\item Mock perfectly calibrated data: inference using spectroscopy and all
+  photometry, with both full calibration model and assuming no
+  calibration uncertainty.
+
+\item Real calibrated spectrum:   Inference using spectroscopy and all
+  photometry, with full calibration model.
+
+\item Real uncalibrated spectrum:   Inference using spectroscopy and all
+  photometry, with full calibration model.
+
+\item Compare the physical parameters inferred from from the real
+  calibrated and uncalibrated spectrum with each other and with CMD
+  based parameters.
 
@@
 The data we use to test our method consist of optical spectroscopy of
-XX stellar clusters in M31 for which YY-band HST photometric data
-exist.  The optical spectra were obtained using the fiber-fed
-Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
-of the spectra is $3700-9100$\AA. The instrumental resolution is
-$\sim 5$\AA~ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
-calibration happened. Sky subtraction happened.} The data were
-approximately spectrophotometrically calibrated using an average
-calibration vector for the night constructed from {\color{blue} MORE
-HERE. Discuss S/N, sky subtraction.}
+of galactic globular clusters from \citet{schiavon05} for which
+optical and NIR photometry are availbale. The optical spectra were
+obtained by drift-scanning a long-slit spectrograph across the
+cluster.  The wavelength range of the spectra is $3500-6500$\AA. The
+instrumental resolution is $\sim 3.1$\AA~ at $\sim 4500\AA$ and varies
+with wavelength.  These spectra have been placed on the rest-frame,
+though in what follows we will model the effect of redshift
+uncertainties on the data.
 
-An example spectrum, both after and before spectrophotometric
-calibration, is shown in Figure \ref{fig:data}.  When fitting the
-spectra we mask the region around the bright OI5577 sky line, and we
-fit only to the spectrum with $3750 < \lambda < 7200$\AA~ to avoid the low
-S/N edges and, on the red side, imperfect sky line subtraction in a
-region of the spectrum that has a paucity of informative spectral
-lines. Furthermore, the MILES spectral library (see
-\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
-{\color{red} Specify/Justify order of calibration polynomial here?}.
+An example spectrum (and the inferred spectrophotometric calibration
+vector) is shown in Figure \ref{fig:data}.  As stated by
+\citet{schiavon05}, the spectrophotometric calibration of these data are
+only approximate.  When fitting the spectra we mask the region around
+the bright OI5577\AA~ sky line, and we fit only to the spectrum with $3550\AA
+< \lambda < 6500$\AA~ which are covered by the MILES spectral library
+(see \S\ref{sec:cluster_model}).  Absorption lines of the interstellar
+medium (ISM) can significantly affect the spectrum, so we
+additionally mask the Calcium H and K lines and the NaD doublet.
 
-{\color{blue} DRW words about photometry}
+Words about photometry
 
@@
 \end{table}
+
+\subsection{Mock Data}
+Our mock data are designed to mimic the actual data as much as
+possible.  Mock spectra and photometry are generated from the model
+below for a given set of parameters $\theta^\prime$.  We then convolve
+the spectrum with an instrumenal LSF, interpolate onto the observed
+wavelength scale and add noise according to the
+SNR of the real data.  For the photometry we assume a SNR of 10.  We
+also mask the mock spectra at the location of significant sky lines
+and ISM lines.
+
+The mock spectrum is shown in Figure \ref{fig: mock spectrum}.  We
+will refer to this spectrum as the \emph{perfectly calibrated}
+mock spectrum.  We also produce a mock spectrum by dividing this
+perfectly calibrated spectrum by the spectrophotometric calibration vector
+taken from the real data
+\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}, which we refer to as
+the \emph{uncalibrated} mock spectrum.
 
@@
 and redshift $z$.
-The observed frame wavelengths $\lambda_o$ are related to the restframe
-wavelengths $\lambda$ in the usual way.
+The shape of the dust attenuation curve is given by $k_\lambda \equiv
+\tau_\lambda/\tau_V$.  
+The observed frame wavelengths $\lambda_o$ are related to the
+restframe wavelengths $\lambda$ in the usual way.
 
@@
 $\beta$ to be fixed for the purposes of this exercise, with no loss of
-generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also
-fix the shape of the attenuation curve, $k_\lambda \equiv
-\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
-$R_V=3.1$ and assume that $d_L$ is known to high precision from
-independent methods and can therefore be treated as fixed.  In
-practice, $d_L$ is completely degenerate with $m_*$. We calculate
-$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
-code \citep[FSPS][]{fsps}.  We use the Padova 2007 isochrones
-\citep{girardi00, bertilli94, marigo07} and the MILES stellar spectral
-library \citep{miles_I, miles_II, miles_III}.
-
-The model spectra $F_{\theta^\prime}$ are smoothed by convolution
-with a Gaussian in wavelength space (in this case to model the MMT
-line-spread function) and are interpolated to the wavelength points of
-the of the observed spectrum while taking into account the
-redshift. The instrumental resolution is given by the parameter
-$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
-(MILES), what to do in situations where instrumental resolution is
-higher, lower or comparable (ouch) to intrinsic velocity broadening.}
+generality but significant savings in computational time.  We will
+also fix the shape of the attenuation curve, $k_\lambda $, to the
+Milky way average of \citet{CCM89} with $R_V=3.1$ and assume that
+$d_L$ is known to high precision from independent methods and can
+therefore be treated as fixed.  In practice, $d_L$ is prefectly
+degenerate with $m_*$. We calculate $S(\lambda, t, Z)$ using the
+Flexible Stellar Population Synthesis code \citep[FSPS][]{fsps}.  We
+use the Padova 2007 isochrones \citep{girardi00, bertilli94, marigo07}
+and the MILES stellar spectral library \citep{miles_I, miles_II,
+miles_III}.
 
@@
 
-The final mean model is then given by 
+The model spectra $F_{\theta^\prime}$ are smoothed by convolution with
+the line-spread function of the spectrograph and are interpolated to
+the wavelength points of the of the observed spectrum while taking
+into account the redshift. For computational simplicity we assume that
+the internal velocity dispersion of the cluster is negligible compared
+to the instrumental broadening, though in principle it can and should
+also be modeled. he instrumental resolution is given by the parameter
+$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
+(MILES), what to do in situations where instrumental resolution is
+higher, lower or comparable (ouch) to intrinsic velocity broadening.}
+
+The final mean model is then given by the convolution in wavelength
 \begin{eqnarray}\label{eq:MeanModel} 
-\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
+\mu(\theta) &  = & (LSF(\sigma_{inst}) \otimes F(\theta^\prime))(\lambda) +
 \sum_{\ell=0}^{N_\ell} S_\ell(\lambda) \\
 S_\ell (\lambda) & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
- \lambda_\ell)^2}{2\sigma_e^2})\\
-\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
-  \sigma_e \right]
+\lambda_\ell)^2}{2\sigma_e^2}) \\
+\theta & \equiv & \left[ \{\theta^\prime\}, \sigma_{inst}, \{A_\ell\}_{\ell=0}^{N_l},
+  \sigma_e \right] \\
 \quad ,
 \end{eqnarray}
-where $G_\sigma$ represents a Gaussian of unit area 
-and standard deviation $\sigma$, 
+where $LSF(\sigma_{inst})$ represents the linespread function
+parameterized by $\sigma_{inst}$, 
 $\otimes$ indicates convolution, 
 and the full parameter set $\theta$ now includes
-the instrumental wavelength broadening $\sigma$ 
+the instrumental broadening $\sigma_{inst}$ 
 and the dispersion $\sigma_e$ and
@@
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
 \caption{Spectra resulting from draws from the posterior parameter
@@
 \label{fig:inferred_spectrum}}
-\end{figure*}
-
-\begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/zfig_b192-g242_225_cal.png}
-\caption{Zoom-in on selected regions of the observed spectrum, showing
-also draws from the posterior model for the spectra in these regions
-and residulas of these draws from the observations.
-\label{fig:zoom_spectrum}}
 \end{figure*}
@@
 
-\begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
-\caption{ Model SEDs.  Top: The model photometric SED resulting from
-draws from the posterior parameter space conditioned ({\it cyan}) on
-the observed photometry ({\it magenta}) and spectra.  Bottom:
-uncertainty normalized residuals of the models from the observations.
-\label{fig:inferred_sed}}
-\end{figure}
-
-\begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
-\caption{ Marginalized and joint PDFs of subset of the physical
-parameters $\theta$ inferred from the spectophotometrically calibrated
-spectrum of \excluster. The blue lines indicate the parameter values
-that resulted from the powell minimization.
-\label{fig:inferred_params}}
-\end{figure}
-
-The physical model parameters that we infer indicate that \excluster~
-has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
-extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
-check that this is current mass, not initial mass}.  We find a spectral
-broadening of $\sim 1.75$\AA~ (4.1\AA~ FWHM), which when combined in
-quadrature with the intrinsic resolution of the MILES library, 2.5\AA~
-FWHM \citep{beifiori11}, reproduces the typical line-spread function
-of the MMT Hectospec instrument, $\sim 5$\AA~ \citep{fabricant13}.
-We obtain strong constraints on the systemic velocity.
-
 It is possible to reconstruct the inferred total multiplicative
@@
 \begin{eqnarray} 
-\frac{d}{\mu(\theta)} & = & exp(f(\alpha) + \tilde{\Delta})
+\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
 \quad ,
@@
 
+\begin{figure}[h!]
+%\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
+\caption{ Model SEDs.  Top: The model photometric SED resulting from
+draws from the posterior parameter space conditioned ({\it cyan}) on
+the observed photometry ({\it magenta}) and spectra.  Bottom:
+uncertainty normalized residuals of the models from the observations.
+\label{fig:inferred_sed}}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
+\caption{ Marginalized and joint PDFs of subset of the physical
+parameters $\theta$ inferred from the spectophotometrically calibrated
+spectrum of \excluster. The blue lines indicate the parameter values
+that resulted from the powell minimization.
+\label{fig:inferred_params}}
+\end{figure}
+
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
+%\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
 \caption{Left: Samples of the effective multiplicative calibration
@@
 photometric data ({\it magenta}).  
-%Right: The same, but for the uncalibrated data.
+Right: The same, but for the uncalibrated data.
  \label{fig:inferred_calib}}
@@
 
-We have demonstrated, using a sample of stellar clusters in M31, that
-we can combine photometric and spectroscopic data in a principled way
-to infer physical properties.  We do not resort to an arbitrary
-down-weighting or up-weighting of certain data. Instead, we explicitly
-model our uncertain knowledge of the spectral calibration and infer
-this calibration jointly with the physical properties. For a number of
-applications this combination of spectroscopy and photometry reduces
-the need for spectrophotometric calibration entirely, such that the less
-expensive photometric calibration is sufficient.  Additional calibration
-information, if it exists, can be incorporated into informative priors
-on the calibration parameters of the model, inform the construction
-of the calibration model, or approximately remove gross features
-that are difficult to model parameterically or as a sum of Gaussians.
+We have demonstrated, using using both mock and real spectra of
+galactic stellar clusters, that we can combine photometric and
+spectroscopic data in a principled way to infer physical properties.
+We do not resort to an arbitrary down-weighting or up-weighting of
+certain data. Instead, we explicitly model our uncertain knowledge of
+the spectral calibration and infer this calibration jointly with the
+physical properties. For a number of applications this combination of
+spectroscopy and photometry reduces the need for spectrophotometric
+calibration entirely, such that the less expensive photometric
+calibration is sufficient.  Additional calibration information, if it
+exists, can be incorporated into informative priors on the calibration
+parameters of the model, inform the construction of the calibration
+model, or approximately remove gross features that are difficult to
+model parameterically or via a Gaussian Process.
 
 {\color{blue} BDJ words about the gains that might be made by
-including photometry over a large range in wavelngth with spectroscopy
+including photometry over a large range in wavelength with spectroscopy
 over relatively small ranges.}
+
+{\color{blue} BDJ BDJ discuss the relation of this technique to the typical use of
+continuum normalization when fitting spectroscopy.}
 
@@
 COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
-CHECKING. As I understand it, additional `bad lines' in the mean model
-could be accounted for using narrow quadratics in the covariance
-matrix, though their interpretation would be hellish. The best way is
-probably to explictly model them in the mean model}
+CHECKING.}
 
@@
   from \url{http://github.com/bd-j/bsfh/}.
-This version of the paper was generated
-  from a git repository available at \url{http://github.com/bd-j/speccal/}
-  with git hash \texttt{\githash\,(\gitdate)}.
+%This version of the paper was generated
+%  from a git repository available at \url{http://github.com/bd-j/speccal/}
+%  with git hash \texttt{\githash\,(\gitdate)}.
 
@@
 \begin{thebibliography}{}\raggedright
+
+\bibitem[Becker et al.(2015)]{becker15} Becker, J.~C., Johnson, 
+J.~A., Vanderburg, A., \& Morton, T.~D.\ 2015, arXiv:1503.03874
 
@@
 
-\bibitem[Fabricant \etal(2013)]{fabricant13} 
-Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362
+%\bibitem[Fabricant \etal(2013)]{fabricant13} 
+%Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362
 
@@
 
+\bibitem[Schiavon et al.(2005)]{schiavon05} Schiavon, R.~P., Rose, 
+J.~A., Courteau, S., \& MacArthur, L.~A.\ 2005, \apjs, 160, 163
+
+\bibitem[Sch{\"o}nrich 
+\& Bergemann(2014)]{schonrich14} Sch{\"o}nrich, R., \& Bergemann, M.\ 2014, \mnras, 443, 698
+
 \end{thebibliography}

### 2015-04-24 tex/ms.tex
title change and section reorg, some changes to the mock parameters

@@
 \title{Combining information from photometric and spectroscopic data:\\
-  Don't waste your time in spectrophotometric calibration!}
-\shorttitle{don't waste your time in calibration!}
+  propogating uncertainties in spectrophotometric calibration}
+\shorttitle{Combining Spectroscopy and Photometry}
 \author{
@@
 If you don't believe the reported data noise variances $\sigma_n^2$,
-it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
-This is a trivial modification of the chi-squared log-likelihood:
+it often makes sense to add in quadrature a ``jitter'' variance
+$s^2$.  For photometric data this ``jitter'' is often best described
+as a fractional error, $(s\mu(\theta))^2$, corresponding for example
+to an additional magnitude zero-point uncertainty.
+This is a simple modification of the chi-squared log-likelihood:
 \begin{eqnarray}\label{eq:photometricLF}
 \ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N
-                             \left[\frac{[d_n -
-                             \mu_n(\theta)]^2}{[\sigma_n^2 + (s\, \mu_n(\theta))^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
+                             \left[\frac{[d_n - \mu_n(\theta)]^2}
+                             {[\sigma_n^2 + (s\,\mu_n(\theta))^2]} + 
+                             \ln(2\pi\,[\sigma_n^2 + (s\,\mu(\theta))^2]) \right]
 \quad .
@@
 
-\section{Experiments and Results}
+\section{Data and Experiments}
 
@@
 
-The separate treatment of mock and real data allows us to address two
+This separate treatment of mock and real data allows us to address two
 separate issues.  The inference from mock data (with a realistic
@@
 population synthesis models to recover parameters inferred from
-resolved star CMDs (i.e. some estimate of ground truth)
+resolved star CMDs (i.e. some estimate of ground truth).
 
@@
 spectrophotometric calibration vector determined by
-\citet{schiavon05}. \label{fig:data}}
+\citet{schiavon05}. \label{fig:ggc_data}}
 \end{figure}
 
-\subsection{List of Tests}
+\subsection{List of Experiments}
 
@@
 
-\item Mock data: inference using photometry only, full spectroscopic model
+\item Mock data: inference using photometry only
 
@@
 
-\subsection{Test Data}
+\subsection{Real Data}
 
@@
 of galactic globular clusters from \citet{schiavon05} for which
-optical and NIR photometry are availbale. The optical spectra were
+optical and NIR photometry are available. The optical spectra were
 obtained by drift-scanning a long-slit spectrograph across the
@@
 An example spectrum (and the inferred spectrophotometric calibration
-vector) is shown in Figure \ref{fig:data}.  As stated by
+vector) is shown in Figure \ref{fig:ggc_data}.  As stated by
 \citet{schiavon05}, the spectrophotometric calibration of these data are
@@
 
-Words about photometry
+Words about photometry.
 
@@
 possible.  Mock spectra and photometry are generated from the model
-below for a given set of parameters $\theta^\prime$.  We then convolve
-the spectrum with an instrumenal LSF, interpolate onto the observed
-wavelength scale and add noise according to the
-SNR of the real data.  For the photometry we assume a SNR of 10.  We
-also mask the mock spectra at the location of significant sky lines
-and ISM lines.
+described in below (\S\ref{sec:cluster_model}, equation
+\ref{eq:MeanModel}) for a given set of parameters $\theta^\prime$.  We
+then convolve the spectrum with an instrumenal LSF, interpolate onto
+the observed wavelength scale and add noise according to the SNR of
+the real data.  For the photometry we assume a SNR of 10.  We also
+mask the mock spectra at the location of significant sky lines and ISM
+lines that are present in the real data.
 
-The mock spectrum is shown in Figure \ref{fig: mock spectrum}.  We
-will refer to this spectrum as the \emph{perfectly calibrated}
-mock spectrum.  We also produce a mock spectrum by dividing this
-perfectly calibrated spectrum by the spectrophotometric calibration vector
-taken from the real data
-\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}, which we refer to as
-the \emph{uncalibrated} mock spectrum.
+We will refer to these spectra as the \emph{perfectly calibrated} mock
+spectrum.  An example is shown in Figure \ref{fig: mock data}. We also
+produce mock spectra by dividing the perfectly calibrated spectra by
+the spectrophotometric calibration vector taken from the real data
+\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}.  We refer to these as
+the \emph{uncalibrated} mock spectra.
+
+\begin{figure}[h!]
+%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
+\caption{A mock spectrum for a star cluster with $10^5 M_\odot$ total
+  stellar mass, an age of  9 Gyr, solar
+  metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
+\end{figure}
 
 \subsection{Star Cluster Model}
+\label{sec:cluster_model}
 We model the stellar cluster as a single age SSP. The spectrum of a
@@
 $d_L$ is known to high precision from independent methods and can
-therefore be treated as fixed.  In practice, $d_L$ is prefectly
+therefore be treated as fixed.  In practice, $d_L$ is perfectly
 degenerate with $m_*$. We calculate $S(\lambda, t, Z)$ using the
@@
 to the instrumental broadening, though in principle it can and should
-also be modeled. he instrumental resolution is given by the parameter
+also be modeled. The instrumental resolution is given by the parameter
 $\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
@@
 instrument is available; or for the parameters of interest $\theta$,
-for example in the case that there is knowledge of the metallicity
+for example if there is knowledge of the metallicity
 distribution of the population from which a given cluster is drawn.
@@
 normalized by the uncertainty.
-\label{fig:inferred_spectrum}}
+\label{fig:speconly_calibrated}}
 \end{figure*}
 
-\subsection{Results}
+\section{Results}
 
+For each test we want to show
+\begin{itemize}
+
+\item Posterior parameter pdfs (and joint pdfs).
+
+\item Samples of the posterior prediction for the observations, and
+  residuals thereform.
+
+\item The calibration vector, and posterior samples of it.
+
+\item Posterior samples of the intrinsic spectrum
+\end{itemize}
+
+\subsection{Mock data}
+
+In Figure \ref{fig:speconly_calibrated} we show the result of our
+inference from the spectrum and a single photometric measurement (SDSS
+$g$) for a perfectly calibrated mock spectrum. To demonstrate the
+quality of the fit we show both the mock
+input spectrum and predictions of the observed spectra that result
+from several draws of the model parameters
+$[\theta, \alpha]$ from posterior distribution.  We also show samples
+of the inferred calibration vector,
+\begin{eqnarray} 
+\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
+\quad ,
+\end{eqnarray}
+where $\tilde{\Delta}$ is the Gaussian process mean prediction for the
+logarithmic residual between the data and the model.  For the
+perfectly calibrated spectrum the true calibration vector (shown in
+black) is one everywhere.  The spread of the inferred calibration
+vectors approximately indicates our uncertainty in the spectrophotometric
+calibration when no additional calibration information is available
+and only a single photometric point is available.
+
+Even in the case of a single photometric data point, several of the
+physical parameters are well-constrained and only minimally biased,
+e.g. age and metallicity.  These are the parameters that are
+constrained well by the spectrum itself and are not strongly sensitive
+to the overall shape of the spectral continuum.  Such parameters can
+be reasonably well recovered by fitting continuum normalized spectra,
+though hewre we have propogated the uncertainty in this normalization
+into the uncertainties on the physical parameters.
+
+On the other hand, the posterior PDF for the dust attenuation optical
+depth $A_v$ is extremely broad.
+
+The uncertainty on the total stellar mass incorporates both the
+uncertainty in the photometric flux and the uncertainty in the $g$-
+band mass-to-light ratio.
+
+In Figure \ref{fig:speconly_uncalibrated} we show the results of
+inference on an \emph{uncalibrated} mock spectrum.
+
+\subsection{Real Data: NGCXXX} 
 We first infer the parameters of interest $\theta$ for a calibrated
@@
 which the priors were conditioned, and residuals between the posterior
-models and the observed data.  The agreement is quite good, though
-some lines are not accurately predicted.  For example, the observed
-Mg$b$ absorption appears stronger than the modeled
-absorption.
+models and the observed data.
 
@@
 
-\subsection{Dependence on Photometric Data}
-In this section we examine how the constraints on physical (and
-calibration) parameters vary as a function of the number and type of
-photometric points available. {\color{red} BDJ DO THIS TEST.}
-
 \section{Discussion}
@@
 
-{\color{blue} BDJ BDJ discuss the relation of this technique to the typical use of
+{\color{blue} BDJ discuss the relation of this technique to the typical use of
 continuum normalization when fitting spectroscopy.}
@@
 In this sense, one should never use a single point estimate of the
-calibration, the full distribution of the possible calibrations should
-be inferred from our probabilistic knowledge of the calibration object
-and forward propogated \citep[e.g.][]{lee11}. Once this is done, the
-only distinction between 'calibration' objects and targets of interest
-is the complexity of the model for the object and the level of
-uncertainty in the calibration object spectrum.  If one is interested
-in inferring parameters of interest of spectral models of
-astrophysical objects, then there is often no reason not to use those
-objects themselves as calibration objects.
+spectrophotometric calibration, the full distribution of the possible
+calibrations should be inferred from our probabilistic knowledge of
+the calibration object and forward propogated
+\citep[e.g.][]{lee11}. Indeed, even if the calibration object is known
+perfectly, the observation of it will be noisy and thus so will the
+inferred calibration. Once this forward propogation of calibration
+uncertainty is done, the only distinction between 'calibration'
+objects and targets of interest is the uncertainty in the model for
+the object and the level of uncertainty in the observed object
+spectrum -- this is why calibration objects are typically bright and
+simple.  If one is interested in inferring parameters of interest of
+spectral models of astrophysical objects, then there is often no
+reason not to use those objects themselves as calibration objects
+(especially if you expect your calibration to be spatially or
+temporally variable, or to change with the brightness of the object)
 
@@
 keep me from cluttering up the main text: Model resolution and
-instrument resolution.  How to interpret GP residuals, as a fn of S/N?
-Photometric upper limits? Infer the wavelength solution as well -
-stellar population (and telluric lines) as your arc. Combinations of
-broadening in velocity space (physical) and in wavelength space
-(instrumental)
+instrument resolution, ombinations of broadening in velocity space
+(physical) and in wavelength space (instrumental).  Photometric upper
+limits? Infer the wavelength solution as well - stellar population
+(and telluric lines) as your arc.
 

### 2015-04-24 code/ggcdata.py

@@ -55,7 +55,7 @@ def ggc_spec(objname, exp='a', ext='1',
 
 
 def spec_lsf(wave, sigma_smooth=1.31,
-             sigma_library=1.08, ref_wave=4838,
+             sigma_library=1.08, lsf_ref_wave=4838,
              **extras):
     """Line spread function of the GGC spectroscopy from Schiavon.
 
@@ -67,11 +67,12 @@ def spec_lsf(wave, sigma_smooth=1.31,
         
     :param sigma_lib:
         Resolution of the spectral library.  It will be subtracted in
-        quadrature from the desired total resolution
+        quadrature from the desired total resolution, so when the
+        library is convolved with the result the desired LSF is
+        acheived
 
-    :param ref_wave:
-        The wavelength in AA at which sigma_smooth is defined,
-        defaults to 5500AA
+    :param lsf_ref_wave:
+        The wavelength in AA at which sigma_smooth is defined.
         
     :returns disp:
         The dispersion (or fwhm if sigma_smooth was gien as such) at
@@ -80,9 +81,23 @@ def spec_lsf(wave, sigma_smooth=1.31,
     coeffs = np.array([15.290, -6.079e-3, 9.472e-7, -4.395e-11])
     powers = np.arange(len(coeffs))
     fwhm = np.dot(coeffs, wave[None, :] ** powers[:, None])
-    fwhm_ref = (coeffs * ref_wave**powers).sum()
+    fwhm_ref = (coeffs * lsf_ref_wave**powers).sum()
     target = (fwhm/fwhm_ref) * sigma_smooth
-    return np.sqrt(target**2 - sigma_library**2)
+    delta_sigma_sq = np.clip(target**2 - sigma_library**2, 0, np.inf)
+    return np.sqrt(delta_sigma_sq)
+
+def broaden_ggcspec(wave, flux, minsig=1e-6):
+    """Convolve the observed spectrum to have have constant wavelength
+    resolution across the spectral range.  This is not kosher, but
+    makes run times tractable.
+    """
+    sigma_data = spec_lsf(wave, sigma_library=0.0, sigma_smooth=1.31)
+    delta_sigma = np.sqrt(sigma_data.max()**2 - sigma_data**2)
+    delta_sigma[delta_sigma <= 0.0] = minsig
+    def lsf():
+        return delta_sigma
+    newflux = observate.lsf_broaden(wave, flux, lsf=lsf)
+    return newflux
 
 def ggc_phot(objname, datadir='', **extras):
     

### 2015-04-24 code/make_ggc_mocks.py

@@ -110,7 +110,7 @@ model_params.append({'name': 'zred', 'N':1,
 
 model_params.append({'name': 'sigma_smooth', 'N': 1,
                         'isfree': False,
-                        'init': 1.31,
+                        'init': 1.3,
                         'units': r'$\AA$',
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':0.0, 'maxi':3}})
@@ -205,7 +205,7 @@ if __name__ == "__main__":
     noisetype = ['0','1']
     name_template = os.path.join(info['outdir'], lib,
                                  'ggc_mock.{0}{1}.t{2:3.1f}_z{3:3.1f}_a{4:3.1f}.pkl')
-    vary_params = {'tage': [0.3, 1.0, 3.0, 6.0, 9.0],
+    vary_params = {'tage': [0.3, 1.1, 3.0, 6.0, 9.0],
                    'zmet': [-1.5, -1.0, -0.5, 0.0],
                    'dust2': [0, 0.5, 1.0, 2.0]
                    }

### 2015-04-24 code/paramfiles/mock_speconly.py

@@ -4,7 +4,7 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock',
+              'outfile':'results/ggc_mock_c0_t9.0_z0.0_a0.5',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
@@ -15,7 +15,7 @@ run_params = {'verbose':True,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,
-              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t1.0_z0.0_a0.5.pkl',
+              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl',
               'wlo':3350.,
               'whi':6500.
               }

### 2015-04-25 tex/figures.tex
move figures to end, change captions around

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated spectrum for \excluster, along with the
uncertainties (bottom panel).The right panel shows the
spectrophotometric calibration vector determined by
\citet{schiavon05}. \label{fig:ggc_data}}
\end{figure}

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{A mock spectrum for a star cluster with $10^5 M_\odot$ total
  stellar mass, an age of  9 Gyr, solar
  metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
\end{figure}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from a mock spectrum and a single photometric data point where the spectrophotometric calibration is assumed to be perfectly known.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it green}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_ideal}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from a \emph{perfectly calibrated} mock
  spectrum and a single photometric data point.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it green}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.
Top Left: The observed spectrum. The mock observed spectrum ({\it
black}) is shown as well as YY model spectra constructed from draws
from the posterior PDFs of the model parameters, including calibration
parameters {\it green}.
Bottom Left: The calibration vector. The true calibration vector ({\it
black}) that was used to construct the mock spectrum is compared to
posterior samples of the inferred calibration vector ({\it green})
which include both the polynomial and the Gaussian Process mean
prediction (Equation
\ref{eq:calibration}).
Top Right: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the photometry only.
Top: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the combination of mock 
Top Left: The observed spectrum. The mock observed spectrum ({\it
black}) is shown as well as YY model spectra constructed from draws
from the posterior PDFs of the model parameters, including calibration
parameters {\it green}.
Bottom Left: The calibration vector. The true calibration vector ({\it
black}) that was used to construct the mock spectrum is compared to
posterior samples of the inferred calibration vector ({\it green})
which include both the polynomial and the Gaussian Process mean
prediction (Equation
\ref{eq:calibration}).
Top Right: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

### 2015-04-25 tex/ms.tex
move figures to end, change captions around

@@
 \DeclareGraphicsExtensions{.png,.pdf}
-\newcommand{\excluster}{B192-G242}
+\newcommand{\excluster}{NGC7089}
 
@@
 $s^2$.  For photometric data this ``jitter'' is often best described
-as a fractional error, $(s\mu(\theta))^2$, corresponding for example
+as a fractional error, $(\hat{s}\mu(\theta))^2$, corresponding for example
 to an additional magnitude zero-point uncertainty.
@@
                              \left[\frac{[d_n - \mu_n(\theta)]^2}
-                             {[\sigma_n^2 + (s\,\mu_n(\theta))^2]} + 
-                             \ln(2\pi\,[\sigma_n^2 + (s\,\mu(\theta))^2]) \right]
+                             {[\sigma_n^2 + s^2]} + 
+                             \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
 \quad .
@@
 log-likelihood function we are going to use for the photometric
-measurements in what follows.  
-In this formulation, if $\theta$ are the parameters of interest, the
-jitter variance $s^2$ is a nuisance noise-model parameter representing
-additonal fractional uncertainty in the flux.  The
-Gaussian Process will be a generalization of this modification.
+measurements in what follows.  In this formulation, if $\theta$ are
+the parameters of interest, the jitter variance $\hat{s}^2\equiv
+s/\mu(\theta)$ is a nuisance noise-model parameter representing
+additonal fractional uncertainty in the flux.  The Gaussian Process
+will be a generalization of this modification.
 
@@
 (and therefore fast) and the calibration vector is forced to be
-positive everywhere.  Additionally, at high signal to noise the distortion
-of the uncertainties will be minimal.
+positive everywhere.  Additionally, at high signal to noise the
+distortion of the uncertainties will be minimal.
 
@@
 The calibration vector $f(\alpha)$ is going to take care of the
-large-scale calibration residual; the Gaussian process is going to
+large-scale calibration residual; the Gaussian Process is going to
 pick up smaller-scale residuals away from \emph{that}.
+The flexibility of the Gaussian Process specified by $C$ will obviate
+the need for numerous high order polynomial terms in $f(\alpha)$ and
+thus reduce the number of free parameters required in the model.  The
+prior over functions implied by $C$ is analytically conditioned on the
+residuals $\Delta$.
 The residual column vector is defined in terms of the logarithmic
@@
 \\
-C_{nn'} &\equiv& [\sigma_n^2 + (s * \mu)^2]\,\delta_{nn'} +
+C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} * \mu)^2]\,\delta_{nn'} +
 \transpose{\mu} \, K_\alpha(\lambda_n - \lambda_{n'}) \, \mu
@@
 effect of calibration uncertainties on the inferred parameters in the
-case of a perfect mean model $mu(\theta)$.  The inference from real
+case of a perfect mean model $\mu(\theta)$.  The inference from real
 data tests a combination of our methodology and the ability of the
@@
 ancillary spectrophotometric calibration data.
-
-\begin{figure}[h!]
-%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{The calibrated spectrum for \excluster, along with the
-uncertainties (bottom panel).The right panel shows the
-spectrophotometric calibration vector determined by
-\citet{schiavon05}. \label{fig:ggc_data}}
-\end{figure}
-
-\subsection{List of Experiments}
-
-\begin{enumerate}
-
-\item Mock perfectly calibrated data: inference using spectroscopy and one
-  photometric band, with both full calibration model and assuming no
-  calibration uncertainty.
-
-\item Mock uncalibrated data:  inference using spectroscopy and one
-  photometric band, with full calibration model
-
-\item Mock data: inference using photometry only
-
-\item Mock uncalibrated data: inference using spectroscopy and all
-  photometry, full calibration model.
-
-\item Mock perfectly calibrated data: inference using spectroscopy and all
-  photometry, with both full calibration model and assuming no
-  calibration uncertainty.
-
-\item Real calibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model.
-
-\item Real uncalibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model.
-
-\item Compare the physical parameters inferred from from the real
-  calibrated and uncalibrated spectrum with each other and with CMD
-  based parameters.
-
-\end{enumerate}
 
@@
 the \emph{uncalibrated} mock spectra.
-
-\begin{figure}[h!]
-%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{A mock spectrum for a star cluster with $10^5 M_\odot$ total
-  stellar mass, an age of  9 Gyr, solar
-  metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
-\end{figure}
 
@@
 
+At each iteration of the sampler the photometric and spectroscopic
+likelihood are computed, multiplied together, and multiplied by the
+the prior probability of that parameter position to obtain an estimate
+of the posterior probability for those parameters given the data.
+
 Our prior distributions are in all cases top-hat functions, described
@@
 
-\begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Spectra resulting from draws from the posterior parameter
-space conditioned on the calibrated \excluster~ spectrum and
-photometry.  Left: For each of 5 draws from the posterior we show from
-top to bottom, three components of the model: the mean cluster
-spectrum, the calibration vector, and the mean prediction of $\Delta$
-for the Gaussian process.  Right: From top to bottom, the full model
-({\it magenta}) compared to the observed, calibrated spectrum ({\it
-grey}), the ratio of the observed to the modeled spectrum, and the
-difference between the observed spectrum and the modeled spectrum
-normalized by the uncertainty.
-\label{fig:speconly_calibrated}}
-\end{figure*}
+\subsection{List of Experiments}
+
+\begin{enumerate}
+
+\item Mock perfectly calibrated data: inference using spectroscopy and one
+  photometric band, with both full calibration model and assuming no
+  calibration uncertainty.
+
+\item Mock uncalibrated data:  inference using spectroscopy and one
+  photometric band, with full calibration model
+
+\item Mock data: inference using photometry only
+
+\item Mock uncalibrated data: inference using spectroscopy and all
+  photometry, full calibration model.
+
+\item Mock perfectly calibrated data: inference using spectroscopy and all
+  photometry, with both full calibration model and assuming no
+  calibration uncertainty.
+
+\item Real calibrated spectrum:   Inference using spectroscopy and all
+  photometry, with full calibration model.
+
+\item Real uncalibrated spectrum:   Inference using spectroscopy and all
+  photometry, with full calibration model.
+
+\item Compare the physical parameters inferred from from the real
+  calibrated and uncalibrated spectrum with each other and with CMD
+  based parameters.
+
+\end{enumerate}
 
@@
 
-\subsection{Mock data}
+\subsection{Mocks}
+We first present the results of our inference from a spectrum where we
+assume the calibration is known perfectly.  That is, we fix the
+calibration parameters $\alpha$ to the values used to construct the
+mock data.  This sets a baseline for the kind of posterior PDFs that
+could be obtained for the physical parameters given the
+signal-to-noise of the mock data, perfect models, and perfectly known
+calibration.
 
-In Figure \ref{fig:speconly_calibrated} we show the result of our
-inference from the spectrum and a single photometric measurement (SDSS
-$g$) for a perfectly calibrated mock spectrum. To demonstrate the
-quality of the fit we show both the mock
-input spectrum and predictions of the observed spectra that result
-from several draws of the model parameters
-$[\theta, \alpha]$ from posterior distribution.  We also show samples
-of the inferred calibration vector,
+{\color{blue}BDJ Describe results from the ideal case.}
+
+Next we will \emph{not} assume that the calibration is perfectly known
+and we will therefore allow the calibration parameters $\alpha$ in our
+model to vary.  In Figure
+\ref{fig:speconly_calibrated} we show the result of our inference from
+the spectrum and a single photometric measurement (SDSS $g$) for a
+perfectly calibrated mock spectrum. To demonstrate the quality of the
+fit we show both the mock input spectrum and predictions of the
+observed spectra that result from several draws of the model
+parameters $[\theta, \alpha]$ from posterior distribution.  We also
+show samples of the inferred calibration vector,
 \begin{eqnarray} 
@@
 \end{eqnarray}
-where $\tilde{\Delta}$ is the Gaussian process mean prediction for the
+where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
 logarithmic residual between the data and the model.  For the
@@
 
-Even in the case of a single photometric data point, several of the
+Even in the case of a single photometric data point, many of the
 physical parameters are well-constrained and only minimally biased,
@@
 be reasonably well recovered by fitting continuum normalized spectra,
-though hewre we have propogated the uncertainty in this normalization
+though here we have propogated the uncertainty in this normalization
 into the uncertainties on the physical parameters.
@@
 
-\subsection{Real Data: NGCXXX} 
+\subsection{Real Data: NGCXXXX} 
 We first infer the parameters of interest $\theta$ for a calibrated
@@
 for the total effective multiplicative calibration, where
-$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
+$\tilde{\Delta}$ is now the Gaussian Process mean prediction for the
 logarithmic residual between the data and the model. The inverse of
@@
 vector to be constant as a function of wavelength.
-
-\begin{figure}[h!]
-%\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
-\caption{ Model SEDs.  Top: The model photometric SED resulting from
-draws from the posterior parameter space conditioned ({\it cyan}) on
-the observed photometry ({\it magenta}) and spectra.  Bottom:
-uncertainty normalized residuals of the models from the observations.
-\label{fig:inferred_sed}}
-\end{figure}
-
-\begin{figure}[h!]
-%\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
-\caption{ Marginalized and joint PDFs of subset of the physical
-parameters $\theta$ inferred from the spectophotometrically calibrated
-spectrum of \excluster. The blue lines indicate the parameter values
-that resulted from the powell minimization.
-\label{fig:inferred_params}}
-\end{figure}
-
-\begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
-\caption{Left: Samples of the effective multiplicative calibration
-vector for the spectrophotometrically calibrated spectrum of
-\excluster~ ({\it cyan}) compared to that obtained from ancillary
-photometric data ({\it magenta}).  
-Right: The same, but for the uncalibrated data.
- \label{fig:inferred_calib}}
-\end{figure*}
-
-\begin{figure}[h!]
-%\includegraphics[width =0.5\textwidth]{figures/B192_020_cratio.pdf}
-\caption{Money plot.  Show the difference between the parameters
-  inferred from the calibrated and uncalibrated spectra, for each
-  cluster. Tjis is a placeholder, since it only shows B192 for fixed
-  GP parameters. \label{fig:boom}}
-\end{figure}
 
@@
 parameters of the model, inform the construction of the calibration
-model, or approximately remove gross features that are difficult to
-model parameterically or via a Gaussian Process.
+model (including the form of the covariance kernel), or approximately
+remove gross features that are difficult to model parametrically or
+via a Gaussian Process.
 
@@
 include for example night sky-line emission in the spectroscopy (or
-residuals from an intial sky-line subtraction), and uncertainties in
+residuals from an intial sky-line subtraction) and uncertainties in
 wavelength calibration. Furthermore, more complex physical models may
@@
 
+\input{figures.tex}
+
 \end{document}

### 2015-04-25 code/mock_figures.py

@@ -138,7 +138,7 @@ if __name__ == "__main__":
                                                   gp=gp)
     pwave, mosed, mosed_unc, pvecs = comp_samples_phot(thetas, mod, obsdat, sps=sps)
 
-    calvec = obsdat['calibration'].copy()
+    calvec = obsdat['calibration']
     if np.size(calvec) == 1:
         calvec = np.zeros(len(mwave)) + calvec
     else:

### 2015-04-25 code/paramfiles/mock_speconly_losn.py

@@ -1,18 +1,40 @@
 import numpy as np
 import pickle, os
-from bsfh import sps_basis, priors, sedmodel, elines
+from bsfh import priors, sedmodel
 from sedpy import attenuation
-import ggcdata
 
-sps = sps_basis.StellarPopBasis()
-nw = len(sps.ssp.wavelengths)
-if nw > 7000:
-    lib = 'ckc'
-elif nw > 2000:
-    lib = 'miles'
-    sigma_library = 1.08
-else:
-    lib = 'basel'
+run_params = {'verbose':True,
+              'outfile':'results/ggc_mock_c0_t9.0_z0.0_a0.5',
+              'do_powell': False,
+              'ftol':0.5e-4, 'maxfev':5000,
+              'nwalkers':64, 
+              'nburn':[64, 128, 256], 'niter':512,
+              'initial_disp':0.1,
+              'debug':False,
+              'logify_spectrum':True,
+              'normalize_spectrum':True,
+              'norm_band_name':'sdss_g0',
+              'rescale':True,
+              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl',
+              'wlo':3350.,
+              'whi':6500.,
+              'noisefactor':10
+              }
+
+##### OBSERVATIONAL DATA ######
+
+def load_obs(filename=None, noisefactor=1.0, **extras):
+    with open(filename) as f:
+        obs = pickle.load(f)
+    obs['phot_mask'] = np.array(['sdss_g' in filt.name for filt in obs['filters']])
+    obs['unc'] *= noisefactor
+    obs['noisefactor'] = noisefactor
+    return obs
+
+obs = load_obs(**run_params)
+
+###### MODEL ###########
+model_type = sedmodel.SedModel
 
 model_params = []
 
@@ -27,22 +49,22 @@ model_params.append({'name': 'lumdist', 'N': 1,
 ###### SFH ################
 
 model_params.append({'name': 'mass', 'N': 1,
-                     'isfree': False,
-                     'init': 1e5,
+                     'isfree': True,
+                     'init': 2e5,
                      'units': r'M$_\odot$',
                      'prior_function': priors.tophat,
                      'prior_args': {'mini':1e4, 'maxi': 1e6}})
 
 model_params.append({'name': 'tage', 'N': 1,
                         'isfree': True,
-                        'init': 9.0,
+                        'init': 5.0,
[…]

### 2015-04-27 tex/figures.tex
new figure captions, untrack all old figures

@@
 \begin{figure}[h!]
-%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{The calibrated spectrum for \excluster, along with the
-uncertainties (bottom panel).The right panel shows the
-spectrophotometric calibration vector determined by
-\citet{schiavon05}. \label{fig:ggc_data}}
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
+\caption{Observational data. 
+Top: The calibrated spectrum for \excluster.
+Middle: The signal-to-noise ratio.
+Bottom: The spectrophotometric calibration vector determined by
+\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
+\end{center}
 \end{figure}
@@
 %\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{A mock spectrum for a star cluster with $10^5 M_\odot$ total
-  stellar mass, an age of  9 Gyr, solar
+\caption{A mock spectrum for a star cluster with the fiducial
+parameters $10^5 M_\odot$ total stellar mass, an age of 9 Gyr, solar
 metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
@@
 \caption{Results of inference from an \emph{uncalibrated} mock
-  spectrum and a single photometric data point.
-Top Left: The observed spectrum. The mock observed spectrum ({\it
-black}) is shown as well as YY model spectra constructed from draws
-from the posterior PDFs of the model parameters, including calibration
-parameters {\it green}.
-Bottom Left: The calibration vector. The true calibration vector ({\it
-black}) that was used to construct the mock spectrum is compared to
-posterior samples of the inferred calibration vector ({\it green})
-which include both the polynomial and the Gaussian Process mean
-prediction (Equation
-\ref{eq:calibration}).
-Top Right: The intrinsic spectrum. Samples of the posterior prediction
-for the \emph{intrinsic} spectrum ({\it green}) as well as for the
-photometry ({\it magenta}).  The true mock photometry is also shown
+  spectrum and a single photometric data point.  Panels and colors are
+  as in Figure \ref{fig:speconly_calibrated}.  In this case the
+  observed spectrum is in arbitrary units and the true
+  calibration vector is not a constant with wavelength.
+\label{fig:speconly_uncalibrated}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\caption{Results of inference from the photometric data only.
+Top: The intrinsic spectrum. Samples of the posterior prediction
+for the \emph{intrinsic} spectrum ({\it green}) and the
+photometry ({\it magenta}).  The mock photometry is also shown
 ({\it black}).
-Bottom Right: Marginalized posterior PDFs for several of the physical
+Right: Marginalized posterior PDFs for several of the physical
 parameters of interest.  The input mock parameters are shown as
 vertical lines.
+\label{fig:photonly}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\caption{Results of inference from the combination of
+  \emph{uncalibrated} spectroscopy and all the photometric data
+  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
 \label{fig:speconly_calibrated}}
@@
 %\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Results of inference from the photometry only.
-Top: The intrinsic spectrum. Samples of the posterior prediction
-for the \emph{intrinsic} spectrum ({\it green}) as well as for the
-photometry ({\it magenta}).  The true mock photometry is also shown
-({\it black}).
-Right: Marginalized posterior PDFs for several of the physical
-parameters of interest.  The input mock parameters are shown as
-vertical lines.
-\label{fig:speconly_calibrated}}
+\caption{Joint posterior PDFs for several physical parameters. The
+  posteriors obtained from photometry only is in {\it red}, from
+  \emph{uncalibrated} spectroscopy and a single photometric point in {\it blue}, and from
+  the photometry and spectroscopy combined in {\it magenta}.
+\label{fig:combined_posterior}}
 \end{figure*}
@@
 %\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Results of inference from the combination of mock 
-Top Left: The observed spectrum. The mock observed spectrum ({\it
-black}) is shown as well as YY model spectra constructed from draws
-from the posterior PDFs of the model parameters, including calibration
-parameters {\it green}.
-Bottom Left: The calibration vector. The true calibration vector ({\it
-black}) that was used to construct the mock spectrum is compared to
-posterior samples of the inferred calibration vector ({\it green})
-which include both the polynomial and the Gaussian Process mean
-prediction (Equation
-\ref{eq:calibration}).
-Top Right: The intrinsic spectrum. Samples of the posterior prediction
-for the \emph{intrinsic} spectrum ({\it green}) as well as for the
-photometry ({\it magenta}).  The true mock photometry is also shown
-({\it black}).
-Bottom Right: Marginalized posterior PDFs for several of the physical
-parameters of interest.  The input mock parameters are shown as
-vertical lines.
-\label{fig:speconly_calibrated}}
+\caption{Posterior PDFs obtained from multiple noise realizations of the
+  mock photometry and uncalibrated spectra, for a single set of
+  parameters.  The input mock parameters are shown as a 
+  vertical line, medians of the posterior CDF for each realization are
+  shown as dotted lines.
+\label{fig:noise_realizations}}
 \end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\caption{Posterior PDFs obtained from mock spectra and photometry
+  created with  a variety of mock physical parameters, as a function
+  of those parameters.
+\label{fig:mock_parameter_space}}
+\end{figure*}

### 2015-04-27 tex/ms.tex
new figure captions, untrack all old figures

@@
 \begin{eqnarray}\label{eq:spectroscopicLF_v2}
-\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
+\ln p(d\given\theta,\alpha) &=&
+                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
+                                + \ln([2\pi]^N\,\det{C}) \right]
 \\
@@
 
-\item Mock perfectly calibrated data: inference using spectroscopy and all
-  photometry, with both full calibration model and assuming no
-  calibration uncertainty.
+\item Do this for a bunch of ages, metallicities, and dust
+  attenuations, possibly compare to the ideal posteriors.
 
@@
 residuals from an intial sky-line subtraction) and uncertainties in
-wavelength calibration. Furthermore, more complex physical models may
+wavelength calibration \citep[e.g.,][]{walker15}. Furthermore, more complex physical models may
 be considered for the mean object model, for example including SFH
@@
 
+\bibitem[Walker et al.(2015)]{walker15} Walker, M.~G., 
+Olszewski, E.~W., \& Mateo, M.\ 2015, \mnras, 448, 2717
+
 \end{thebibliography}

### 2015-04-27 code/ggcdata.py

@@ -235,7 +235,7 @@ def integrated_flux_king(outer, A, r_c=1, r_t=30):
     return -2.5*np.log10(total_flux)
 
 
-def make_skymask(wave, flux, width=10, thresh=5., lsf=6.):
+def make_skymask(wave, flux, width=10, thresh=5., lsf=6., **extras):
     """Generate a mask based on peaks in the sky spectrum, found using
     median filtering.
 
@@ -313,13 +313,13 @@ def ggc_mock(model, theta, sps, objname='', apply_cal=True, mask=True,
     
     return mock
 
-def ggc_mask(obs, minwave=3602, maxwave=1e4, pad=6.0):
+def ggc_mask(obs, minwave=3602, maxwave=1e4, pad=6.0, **kwargs):
     """Generate a mask based on peaks in the sky spectrum, min and max
     wavelengths, and regions around ISM and sky lines.
     """
     from bsfh import elines
     wave = obs['wavelength']
-    skymask = make_skymask(wave, obs['sky'], lsf=3)
+    skymask = make_skymask(wave, obs['sky'], lsf=6, **kwargs)
     mask = (skymask & (wave > minwave) &
             (wave < maxwave))
         

### 2015-04-27 code/make_ggc_mocks.py

@@ -191,7 +191,6 @@ model_params.append({'name': 'phot_jitter', 'N':1,
                         'prior_args': {'mini':0.0, 'maxi':0.1}})
 
 
-
 if __name__ == "__main__":
     
     info = {'objname': 'NGC7089',

### 2015-04-27 code/mock_figures.py

@@ -134,6 +134,9 @@ if __name__ == "__main__":
     
     fsamples = np.random.uniform(0,1,nsample)
     thetas, start, samples = theta_samples(res, samples=fsamples, start=0.75, thin=1)
+    fwave, mospec, mounc, fspecvecs = comp_samples_fullspec(thetas, mod, obsdat, sps=sps,
+                                                  gp=gp)
+
     mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat, sps=sps,
                                                   gp=gp)
     pwave, mosed, mosed_unc, pvecs = comp_samples_phot(thetas, mod, obsdat, sps=sps)

### 2015-04-27 code/paramfiles/mock_speconly_ideal.py

@@ -4,11 +4,11 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_c0_t9.0_z0.0_a0.5',
+              'outfile':'results/ggc_mock_ideal.c0.t9.0_z0.0_a0.5',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
-              'nburn':[64, 64, 128, 128, 256], 'niter':512,
+              'nburn':[64, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
               'logify_spectrum':True,
@@ -125,7 +125,7 @@ model_params.append({'name': 'imf3', 'N':1,
 
 model_params.append({'name': 'zred', 'N':1,
                         'isfree': True,
-                        'init': 0.000001,
+                        'init': 0.00001,
                         'units': None,
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':-0.001, 'maxi':0.001}})
@@ -167,35 +167,35 @@ polymax = [5e1, 1e2]
 polyinit = [0.01, 0.01]
 
 model_params.append({'name': 'poly_coeffs', 'N': polyorder,
-                        'isfree': True,
-                        'init': polyinit,
+                        'isfree': False,
+                        'init': obs['mock_params']['poly_coeffs'],
                         'units': None,
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':polymin, 'maxi':polymax}})
     
 model_params.append({'name': 'spec_norm', 'N':1,
-                        'isfree': True,
-                        'init':0.0001,
+                        'isfree': False,
+                        'init':0.0000,
                         'units': None,
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':-1.0, 'maxi':1.0}})
 
 model_params.append({'name': 'gp_jitter', 'N':1,
-                        'isfree': True,
-                        'init': 0.0001,
+                        'isfree': False,
+                        'init': 0.0000,
                         'units': 'spec units',
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':0.0, 'maxi':0.2}})
 
 model_params.append({'name': 'gp_amplitude', 'N':1,
-                        'isfree': True,
-                        'init': 0.0001,
+                        'isfree': False,
+                        'init': 0.0000,
                         'units': 'spec units',
                         'prior_function': priors.tophat,
[…]

### 2015-04-27 code/plotting.py

@@ -1,9 +1,14 @@
 import numpy as np
 import matplotlib.pyplot as pl
 import bsfh.read_results as bread
+from copy import deepcopy
 
 def comp_samples(thetas, model, obs, sps=None, gp=None):
-    """Different components of the model for 
+    """Different components of the model for a given set of thetas.
+
+    :returns wave:
+        The full wavelength array
+    :return 
     """
     specvecs = []
     wave, ospec, mask = obs['wavelength'], obs['spectrum'], obs['mask']
@@ -40,6 +45,33 @@ def comp_samples_phot(thetas, model, obs, sps=None):
         specvecs += [ [mu, zero, zero, mu, mospec - mu, (mospec - mu)/mounc] ]
     return wave[mask], mospec, mounc, specvecs
 
+def comp_samples_fullspec(thetas, model, obs, sps=None, gp=None):
+    specvecs = []
+    mospec, mounc = None
+    fullobs = deepcopy(obs)
+    fullobs['wavelength'] = sps.wavelengths.copy()
+    fullobs['mask'] = np.ones( len(fullobs['wavelength']), dtype= bool)
+    for theta in thetas:
+        mu, cal, delta, mask, wave = bread.model_comp(theta, model, obs, sps,
+                                                      gp=gp, photflag=0)
+        cal = np.exp(cal)
+        full_cal = np.exp(np.log(cal) + delta)
+        mod = np.exp(np.log(mu) + np.log(cal) + delta)
+        specvecs += [[mu, cal, delta, mod]]
+        
+    return wave, mospec, mounc, specvecs
+
+def true_sed(model, obs, sps=None, fullspec=False):
+    fullobs = deepcopy(obs)
+    mockpars = deepcopy(obs['mock_params'])
+    model.params = mockpars
+    theta = model.theta.copy()
+    if fullspec:
+        fullobs['wavelength'] = sps.wavelengths.copy()
+        fullobs['mask'] = np.ones( len(fullobs['wavelength']), dtype= bool)
+
+    mu, phot, x = model.sed(theta, fullobs, sps=sps)
+        
 def theta_samples(res, samples=[1.0], start=0.0, thin=1):
 
     nw, niter = res['chain'].shape[:-1]

### 2015-04-29 tex/ms.tex
updates to bib, small changes throughout text, add some plotting code

@@
 If you don't believe the reported data noise variances $\sigma_n^2$,
-it often makes sense to add in quadrature a ``jitter'' variance
-$s^2$.  For photometric data this ``jitter'' is often best described
-as a fractional error, $(\hat{s}\mu(\theta))^2$, corresponding for example
-to an additional magnitude zero-point uncertainty.
-This is a simple modification of the chi-squared log-likelihood:
+it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
+For photometric data this ``jitter'' is often best described as a
+fractional error, $s^2 \equiv \hat{s}^2\mu(\theta)^2$, corresponding
+for example to an additional magnitude zero-point uncertainty.  This
+is a simple modification of the chi-squared log-likelihood:
 \begin{eqnarray}\label{eq:photometricLF}
@@
 measurements in what follows.  In this formulation, if $\theta$ are
-the parameters of interest, the jitter variance $\hat{s}^2\equiv
+the parameters of interest, the jitter variance $\hat{s} = 
 s/\mu(\theta)$ is a nuisance noise-model parameter representing
@@
 
+{\color{blue} BDJ This paragraph should explain why we are using the
+GP, not just how it works.}
+The multiplicative calibration vector can be explicitly modeled, for
+example using polynomials.  However, for complex calibration vectors
+over large wavelength ranges, the number of parameters required to
+model the calibration can become quite large (e.g., very high order
+polynomials) and the correct parameterization may be unknown.  It is
+therefore desirable to introduce a non-parameteric model of the
+calibration.  We do this using a Gaussian Process: prior over
+functions, analytically marginalizable, covariant fractional
+uncertainties the same as multiplying by a function (covariant
+uncertainties the same as adding a function)
+
 The calibration-vector and Gaussian-Process modified log-likelihood is
 \begin{eqnarray}\label{eq:spectroscopicLF}
-\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
+\ln p(d\given\theta,\alpha) &=&
+                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
+                                + \ln([2\pi]^N\,\det{C}) \right]
 \\
@@
 difference between the data and the mean model $\mu$ since we are
-taking the calibration vector to be multiplicative with respect to
-the mean model $\mu$. In this formulation the the mean model $\mu$ will be effectively
-multiplied by $e ^{f(\alpha)}$ 
+taking the calibration vector to be multiplicative with respect to the
+mean model $\mu$. In this formulation the the mean model $\mu$ will be
+effectively multiplied by $e ^{f(\alpha)}$
 This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
@@
 show samples of the inferred calibration vector,
-\begin{eqnarray} 
+\begin{eqnarray} \label{eq:calibration}
 \frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
@@
 where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
-logarithmic residual between the data and the model.  For the
+logarithmic residual between the data and the model \citep{RW}.  For the
 perfectly calibrated spectrum the true calibration vector (shown in
@@
 
-\subsection{Real Data: NGCXXXX} 
+\subsection{Real Data: \excluster} 
 We first infer the parameters of interest $\theta$ for a calibrated
@@
 It is possible to reconstruct the inferred total multiplicative
-calibration vector for each draw of the model parameters.  Rearranging
-equation \ref{eq:spectroscopicLF} yields
-\begin{eqnarray} 
-\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
-\quad ,
-\end{eqnarray}
-for the total effective multiplicative calibration, where
-$\tilde{\Delta}$ is now the Gaussian Process mean prediction for the
-logarithmic residual between the data and the model. The inverse of
-this ratio is shown in the left panel of Figure
-\ref{fig:inferred_calib} as our inferred total multiplicative
-calibration function; if the spectrophotometric calibration were
+calibration vector for each draw of the model parameters (Equation
+\ref{eq:calibration}) If the spectrophotometric calibration were
 perfect and we had correctly inferred it, then we would expect this
@@
 remove gross features that are difficult to model parametrically or
-via a Gaussian Process.
+via a Gaussian Process.  {\color{blue} Discuss more complicated
+covariance kernels, multiple kernels}
 
@@
 Our strategy is easily extensible to more complicated models, which
-include for example night sky-line emission in the spectroscopy (or
-residuals from an intial sky-line subtraction) and uncertainties in
-wavelength calibration \citep[e.g.,][]{walker15}. Furthermore, more complex physical models may
-be considered for the mean object model, for example including SFH
-parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
-COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
-CHECKING.}
+include for example night sky-line emission in the spectroscopy
+\citep[e.g.,][]{gullikson14} or residuals from an intial sky-line
+subtraction and uncertainties in wavelength calibration
+\citep[e.g.,][]{walker15}. Furthermore, more complex physical models
+may be considered for the mean object model, for example including SFH
+parameters so as to model galaxies. {\color{blue} Discuss background
+modeling}
 
@@
 to molecular bands or absorption line complexes) will be absorbed into
-the Gaussian process. Third, we have made the assumption that the
-spectroscopy and the photometry are sampling the same populations.  In
-practice, differences between spectroscopic and photometric apertures
-often mean that the photometry and the spectroscopy are sampling
-slightly different physical regions.  The correct response to this
-situation is to explicitly model the differences, incorporating prior
-information about the spatial variation of physical properties.
-Fourth, the method will break down at very low S/N due to the
-logarithmic formulation of the residual in
-equation~(\ref{eq:spectroscopicLF}).  Finally, this method is
-computationally intensive and expensive, since we are constantly
-inverting largish matrices.
+the Gaussian process if not properly included in the mean
+model. Third, we have made the assumption that the spectroscopy and
+the photometry are sampling the same populations.  In practice,
+differences between spectroscopic and photometric apertures often mean
+that the photometry and the spectroscopy are sampling slightly
+different physical regions.  The correct response to this situation is
+to explicitly model the differences, incorporating prior information
+about the spatial variation of physical properties.  Fourth, the
+method will break down at very low S/N due to the logarithmic
+formulation of the residual in equation~(\ref{eq:spectroscopicLF}).
+Finally, this method is computationally intensive and expensive, since
+we are constantly inverting largish matrices.
 
@@
 
+\bibitem[Gullikson et al.(2014)]{gullikson14} Gullikson, K., 
+Dodson-Robinson, S., \& Kraus, A.\ 2014, \aj, 148, 53
+
 \bibitem[Lee et al.(2011)]{xray_calunc} Lee, H., Kashyap, V.~L., 

### 2015-04-29 code/mock_figures.py

@@ -18,6 +18,8 @@ gp = george.GP(kernel, solver=george.HODLRSolver)
 
 
 def calfig(wave, calvec, specvecs, norm=1.0, fax=None):
+    """Plot the calibration and posterior samples of it
+    """
     if fax is None:
         cfig, cax = pl.subplots()
     else:
@@ -37,6 +39,8 @@ def calfig(wave, calvec, specvecs, norm=1.0, fax=None):
     return cfig, cax
 
 def obsfig(wave, obsvec, specvecs, unc=None, fax=None):
+    """Plot the observed spectrum and posterior samples of it
+    """
     if fax is None:
         ofig, oax = pl.subplots()
     else:
@@ -58,7 +62,9 @@ def obsfig(wave, obsvec, specvecs, unc=None, fax=None):
     return ofig, oax
 
 def sedfig(wave, specvecs, phot, photvecs, norm = 1.0, fax=None):
-
+    """Plot the photometric SED, posterior samples of it, and
+    posterior samples of the intrinsic spectrum.
+    """
     if fax is None:
         sfig, sax = pl.subplots()
     else:

### 2015-04-29 code/paramfiles/mock_photonly.py

@@ -4,7 +4,7 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock',
+              'outfile':'results/ggc_mock_photonly',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
@@ -15,7 +15,7 @@ run_params = {'verbose':True,
               'normalize_spectrum':False,
               'norm_band_name':'sdss_g0',
               'rescale':False,
-              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t10.0_z0.0_a0.5.pkl',
+              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl',
               'wlo':3350.,
               'whi':6500.
               }
@@ -121,7 +121,7 @@ model_params.append({'name': 'imf3', 'N':1,
 ###### WAVELENGTH SCALE ######
 
 model_params.append({'name': 'zred', 'N':1,
-                        'isfree': True,
+                        'isfree': False,
                         'init': 0.0000,
                         'units': None,
                         'prior_function': priors.normal,

### 2015-04-29 code/paramfiles/mock_speconly_ideal.py

@@ -8,7 +8,7 @@ run_params = {'verbose':True,
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
-              'nburn':[64, 128, 256], 'niter':512,
+              'nburn':[16, 32, 32, 64, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
               'logify_spectrum':True,

### 2015-04-29 code/plot_data.py

@@ -1,0 +1,37 @@
+import numpy as np
+import matplotlib.pyplot as pl
+import ggcdata
+
+
+##### OBSERVATIONAL DATA ######
+
+if __name__ == "__main__":
+
+    try:
+        objname = sys.argv[1]
+    except:
+        objname = 'NGC7089'
+    try:
+        noisefactor = float(sys.argv[2])
+    except:
+        noisefactor = 1.0
+        print('noisefactor = 1')
+
+    datadir = '/Users/bjohnson/Projects/speccal/data/ggclib/spectra/'
+    dat = ggcdata.ggc_spec(datadir+objname, 'a', '1', fluxtype=None)
+    mdat = ggcdata.ggc_mask(dat, thresh=3)
+    mask = mdat['mask']
+    #skymask = ggcdata.make_skymask(dat['wavelength'],
+    #                               dat['sky'], thresh=3, lsf=6)
+    fig, ax = pl.subplots(3, 1, sharex=True, figsize=(5, 8))
+    ax[0].plot(dat['wavelength'][mask],
+               dat['spectrum'][mask]*1e14, label='Spectrum')
+    ax[0].set_ylabel(r'F$_\lambda$ ($10^{-14} erg\, s^{-1} cm^{-2} \AA^{-1}$)')
+    ax[1].plot(dat['wavelength'][mask],
+               dat['spectrum'][mask]/(dat['unc'][mask] * noisefactor), label='SNR')
+    ax[1].set_ylabel('S/N')
+    ax[2].plot(dat['wavelength'][mask], 1/dat['calibration'][mask]*1e18, label='cal')
+    ax[2].set_ylabel(r'Calibration (F$_\lambda/$counts)')
+    ax[2].set_xlabel(r'$\lambda (\AA)$')
+    fig.show()
+    fig.savefig('../tex/figures/data.pdf')

### 2015-04-29 tex/figures.tex
moving plotting code around, some caption text rewritten

@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/ideal.pdf}
 \caption{Results of inference from a mock spectrum and a single photometric data point where the spectrophotometric calibration is assumed to be perfectly known.
@@
 model parameters, including calibration parameters {\it green}.
-Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
-Posterior samples of the inferred calibration vector ({\it green}) include both
-the polynomial and the Gaussian Process mean prediction (Equation
-\ref{eq:calibration}).
+Bottom Left: The calibration vector. In this case the true calibration
+vector ({\it black}) is a constant and it is not inferred as part of
+the model
 Top Right: Samples of the posterior prediction for the
@@
 \caption{Results of inference from a \emph{perfectly calibrated} mock
-  spectrum and a single photometric data point.
+  spectrum and a single photometric data point, where uncertainties in
+  the calibration are modeled.
 Top Left: The mock observed spectrum ({\it black}) is shown as well as
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Results of inference from the photometric data only.
+\includegraphics[width=0.5 \textwidth]{figures/photonly.pdf}
+\caption{Results of inference from the photometric data only.  The
+  redshift is fixed {\color{blue} (should just use a tight prior)} and
+ spectroscopic calibration parameters are not modeled.
 Top: The intrinsic spectrum. Samples of the posterior prediction
@@
   points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
-\label{fig:speconly_calibrated}}
+\label{fig:specphot_uncalibrated}}
 \end{figure*}

### 2015-04-29 tex/ms.tex
moving plotting code around, some caption text rewritten

@@
 \bibliographystyle{apj}
-%\input{vc}
+\input{vc}
 
@@
 We model the stellar cluster as a single age SSP. The spectrum of a
-star cluster under this assumption is given by
+star cluster under this assumption is given by a vector
 \begin{eqnarray}\displaystyle
-F_{\theta^\prime}(\lambda_o) & = &
-\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
+f_{\theta_s}(\lambda_o) & = &
+\frac{m_*}{4\pi d_L^2(1+z)} \, L(\sigma_*, z) \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
 \nonumber \\ 
@@
 \\
-\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
+\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
 \quad ,
 \end{eqnarray} where the
-parameters $\theta^\prime$ include 
+parameters $\theta_s$ include 
 the stellar mass $m_*$, 
@@
 and redshift $z$.
+The matrix $L(\sigma_*, z)$ is a convolution kernel representing the
+stellar velocity profile,
+and $\sigma_*$ is the stellar velocity dispersion. 
 The shape of the dust attenuation curve is given by $k_\lambda \equiv
@@
 The spectrum of one solar mass of stars that formed at lookback time
-$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
+$t$ with metallicity $Z$ is given by $s(\lambda, t, Z [, \beta])$.
 Here the additional parameters $\beta$ may include details of the
@@
 therefore be treated as fixed.  In practice, $d_L$ is perfectly
-degenerate with $m_*$. We calculate $S(\lambda, t, Z)$ using the
+degenerate with $m_*$. We calculate $s(\lambda, t, Z)$ using the
 Flexible Stellar Population Synthesis code \citep[FSPS][]{fsps}.  We
@@
 clusters or from diffuse ionized gas) and interstellar absorption
-lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
-all of the same width $\sigma_e$ (which need not be the same as
-stellar broadening $\sigma$) and with known central wavelengths
-$\lambda_\ell$.  For emission lines the amplitudes are constrained to
-be positive, while for interstellar absorption (e.g. Na D and Ca K)
-the amplitudes are constrained to be negative. This framework can be
-easily extended to include more complex models for the nebular
-emission, such as allowing line dependent widths and velocities, and
-using Voight profiles for the line shapes.
+lines are modeled as a sum of $\delta$-functions of unknown amplitude
+$a_\ell$, and with known central wavelengths $\lambda_\ell$, broadened
+by the gas velocity profile, $\sigma_{gas}$.  For emission lines the
+amplitudes are constrained to be positive, while for interstellar
+absorption (e.g. Na D and Ca K) the amplitudes are constrained to be
+negative. This framework can be easily extended to include more
+complex models for the nebular emission, such as allowing line
+dependent widths and velocities, and using Voight profiles for the
+line shapes.
 
-The model spectra $F_{\theta^\prime}$ are smoothed by convolution with
+The model spectra $f_{\theta_s}$ are smoothed by convolution with
 the line-spread function of the spectrograph and are interpolated to
@@
 also be modeled. The instrumental resolution is given by the parameter
-$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
+$\sigma_{inst}$.  {\color{blue}Discuss intrinsic resolution of model spectra
 (MILES), what to do in situations where instrumental resolution is
@@
 \begin{eqnarray}\label{eq:MeanModel} 
-\mu(\theta) &  = & (LSF(\sigma_{inst}) \otimes F(\theta^\prime))(\lambda) +
-\sum_{\ell=0}^{N_\ell} S_\ell(\lambda) \\
-S_\ell (\lambda) & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
-\lambda_\ell)^2}{2\sigma_e^2}) \\
-\theta & \equiv & \left[ \{\theta^\prime\}, \sigma_{inst}, \{A_\ell\}_{\ell=0}^{N_l},
-  \sigma_e \right] \\
+\mu(\theta) &  = & L(\sigma_{inst}) \, \left[ f_{\theta_s}(\lambda_o)
+                   + f_{\theta_g}(\lambda_o) \right]\\
+f_{\theta_g}(\lambda_o) & = & L(\sigma_{gas}, z) \,  \{a_\ell\delta(\lambda-\lambda_\ell)\}\\
+\theta & \equiv & \left[ \{\theta_s\}, \{\theta_{g}\}, \sigma_{inst} \right]
 \quad ,
 \end{eqnarray}
-where $LSF(\sigma_{inst})$ represents the linespread function
-parameterized by $\sigma_{inst}$, 
-$\otimes$ indicates convolution, 
+where the matrix $L(\sigma_{inst})$ represents the convolution kernel
+for the instrumental linespread function parameterized by
+$\sigma_{inst}$,
 and the full parameter set $\theta$ now includes
 the instrumental broadening $\sigma_{inst}$ 
-and the dispersion $\sigma_e$ and
-amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
-absorption lines.
+and the gas-phase parameters $\theta_g$.
 This is the mean model which appears in equation
@@
 \item Mock perfectly calibrated data: inference using spectroscopy and one
-  photometric band, with both full calibration model and assuming no
-  calibration uncertainty.
+  photometric band, assuming no calibration uncertainty.  This is as
+  good as we could get given the data and its uncertainties.
+
+\item Mock perfectly calibrated data: inference using spectroscopy and one
+  photometric band, with the full calibration model.  This is how much
+  including additional calibration flexibility hurts the posterior
+  PDFs compared to perfectly known calibration.
 
 \item Mock uncalibrated data:  inference using spectroscopy and one
-  photometric band, with full calibration model
+  photometric band, with full calibration model.  This is how well we
+  can get the calibration \emph{and} the physical parameters with
+  spectroscopy only.
 
-\item Mock data: inference using photometry only
+\item Mock data: inference using photometry only.  This is how well we
+  can get the physical parameters using photometry only.
 
 \item Mock uncalibrated data: inference using spectroscopy and all
-  photometry, full calibration model.
+  photometry, full calibration model.  This is how well we
+  can get the calibration and physical parameters using spectroscopy
+  and photometry.
 
 \item Do this for a bunch of ages, metallicities, and dust
-  attenuations, possibly compare to the ideal posteriors.
+  attenuations, possibly compare to the ideal posteriors in each case.
 
 \item Real calibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model.
+  photometry, with full calibration model. The calibration vector
+  inferred will highlight differences between the calibrated spectrum
+  and the model (which could either be due to calibration problems or
+  model problems)
 
 \item Real uncalibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model.
+  photometry, with full calibration model. This is to show how much
+  the inferred physical parameters change when the calibration is
+  basically unknown.
 
@@
   based parameters.
+
+\item Mock uncalibrated data:  vary the photometric bands to see how
+  much it changes the recovery of the parameters.
+
+\item how (some) of these things vary with S/N
 
@@
 
-BDJ misc issues, collected here in case we want to address them and to
-keep me from cluttering up the main text: Model resolution and
-instrument resolution, ombinations of broadening in velocity space
-(physical) and in wavelength space (instrumental).  Photometric upper
-limits? Infer the wavelength solution as well - stellar population
-(and telluric lines) as your arc.
+{\color{blue} BDJ misc issues, collected here in case we want to
+address them and to keep me from cluttering up the main text:} Model
+resolution and instrument resolution, combinations of broadening in
+velocity space (physical) and in wavelength space (instrumental).
+Photometric upper limits? Infer the wavelength solution as well -
+stellar population (and telluric lines) as your arc.
 
@@
   from \url{http://github.com/bd-j/bsfh/}.
-%This version of the paper was generated
-%  from a git repository available at \url{http://github.com/bd-j/speccal/}
-%  with git hash \texttt{\githash\,(\gitdate)}.
+This version of the paper was generated
+  from a git repository available at \url{http://github.com/bd-j/speccal/}
+  with git hash \texttt{\githash\,(\gitdate)}.
 

### 2015-04-29 code/mock_figures.py

@@ -17,115 +17,6 @@ kernel = (george.kernels.WhiteKernel(0.0) +
 gp = george.GP(kernel, solver=george.HODLRSolver)
 
 
-def calfig(wave, calvec, specvecs, norm=1.0, fax=None):
-    """Plot the calibration and posterior samples of it
-    """
-    if fax is None:
-        cfig, cax = pl.subplots()
-    else:
-        cfig, cax = fax
-    #plot the calibration vector 
-    cax.plot(wave, calvec, color='black', label='Mock Truth',
-             linewidth=3.0)
-    # and posterior samples of it
-    for i, specs in enumerate(specvecs):
-        if i==0:
-            label = 'Posterior sample'
-        else:
-            label = None
-        cax.plot(wave, norm * np.exp(np.log(specs[1]) + specs[2]),
-                 color='green', alpha=0.3, label=label)
-    
-    return cfig, cax
-
-def obsfig(wave, obsvec, specvecs, unc=None, fax=None):
-    """Plot the observed spectrum and posterior samples of it
-    """
-    if fax is None:
-        ofig, oax = pl.subplots()
-    else:
-        ofig, oax = fax
-    # Plot posterior samples of the observed spectrum
-    for i, specs in enumerate(specvecs):
-        if i==0:
-            label = 'Posterior samples'
-        else:
-            label = None
-        oax.plot(wave, specs[3],
-                 color='green', alpha = 0.3, label=label)
-    #plot the observation itself
-    if unc is not None:
-        x, y, e = wave, obsvec, unc
-        oax.fill_between(x, y-e, y+e, facecolor='grey', alpha=0.3)
-    oax.plot(wave, obsvec, color='black', label='Mock Observed Spectrum',
-             linewidth=1.0, alpha=1.0)
-    return ofig, oax
-
-def sedfig(wave, specvecs, phot, photvecs, norm = 1.0, fax=None):
-    """Plot the photometric SED, posterior samples of it, and
-    posterior samples of the intrinsic spectrum.
-    """
-    if fax is None:
-        sfig, sax = pl.subplots()
-    else:
-        sfig, sax = fax
-    pwave, sed, sed_unc = phot
-    # to convert from f_lambda cgs/AA to lambda*f_lambda cgs
-    sconv = wave * norm
-    # to convert from maggies to nu * f_nu cgs
-    pconv = 3631e-23 * 2.998e18/pwave
-
[…]

### 2015-04-29 code/plot_data.py

@@ -14,9 +14,11 @@ if __name__ == "__main__":
     try:
         noisefactor = float(sys.argv[2])
     except:
-        noisefactor = 1.0
+        noisefactor = 10.0
         print('noisefactor = 1')
 
+    clr = 'black'
+    
     datadir = '/Users/bjohnson/Projects/speccal/data/ggclib/spectra/'
     dat = ggcdata.ggc_spec(datadir+objname, 'a', '1', fluxtype=None)
     mdat = ggcdata.ggc_mask(dat, thresh=3)
@@ -25,12 +27,15 @@ if __name__ == "__main__":
     #                               dat['sky'], thresh=3, lsf=6)
     fig, ax = pl.subplots(3, 1, sharex=True, figsize=(5, 8))
     ax[0].plot(dat['wavelength'][mask],
-               dat['spectrum'][mask]*1e14, label='Spectrum')
+               dat['spectrum'][mask]*1e14, label='Spectrum',
+               color = clr)
     ax[0].set_ylabel(r'F$_\lambda$ ($10^{-14} erg\, s^{-1} cm^{-2} \AA^{-1}$)')
     ax[1].plot(dat['wavelength'][mask],
-               dat['spectrum'][mask]/(dat['unc'][mask] * noisefactor), label='SNR')
+               dat['spectrum'][mask]/(dat['unc'][mask] * noisefactor), label='SNR',
+               color='black')
     ax[1].set_ylabel('S/N')
-    ax[2].plot(dat['wavelength'][mask], 1/dat['calibration'][mask]*1e18, label='cal')
+    ax[2].plot(dat['wavelength'][mask], 1/dat['calibration'][mask]*1e18, label='cal',
+               color=clr)
     ax[2].set_ylabel(r'Calibration (F$_\lambda/$counts)')
     ax[2].set_xlabel(r'$\lambda (\AA)$')
     fig.show()

### 2015-04-29 code/plotting.py

@@ -47,13 +47,13 @@ def comp_samples_phot(thetas, model, obs, sps=None):
 
 def comp_samples_fullspec(thetas, model, obs, sps=None, gp=None):
     specvecs = []
-    mospec, mounc = None
+    mospec, mounc = None, None
     fullobs = deepcopy(obs)
-    fullobs['wavelength'] = sps.wavelengths.copy()
+    fullobs['wavelength'] = sps.ssp.wavelengths.copy()
     fullobs['mask'] = np.ones( len(fullobs['wavelength']), dtype= bool)
     for theta in thetas:
-        mu, cal, delta, mask, wave = bread.model_comp(theta, model, obs, sps,
-                                                      gp=gp, photflag=0)
+        mu, cal, delta, mask, wave = bread.model_comp(theta, model, fullobs, sps,
+                                                      gp=None, photflag=0)
         cal = np.exp(cal)
         full_cal = np.exp(np.log(cal) + delta)
         mod = np.exp(np.log(mu) + np.log(cal) + delta)
@@ -67,10 +67,11 @@ def true_sed(model, obs, sps=None, fullspec=False):
     model.params = mockpars
     theta = model.theta.copy()
     if fullspec:
-        fullobs['wavelength'] = sps.wavelengths.copy()
+        fullobs['wavelength'] = sps.ssp.wavelengths.copy()
         fullobs['mask'] = np.ones( len(fullobs['wavelength']), dtype= bool)
-
+        
     mu, phot, x = model.sed(theta, fullobs, sps=sps)
+    return mu, phot
         
 def theta_samples(res, samples=[1.0], start=0.0, thin=1):
 
@@ -82,3 +83,116 @@ def theta_samples(res, samples=[1.0], start=0.0, thin=1):
     ns = flatchain.shape[0]
     thetas = [flatchain[s,:] for s in np.floor(np.array(samples) * (ns-1)).astype(int)]
     return thetas, start_index, np.floor(np.array(samples) * (ns-1)).astype(int)
+
+def calfig(wave, calvec, specvecs, norm=1.0, fax=None):
+    """Plot the calibration and posterior samples of it
+    """
+    if fax is None:
+        cfig, cax = pl.subplots()
+    else:
+        cfig, cax = fax
+    #plot the calibration vector 
+    cax.plot(wave, calvec, color='black', label='Mock Truth',
+             linewidth=3.0)
+    # and posterior samples of it
+    for i, specs in enumerate(specvecs):
[…]

### 2015-04-29 code/paramfiles/mock_cal.py
change parameter files around, start on joint pdf plot

@@ -1,195 +1,0 @@
-import numpy as np
-import pickle, os
-from bsfh import priors, sedmodel
-from sedpy import attenuation
-
-run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_cal',
-              'do_powell': False,
-              'ftol':0.5e-4, 'maxfev':5000,
-              'nwalkers':32,
-              'nburn':[64, 128, 256], 'niter':512,
-              'initial_disp':0.1,
-              'debug':False,
-              'logify_spectrum':True,
-              'normalize_spectrum':True,
-              'norm_band_name':'sdss_g0',
-              'rescale':True,
-              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t1.0_z0.0_a0.5.pkl',
-              'wlo':3350.,
-              'whi':6500
-              }
-
-##### OBSERVATIONAL DATA ######
-with open(run_params['filename']) as f:
-    obs = pickle.load(f)
-
-###### MODEL ###########
-model_type = sedmodel.SedModel
-
-model_params = []
-
-###### Distance ##########
-model_params.append({'name': 'lumdist', 'N': 1,
-                     'isfree': False,
-                     'init': 0.01,
-                     'units': 'Mpc',
-                     'prior_function': None,
-                     'prior_args': None})
-
-###### SFH ################
-
-model_params.append({'name': 'mass', 'N': 1,
-                     'isfree': True,
-                     'init': 2e5,
-                     'units': r'M$_\odot$',
-                     'prior_function': priors.tophat,
-                     'prior_args': {'mini':1e4, 'maxi': 1e6}})
-
-model_params.append({'name': 'tage', 'N': 1,
-                        'isfree': True,
-                        'init': 5.0,
-                        'units': 'Gyr',
-                        'prior_function': priors.tophat,
-                        'prior_args':{'mini':0.1, 'maxi':15.0}})
-
-model_params.append({'name': 'zmet', 'N': 1,
-                        'isfree': True,
-                        'init': -0.5,
-                        'units': r'$\log (Z/Z_\odot)$',
-                        'prior_function': priors.tophat,
-                        'prior_args': {'mini':-2, 'maxi':0.19}})
-
-model_params.append({'name': 'sfh', 'N':1,
-                        'isfree': False,
-                        'init': 0,
-                        'units': None})
-
-###### DUST ##################
-
-model_params.append({'name': 'dust_curve', 'N': 1,
[…]

### 2015-04-29 code/paramfiles/mock_specphot.py

@@ -4,30 +4,34 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock',
+              'outfile':'results/ggc_mock_u0_t9.0_z0.0_a0.5',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
-              'nburn':[64, 128, 256], 'niter':512,
+              'nburn':[64, 64, 128, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
               'logify_spectrum':True,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,
-              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t1.0_z0.0_a0.5.pkl',
+              'filename':'/Users/bjohnson/Projects/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl',
               'wlo':3350.,
-              'whi':6500.
+              'whi':6500.,
+              'noisefactor':10
               }
 
 ##### OBSERVATIONAL DATA ######
 
-def load_obs(filename=run_params['filename'], **extras):
+def load_obs(filename=None, noisefactor=1.0, **extras):
     with open(filename) as f:
         obs = pickle.load(f)
+    #obs['phot_mask'] = np.array(['sdss_g' in filt.name for filt in obs['filters']])
+    obs['unc'] *= noisefactor
+    obs['noisefactor'] = noisefactor
     return obs
 
-obs = load_obs()
+obs = load_obs(**run_params)
 
 ###### MODEL ###########
 model_type = sedmodel.SedModel
@@ -121,7 +125,7 @@ model_params.append({'name': 'imf3', 'N':1,
 
 model_params.append({'name': 'zred', 'N':1,
                         'isfree': True,
-                        'init': 0.0000,
+                        'init': 0.000001,
                         'units': None,
                         'prior_function': priors.tophat,
                         'prior_args': {'mini':-0.001, 'maxi':0.001}})

### 2015-04-29 code/plot_joint_posterior.py

@@ -1,0 +1,29 @@
+import sys, pickle
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib import gridspec
+
+from bsfh import read_results as bread
+from bsfh import sps_basis
+from bsfh.gp import GaussianProcess
+
+
+
+if __name__ == "__main__":
+    photonly = ''
+    speconly = ''
+    specphot = ''
+
+    results = [bread.read_pickles(rfile, model_file=rfile.replace('mcmc','model'))[0]
+               for rfile in resfiles]
+
+    showpars = np.array(['mass', 'tage', 'zmet', 'dust2'])
+
+    gs2 = gridspec.GridSpec(4, 2)
+    for i, p1 in enumerate(showpars):
+        for j, p2 in enumerate(showpars[i:])
+            k = j+i
+            ax = axes[i, k]
+            pdf = joint_pdf(res, p1, p2)
+            
+    

### 2015-04-30 tex/figures.tex
change parameter files around, start on joint pdf plot
working joint posterior plotting

@@
 \includegraphics[width=\textwidth]{figures/ideal.pdf}
-\caption{Results of inference from a mock spectrum and a single photometric data point where the spectrophotometric calibration is assumed to be perfectly known.
+\caption{Results of inference from a mock spectrum and a single
+  photometric data point where the spectrophotometric calibration is
+  assumed to be perfectly known. 
 Top Left: The mock observed spectrum ({\it black}) is shown as well as
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/speconly_calibrated.pdf}
 \caption{Results of inference from a \emph{perfectly calibrated} mock
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/speconly_uncalibrated.pdf}
 \caption{Results of inference from an \emph{uncalibrated} mock
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+%\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
 \caption{Results of inference from the combination of
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/combined_post.pdf}
 \caption{Joint posterior PDFs for several physical parameters. The
-  posteriors obtained from photometry only is in {\it red}, from
-  \emph{uncalibrated} spectroscopy and a single photometric point in {\it blue}, and from
-  the photometry and spectroscopy combined in {\it magenta}.
+  posteriors obtained from photometry only are in {\it blue}, from
+  \emph{uncalibrated} spectroscopy and a single photometric point in {\it red}, and from
+  the photometry and spectroscopy combined in {\it magenta}.  The
+  contours are 1 and 2-sigma contours. The true
+  values are indicated by {\it black points}.
 \label{fig:combined_posterior}}

### 2015-04-30 code/paramfiles/mock_specphot.py

@@ -7,7 +7,7 @@ from sedpy import attenuation
 sdir = os.path.join.(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_u0_t9.0_z0.0_a0.5',
+              'outfile':'results/ggc_mock_specphot_u0_t9.0_z0.0_a0.5',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 

### 2015-04-30 code/plot_joint_posterior.py

@@ -4,27 +4,88 @@ import matplotlib.pyplot as pl
 from matplotlib import gridspec
 
 from bsfh import read_results as bread
-from bsfh import sps_basis
-from bsfh.gp import GaussianProcess
+from plotting import *
 
-def joint_pdf():
-    pass
+def joint_pdf(res, p1, p2, **kwargs):
+    trace, pars = hist_samples(res, res['model'], [p1, p2], **kwargs)
+    trace = trace.copy().T
+    xbins, ybins, sigma = compute_sigma_level(trace[0], trace[1])
+    return xbins, ybins, sigma.T
+
+
+def compute_sigma_level(trace1, trace2, nbins=20):
+    """From a set of traces, bin by number of standard deviations"""
+    L, xbins, ybins = np.histogram2d(trace1, trace2, nbins)
+    L[L == 0] = 1E-16
+    logL = np.log(L)
+
+    shape = L.shape
+    L = L.ravel()
+
+    # obtain the indices to sort and unsort the flattened array
+    i_sort = np.argsort(L)[::-1]
+    i_unsort = np.argsort(i_sort)
+
+    L_cumsum = L[i_sort].cumsum()
+    L_cumsum /= L_cumsum[-1]
+    
+    xbins = 0.5 * (xbins[1:] + xbins[:-1])
+    ybins = 0.5 * (ybins[1:] + ybins[:-1])
+
+    return xbins, ybins, L_cumsum[i_unsort].reshape(shape)
+
 
 if __name__ == "__main__":
-    photonly = ''
-    speconly = ''
+    photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
+    speconly = 'results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430010665_mcmc'
     specphot = ''
-
+    resfiles = [photonly, speconly]#, specphot]
+    clr = ['red','blue', 'magenta']
     results = [bread.read_pickles(rfile, model_file=rfile.replace('mcmc','model'))[0]
                for rfile in resfiles]
-
+    obsdat = results[0]['obs']
     showpars = np.array(['mass', 'tage', 'zmet', 'dust2'])
+    npar = len(showpars)
 
-    gs2 = gridspec.GridSpec(4, 2)
-    for i, p1 in enumerate(showpars):
-        for j, p2 in enumerate(showpars[i:])
-            k = j+i
-            ax = axes[i, k]
[…]

### 2015-04-30 code/plotting.py

@@ -162,7 +162,7 @@ def sedfig(wave, specvecs, phot, photvecs, norm = 1.0, fax=None, peraa=False):
     sax.set_ylabel(ylabel)
     return sfig, sax
 
-def hist_samples(res, model, showpars, start=0, thin=1, **kwargs):
+def hist_samples(res, model, showpars, start=0, thin=1, **extras):
     
     nw, niter = res['chain'].shape[:-1]
     parnames = np.array(model.theta_labels())

### 2015-04-30 tex/ms.tex
working joint posterior plotting
fix bugs in uncertainties plotting for dashboards and in setting the speccal directory in paramfiles, add text about photometry beyond the spectra even with perfect spec cal

@@
 described above to both \emph{mock} and \emph{real} optical spectra of
-Galactic globular clusters.  Spectra of globular clusters provide a good test case,
-as they are less complex than galaxy spectra (for which it is
-necessary to model the star formation history) but are by no means
-trivial. In this way the key features of the calibration model and
-methodology are not obscured.  Additionally, information
+Galactic globular clusters.  Spectra of globular clusters provide a
+good test case, as they are less complex than galaxy spectra (for
+which it is necessary to model the star formation history) but are by
+no means trivial. In this way the key features of the calibration
+model and methodology are not obscured.  Additionally, information
 about the physical parameters of the cluster is available from
-resolved stellar CMDs, providing an important check on our inference methodology
-and especially our population synthesis models.
+resolved stellar CMDs, providing an important check on our inference
+methodology and especially our population synthesis models.
 
@@
 $\theta$ from a spectrum both \emph{before} and \emph{after} it has
-been spectrophotometrically calibrated using and
-ancillary spectrophotometric calibration data.
+been spectrophotometrically calibrated using and ancillary
+spectrophotometric calibration data.
 
@@
 vector) is shown in Figure \ref{fig:ggc_data}.  As stated by
-\citet{schiavon05}, the spectrophotometric calibration of these data are
-only approximate.  When fitting the spectra we mask the region around
-the bright OI5577\AA~ sky line, and we fit only to the spectrum with $3550\AA
-< \lambda < 6500$\AA~ which are covered by the MILES spectral library
-(see \S\ref{sec:cluster_model}).  Absorption lines of the interstellar
-medium (ISM) can significantly affect the spectrum, so we
-additionally mask the Calcium H and K lines and the NaD doublet.
+\citet{schiavon05}, the spectrophotometric calibration of these data
+are only approximate.  When fitting the spectra we mask the region
+around the bright OI5577\AA~ sky line, and we fit only to the spectrum
+with $3550\AA < \lambda < 6500$\AA~ which are covered by the MILES
+spectral library (see \S\ref{sec:cluster_model}).  Absorption lines of
+the interstellar medium (ISM) can significantly affect the spectrum,
+so we additionally mask the Calcium H and K lines and the NaD doublet.
 
@@
 described in below (\S\ref{sec:cluster_model}, equation
-\ref{eq:MeanModel}) for a given set of parameters $\theta^\prime$.  We
-then convolve the spectrum with an instrumenal LSF, interpolate onto
-the observed wavelength scale and add noise according to the SNR of
-the real data.  For the photometry we assume a SNR of 10.  We also
-mask the mock spectra at the location of significant sky lines and ISM
+\ref{eq:StarModel}) for a given set of parameters $\theta_s$.  We then
+convolve the spectrum with an instrumenal LSF, interpolate onto the
+observed wavelength scale and add noise according to the SNR of the
+real data.  For the photometry we assume a SNR of 10.  We also mask
+the mock spectra at the location of significant sky lines and ISM
 lines that are present in the real data.
@@
 star cluster under this assumption is given by a vector
-\begin{eqnarray}\displaystyle
+\begin{eqnarray} \label{eq:StarModel}\displaystyle
 f_{\theta_s}(\lambda_o) & = &
@@
 and the full parameter set $\theta$ now includes
-the instrumental broadening $\sigma_{inst}$ 
+this instrumental broadening $\sigma_{inst}$ 
 and the gas-phase parameters $\theta_g$.
@@
 We do not resort to an arbitrary down-weighting or up-weighting of
-certain data. Instead, we explicitly model our uncertain knowledge of
-the spectral calibration and infer this calibration jointly with the
-physical properties. For a number of applications this combination of
-spectroscopy and photometry reduces the need for spectrophotometric
-calibration entirely, such that the less expensive photometric
-calibration is sufficient.  Additional calibration information, if it
-exists, can be incorporated into informative priors on the calibration
-parameters of the model, inform the construction of the calibration
-model (including the form of the covariance kernel), or approximately
-remove gross features that are difficult to model parametrically or
-via a Gaussian Process.  {\color{blue} Discuss more complicated
-covariance kernels, multiple kernels}
+certain data. Instead, we explicitly and flexibly model our uncertain
+knowledge of the spectral calibration and infer this calibration
+jointly with the physical properties. For a number of applications
+this combination of spectroscopy and photometry reduces the need for
+spectrophotometric calibration entirely, such that the less expensive
+photometric calibration is sufficient.  Additional calibration
+information, if it exists, can be incorporated into informative priors
+on the calibration parameters of the model, inform the construction of
+the calibration model (including the form of the covariance kernel),
+or approximately remove gross features that are difficult to model
+parametrically or via a Gaussian Process.  {\color{blue} Discuss more
+complicated covariance kernels, multiple kernels.}
 
-{\color{blue} BDJ words about the gains that might be made by
-including photometry over a large range in wavelength with spectroscopy
-over relatively small ranges.}
+{\color{blue} BDJ words (and experiments?) about the gains that might
+be made by including photometry over a large range in wavelength with
+spectroscopy over relatively small ranges.}  In this case even with
+perfectly known spectrophotometric calibration, the photometry would
+in principle add information.  This would occur if models with very
+similar spectra in the observed range had differing SEDs outside that
+range.
 

### 2015-04-30 code/paramfiles/mock_photonly.py

@@ -4,7 +4,7 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 #The speccal directory
-sdir = os.path.join.(os.environ['PROJECTS'], 'speccal')
+sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
               'outfile':'results/ggc_mock_photonly',

### 2015-04-30 code/paramfiles/mock_speconly_losn.py

@@ -4,7 +4,7 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 #The speccal directory
-sdir = os.path.join.(os.environ['PROJECTS'], 'speccal')
+sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
               'outfile':'results/ggc_mock_c0_t9.0_z0.0_a0.5',

### 2015-04-30 code/paramfiles/mock_specphot.py

@@ -4,7 +4,7 @@ from bsfh import priors, sedmodel
 from sedpy import attenuation
 
 #The speccal directory
-sdir = os.path.join.(os.environ['PROJECTS'], 'speccal')
+sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
               'outfile':'results/ggc_mock_specphot_u0_t9.0_z0.0_a0.5',

### 2015-04-30 code/plot_joint_posterior.py

@@ -38,8 +38,8 @@ def compute_sigma_level(trace1, trace2, nbins=20):
 if __name__ == "__main__":
     photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
     speconly = 'results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430010665_mcmc'
-    specphot = ''
-    resfiles = [photonly, speconly]#, specphot]
+    specphot = 'results/ggc_mock_specphot.u0.t9.0_z0.0_a0.5_1430380402_mcmc'
+    resfiles = [photonly, speconly, specphot]
     clr = ['red','blue', 'magenta']
     results = [bread.read_pickles(rfile, model_file=rfile.replace('mcmc','model'))[0]
                for rfile in resfiles]
@@ -53,7 +53,7 @@ if __name__ == "__main__":
     for i, p1 in enumerate(showpars):
         dax = pl.subplot(gs[i,i])
         for n, res in enumerate(results):
-            trace, p = hist_samples(res, res['model'], [p1])
+            trace, p = hist_samples(res, res['model'], [p1], start=0.5)
             dax.hist(trace, bins = 50, color=clr[n], normed=True,
                      alpha=0.5, histtype='stepfilled')
             if i == 0:
@@ -73,7 +73,7 @@ if __name__ == "__main__":
             print('*****')
 
             for n, res in enumerate(results):
-                pdf = joint_pdf(res, p2, p1)
+                pdf = joint_pdf(res, p2, p1, start=0.5)
                 ax.contour(pdf[0], pdf[1], pdf[2], levels = [0.683, 0.955], colors=clr[n])
             if i == 0:
                 ax.set_ylabel(p2)

### 2015-04-30 code/plotting.py

@@ -30,7 +30,7 @@ def comp_samples(thetas, model, obs, sps=None, gp=None):
                        np.exp(np.log(mospec)-np.log(mod)),
                        (np.log(mospec)-np.log(mod)) / mounc] ]
             
-    return wave, mospec, mounc, specvecs
+    return wave, mospec, mounc*mospec, specvecs
 
 def comp_samples_phot(thetas, model, obs, sps=None):
     specvecs = []

### 2015-05-01 tex/ms.tex
expand gp length priors

@@
 HOGG: A model is a parameterized likelihood function, with prior PDFs on the nuisance parameters (at least)...
-
-HOGG: There is a likelihood for the photometry and for the spectroscopy...
-
-HOGG: Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...
+There is a likelihood for the photometry and for the spectroscopy...
+Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...
 
@@
 algorithm we use is the affine-invariant ensemble sampling scheme of
-\citet{goodman}, as implemented in the \texttt{emcee} package \citep{emcee}
-Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
-sampler does not require the specification of step sizes in each
-dimension.  {\color{blue}ASSESSING SAMPLER CONVERGENCE}
+\citet{goodman}, as implemented in the \texttt{emcee} package
+\citep{emcee} Unlike typical Metropolis-Hastings MCMC sampling, the
+affine-invariant sampler does not require the specification of step
+sizes in each dimension.
 
@@
 the prior probability of that parameter position to obtain an estimate
-of the posterior probability for those parameters given the data.
+of the posterior probability for those parameters given the
+data. {\color{blue}Assessing sampler convergence.}
 
@@
 spectral models of astrophysical objects, then there is often no
-reason not to use those objects themselves as calibration objects
-(especially if you expect your calibration to be spatially or
-temporally variable, or to change with the brightness of the object)
+reason not to use those objects themselves as calibration objects,
+especially if you expect your calibration to be spatially or 
+temporally variable, or to change with the brightness of the object.
 

### 2015-05-01 code/mock_figures_photonly.py

@@ -31,56 +31,45 @@ if __name__ == "__main__":
     
     fsamples = np.random.uniform(0,1,nsample)
     thetas, start, samples = theta_samples(res, samples=fsamples, start=0.75, thin=1)
-    fwave, _, _, fspecvecs = comp_samples_fullspec(thetas, mod, obsdat,
-                                                   sps=sps, gp=None)
-    mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat, sps=sps,
-                                                  gp=gp)
+    fwave, mospec, mounc, specvecs = comp_samples_fullspec(thetas, mod, obsdat, sps=sps,
+                                                  gp=None)
     pwave, mosed, mosed_unc, pvecs = comp_samples_phot(thetas, mod, obsdat, sps=sps)
 
     tspec, tphot, ttheta = true_sed(mod, obsdat, sps=sps, fullspec=True)
     twave = sps.ssp.wavelengths
-    tspec /= obsdat['normalization_guess']
     
-    calvec = obsdat['calibration']
-    if np.size(calvec) == 1:
-        calvec = np.zeros(len(mwave)) + calvec
-    else:
-        calvec = calvec[obsdat['mask']]
-    norm = obsdat['normalization_guess'] * obsdat['rescale']
+    #calvec = np.copy(obsdat['calibration'])
+    #if np.size(calvec) == 1:
+    #    calvec = np.zeros(len(fwave)) + calvec
+    #else:
+    #    calvec = calvec[obsdat['mask']]
+    #norm = obsdat['normalization_guess'] * obsdat['rescale']
 
-    fig = pl.figure(figsize=(10,8))
-    gs1 = gridspec.GridSpec(3, 1)
-    gs1.update(left=0.05, right=0.48, wspace=0.05)
-    oax = pl.subplot(gs1[:-1,0])
-    cax = pl.subplot(gs1[-1,0])
+    obsdat['normalization_guess'] = 1.0
+    fig = pl.figure(figsize=(6,8))
+    #gs1 = gridspec.GridSpec(3, 1)
+    #gs1.update(left=0.05, right=0.48, wspace=0.05)
+    #oax = pl.subplot(gs1[:-1,0])
+    #cax = pl.subplot(gs1[-1,0])
     
     gs2 = gridspec.GridSpec(4, 2)
-    gs2.update(left=0.55, right=0.98, hspace=0.5)
[…]

### 2015-05-01 code/paramfiles/mock_speconly.py

@@ -199,7 +199,7 @@ model_params.append({'name': 'gp_length', 'N':1,
                         'init': 60.0,
                         'units': r'$\AA$',
                         'prior_function': priors.lognormal,
-                        'prior_args': {'log_mean':np.log(100.0)+0.1**2, 'sigma':0.1}})
+                        'prior_args': {'log_mean':np.log(100.0)+0.75**2, 'sigma':0.75}})
 
 model_params.append({'name': 'phot_jitter', 'N':1,
                         'isfree': False,

### 2015-05-01 code/paramfiles/mock_speconly_losn.py

@@ -199,11 +199,12 @@ model_params.append({'name': 'gp_amplitude', 'N':1,
 
 model_params.append({'name': 'gp_length', 'N':1,
                         'isfree': True,
-                        'init': 60.0,
+                        'init': 100.0,
                         'units': r'$\AA$',
-                        'prior_function': priors.lognormal,
-                        'prior_args': {'log_mean':np.log(100.0)+0.1**2, 'sigma':0.1}})
-
+                        #'prior_function': priors.lognormal,
+                        #'prior_args': {'log_mean':np.log(100.0)+0.75**2, 'sigma':0.75}})
+                        'prior_function':priors.tophat,
+                        'prior_args': {'mini':10.0, 'maxi':1000}
 model_params.append({'name': 'phot_jitter', 'N':1,
                         'isfree': False,
                         'init': 0.0,

### 2015-05-01 code/paramfiles/mock_specphot.py

@@ -202,7 +202,7 @@ model_params.append({'name': 'gp_length', 'N':1,
                         'init': 60.0,
                         'units': r'$\AA$',
                         'prior_function': priors.lognormal,
-                        'prior_args': {'log_mean':np.log(100.0)+0.1**2, 'sigma':0.1}})
+                        'prior_args': {'log_mean':np.log(100.0)+0.75**2, 'sigma':0.75}})
 
 model_params.append({'name': 'phot_jitter', 'N':1,
                         'isfree': False,

### 2015-05-01 code/plotting.py

@@ -71,7 +71,7 @@ def true_sed(model, obs, sps=None, fullspec=False):
         fullobs['mask'] = np.ones( len(fullobs['wavelength']), dtype= bool)
         
     mu, phot, x = model.sed(theta, fullobs, sps=sps)
-    return mu, phot
+    return mu, phot, theta
         
 def theta_samples(res, samples=[1.0], start=0.0, thin=1):
 
@@ -162,16 +162,21 @@ def sedfig(wave, specvecs, phot, photvecs, norm = 1.0, fax=None, peraa=False):
     sax.set_ylabel(ylabel)
     return sfig, sax
 
-def hist_samples(res, model, showpars, start=0, thin=1, **extras):
+def hist_samples(res, model, showpars, start=0, thin=1,
+                 return_lnprob=False, **extras):
     
     nw, niter = res['chain'].shape[:-1]
     parnames = np.array(model.theta_labels())
     start_index = np.floor(start * (niter-1)).astype(int)
     flatchain = res['chain'][:,start_index::thin,:]
-    flatchain = flatchain.reshape(flatchain.shape[0] * flatchain.shape[1],
-                                  flatchain.shape[2])
+    dims = flatchain.shape[0], flatchain.shape[1], flatchain.shape[2]
+    flatchain = flatchain.reshape(dims[0]*dims[1], dims[2])
     ind_show = np.array([p in showpars for p in parnames], dtype= bool)
-    flatchain = flatchain[:,ind_show]
+    flatchain = flatchain[:, ind_show]
+    if return_lnprob:
+        flatlnprob = res['lnprobability'][:, start_index::thin].reshape(dims[0]*dims[1])
+        return flatchain, parnames[ind_show], flatlnprob
+    
     return flatchain, parnames[ind_show]
 
 def histfig(samples, parnames, truths=None, fax=None, truth_color='k', **kwargs):

### 2015-05-06 tex/ms.tex
real obs param file, homogenize burn-in sequnces, fixes for non-george GP plotting

@@
 \usepackage{color, hyperref}
+\usepackage[normalem]{ulem}
 \bibliographystyle{apj}
@@
 f_{\theta_s}(\lambda_o) & = &
-\frac{m_*}{4\pi d_L^2(1+z)} \, L(\sigma_*, z) \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
+L(\sigma_s, z) ,\, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
 \nonumber \\ 
@@
 and redshift $z$.
-The matrix $L(\sigma_*, z)$ is a convolution kernel representing the
+The matrix $L(\sigma_s, z)$ is a convolution kernel representing the
 stellar velocity profile,
-and $\sigma_*$ is the stellar velocity dispersion. 
+and $\sigma_s$ is the stellar velocity dispersion. 
 The shape of the dust attenuation curve is given by $k_\lambda \equiv
@@
 
-\item Mock perfectly calibrated data: inference using spectroscopy and one
+\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
   photometric band, assuming no calibration uncertainty.  This is as
-  good as we could get given the data and its uncertainties.
+  good as we could get given the data and its uncertainties.}
 
-\item Mock perfectly calibrated data: inference using spectroscopy and one
+\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
   photometric band, with the full calibration model.  This is how much
   including additional calibration flexibility hurts the posterior
-  PDFs compared to perfectly known calibration.
+  PDFs compared to perfectly known calibration.}
 
-\item Mock uncalibrated data:  inference using spectroscopy and one
+\item \sout{Mock uncalibrated data:  inference using spectroscopy and one
   photometric band, with full calibration model.  This is how well we
   can get the calibration \emph{and} the physical parameters with
-  spectroscopy only.
+  spectroscopy only.}
 
-\item Mock data: inference using photometry only.  This is how well we
-  can get the physical parameters using photometry only.
+\item \sout{Mock data: inference using photometry only.  This is how well we
+  can get the physical parameters using photometry only.}
 
-\item Mock uncalibrated data: inference using spectroscopy and all
+\item \sout{Mock uncalibrated data: inference using spectroscopy and all
   photometry, full calibration model.  This is how well we
   can get the calibration and physical parameters using spectroscopy
-  and photometry.
+  and photometry.}
 

### 2015-05-06 code/diagnostic_figures.py

@@ -3,7 +3,7 @@ import numpy as np
 import matplotlib.pyplot as pl
 
 import bsfh.read_results as bread
-from bsfh.gp import GaussianProcess
+from bsfh.gp import ExpSquared as GaussianProcess
 from bsfh import sps_basis
 sps = sps_basis.StellarPopBasis()
 gp = GaussianProcess(None, None)

### 2015-05-06 code/paramfiles/mock_speconly.py

@@ -11,7 +11,7 @@ run_params = {'verbose':True,
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
-              'nburn':[64, 128, 256], 'niter':512,
+              'nburn':[64, 64, 128, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
               'logify_spectrum':True,

### 2015-05-06 code/paramfiles/real_specphot.py

@@ -2,15 +2,16 @@ import numpy as np
 import pickle, os
 from bsfh import priors, sedmodel
 from sedpy import attenuation
+from ggcdata import *
 
 #The speccal directory
 sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_specphot_u0_t9.0_z0.0_a0.5',
+              'outfile':'results/ggc_ngc7089',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
-              'nwalkers':64, 
+              'nwalkers':64,
               'nburn':[64, 64, 128, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
@@ -18,7 +19,7 @@ run_params = {'verbose':True,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,
-              'filename':os.path.join(sdir, 'data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl'),
+              'objname':'NGC7089',
               'wlo':3350.,
               'whi':6500.,
               'noisefactor':10
@@ -26,10 +27,22 @@ run_params = {'verbose':True,
 
 ##### OBSERVATIONAL DATA ######
 
-def load_obs(filename=None, noisefactor=1.0, **extras):
-    with open(filename) as f:
-        obs = pickle.load(f)
-    #obs['phot_mask'] = np.array(['sdss_g' in filt.name for filt in obs['filters']])
+def load_obs(objname=None, noisefactor=1.0, calibrated=True,
+             mask=True, **extras):
+    # get the spectrum
+    if calibrated:
+        fluxtype=None
+    else:
+        fluxtype=1
+    obs = ggc_spec(objname, 'a', '1', fluxtype=fluxtype,
+                   datadir=os.path.join(sdir, 'data/ggclib/spectra'), **extras)
+    #mask the spectrum
+    if mask:
+        obs = ggc_mask(obs)
+    #add the photometric data
+    obs.update(ggc_phot(objname, datadir=os.path.join(sdir, 'data/ggclib/photometry')))
+    obs['phot_mask'] = np.array(['sdss' in filt.name for filt in obs['filters']])
+    #adjust uncertainties
     obs['unc'] *= noisefactor
     obs['noisefactor'] = noisefactor
     return obs

### 2015-05-06 code/plot_joint_posterior.py

@@ -37,7 +37,7 @@ def compute_sigma_level(trace1, trace2, nbins=20):
 
 if __name__ == "__main__":
     photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
-    speconly = 'results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1430517825_mcmc'
+    speconly = 'results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430808300_mcmc'
     specphot = 'results/ggc_mock_specphot.u0.t9.0_z0.0_a0.5_1430380402_mcmc'
     resfiles = [photonly, speconly, specphot]
     clr = ['red','blue', 'magenta']

### 2015-05-11 tex/figures.tex
fix bugs in uncertainties plotting for dashboards and in setting the speccal directory in paramfiles, add text about photometry beyond the spectra even with perfect spec cal
param file and plotting code for real data

--- 2015-04-29 tex/figures.tex
@@
 \includegraphics[width=\textwidth]{figures/ideal.pdf}
-\caption{Results of inference from a mock spectrum and a single photometric data point where the spectrophotometric calibration is assumed to be perfectly known.
+\caption{Results of inference from a mock spectrum and a single
+  photometric data point where the spectrophotometric calibration is
+  assumed to be perfectly known. 
 Top Left: The mock observed spectrum ({\it black}) is shown as well as
 YY model spectra constructed from draws from the posterior PDFs of the
-model parameters, including calibration parameters {\it green}.
-Bottom Left: The calibration vector. In this case the true calibration
-vector ({\it black}) is a constant and it is not inferred as part of
-the model
-Top Right: Samples of the posterior prediction for the
-\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
-({\it magenta}).  The true mock photometry is also shown ({\it
-black}).
+model parameters.
 Bottom Right: Marginalized posterior PDFs for several of the physical
 parameters of interest.  The input mock parameters are shown as
-vertical lines.
+vertical black lines.
+{\color{red} Remove calibration plot and intrinsic plot, since it is
+  the same as observed spectrum.  Show residuals.}
 \label{fig:speconly_ideal}}
@@
 vertical lines.
+ {\color{red} This is not converged.  mass and dust2 PDFs will become
+   much broader.}
 \label{fig:speconly_calibrated}}
@@
   calibration vector is not a constant with wavelength.
+ {\color{red} This is not converged.}
 \label{fig:speconly_uncalibrated}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
 \caption{Results of inference from the combination of
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
+\includegraphics[width=\textwidth]{figures/combined_post.pdf}
 \caption{Joint posterior PDFs for several physical parameters. The
-  posteriors obtained from photometry only is in {\it red}, from
-  \emph{uncalibrated} spectroscopy and a single photometric point in {\it blue}, and from
-  the photometry and spectroscopy combined in {\it magenta}.
+posteriors obtained from photometry only are in {\it red}, from
+\emph{uncalibrated} spectroscopy and a single photometric point in
+{\it blue}, and from the photometry and spectroscopy combined in {\it
+magenta}.  The contours are 1 and 2-sigma contours. The true values
+are indicated by {\it black points}.
 \label{fig:combined_posterior}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Posterior PDFs obtained from mock spectra and photometry
-  created with  a variety of mock physical parameters, as a function
-  of those parameters.
+%\includegraphics[width=\textwidth]{figures/vary_params.pdf}
+\caption{Offset from the input parameters of the medians of the
+posterior PDFs for model parameters obtained from mock spectra and
+photometry. Lines connect a single model.
  \label{fig:mock_parameter_space}}
 \end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\caption{The value of more photometry. Marginalized posterior PDFs
+obtained from mock spectra and photometry, for different numbers of
+photometric bands.  The pdfs $g$-band only ({\it red}), $g$- and $i-$
+band ({\it blue}), and the combined SDSS $griz$ and 2MASS $JHK_s$ set of
+bands ({\it orange}).
+\label{fig:vary_phot}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\caption{Inference from a real, calibrated, spectrum.  Top left:
+  Observed spectrum and posterior samples thereof.  Bottom left:
+  residuals.  Top right: inferred calibration vector, samples.
+  Bottom right: posterior PDFs (corner plot?) for physical parameters.
+\label{fig:real_calibrated}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\caption{Inference from a real, uncalibrated, spectrum.  Top left:
+  Observed spectrum and posterior samples thereof.  Bottom left:
+  residuals.  Top right: inferred calibration vector, samples.
+  Bottom right: posterior PDFs (corner plot?) for physical parameters.
+\label{fig:real_uncalibrated}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\caption{Ratio of the calibration vector inferred from the
+  real uncalibrated spectrum to that inferred from the real calibrated
+  spectrum ({\it green}). Taking the ratio reduces the effects of model
+  imperfections and shows how well we are able to infer the
+  calibration vector of \citet{schiavon05} ({\it black}).  
+\label{fig:real_calibration_ratio}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\caption{Inferred parameters for \excluster.  We show the inference from the
+  calibrated spectrum ({\it red}), from the uncalibrated spectrum
+  ({\it blue}), and from the CMD ({\it black}).
+\label{fig:real_parameters}}
+\end{figure*}

### 2015-05-11 tex/ms.tex
param file and plotting code for real data

@@
 
-We take the calibration-vector that modifies the mean model to produce
-the observed spectrum as multiplicative with respect to the mean
-model.  In this case we define the residual of the data from the model
-in terms of the logarithmic differences.  This logarithmic formulation
-requires that $d$ be everywhere positive, and distorts the
-uncertainties, especially at low S/N ratio.  The advantages of
-defining the residual in this way are that the model remains linear
-(and therefore fast) and the calibration vector is forced to be
-positive everywhere.  Additionally, at high signal to noise the
-distortion of the uncertainties will be minimal.
+For the spectroscopic measurements we are going to account for
+the spectrophotometric calibration in our likelihood function.  We
+take this calibration-vector that modifies the mean spectroscopic
+model to produce the observed spectrum to be multiplicative with
+respect to the mean model.  In this case we define the residual of the
+data from the model in terms of the logarithmic differences.  This
+logarithmic formulation requires that $d$ be everywhere positive, and
+distorts the uncertainties, especially at low S/N ratio.  The
+advantages of defining the residual in this way are that the model
+remains linear (and therefore fast) and the calibration vector is
+forced to be positive everywhere.  Additionally, at high signal to
+noise the distortion of the uncertainties will be minimal.
 
@@
 over large wavelength ranges, the number of parameters required to
-model the calibration can become quite large (e.g., very high order
+model the calibration can become quite large (e.g. very high order
 polynomials) and the correct parameterization may be unknown.  It is
 therefore desirable to introduce a non-parameteric model of the
-calibration.  We do this using a Gaussian Process: prior over
+calibration.  We do this using a Gaussian Process: BDJ: prior over
 functions, analytically marginalizable, covariant fractional
@@
 resolved stellar CMDs, providing an important check on our inference
-methodology and especially our population synthesis models.
+methodology and especially our models for star cluster spectra.  However,
+our methodology is applicable any spectral model: stars, galaxies or
+ISM emission.
 
@@
 with wavelength.  These spectra have been placed on the rest-frame,
-though in what follows we will model the effect of redshift
-uncertainties on the data.
+though in throughout our analysis we allow the redshift to vary as one
+of the model parameters.
 
@@
 are only approximate.  When fitting the spectra we mask the region
-around the bright OI5577\AA~ sky line, and we fit only to the spectrum
+around  several bright sky lines, and we fit only to the spectrum
 with $3550\AA < \lambda < 6500$\AA~ which are covered by the MILES
@@
 
-Words about photometry.
+The line-spread function of the data is not constant as a function of
+velocity or wavelength.  While a wavelength dependent line spread
+function can be included in the model, it is computationally
+intensive. Therefore, we have convolved the observed spectra with a
+wavelength-dependent kernel to bring it to an approximately constant
+dispersion in wavelength across the whole spectrum. This dispersion is
+a free parameter in our model.
+
+Optical photometry is available from \citep{vanderbeke14} based on
+SDSS for objects in the northern hemisphere and on data from CTIO for
+southern hemisphere objects.  Briefly, total fluxes within the half-light radii
+of the clusters \citet{harris98} were calculated, with small
+corrections for stars unlikely to be cluster members based on their
+positions in the CMD. For this data the formal Poisson uncertainties
+are typically exceedingly small.  The dominant source of uncertainty
+comes from the photometric calibration and from uncertainties in
+cluster membership.
+
+Near-Infrared photometry is available from \citet{cohen07}, who fit
+King profiles \citet{king65} to 2MASS data in the $J$, $H$, and $K_s$
+bands.  To produce NIR photometry consistent with the optical we
+integrated the King profiles to the half-light radii used by
+\citet{vanderbeke14}.
 
@@
 and redshift $z$.
-The matrix $L(\sigma_s, z)$ is a convolution kernel representing the
-stellar velocity profile,
+Multiplication by the matrix $L(\sigma_s, z)$ represents a convolution
+with the stellar velocity profile,
 and $\sigma_s$ is the stellar velocity dispersion. 
@@
 also be modeled. The instrumental resolution is given by the parameter
-$\sigma_{inst}$.  {\color{blue}Discuss intrinsic resolution of model spectra
-(MILES), what to do in situations where instrumental resolution is
-higher, lower or comparable (ouch) to intrinsic velocity broadening.}
+$\sigma_{inst}$.
 
@@
 
-\item Real calibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model. The calibration vector
+\item Real calibrated spectrum:   \sout{Inference using spectroscopy and all
+  photometry, with full calibration model.} The calibration vector
   inferred will highlight differences between the calibrated spectrum
@@
 \item Real uncalibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model. This is to show how much
-  the inferred physical parameters change when the calibration is
-  basically unknown.
+  photometry, with full calibration model.
 
@@
 
-For each test we want to show
-\begin{itemize}
-
-\item Posterior parameter pdfs (and joint pdfs).
-
-\item Samples of the posterior prediction for the observations, and
-  residuals thereform.
-
-\item The calibration vector, and posterior samples of it.
-
-\item Posterior samples of the intrinsic spectrum
-\end{itemize}
+In this section we describe the results of our experiments with mock
+data and with real data.  For the mock data we investigate the
+dependence of the recovered parameters on the type of data used in the
+inference.
 
@@
 
-{\color{blue}BDJ Describe results from the ideal case.}
+The posterior parameter PDFs for the case of perfectly known
+calibration are shown in the bottom right panels of Figure
+\ref{fig:speconly_ideal}, along with the mock spectrum and posterior
+samples of the mock spectrum.  In this case the observed spectrum is
+the same as the intrinsic spectrum except for a distance dimming
+factor, as we have assumed that the calibration vector is one
+everywhere, wth no uncertainty. The PDF for stellar mass is extremely
+narrow is information about the overall normalization comes from all
+$\sim 3000$ spectral data points.  The single photometric data point,
+with S/N of 10, adds essentially no information beyond what is
+obtained from the spectrum.
 
@@
 and we will therefore allow the calibration parameters $\alpha$ in our
-model to vary.  In Figure
+model to vary.  {\color{red} This is not converged.} In Figure
 \ref{fig:speconly_calibrated} we show the result of our inference from
@@
 
-Even in the case of a single photometric data point, many of the
-physical parameters are well-constrained and only minimally biased,
-e.g. age and metallicity.  These are the parameters that are
-constrained well by the spectrum itself and are not strongly sensitive
-to the overall shape of the spectral continuum.  Such parameters can
-be reasonably well recovered by fitting continuum normalized spectra,
-though here we have propogated the uncertainty in this normalization
-into the uncertainties on the physical parameters.
+When the spectrophotometric calibration is assumed to be unknown,
+the posterior PDFs for stellar mass and especially $A_v$ become
+extremely large.  There is now no information about the overall shape
+of the SED (and hence the dust attenuation), and the overall
+normalization is constrained entirely by the single photometric point.
+The uncertainty in the stellar mass is somewhat broader than the
+uncertainty on the $g$-band flux because of the variation in
+mass-to-light ratio due to uncertainties in dust and, to a lesser
+extent, age.
 
-On the other hand, the posterior PDF for the dust attenuation optical
-depth $A_v$ is extremely broad.
-
-The uncertainty on the total stellar mass incorporates both the
-uncertainty in the photometric flux and the uncertainty in the $g$-
-band mass-to-light ratio.
+On the other hand, age and metallicity remain well-constrained.  These
+are the parameters that are constrained well by spectral lines and are
+not strongly sensitive to the overall shape of the spectral continuum.
+The posterior PDFs are only slightly broader than in the case of a
+perfectly known calibration. Such parameters can be reasonably well
+recovered by fitting continuum normalized spectra, though here we have
+propogated the uncertainty in this normalization into the
+uncertainties on the physical parameters, leading to slightly larger
+total uncertainties.
 
 In Figure \ref{fig:speconly_uncalibrated} we show the results of
-inference on an \emph{uncalibrated} mock spectrum.
+inference on an \emph{uncalibrated} mock spectrum. {\color{red} This
+  is not converged}
 

### 2015-05-11 code/runjob_mac.sh

@@ -38,6 +38,6 @@ mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/
 
 #real data
 mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/real_specphot.py \
-  --objname=NGC7089 --noisefactor=10.0
+  --objname=NGC7089 --noisefactor=10.0 --calibrated=True
   --outfile=$PROJECTS/speccal/code/results/ggc_ngc7089 \
   --nwalkers=126 --niter=1024 --do_powell=True

### 2015-05-12 tex/ms.tex
fix definition covariance matrix in alternative formulation

@@
 C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} * \mu)^2]\,\delta_{nn'} +
-\transpose{\mu} \, K_\alpha(\lambda_n - \lambda_{n'}) \, \mu
+ K_\alpha(\lambda_n - \lambda_{n'}) \ast \mu \, \transpose{\mu}
 \quad ,
 \end{eqnarray}
-where the multiplication of $s$ and $K_\alpha$ by $\mu$ in the
-construction of $C_{nn'}$ means that they are defined in
-\emph{fractional} terms, and the uncertainties remain Gaussian in
-linear flux space.  It remains to be seen whether this actually works.
+where $\ast$ denotes element-wise multiplication and the
+multiplication of $s$ and $K_\alpha$ by $\mu$ and
+$\mu\,\transpose{\mu}$ respectively in the construction of $C_{nn'}$
+means that they are defined in \emph{fractional} terms, and the
+uncertainties remain Gaussian in linear flux space.  It remains to be
+seen whether this actually works.
 

### 2015-05-12 tex/ms.tex
remove much of the introductory text, plotting for fully burned-in mocks

@@
 
-In probabilistic inference, all information flows from the data to the
-parameters of interest by means of a likelihood function, or an
-expression for the probability of the data conditioned on the
-parameters.
-If there are $N$ independent sources of data, for each of which there
-is a likelihood function, the full-data likelihood is the product of
-the $N$ individual likelihoods (or the log-likelihood is a sum of the
-$N$ individual log-likelihoods).
-There is no bespoke ``weighting'' of the data that is justifiable in
-this framework.
-This creates some apparent paradoxes!
-One is the following:
-
 Imagine you have three photometric bands through which you have
@@
 log-likelihood function, and these 2503 log-likelihood functions must
-be (by the Rules of Righteousness) coadded equally into one full-data
+be coadded equally into one full-data
 log-likelihood.
@@
 
-What is a Righteous Probabilistic Investigator (RPI) to do?
-One option---fully unjustified---is to ``down-weight'' the
-log-likelihoods of the spectral pixels relative to the photometric
-measurements.
-This is equivalent to taking the likelihoods to some power, which has
-no justification in inference (though it is sometimes used in
-optimization and sampling as an ``annealing'' move).
-This down-weighting is not justified, but there is even more
-ad-hockery than this, because there is no principled way to choose the
-unprincipled weights.
-
-The Right Thing To Do is to express the \emph{reason} that the RPI
-believes the spectroscopic data to be less reliable \emph{within} the
+The Right Thing To Do is to express the \emph{reason} that the
+spectroscopic data are less reliable \emph{within} the
 likelihood function.
-That is, the RPI must add nuisance parameters to parameterize the
+That is, the one must add nuisance parameters to parameterize the
 unreliability of the spectroscopy, and infer those along with the
@@
 This will reduce the importance of the spectroscopy relative to the
-photometry and the RPI will be well pleased with the dominance of the
-photometric data in the final inferences of the parameters of
-interest.
+photometry.
 This amounts to propogating the uncertainties in the
@@
 calibration of the spectral data.
-That is, the method we present has the potential to \emph{obviate
-spectrophotometric calibration}.
-
-We find that this potential---obviation of calibration---is realized.
-That is, if the procedures demonstrated below become widely adopted,
-some or perhaps most astronomical spectroscopic projects could
-potentially drop or dramatically reduce their spectrophotometric
-calibration programs.
-This would reduce telescope overheads and data-analysis time and
-complexity, delivering economic and sanity benefits to the whole
-community.
 
@@
 amplitudes are constrained to be positive, while for interstellar
-absorption (e.g. Na D and Ca K) the amplitudes are constrained to be
+absorption (e.g. NaD and CaK) the amplitudes are constrained to be
 negative. This framework can be easily extended to include more
@@
 
+\item Mock uncalibrated data:  vary the photometric bands to see how
+  much it changes the recovery of the parameters.
+
 \item Real calibrated spectrum:   \sout{Inference using spectroscopy and all
@@
   based parameters.
-
-\item Mock uncalibrated data:  vary the photometric bands to see how
-  much it changes the recovery of the parameters.
 
@@
 In Figure \ref{fig:speconly_uncalibrated} we show the results of
-inference on an \emph{uncalibrated} mock spectrum. {\color{red} This
-  is not converged}
+inference on an \emph{uncalibrated} mock spectrum.  The results are
+similar to the case of the \emph{calibrated} spectrum.
 

### 2015-05-12 code/plot_joint_posterior.py

@@ -13,7 +13,7 @@ def joint_pdf(res, p1, p2, **kwargs):
     return xbins, ybins, sigma.T
 
 
-def compute_sigma_level(trace1, trace2, nbins=20):
+def compute_sigma_level(trace1, trace2, nbins=30):
     """From a set of traces, bin by number of standard deviations"""
     L, xbins, ybins = np.histogram2d(trace1, trace2, nbins)
     L[L == 0] = 1E-16
@@ -37,7 +37,7 @@ def compute_sigma_level(trace1, trace2, nbins=20):
 
 if __name__ == "__main__":
     photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
-    speconly = 'results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430808300_mcmc'
+    speconly = 'results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc'
     specphot = 'results/ggc_mock_specphot.u0.t9.0_z0.0_a0.5_1430380402_mcmc'
     resfiles = [photonly, speconly, specphot]
     clr = ['red','blue', 'magenta']
@@ -45,6 +45,10 @@ if __name__ == "__main__":
                for rfile in resfiles]
     obsdat = results[0]['obs']
     showpars = np.array(['mass', 'tage', 'zmet', 'dust2'])
+    parlims = np.array([[0.4e5, 4e5],
+                        [None, None],
+                        [-1.0, 0.19],
+                        [0, 1.5]])
     npar = len(showpars)
 
     fig = pl.figure()
@@ -54,17 +58,21 @@ if __name__ == "__main__":
         dax = pl.subplot(gs[i,i])
         for n, res in enumerate(results):
             trace, p = hist_samples(res, res['model'], [p1], start=0.5)
-            dax.hist(trace, bins = 50, color=clr[n], normed=True,
+            dax.hist(trace, bins = 30, color=clr[n], normed=True,
                      alpha=0.5, histtype='stepfilled')
-            if i == 0:
-                dax.set_ylabel(p1)
-            else:
-                dax.set_yticklabels('')
-            if i == (npar-1):
-                dax.set_xlabel(p2)
-            else:
-                dax.set_xticklabels('')
-            
+        # Axis label foo
+        if i == 0:
+            dax.set_ylabel(p1)
+        else:
+            dax.set_yticklabels('')
+        if i == (npar-1):
[…]

### 2015-05-12 code/runjob_mac.sh

@@ -19,10 +19,9 @@ mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/
 
 #speconly_uncalibrated, lo S/N
 mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_losn.py \
-  --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl  \
-  --outfile=$PROJECTS/speccal/code/results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5 \
-  --nwalkers=126 --niter=1024 --do_powell=False
-
+       --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl \
+       --outfile=$PROJECTS/speccal/code/results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5 \
+       --nwalkers=254 --niter=6144 --do_powell=False
 
 # photonly
 mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_photonly.py \

### 2015-05-12 tex/ms.tex
change title

@@
 \title{Combining information from photometric and spectroscopic data:\\
-  propogating uncertainties in spectrophotometric calibration}
+  Probabilistic spectrophotometric inference}
 \shorttitle{Combining Spectroscopy and Photometry}
@@
   parameters of interest.
-This obviation of calibration overheads will pay \emph{all yall mad cheddar},
-  at least if yall employ full cost accounting.
 \end{abstract}

### 2015-05-15 tex/ms.tex
code and text for inference without logarithmic transform of the data

@@
 
-HOGG: A model is a parameterized likelihood function, with prior PDFs on the nuisance parameters (at least)...
-There is a likelihood for the photometry and for the spectroscopy...
-Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...
+HOGG: A model is a parameterized likelihood function, with prior PDFs
+on the nuisance parameters (at least)...  There is a likelihood for
+the photometry and for the spectroscopy...  Each of these penalizes
+the difference between a column vector of data and a column vector of
+model expectation value...
 
@@
 it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
-For photometric data this ``jitter'' is often best described as a
-fractional error, $s^2 \equiv \hat{s}^2\mu(\theta)^2$, corresponding
-for example to an additional magnitude zero-point uncertainty.  This
-is a simple modification of the chi-squared log-likelihood:
+This is a simple modification of the chi-squared log-likelihood:
 \begin{eqnarray}\label{eq:photometricLF}
@@
 log-likelihood function we are going to use for the photometric
-measurements in what follows.  In this formulation, if $\theta$ are
-the parameters of interest, the jitter variance $\hat{s} = 
+measurements in what follows.  For photometric data this ``jitter'' is
+often best described as a fractional error, $s^2 \equiv
+\hat{s}^2\mu(\theta)^2$, corresponding for example to an additional
+magnitude zero-point uncertainty.  In this formulation, if $\theta$
+are the parameters of interest, the jitter variance $\hat{s} =
 s/\mu(\theta)$ is a nuisance noise-model parameter representing
@@
 
-For the spectroscopic measurements we are going to account for
-the spectrophotometric calibration in our likelihood function.  We
-take this calibration-vector that modifies the mean spectroscopic
-model to produce the observed spectrum to be multiplicative with
-respect to the mean model.  In this case we define the residual of the
-data from the model in terms of the logarithmic differences.  This
-logarithmic formulation requires that $d$ be everywhere positive, and
-distorts the uncertainties, especially at low S/N ratio.  The
-advantages of defining the residual in this way are that the model
-remains linear (and therefore fast) and the calibration vector is
-forced to be positive everywhere.  Additionally, at high signal to
-noise the distortion of the uncertainties will be minimal.
-
 {\color{blue} BDJ This paragraph should explain why we are using the
 GP, not just how it works.}
-The multiplicative calibration vector can be explicitly modeled, for
-example using polynomials.  However, for complex calibration vectors
-over large wavelength ranges, the number of parameters required to
-model the calibration can become quite large (e.g. very high order
-polynomials) and the correct parameterization may be unknown.  It is
-therefore desirable to introduce a non-parameteric model of the
-calibration.  We do this using a Gaussian Process: BDJ: prior over
-functions, analytically marginalizable, covariant fractional
-uncertainties the same as multiplying by a function (covariant
-uncertainties the same as adding a function)
+For the spectroscopic measurements we are going to account for the
+spectrophotometric calibration in our likelihood function.  We take
+this calibration-vector that modifies the mean spectroscopic model to
+produce the observed spectrum to be multiplicative with respect to the
+mean model.  The multiplicative calibration vector can be explicitly
+modeled, for example using polynomials.  However, for complex
+calibration vectors over large wavelength ranges, the number of
+parameters required to model the calibration can become quite large
+(e.g. very high order polynomials) and the correct parameterization
+may be unknown.  It is therefore desirable to introduce a
+non-parameteric model of the calibration.  We do this using a Gaussian
+Process: BDJ: prior over functions, analytically marginalizable,
+covariant fractional uncertainties the same as multiplying by a
+function (covariant uncertainties the same as adding a function.)
 
 The calibration-vector and Gaussian-Process modified log-likelihood is
-\begin{eqnarray}\label{eq:spectroscopicLF}
+\begin{eqnarray}\label{eq:spectroscopicLF_v2}
 \ln p(d\given\theta,\alpha) &=&
@@
 \\
-\Delta &\equiv& \ln d - \ln \mu(\theta) - f(\alpha) 
+\Delta &\equiv& d - \mu(\theta) \ast f(\alpha) 
 \\
-C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
-K_\alpha(\lambda_n - \lambda_{n'})
-\\
-\hat{\sigma_n} & = &\sigma_n/d
+C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} \, \mu)^2]\,\delta_{nn'} +
+ K_\alpha(\lambda_n - \lambda_{n'}) \ast \mu \, \transpose{\mu}
 \quad ,
 \end{eqnarray}
-where $\alpha$ is a blob of nuisance parameters
+where $\ast$ denotes element-wise multiplication,
+$\theta$ are the physical parameters,
+$\alpha$ is a blob of nuisance parameters
 (which determine the jitter, the calibration vector and the kernel function),
@@
 amplitude of the residual calibration issues,
-$\hat{\sigma}_n$ are the fractional uncertainties of the data,
 and each $\lambda_n$ is the wavelength of spectral pixel $n$.
+The multiplication of $\hat{s}$ and $K_\alpha$ by $\mu$ and
+$\mu\,\transpose{\mu}$ respectively in the construction of $C_{nn'}$
+signifies that they are defined in \emph{fractional} terms.
 The calibration vector $f(\alpha)$ is going to take care of the
@@
 residuals $\Delta$.
+This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
+are going to use for the spectroscopic data in what follows.
+
+In detail, we are going to choose the exponential of a $M$th-order
+polynomial form for the calibration vector $f(\alpha)$ and a bell
+shape (Gaussian) for the kernel function $K_\alpha(\cdot)$:
+\begin{eqnarray}\displaystyle
+f(\alpha) &=& \exp\left(\sum_{m=o}^M c_m\,x^m\right)
+\\
+x &\equiv& \frac{\lambda}{\lambda_0} - 1
+\\
+K_\alpha(\lambda_n - \lambda_{n'}) &=& a^2\,\exp\left(-\frac{[\lambda_n - \lambda_{n'}]^2}{2\,\ell^2}\right)
+\\
+\transpose{\alpha} &\equiv& \left[ \{c_m\}_{m=0}^M, s^2, a^2, \ell^2 \right]
+\quad ,
+\end{eqnarray}
+where $\lambda$ is a column vector made up of the wavelengths
+$\lambda_m$ and $x$ is a scaled and shifted version of the same,
+scaled by a fiducial wavelength $\lambda_0$.  The exponentiation of
+the polynomial in ensures that $f(\alpha)$ is everywhere positive.
+Nuisance parameters $c_m$ set the shape of the large-scale calibration
+issues, while $a^2$ and $\ell^2$ set the variance and correlation
+length of the remaining covariant calibration noise.
+
+XXX logarithmic Alternative XXX
+In this case we define the residual of the data from the model in
+terms of the logarithmic differences.  This logarithmic formulation
+requires that $d$ be everywhere positive, and distorts the
+uncertainties, especially at low S/N ratio.  The advantages of
+defining the residual in this way are that the model remains linear
+(and therefore fast) and the calibration vector is forced to be
+positive everywhere.  Additionally, at high signal to noise the
+distortion of the uncertainties will be minimal.
+
+The calibration-vector and Gaussian-Process modified log-likelihood is
+\begin{eqnarray}\label{eq:spectroscopicLF}
+\ln p(d\given\theta,\alpha) &=&
+                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
+                                + \ln([2\pi]^N\,\det{C}) \right]
+\\
+\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
+\\
+C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
+K_\alpha(\lambda_n - \lambda_{n'})
+\\
+\hat{\sigma_n} & = &\sigma_n/d
+\quad ,
+\end{eqnarray}
+where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
 The residual column vector is defined in terms of the logarithmic
@@
 effectively multiplied by $e ^{f(\alpha)}$
-This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
-are going to use for the spectroscopic data in what follows.
-
-In detail, we are going to choose a $M$th-order polynomial form for
-the calibration vector $f(\alpha)$ and a bell shape (Gaussian) for the
-kernel function $K_\alpha(\cdot)$:
-\begin{eqnarray}\displaystyle
-f(\alpha) &=& c_0\,[1 + \sum_{m=1}^M c_m\,x^m]
-\\
-x &\equiv& \frac{\lambda}{\lambda_0} - 1
-\\
-K_\alpha(\lambda_n - \lambda_{n'}) &=& a^2\,\exp(-\frac{[\lambda_n - \lambda_{n'}]^2}{2\,\ell^2})
-\\
-\transpose{\alpha} &\equiv& \left[ \{c_m\}_{m=0}^M, s^2, a^2, \ell^2 \right]
-\quad ,
-\end{eqnarray}
-where $\lambda$ is a column vector made up of the wavelengths $\lambda_m$
-and $x$ is a scaled and shifted version of the same,
-scaled by a fiducial wavelength $\lambda_0$.
-Nuisance parameters $c_m$ set the shape of the large-scale calibration
-issues, while $a^2$ and $\ell^2$ set the variance and correlation
-length of the remaining covariant calibration noise.
-
-XXX Alternative XXX
-To avoid making the logarithmic transform described above, which
-distorts the errors, we can formulate the problem in a different way,
-modifying Equation \label{eq:spectroscopicLF} above as 
-\begin{eqnarray}\label{eq:spectroscopicLF_v2}
-\ln p(d\given\theta,\alpha) &=&
-                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
-                                + \ln([2\pi]^N\,\det{C}) \right]
-\\
-\Delta &\equiv& d - \mu(\theta) * f(\alpha) 
-\\
-C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} * \mu)^2]\,\delta_{nn'} +
- K_\alpha(\lambda_n - \lambda_{n'}) \ast \mu \, \transpose{\mu}
-\quad ,
-\end{eqnarray}
-where $\ast$ denotes element-wise multiplication and the
-multiplication of $s$ and $K_\alpha$ by $\mu$ and
-$\mu\,\transpose{\mu}$ respectively in the construction of $C_{nn'}$
-means that they are defined in \emph{fractional} terms, and the
-uncertainties remain Gaussian in linear flux space.  It remains to be
-seen whether this actually works.
 

### 2015-05-15 code/paramfiles/mock_specphot_linear.py

@@ -7,7 +7,7 @@ from sedpy import attenuation
 sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_c0_t9.0_z0.0_a0.5',
+              'outfile':'results/ggc_mock_u0_t9.0_z0.0_a0.5',
               'do_powell': False,
               'ftol':0.5e-4, 'maxfev':5000,
               'nwalkers':64, 
@@ -18,7 +18,7 @@ run_params = {'verbose':True,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,
-              'filename':os.path.join(sdir, 'data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl'),
+              'filename':os.path.join(sdir, 'data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl'),
               'wlo':3350.,
               'whi':6500.,
               'noisefactor':10
@@ -29,7 +29,7 @@ run_params = {'verbose':True,
 def load_obs(filename=None, noisefactor=1.0, **extras):
     with open(filename) as f:
         obs = pickle.load(f)
-    obs['phot_mask'] = np.array(['sdss' in filt.name for filt in obs['filters']])
+    #obs['phot_mask'] = np.array(['sdss' in filt.name for filt in obs['filters']])
     obs['unc'] *= noisefactor
     obs['noisefactor'] = noisefactor
     return obs
@@ -48,7 +48,7 @@ model_params.append({'name': 'lumdist', 'N': 1,
                      'units': 'Mpc',
                      'prior_function': None,
                      'prior_args': None})
-
+                         
 ###### SFH ################
 
 model_params.append({'name': 'mass', 'N': 1,

### 2015-05-15 tex/ms.tex
updates to plotting for the linear data inference

@@
 everywhere, wth no uncertainty. The PDF for stellar mass is extremely
-narrow is information about the overall normalization comes from all
-$\sim 3000$ spectral data points.  The single photometric data point,
+narrow since information about the overall normalization comes from all
+$\sim 3000$ spectral data points.  The uncertainty in stellar mass
+largely reflects uncertainty in the mass-to-light ratio due to the
+small uncertainties in dust, metallicity, and age given the
+spectroscopic data. The single photometric data point,
 with S/N of 10, adds essentially no information beyond what is
@@
 \begin{eqnarray} \label{eq:calibration}
-\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
+\frac{d}{\mu(\theta)} & = & f(\alpha) + \frac{\tilde{\Delta}}{\mu(\theta)}
 \quad ,

### 2015-05-15 code/mock_figures.py

@@ -10,12 +10,12 @@ from bsfh.gp import ExpSquared
 from plotting import *
 
 sps = sps_basis.StellarPopBasis()
-#gp = GaussianProcess(None, None)
+#
 import george
 kernel = (george.kernels.WhiteKernel(0.0) +
           0.0 * george.kernels.ExpSquaredKernel(0.0))
 gp = george.GP(kernel)#, solver=george.HODLRSolver)
-
+gp = ExpSquared(None, None)
 
 if __name__ == "__main__":
 

### 2015-06-01 code/ggcdata.py
summary plotting for varied physical parameters, start on noisy mocks and change to using the NGC1851 calibration vector for mocks

@@ -297,7 +297,7 @@ def ggc_mock(model, theta, sps, objname='', apply_cal=True, mask=True,
     mock['mock_theta'] = model.theta.copy()
 
     mock['calibration'], noise = 1.0, 0.0
-    mock['added_noise'] = add_noise
+    mock['added_noise'] = None
     if apply_cal:
         s *= cal['calibration']
         mock['calibration'] = cal['calibration'].copy()
@@ -306,8 +306,10 @@ def ggc_mock(model, theta, sps, objname='', apply_cal=True, mask=True,
     if add_noise:
         noise = np.random.normal(0, 1, len(s)) * noise_sigma
         s += noise
+        mock['added_noise'] = noise
         pnoise = np.random.normal(0, 1, len(p)) * pnoise_sigma
         p += pnoise
+        mock['added_phot_noise'] = pnoise
         
     mock['spectrum'] = s
     mock['maggies'] = p

### 2015-06-01 code/make_ggc_mocks.py

@@ -197,7 +197,7 @@ model_params.append({'name': 'phot_jitter', 'N':1,
 if __name__ == "__main__":
 
      
-    info = {'objname': 'NGC7089',
+    info = {'objname': 'NGC1851',
             'datadir': os.path.join(sdir, 'data/ggclib/spectra/'),
             'outdir': os.path.join(sdir, 'data/ggclib/mocks/'),
             'apply_cal': True,
@@ -216,7 +216,8 @@ if __name__ == "__main__":
     #theta_default = np.array([1.0, 0.0, 0.5])
     model = sedmodel.SedModel(model_params)
     theta_default = model.initial_theta.copy()
-    
+
+    #make mocks with varied parameters
     for p, vals in vary_params.iteritems():
         ind = model.theta_labels().index(p)
         theta = theta_default.copy()
@@ -231,3 +232,17 @@ if __name__ == "__main__":
             print('writing to {0}'.format(filename))
             with open(filename, 'w') as f:
                 pickle.dump(mock, f)
+
+    #make mocks with different noise realizations
+    info['add_noise'] = True
+    theta = theta_default.copy()
+    nnoise = 10 #number of noise realizations
+    for i in range(nnoise):
+        mock = ggcdata.ggc_mock(model, theta, sps,
+                                phot_snr=10, **info)
+        filename = name_template.format(caltype[info['apply_cal']], i+1,
+                                        *theta)
+            print('writing to {0}'.format(filename))
+            with open(filename, 'w') as f:
+                pickle.dump(mock, f)
+        

### 2015-06-01 code/plotting.py

@@ -221,3 +221,43 @@ def histfig(samples, parnames, truths=None, fax=None, truth_color='k', **kwargs)
         ax.set_yticklabels([])
         pl.setp(ax.get_xticklabels(), fontsize=6)
     return hfig, haxes
+
+def plot_delta_params(results, models, pnames,
+                      pmap={}, plabel_map={},
+                      sfraction=0.9, thin=10,
+                      ptile=[16, 50, 84], fax=None,
+                      colors=None, labels=None):
+    if fax is None:
+        pfig, pax = pl.subplots()
+    else:
+        pfig, pax = fax
+    if labels is None:
+        labels = len(results) * ['']
+    if colors is None:
+        colors = len(results) * ['k']
+
+    def identity(x):
+        return x
+        
+    for res, mod, label, clr in zip(results, models, labels, colors):
+        samples, pnames_ord = hist_samples(res, mod, pnames, start=sfraction, thin=thin)
+        truths = np.array([res['obs']['mock_params'][k][0] for k in pnames_ord])
+        pct = np.percentile(samples, ptile, axis=0)
+        
+        pct = np.array([pmap.get(k, identity)(pct[:,i])
+                        for i,k in enumerate(pnames_ord)])
+        truths = np.array([pmap.get(k, identity)(truths[i])
+                           for i,k in enumerate(pnames_ord)])
+            
+        delta = (pct - truths[:, None]) / truths[:, None]
+        print(delta)
+        pax.plot(delta[:,1], '-o', color=clr, label=label)
+        pax.fill_between(np.arange(len(pnames)), delta[:,0], delta[:,2],
+                         alpha=0.3, color=clr)
+
+    pretty_pname = [plabel_map.get(k, k) for k in pnames_ord]
+    pax.set_xticks(np.arange(len(pnames_ord)))
+    pax.set_xticklabels(pretty_pname)
+    pax.set_ylabel(r'(Post-True) / True')
+    return pfig, pax
+    

### 2015-06-01 code/summary_phys_plot.py

@@ -1,0 +1,54 @@
+import sys, pickle
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib import gridspec
+
+from bsfh import read_results as bread
+from plotting import *
+
+pnames = ['mass','tage','zmet','dust2']
+pmap = {'zmet': lambda x: 10**x
+        }
+plabel_map = {'mass':r'M$_*$',
+              'tage': 'Age',
+              'zmet': r'$Z/Z_\odot$',
+              'dust2':r'A$_V$'
+              }
+    
+sfraction = 0.90
+thin = 10
+
+def read_results(runs):
+    results, models = [], []
+    for run in runs:
+        res, pr, mod = bread.read_pickles(run, model_file=run.replace('_mcmc','_model'))
+        results.append(res)
+        models.append(mod)
+    return results, models
+
+if __name__ == "__main__":
+    
+    truns = ['results/ggc_mock_specphot_linear.u0.t0.3_z0.0_a0.5_5305122_1432333491_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t1.1_z0.0_a0.5_5305126_1432333542_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t3.0_z0.0_a0.5_5305127_1432333568_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t9.0_z0.0_a0.5_5280432_1431898211_mcmc']
+    zruns = []
+    aruns = []
+    runs = [truns]#, aruns, zruns]
+    colors = pl.rcParams['axes.color_cycle'][:3] + ['red']
+    labels = ['0.3', '1.1', '3.0', '9.0']
+    pfig, paxes = pl.subplots(len(runs), 1)
+
+    
+    for ip, pruns in enumerate(runs):
+        ax = np.array(paxes).flat[ip]
+        results, models = read_results(pruns)
+        pfig, ax = plot_delta_params(results, models, pnames,
+                                     sfraction=sfraction, thin=thin,
+                                     fax=(pfig, ax),
+                                     pmap=pmap, plabel_map=plabel_map,
+                                     colors=colors, labels=labels)
+
+        ax.plot(np.arange(4), np.zeros(4), ':k')
+        ax.legend(loc=0)
+    pfig.show()

### 2015-06-04 tex/figures.tex
remove much of the introductory text, plotting for fully burned-in mocks
save summary figure to figs directory and add to ms

@@
   calibration vector is not a constant with wavelength.
- {\color{red} This is not converged.}
 \label{fig:speconly_uncalibrated}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_params.pdf}
+\includegraphics[width=\textwidth]{figures/vary_params.pdf}
 \caption{Offset from the input parameters of the medians of the
-posterior PDFs for model parameters obtained from mock spectra and
-photometry. Lines connect a single model.
+posterior PDFs for  inference from mock spectra and
+photometry, as a function of the mock parameter that is varied.
  \label{fig:mock_parameter_space}}

### 2015-06-04 code/summary_phys_plot.py

@@ -66,12 +66,13 @@ if __name__ == "__main__":
         ytitle=r'$\Delta$'
         fig = pl.figure(figsize=(15,5))
         gs = [gridspec.GridSpec(2, 2) for i in range(len(runs))]
-        width, leftpad, rightpad = 1.0/len(gs), 0.08, 0.02
-        
+        leftpad, rightpad, margin = 0.06, 0.00, 0.05
+        width = (1.0 - 2*margin)/len(gs)
         for ivp, (pruns, pvary, tgs) in enumerate(zip(runs, vary_params, gs)):
             results, models = read_results(pruns)
-            left = width * ivp + leftpad
-            right =  width * (ivp+1) - rightpad
+            left = margin + width * ivp + leftpad
+            right =  margin + width * (ivp+1) - rightpad 
+            print(left, right)
             tgs.update(left=left, right=right, hspace=0.0, wspace=0.0)
             paxes = [pl.Subplot(fig, spec) for spec in tgs]
             for ip, pname in enumerate(pnames):
@@ -80,7 +81,7 @@ if __name__ == "__main__":
                                            sfraction=sfraction, thin=thin,
                                            fax=(None, dax), pmap=pmap,
                                            xlims=vary_lims[ivp],
-                                           verbose=True, fractional=False)
+                                           verbose=False, fractional=False)
                 pretty_pname = plabel_map.get(pname, pname)
                 pretty_vpname = pvlabel_map.get(pvary, pvary)
                 dax.axhline(0.0, linestyle=':', color='k')
@@ -97,7 +98,8 @@ if __name__ == "__main__":
                 else:
                     dax.set_yticks([])
                 fig.add_subplot(dax)
-        fig.show()
+        fig.savefig('../tex/figures/vary_params.pdf')
+        pl.close(fig)
                 
     if oldstyle:
         labels = [['0.3 Gyr', '1.1  Gyr', '3 Gyr', '6 Gyr', '9 Gyr'],

### 2015-06-15 tex/figures.tex
add noise realizations plot to manuscript

@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
-\caption{Posterior PDFs obtained from multiple noise realizations of the
-  mock photometry and uncalibrated spectra, for a single set of
-  parameters.  The input mock parameters are shown as a 
-  vertical line, medians of the posterior CDF for each realization are
-  shown as dotted lines.
+\includegraphics[width=\textwidth]{figures/noise_realizations.pdf}
+\caption{Percentiles of the posterior PDFs for four of the parameters,
+  obtained from multiple noise realizations of the
+  mock photometry and uncalibrated spectra.  The input mock parameters are shown as a 
+ black horizontal line, The red shaded region gives the 16th to 84th percentile
+ range for a noiseless mock.
 \label{fig:noise_realizations}}

### 2015-06-15 tex/ms.tex
summary plotting for varied physical parameters, start on noisy mocks and change to using the NGC1851 calibration vector for mocks
add noise realizations plot to manuscript

@@
 \DeclareGraphicsExtensions{.png,.pdf}
-\newcommand{\excluster}{NGC7089}
+\newcommand{\excluster}{NGC1851}
 
@@
 
-\item Do this for a bunch of ages, metallicities, and dust
-  attenuations, possibly compare to the ideal posteriors in each case.
+\item \sout{Do this for a bunch of ages, metallicities, and dust
+  attenuations, possibly compare to the ideal posteriors in each case.}
 
@@
   much it changes the recovery of the parameters.
+
+\item \sout{Mock uncalibrated data: do the inference with multiple noise
+  realizations to see how the recovered PDFs cover the true value.}
 

### 2015-06-15 code/plot_noise_realizations.py

@@ -84,7 +84,7 @@ if __name__ == "__main__":
         hfig.show()
 
     else:
-        nfig, naxes = pl.subplots(2,2, figsize=(6, 4))
+        nfig, naxes = pl.subplots(2,2, figsize=(8, 5))
         res, pr, mod = bread.read_pickles(noiseless_run,
                                           model_file=noiseless_run.replace('_mcmc','_model'))
         samples, pord = hist_samples(res, mod, pnames, thin=thin,
@@ -92,9 +92,10 @@ if __name__ == "__main__":
         ptiles = np.percentile(samples,[16, 50, 84], axis=0)
         truths = [res['obs']['mock_params'][k] for k in pord]
         for i, (ax, name) in enumerate(zip(naxes.flatten(), pnames)):
-            ax.plot(np.arange(nreal+2)-1, np.zeros(nreal+2) + ptiles[1,i], color='r')
-            ax.fill_between(np.arange(nreal+2)-1, np.zeros(nreal+2) + ptiles[0,i],
-                            np.zeros(nreal+2) + ptiles[1,i], color='red', alpha=0.3)
+            x = np.arange(nreal+2)-1
+            ax.plot(x, x*0 + ptiles[1,i], color='r')
+            ax.fill_between(x, x*0 + ptiles[0,i], x*0 + ptiles[2,i],
+                            color='red', alpha=0.3)
             ax.axhline(truths[i], color=kwargs.get('truth_color','k'),
                        label='Mock Truth')
             ax.set_ylabel(name, fontsize=8)
@@ -112,3 +113,4 @@ if __name__ == "__main__":
                 ax.errorbar([j], [ptiles[1,i]], yerr, capthick=2, color='black')
                 ax.plot([j], [ptiles[1,i]], 'ok')
         nfig.show()
+        nfig.savefig('../tex/figures/noise_realizations.pdf')

### 2015-06-16 tex/figures.tex
clean up plotting scripts

@@
 
-\begin{figure}[h!]
-%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
-\caption{A mock spectrum for a star cluster with the fiducial
-parameters $10^5 M_\odot$ total stellar mass, an age of 9 Gyr, solar
-metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
-\end{figure}
-
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/ideal.pdf}
+\includegraphics[width=0.5 \textwidth]{figures/ideal.pdf}
 \caption{Results of inference from a mock spectrum and a single
@@
   assumed to be perfectly known. 
-Top Left: The mock observed spectrum ({\it black}) is shown as well as
-YY model spectra constructed from draws from the posterior PDFs of the
-model parameters.
-Bottom Right: Marginalized posterior PDFs for several of the physical
+Top: Model spectra ({\it green}) and photometry ({\it orange})
+constructed from draws from the posterior PDFs of the model
+parameters, compared to the true intrinsic spectroscopy and photomtry
+({\it black})
+Bottom: Marginalized posterior PDFs for several of the physical
 parameters of interest.  The input mock parameters are shown as
 vertical black lines.
-{\color{red} Remove calibration plot and intrinsic plot, since it is
-  the same as observed spectrum.  Show residuals.}
+{\color{red} Show residuals.}
 \label{fig:speconly_ideal}}
@@
   the calibration are modeled.
-Top Left: The mock observed spectrum ({\it black}) is shown as well as
-YY model spectra constructed from draws from the posterior PDFs of the
-model parameters, including calibration parameters {\it green}.
+Top Left: The uncertainty normalized residuals between the mock
+observed spectrum ({\it black}) and YY model spectra constructed from
+draws from the posterior PDFs of the model parameters, including
+calibration parameters {\it blue}.
 Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
-Posterior samples of the inferred calibration vector ({\it green}) include both
+Posterior samples of the inferred calibration vector ({\it blue}) include both
 the polynomial and the Gaussian Process mean prediction (Equation
@@
 Top Right: Samples of the posterior prediction for the
-\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
-({\it magenta}).  The true mock photometry is also shown ({\it
+\emph{intrinsic} spectrum ({\it blue}) as well as for the photometry
+({\it orange}).  The true mock photometry is also shown ({\it
 black}).
@@
 Top: The intrinsic spectrum. Samples of the posterior prediction
-for the \emph{intrinsic} spectrum ({\it green}) and the
-photometry ({\it magenta}).  The mock photometry is also shown
+for the \emph{intrinsic} spectrum ({\it red}) and the
+photometry ({\it orange}).  The mock photometry is also shown
 ({\it black}).
@@
 \caption{Results of inference from the combination of
-  \emph{uncalibrated} spectroscopy and all the photometric data
-  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
+\emph{uncalibrated} spectroscopy and all the photometric data points.
+Panels and are as in Figure \ref{fig:speconly_calibrated}.
 \label{fig:specphot_uncalibrated}}
@@
 \begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
+\caption{Joint Posterior PDFs for the calibration parameters inferred
+from the combination of \emph{uncalibrated} spectroscopy and all the
+photometric data points.
+\label{fig:cal_posterior}}
+\end{figure*}
+
+\begin{figure*}[h!]
 \includegraphics[width=\textwidth]{figures/combined_post.pdf}
-\caption{Joint posterior PDFs for several physical parameters. The
-posteriors obtained from photometry only are in {\it red}, from
-\emph{uncalibrated} spectroscopy and a single photometric point in
-{\it blue}, and from the photometry and spectroscopy combined in {\it
-magenta}.  The contours are 1 and 2-sigma contours. The true values
-are indicated by {\it black points}.
+\caption{Corner plot of joint and marginal posterior PDFs for several
+physical parameters. The posteriors obtained from photometry only are
+in {\it red}, from \emph{uncalibrated} spectroscopy and a single
+photometric point in {\it blue}, and from the photometry and
+spectroscopy combined in {\it magenta}.  The contours are 1 and
+2-sigma contours. The true values are indicated by {\it black points}.
 \label{fig:combined_posterior}}
@@
 \caption{Percentiles of the posterior PDFs for four of the parameters,
-  obtained from multiple noise realizations of the
-  mock photometry and uncalibrated spectra.  The input mock parameters are shown as a 
- black horizontal line, The red shaded region gives the 16th to 84th percentile
- range for a noiseless mock.
+obtained from multiple noise realizations of the mock photometry and
+uncalibrated spectra.  The input mock parameters are shown as a black
+horizontal line, The green shaded region gives the 16th to 84th
+percentile range for a noiseless mock.
 \label{fig:noise_realizations}}
@@
 \includegraphics[width=\textwidth]{figures/vary_params.pdf}
-\caption{Offset from the input parameters of the medians of the
-posterior PDFs for  inference from mock spectra and
-photometry, as a function of the mock parameter that is varied.
+\caption{Offset of the posteriors from the input parameters for
+inference from mock spectra and photometry, as a function of the mock
+parameter that is varied.  The medians of the posterior PDFs are shown
+as connected black circles, the 16th and 84th percentile of the
+posteriors are indicated by the gray shaded region.
+Left: Results when varying age.
+Middle: Results when varying metallicity.
+Right: Results when varying dust attenuation.
  \label{fig:mock_parameter_space}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
-\caption{Inference from a real, calibrated, spectrum.  Top left:
-  Observed spectrum and posterior samples thereof.  Bottom left:
-  residuals.  Top right: inferred calibration vector, samples.
-  Bottom right: posterior PDFs (corner plot?) for physical parameters.
+\includegraphics[width=\textwidth]{figures/real_calibrated.pdf}
+\caption{Inference from a real, \emph{calibrated}, spectrum. 
+ Top left: Residuals.  
+Bottom left: Inferred calibration vactor.  
+Top right: Inferred instrinsic SED.
+Bottom right: posterior PDFs for selected physical parameters.
 \label{fig:real_calibrated}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
-\caption{Inference from a real, uncalibrated, spectrum.  Top left:
-  Observed spectrum and posterior samples thereof.  Bottom left:
-  residuals.  Top right: inferred calibration vector, samples.
-  Bottom right: posterior PDFs (corner plot?) for physical parameters.
+\includegraphics[width=\textwidth]{figures/real_uncalibrated.pdf}
+\caption{Inference from a real, \emph{uncalibrated}, spectrum.   
+Top left: Residuals.  
+Bottom left: Inferred calibration vactor.  
+Top right: Inferred instrinsic SED.
+Bottom right: posterior PDFs for selected physical parameters.
 \label{fig:real_uncalibrated}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
-\caption{Ratio of the calibration vector inferred from the
+%\includegraphics[width=\textwidth]{figures/inferred_calibration.pdf}
+\caption{Left: Ratio of the calibration vector inferred from the
   real uncalibrated spectrum to that inferred from the real calibrated
@@
   calibration vector of \citet{schiavon05} ({\it black}).  
+Right: Joint posterior PDFs for the inferred calibration parameters.
 \label{fig:real_calibration_ratio}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+%\includegraphics[width=\textwidth]{figures/real_phys_posterior.png}
 \caption{Inferred parameters for \excluster.  We show the inference from the

### 2015-06-16 tex/ms.tex
clean up plotting scripts

@@
 
-XXX logarithmic Alternative XXX
-In this case we define the residual of the data from the model in
-terms of the logarithmic differences.  This logarithmic formulation
-requires that $d$ be everywhere positive, and distorts the
-uncertainties, especially at low S/N ratio.  The advantages of
-defining the residual in this way are that the model remains linear
-(and therefore fast) and the calibration vector is forced to be
-positive everywhere.  Additionally, at high signal to noise the
-distortion of the uncertainties will be minimal.
+%XXX logarithmic Alternative XXX
+%In this case we define the residual of the data from the model in
+%terms of the logarithmic differences.  This logarithmic formulation
+%requires that $d$ be everywhere positive, and distorts the
+%uncertainties, especially at low S/N ratio.  The advantages of
+%defining the residual in this way are that the model remains linear
+%(and therefore fast) and the calibration vector is forced to be
+%positive everywhere.  Additionally, at high signal to noise the
+%distortion of the uncertainties will be minimal.
 
-The calibration-vector and Gaussian-Process modified log-likelihood is
-\begin{eqnarray}\label{eq:spectroscopicLF}
-\ln p(d\given\theta,\alpha) &=&
-                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
-                                + \ln([2\pi]^N\,\det{C}) \right]
-\\
-\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
-\\
-C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
-K_\alpha(\lambda_n - \lambda_{n'})
-\\
-\hat{\sigma_n} & = &\sigma_n/d
-\quad ,
-\end{eqnarray}
-where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
-The residual column vector is defined in terms of the logarithmic
-difference between the data and the mean model $\mu$ since we are
-taking the calibration vector to be multiplicative with respect to the
-mean model $\mu$. In this formulation the the mean model $\mu$ will be
-effectively multiplied by $e ^{f(\alpha)}$
+%The calibration-vector and Gaussian-Process modified log-likelihood is
+%\begin{eqnarray}\label{eq:spectroscopicLF}
+%\ln p(d\given\theta,\alpha) &=&
+%                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
+%                                + \ln([2\pi]^N\,\det{C}) \right]
+%\\
+%\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
+%\\
+%C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
+%K_\alpha(\lambda_n - \lambda_{n'})
+%\\
+%\hat{\sigma_n} & = &\sigma_n/d
+%\quad ,
+%\end{eqnarray}
+%where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
+%The residual column vector is defined in terms of the logarithmic
+%difference between the data and the mean model $\mu$ since we are
+%taking the calibration vector to be multiplicative with respect to the
+%mean model $\mu$. In this formulation the the mean model $\mu$ will be
+%effectively multiplied by $e ^{f(\alpha)}$
 
@@
 observed wavelength scale and add noise according to the SNR of the
-real data.  For the photometry we assume a SNR of 10.  We also mask
-the mock spectra at the location of significant sky lines and ISM
-lines that are present in the real data.
+real data.  We also mask the mock spectra at the location of
+significant sky lines and ISM lines that are present in the real data.
+For the mock photometry we assume a SNR of 10.
 
 We will refer to these spectra as the \emph{perfectly calibrated} mock
-spectrum.  An example is shown in Figure \ref{fig: mock data}. We also
-produce mock spectra by dividing the perfectly calibrated spectra by
-the spectrophotometric calibration vector taken from the real data
-\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}.  We refer to these as
-the \emph{uncalibrated} mock spectra.
+spectrum. We also produce mock spectra by dividing the perfectly
+calibrated spectra by the spectrophotometric calibration vector taken
+from the real data \citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}.
+We refer to these as the \emph{uncalibrated} mock spectra.
 

### 2015-06-16 code/make_paper.sh

@@ -1,0 +1,58 @@
+#!bin/sh
+
+# First we make the mocks
+ft="9.0"
+fz="0.0"
+fa="0.5"
+fall="t${ft}_z${fz}_a${fa}"
+python make_ggc_mocks #$ft $fz $fa
+
+### Then we fit the mocks and assign output names to variables
+./runjobs.sh
+specphot_ideal= ""
+speconly_cal=""
+speconly_uncal=""
+specphot_uncal=""
+photonly=""
+
+noise_runs="ls results/ggc_mock_specphot_linear.u[1-9]*.${fall}_*_mcmc"
+age_runs="ls results/ggc_mock_specphot_linear.u0.t*_z${fz}_a${fa}_*_mcmc"
+z_runs="ls results/ggc_mock_specphot_linear.u0.t${ft}_z*_a${fa}_*_mcmc"
+dust_runs="ls results/ggc_mock_specphot_linear.u0.t${ft}_z${fz}_a*_*_mcmc"
+
+real_cal="results/ggc_ngc1851_1432787257_mcmc"
+real_uncal="results/ggc_ngc1851_uncal_tightprior_1433448554_mcmc"
+### Then we make figures for mocks ###
+#fig 1
+python plot_data.py
+#fig 2
+python plot_ideal_dashboard.py $specphot_ideal green
+cp "${specphot_ideal%_mcmc}_dashboard.pdf" ../tex/figures/ideal.pdf
+#fig 3
+python plot_speconly_dashboard.py $speconly_cal blue
+cp "${speconly_cal%_mcmc}_dashboard.pdf" ../tex/figures/speconly_calibrated.pdf
+#fig 4
+python plot_speconly_dashboard.py $speconly_uncal blue
+cp "${speconly_uncal%_mcmc}_dashboard.pdf" ../tex/figures/speconly_uncalibrated.pdf
+#fig 5
+python plot_photonly_dashboard.py $photonly red
+cp "${photonly%_mcmc}_dashboard.pdf" ../tex/figures/photonly.pdf
+#fig 6
+python plot_dashboard.py $specphot_uncal magenta
+cp "${specphot_uncal%_mcmc}_dashboard.pdf" ../tex/figures/specphot_uncalibrated.pdf
+#fig 7
+python plot_joint_posterior.py $speconly_uncal $photonly $specphot_uncal
+#fig 8
+python plot_noise_realizations.py $noise_runs
+#fig 9
[…]

### 2015-06-16 code/plot_dashboard.py

@@ -13,7 +13,7 @@ sps = sps_basis.StellarPopBasis()
 import george
 kernel = (george.kernels.WhiteKernel(0.0) +
           0.0 * george.kernels.ExpSquaredKernel(0.0))
-gp = george.GP(kernel)#, solver=george.HODLRSolver)
+#gp = george.GP(kernel)#, solver=george.HODLRSolver)
 gp = ExpSquared(None, None)
 
 if __name__ == "__main__":
@@ -23,23 +23,28 @@ if __name__ == "__main__":
     else:
         resfile = 'results/ggc_mock.u0.t1.0_z0.0_a0.5_1426268715_mcmc'
     model_file = resfile.replace('_mcmc','_model')
+    bcolor='magenta'
+    pcolor='orange'
     nsample = 10
     
     res, pr, mod = bread.read_pickles(resfile, model_file=model_file)
     obsdat = res['obs']
     
+    # Get samples and component spectra
     fsamples = np.random.uniform(0,1,nsample)
     thetas, start, samples = theta_samples(res, samples=fsamples, start=0.95, thin=1)
     fwave, _, _, fspecvecs = comp_samples_fullspec(thetas, mod, obsdat,
                                                    sps=sps, gp=None)
-    mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat, sps=sps,
-                                                  gp=gp)
+    mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat,
+                                                  sps=sps, gp=gp)
     pwave, mosed, mosed_unc, pvecs = comp_samples_phot(thetas, mod, obsdat, sps=sps)
 
+    # Get truth spectrum and sed
     tspec, tphot, ttheta = true_sed(mod, obsdat, sps=sps, fullspec=True)
     twave = sps.ssp.wavelengths
     tspec /= obsdat['normalization_guess']
     
+    # Get calibration vector
     calvec = obsdat['calibration']
     if np.size(calvec) == 1:
         calvec = np.zeros(len(mwave)) + calvec
@@ -47,12 +52,13 @@ if __name__ == "__main__":
         calvec = calvec[obsdat['mask']]
     norm = obsdat['normalization_guess'] * obsdat['rescale']
 
-    # Set up left hand side
+    ### Build Figure ###
     fig = pl.figure(figsize=(10,8))
[…]

### 2015-06-16 code/plot_noise_realizations.py

@@ -53,6 +53,7 @@ if __name__ == "__main__":
     nreal = len(runs)
     results, models = read_results(runs)
     noiseless_run = 'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a0.5_5313542_1432675345_mcmc'
+    bcolor = 'magenta'
 
     if as_hist:
         hfig, haxes = pl.subplots(2,2)
@@ -62,7 +63,7 @@ if __name__ == "__main__":
             for i, (ax, name) in enumerate(zip(haxes.flatten(), pnames)):
                 ax.hist(samples[:,i], bins=kwargs.get("bins", 50),
                         histtype="stepfilled",
-                        color=kwargs.get("color", "b"),
+                        color=kwargs.get("color", bcolor),
                         alpha=kwargs.get("alpha",0.3))
         
         res, pr, mod = bread.read_pickles(noiseless_run,
@@ -73,7 +74,7 @@ if __name__ == "__main__":
         for i, (ax, name) in enumerate(zip(haxes.flatten(), pnames)):
             ax.hist(samples[:,i], bins=kwargs.get("bins", 50),
                     histtype="stepfilled",
-                    color="r",
+                    color=bcolor,
                     alpha=kwargs.get("alpha",0.3))
             ax.axvline(truths[i], color=kwargs.get('truth_color','k'),
                        label='Mock Truth')
@@ -93,12 +94,12 @@ if __name__ == "__main__":
         truths = [res['obs']['mock_params'][k] for k in pord]
         for i, (ax, name) in enumerate(zip(naxes.flatten(), pnames)):
             x = np.arange(nreal+2)-1
-            ax.plot(x, x*0 + ptiles[1,i], color='r')
+            ax.plot(x, x*0 + ptiles[1,i], color=bcolor)
             ax.fill_between(x, x*0 + ptiles[0,i], x*0 + ptiles[2,i],
-                            color='red', alpha=0.3)
+                            color=bcolor, alpha=0.3)
             ax.axhline(truths[i], color=kwargs.get('truth_color','k'),
                        label='Mock Truth')
-            ax.set_ylabel(name, fontsize=8)
+            ax.set_ylabel(pvlabel_map[name], fontsize=8)
             ax.set_xticklabels([])
             pl.setp(ax.get_yticklabels(), fontsize=8)
             ax.set_xlim(-0.5, nreal - 0.5)

### 2015-06-16 code/plot_real_dashboard.py

@@ -15,7 +15,7 @@ import george
 kernel = (george.kernels.WhiteKernel(0.0) +
           0.0 * george.kernels.ExpSquaredKernel(0.0))
 gp = george.GP(kernel)#, solver=george.HODLRSolver)
-
+gp = ExpSquared(None, None)
 
 if __name__ == "__main__":
 
@@ -24,80 +24,77 @@ if __name__ == "__main__":
     else:
         resfile = 'results/ggc_mock.u0.t1.0_z0.0_a0.5_1426268715_mcmc'
     model_file = resfile.replace('_mcmc','_model')
+    bcolor='green'
+    pcolor='orange'
     nsample = 10
     
     res, pr, mod = bread.read_pickles(resfile, model_file=model_file)
     obsdat = res['obs']
     
+    # Get samples and component spectra
     fsamples = np.random.uniform(0,1,nsample)
-    thetas, start, samples = theta_samples(res, samples=fsamples, start=0.95, thin=1)
+    thetas, start, samples = theta_samples(res, samples=fsamples, start=0.75, thin=1)
     fwave, _, _, fspecvecs = comp_samples_fullspec(thetas, mod, obsdat,
                                                    sps=sps, gp=None)
-    mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat, sps=sps,
-                                                  gp=gp)
+    mwave, mospec, mounc, specvecs = comp_samples(thetas, mod, obsdat,
+                                                  sps=sps, gp=gp)
     pwave, mosed, mosed_unc, pvecs = comp_samples_phot(thetas, mod, obsdat, sps=sps)
 
-    #tspec, tphot, ttheta = true_sed(mod, obsdat, sps=sps, fullspec=True)
-    #twave = sps.ssp.wavelengths
-    #tspec /= obsdat['normalization_guess']
+    # Get truth spectrum and sed
+    # THERE IS NO TRUTH
     
-    calvec = obsdat['calibration']
-    if np.size(calvec) == 1:
-        calvec = np.zeros(len(mwave)) + calvec
+    # Get calibration vector    
+    if obsdat.get('spec_calibrated', True):
+        norm = 1
+        calvec = np.ones(len(mwave))
     else:
+        import ggcdata
+        cal = ggcdata.ggc_spec(obsdat['object_name'], 'a', '1',
[…]

### 2015-06-16 code/plotting.py

@@ -111,7 +111,8 @@ def theta_samples(res, samples=[1.0], start=0.0, thin=1):
     return thetas, start_index, np.floor(np.array(samples) * (ns-1)).astype(int)
 
 def calfig(wave, calvec, specvecs, norm=1.0,
-           labelprefix='Mock', fax=None):
+           labelprefix='Mock', fax=None,
+           basecolor = 'green'):
     """Plot the calibration and posterior samples of it.
     """
     if fax is None:
@@ -128,7 +129,7 @@ def calfig(wave, calvec, specvecs, norm=1.0,
         else:
             label = None
         cax.plot(wave, norm * specs[1],
-                 color='green', alpha=0.3, label=label)
+                 color=basecolor, alpha=0.3, label=label)
     
     return cfig, cax
 
@@ -156,8 +157,36 @@ def obsfig(wave, obsvec, specvecs, unc=None,
              linewidth=1.0, alpha=1.0)
     return ofig, oax
 
+def residualfig(wave, obsvec, specvecs, unc=None, chi=False,
+                basecolor=None, fax=None):
+    if fax is None:
+        rfig, rax = pl.subplots()
+    else:
+        rfig, rax = fax
+
+    if chi:
+        #normalize residuals by the uncertainty
+        chi_unc = unc.copy()
+    else:
+        chi_unc = 1.0
+        if unc is not None:
+            x, y, e = wave, obsvec, unc
+            rax.fill_between(x, -e, e, facecolor='grey', alpha=0.3)
+    # Plot posterior samples of the observed spectrum as a residual
+    for i, specs in enumerate(specvecs):
+        if i==0:
+            label = 'Posterior samples'
+        else:
+            label = None
+        rax.plot(wave, (specs[3] - obsvec) / chi_unc,
+                 color=basecolor, alpha=0.3, label=label)
+    rax.axhline(0.0, linestyle=':', color='k')
+    return rfig, rax
+                
+        
 def sedfig(wave, specvecs, phot, photvecs, norm = 1.0,
-            labelprefix='Mock', fax=None, peraa=False):
+            labelprefix='Mock', fax=None, peraa=False,
+            basecolor='green', pointcolor='magenta', **kwargs):
     """Plot the photometric SED, posterior samples of it, and
     posterior samples of the intrinsic spectrum.
     """
@@ -181,9 +210,9 @@ def sedfig(wave, specvecs, phot, photvecs, norm = 1.0,
         else:
             label = None
[…]

### 2015-06-16 tex/ms.tex
prettify noise_realization figure, some minor changes in discussion text

@@
 \author{
-  BDJ\altaffilmark{\lick},
-  DRW\altaffilmark{\lick},
-  DFM\altaffilmark{\ccpp},
-  DWH\altaffilmark{\ccpp, \cds, \mpia},
-  CC\altaffilmark{\lick},
-  others}
-\shortauthors{bdj et al}
-\altaffiltext{\lick}{University of California Lick Observatory}
-\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
-\altaffiltext{\cds}{Center for Data Science, New York University}
-\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}
+%  BDJ\altaffilmark{\lick},
+%  DRW\altaffilmark{\lick},
+%  DFM\altaffilmark{\ccpp},
+%  DWH\altaffilmark{\ccpp, \cds, \mpia},
+%  CC\altaffilmark{\lick},
+  AUTHORS}
+\shortauthors{BDJ et al}
+%\altaffiltext{\lick}{University of California Lick Observatory}
+%\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
+%\altaffiltext{\cds}{Center for Data Science, New York University}
+%\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}
 
@@
 We first infer the parameters of interest $\theta$ for a calibrated
-spectrum of one of the clusters, \excluster, using the full YY-band
-photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
+spectrum of one of the clusters, \excluster, using the $griz$-band
+photometry. In Figure \ref{fig:real_calibrated} we show the spectra
 that result from draws of the parameters $[\theta,\alpha]$ from the
@@
 components of the model constructed from each draw. Figure
-\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
-which the priors were conditioned, and residuals between the posterior
-models and the observed data.
-
-In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
-posterior parameter draws, compared to the observed SED. There is some
-tension between the modeled and observed SEDs, I'm not quite sure
-why. Finally, In Figure \ref{fig:inferred_params} we show the
-marginalized and joint PDFs for a subset of the full model parameters.
+\ref{fig:real_calibrated} also shows the marginalized PDFs for a
+subset of the full model parameters.
 
@@
 calibration vector for each draw of the model parameters (Equation
-\ref{eq:calibration}) If the spectrophotometric calibration were
+\ref{eq:calibration}). If the spectrophotometric calibration were
 perfect and we had correctly inferred it, then we would expect this
@@
 parametrically or via a Gaussian Process.  {\color{blue} Discuss more
-complicated covariance kernels, multiple kernels.}
+complicated covariance kernels, multiple kernels, combining fractional
+and absolute covariance amplitudes.}
 
@@
 include for example night sky-line emission in the spectroscopy
-\citep[e.g.,][]{gullikson14} or residuals from an intial sky-line
+\citep[e.g.,][]{gullikson14} or residuals from an initial sky-line
 subtraction and uncertainties in wavelength calibration
@@
 turn infer the parameters of a generative model for the calibration
-\citep[e.g.][]{spectrophot}. This generative model can then be used in
-the (probabilistic) calibration of objects where the spectra are
-difficult to model explicitly.
+parameters \citep[e.g.][]{spectrophot}. This generative model can then
+be used in the (probabilistic) calibration of objects where the
+spectra are difficult to model explicitly.  One aspect of such
+modelling might entail inferring the priors on the Gaussian Process
+parameters $a$ and $\ell$.
 
@@
 to explicitly model the differences, incorporating prior information
-about the spatial variation of physical properties.  Fourth, the
-method will break down at very low S/N due to the logarithmic
-formulation of the residual in equation~(\ref{eq:spectroscopicLF}).
-Finally, this method is computationally intensive and expensive, since
-we are constantly inverting largish matrices.
+about the spatial variation of physical properties.  Finally, this
+method is computationally intensive and expensive, since we are
+constantly inverting largish matrices.
 
@@
 spectral models of astrophysical objects, then there is often no
-reason not to use those objects themselves as calibration objects,
+reason not to use those objects themselves as calibrators,
 especially if you expect your calibration to be spatially or 
-temporally variable, or to change with the brightness of the object.
+temporally variable, or to change with the brightness or other
+properties of the object.
 
@@
 \acknowledgements
-Thanks to X. for bringing us beer.
-DRW is supported by NASA through Hubble Fellowship grant
-  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
-BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
-CC is supported by Packard and Sloan Foundation Fellowships. 
+%Thanks to X. for bringing us beer.
+%DRW is supported by NASA through Hubble Fellowship grant
+%  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
+%BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
+%CC is supported by Packard and Sloan Foundation Fellowships. 
 This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 

### 2015-06-16 code/plot_data.py

@@ -3,7 +3,7 @@ import matplotlib.pyplot as pl
 import ggcdata, os
 
 #The speccal directory
-sdir = os.path.join.(os.environ['PROJECTS'], 'speccal')
+sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
 
 ##### OBSERVATIONAL DATA ######
 
@@ -12,7 +12,7 @@ if __name__ == "__main__":
     try:
         objname = sys.argv[1]
     except:
-        objname = 'NGC7089'
+        objname = 'NGC1851'
     try:
         noisefactor = float(sys.argv[2])
     except:
@@ -23,7 +23,7 @@ if __name__ == "__main__":
     
     datadir = os.path.join(sdir, 'data/ggclib/spectra/')
     dat = ggcdata.ggc_spec(datadir+objname, 'a', '1', fluxtype=None)
-    mdat = ggcdata.ggc_mask(dat, thresh=3)
+    mdat = ggcdata.ggc_mask(dat, thresh=3, lsf=6)
     mask = mdat['mask']
     #skymask = ggcdata.make_skymask(dat['wavelength'],
     #                               dat['sky'], thresh=3, lsf=6)

### 2015-06-16 code/plot_noise_realizations.py

@@ -32,6 +32,9 @@ def read_results(runs):
         models.append(mod)
     return results, models
 
+def identity(x):
+    return x
+
 
 if __name__ == "__main__":
 
@@ -91,27 +94,39 @@ if __name__ == "__main__":
         samples, pord = hist_samples(res, mod, pnames, thin=thin,
                                      start=sfraction)
         ptiles = np.percentile(samples,[16, 50, 84], axis=0)
+        ptiles = np.array([pmap.get(k, identity)(ptiles[:,i])
+                            for i,k in enumerate(pord)])
+
         truths = [res['obs']['mock_params'][k] for k in pord]
+        truths = np.array([pmap.get(k, identity)(truths[i])
+                           for i,k in enumerate(pord)])
+
+        delta = (ptiles - truths).T
         for i, (ax, name) in enumerate(zip(naxes.flatten(), pnames)):
             x = np.arange(nreal+2)-1
-            ax.plot(x, x*0 + ptiles[1,i], color=bcolor)
-            ax.fill_between(x, x*0 + ptiles[0,i], x*0 + ptiles[2,i],
+            ax.plot(x, x*0 + delta[1,i], color=bcolor)
+            ax.fill_between(x, x*0 + delta[0,i], x*0 + delta[2,i],
                             color=bcolor, alpha=0.3)
-            ax.axhline(truths[i], color=kwargs.get('truth_color','k'),
+            ax.axhline(0, linestyle=':', color=kwargs.get('truth_color','k'),
                        label='Mock Truth')
-            ax.set_ylabel(pvlabel_map[name], fontsize=8)
+            ax.set_ylabel('$\Delta$' + plabel_map[name], fontsize=8)
             ax.set_xticklabels([])
             pl.setp(ax.get_yticklabels(), fontsize=8)
             ax.set_xlim(-0.5, nreal - 0.5)
-            
+            ax.set_ylim(-0.1, 0.1)
+            if i > 1:
+                ax.set_xlabel('Noise realization #', fontsize=8)
         for j, (res, mod) in enumerate(zip(results, models)):
             samples, pord = hist_samples(res, mod, pnames, thin=thin,
                                          start=sfraction)
             ptiles = np.percentile(samples,[16, 50, 84], axis=0)
+            ptiles = np.array([pmap.get(k, identity)(ptiles[:,i])
+                            for i,k in enumerate(pord)])
+            delta = (ptiles - truths).T
[…]

### 2015-07-02 tex/ms.tex
more plot prettifying, comment out nebular lines from model description, remove commented out logarithmic model

@@
 
-%XXX logarithmic Alternative XXX
-%In this case we define the residual of the data from the model in
-%terms of the logarithmic differences.  This logarithmic formulation
-%requires that $d$ be everywhere positive, and distorts the
-%uncertainties, especially at low S/N ratio.  The advantages of
-%defining the residual in this way are that the model remains linear
-%(and therefore fast) and the calibration vector is forced to be
-%positive everywhere.  Additionally, at high signal to noise the
-%distortion of the uncertainties will be minimal.
-
-%The calibration-vector and Gaussian-Process modified log-likelihood is
-%\begin{eqnarray}\label{eq:spectroscopicLF}
-%\ln p(d\given\theta,\alpha) &=&
-%                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
-%                                + \ln([2\pi]^N\,\det{C}) \right]
-%\\
-%\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
-%\\
-%C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
-%K_\alpha(\lambda_n - \lambda_{n'})
-%\\
-%\hat{\sigma_n} & = &\sigma_n/d
-%\quad ,
-%\end{eqnarray}
-%where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
-%The residual column vector is defined in terms of the logarithmic
-%difference between the data and the mean model $\mu$ since we are
-%taking the calibration vector to be multiplicative with respect to the
-%mean model $\mu$. In this formulation the the mean model $\mu$ will be
-%effectively multiplied by $e ^{f(\alpha)}$
-
 \section{Data and Experiments}
@@
 
-Nebular emission lines (which may arise from HII regions around the
-clusters or from diffuse ionized gas) and interstellar absorption
-lines are modeled as a sum of $\delta$-functions of unknown amplitude
-$a_\ell$, and with known central wavelengths $\lambda_\ell$, broadened
-by the gas velocity profile, $\sigma_{gas}$.  For emission lines the
-amplitudes are constrained to be positive, while for interstellar
-absorption (e.g. NaD and CaK) the amplitudes are constrained to be
-negative. This framework can be easily extended to include more
-complex models for the nebular emission, such as allowing line
-dependent widths and velocities, and using Voight profiles for the
-line shapes.
+%Nebular emission lines (which may arise from HII regions around the
+%clusters or from diffuse ionized gas) and interstellar absorption
+%lines are modeled as a sum of $\delta$-functions of unknown amplitude
+%$a_\ell$, and with known central wavelengths $\lambda_\ell$, broadened
+%by the gas velocity profile, $\sigma_{gas}$.  For emission lines the
+%amplitudes are constrained to be positive, while for interstellar
+%absorption (e.g. NaD and CaK) the amplitudes are constrained to be
+%negative. This framework can be easily extended to include more
+%complex models for the nebular emission, such as allowing line
+%dependent widths and velocities, and using Voight profiles for the
+%line shapes.
 
@@
 Our strategy is easily extensible to more complicated models, which
-include for example night sky-line emission in the spectroscopy
-\citep[e.g.,][]{gullikson14} or residuals from an initial sky-line
-subtraction and uncertainties in wavelength calibration
+include for example nebular or night sky-line emission in the
+spectroscopy \citep[e.g.,][]{gullikson14} or residuals from an initial
+sky-line subtraction and uncertainties in wavelength calibration
 \citep[e.g.,][]{walker15}. Furthermore, more complex physical models
@@
 to molecular bands or absorption line complexes) will be absorbed into
-the Gaussian process if not properly included in the mean
-model. Third, we have made the assumption that the spectroscopy and
-the photometry are sampling the same populations.  In practice,
+the Gaussian Process if not properly included in the mean model. The
+Gaussian process will also absorb incorrectly modeled attenuation
+curve shapes. Third, we have made the assumption that the spectroscopy
+and the photometry are sampling the same populations.  In practice,
 differences between spectroscopic and photometric apertures often mean

### 2015-07-02 code/plot_components.py

@@ -13,19 +13,6 @@ matplotlib.colors.cnames.update(newcolors)
 sps = sps_basis.StellarPopBasis()
 gp = ExpSquared(None, None)
 
-def format_sedax(sax):
-    sax.set_xscale('log')
-    sax.set_xlim(3e3, 1.6e4)
-    ticks = list(sax.get_xlim()) + [4e3, 6e3, 10e3]
-    sax.set_xticks(ticks)
-    sax.set_xticklabels(['{:4.0f}'.format(t) for t in ticks], fontsize=8)
-    sax.set_xlabel('$\lambda (\AA)$', fontsize=12)
-    sax.set_yscale('log')
-    sax.tick_params(axis='both', which='major', labelsize=8)
-    sax.set_ylabel(sax.get_ylabel(), fontsize=12)
-    sax.set_ylim(3e-14, 1e-12)
-    sax.legend(loc=0, prop={'size':12})
-    return sax
 
 if __name__ == "__main__":
 

### 2015-07-02 code/plot_dashboard.py

@@ -22,36 +22,6 @@ param_name_map = {'tage':'Age (Gyr)',
                   }
 pnmap = param_name_map
 
-def format_sedax(sax):
-    sax.set_xscale('log')
-    sax.set_xlim(3e3, 1.6e4)
-    ticks = list(sax.get_xlim()) + [4e3, 6e3, 10e3]
-    sax.set_xticks(ticks)
-    sax.set_xticklabels(['{:4.0f}'.format(t) for t in ticks], fontsize=8)
-    sax.set_xlabel('$\lambda (\AA)$', fontsize=12)
-    sax.set_yscale('log')
-    sax.tick_params(axis='both', which='major', labelsize=8)
-    sax.set_ylabel(sax.get_ylabel(), fontsize=12)
-    sax.set_ylim(3e-14, 1e-12)
-    sax.legend(loc=0, prop={'size':12})
-    return sax
-
-def format_calax(cax, norm):
-    cax.set_ylabel(r'Calibration $F_{{obs}}/F_{{\lambda, intrinsic}}$',
-                   fontsize=12)
-    cax.legend(loc=0, prop={'size':8})
-    cax.set_ylim(0.2*norm, 1.6*norm)
-
-    #cax.set_xlim(3e3, 1.6e4)
-    #ticks = list(cax.get_xlim()) + [4e3, 6e3, 10e3]
-    #cax.set_xticks(ticks)
-    #cax.set_xticklabels(['{:4.0f}'.format(t) for t in ticks], fontsize=8)
-    cax.set_xlabel('$\lambda (\AA)$', fontsize=12)
-    cax.tick_params(axis='both', which='major', labelsize=8)
-    cax.set_ylabel(cax.get_ylabel(), fontsize=12)
-    cax.legend(loc=0, prop={'size':12})
-    return cax
-
 if __name__ == "__main__":
 
     bcolor='magenta'
@@ -61,6 +31,10 @@ if __name__ == "__main__":
             bcolor = sys.argv[2]
         except:
             pass
+        try:
+            suptitle = sys.argv[3]
+        except:
+            suptitle=''
     else:
         resfile = 'results/ggc_mock.u0.t1.0_z0.0_a0.5_1426268715_mcmc'
     model_file = resfile.replace('_mcmc','_model')
@@ -94,23 +68,36 @@ if __name__ == "__main__":
 
     ### Build Figure ###
     fig = pl.figure(figsize=(10,8))
-    # Set up left hand side
+    # Set up right hand side
[…]

### 2015-07-02 code/plot_real_dashboard.py

@@ -10,25 +10,28 @@ from bsfh.gp import ExpSquared
 from plotting import *
 
 sps = sps_basis.StellarPopBasis()
-#gp = GaussianProcess(None, None)
-try:
-    import george
-    kernel = (george.kernels.WhiteKernel(0.0) +
-            0.0 * george.kernels.ExpSquaredKernel(0.0))
-    gp = george.GP(kernel)#, solver=george.HODLRSolver)
-except:
-    pass
-
 gp = ExpSquared(None, None)
+param_name_map = {'tage':'Age (Gyr)',
+                  'mass': '$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':'$A_V$ (mag)',
+                  'zmet': '$\log Z/Z_\odot$',
+                  'sigma_smooth': '$\sigma_{{LSF}}$',
+                  'zred': '${\it z}$',
+                  }
+pnmap = param_name_map
 
 if __name__ == "__main__":
 
+    bcolor='green'
     if len(sys.argv) > 1:
         resfile=sys.argv[1]
+        try:
+            bcolor = sys.argv[2]
+        except:
+            pass
     else:
         resfile = 'results/ggc_mock.u0.t1.0_z0.0_a0.5_1426268715_mcmc'
     model_file = resfile.replace('_mcmc','_model')
-    bcolor='green'
     pcolor='orange'
     nsample = 10
     
@@ -74,29 +77,28 @@ if __name__ == "__main__":
 
     # Calibration figure
     cfig, cax = calfig(mwave, calvec, specvecs, norm=norm,
-                       labelprefix='Schiavon ', fax=(None, cax), basecolor=bcolor)
-    cax.set_ylabel(r'Calibration $F_{{obs}}/F_{{\lambda, intrinsic}}$')
-    cax.legend(loc=0, prop={'size':8})
-    #cax.set_ylim(0.2, 1.6)
+                       mlabel='Schiavon', caltype='full',
+                       fax=(None, cax), basecolor=bcolor)
+    cax = format_calax(cax, norm)
+    
     # Intrinsic SED figure
     sfig, sax = sedfig(fwave, fspecvecs, [pwave, mosed, mosed_unc], pvecs,
                        norm=1/obsdat['normalization_guess'], fax=(None,sax),
                        labelprefix='Observed', peraa=True, basecolor=bcolor, pointcolor=pcolor)
-    sax.set_xscale('log')
[…]

### 2015-07-04 tex/figures.tex
prettify noise_realization figure, some minor changes in discussion text
prettier plots, add soem info in text about GP not having same degeneracies with real parameters as a polynomial

@@
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
-\caption{Observational data. 
-Top: The calibrated spectrum for \excluster.
-Middle: The signal-to-noise ratio.
-Bottom: The spectrophotometric calibration vector determined by
-\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
-\end{center}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
+%\caption{Observational data. 
+%Top: The calibrated spectrum for \excluster.
+%Middle: The signal-to-noise ratio.
+%Bottom: The spectrophotometric calibration vector determined by
+%\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
+%\end{center}
+%\end{figure}
 
@@
 \label{fig:speconly_uncalibrated}}
+\end{figure*}
+
+\begin{figure*}[h!]
+\includegraphics[width=\textwidth]{figures/components.pdf}
+\caption{Components of the spectroscopic calibration.  
+Top Left: Posterior samples of the smooth component of the calibration
+vector, the exponential of a polynomial.  The input true calibration
+vector is shown in {\it black}.
+Bottom Left: The Gaussian Process prediction conditioned on the residual
+between the data and posterior samples of the mean model including the
+smooth calibration component.
+Top Right: Posterior samples of the sum of the smooth calibration
+component and the Gaussian Process prediction, compared to the input
+true calibration vector ({\it black}).
+Bottom Right: Ratio of the sum of the smooth calibration component and
+the Gaussian Process prediction to the input
+calibration vector ({\it black}).
+\label{fig:components}}
 \end{figure*}
@@
 Left: Results when varying age.
-Middle: Results when varying metallicity.
-Right: Results when varying dust attenuation.
+Middle: Results when varying dust attenuation.
+Right: Results when varying metallicity.
  \label{fig:mock_parameter_space}}

### 2015-07-04 tex/ms.tex
prettier plots, add soem info in text about GP not having same degeneracies with real parameters as a polynomial

@@
 function (covariant uncertainties the same as adding a function.)
+Using a polynomial can result in degeneracies between model and
+polynomial parameters, whereas GP is only for things that {\it can't}
+be fit by model.
 
@@
 
-\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
-  photometric band, with the full calibration model.  This is how much
-  including additional calibration flexibility hurts the posterior
-  PDFs compared to perfectly known calibration.}
+\item \sout{Mock perfectly calibrated data: inference using
+spectroscopy and one photometric band, with the full calibration
+model.  This is how much including additional calibration flexibility
+hurts the posterior PDFs compared to perfectly known calibration.}
+Make sure this is run for the linear model, make sure it is converged.
 
@@
   spectroscopy only.}
+Make sure this is run for the linear model.
 
@@
 
-\item Real uncalibrated spectrum:   Inference using spectroscopy and all
-  photometry, with full calibration model.
+\item \sout{Real uncalibrated spectrum:   Inference using spectroscopy and all
+  photometry, with full calibration model. } Make sure this is
+converged, make sure priors and jitter make sense.
 
@@
 
-\item how (some) of these things vary with S/N
+\item how parameter inference varies with photometric S/N.  Do for mag
+  uncertainties of 0.05.
 

### 2015-07-04 code/make_paper.sh

@@ -5,15 +5,15 @@ ft="9.0"
 fz="0.0"
 fa="0.5"
 fall="t${ft}_z${fz}_a${fa}"
-python make_ggc_mocks #$ft $fz $fa
+#python make_ggc_mocks #$ft $fz $fa
 
 ### Then we fit the mocks and assign output names to variables
-./runjobs.sh
+#./runjobs.sh
 specphot_ideal="results/ggc_mock_ideal.c0.t9.0_z0.0_a0.5_1430261146_mcmc"
 speconly_cal="results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430808300_mcmc"
 speconly_uncal="results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc"
 specphot_uncal="results/ggc_mock_specphot_linear.u0.t9.0_z0.0_a0.5_5280432_1431898211_mcmc"
-photonly=""
+photonly="results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc"
 
 noise_runs="ls results/ggc_mock_specphot_linear.u[1-9]*.${fall}_*_mcmc"
 age_runs="ls results/ggc_mock_specphot_linear.u0.t*_z${fz}_a${fa}_*_mcmc"
@@ -26,20 +26,23 @@ real_uncal="results/ggc_ngc1851_uncal_tightprior_1433448554_mcmc"
 #fig 1
 python plot_data.py
 #fig 2
-python plot_ideal_dashboard.py $specphot_ideal green
-cp "${specphot_ideal%_mcmc}_dashboard.pdf" ../tex/figures/ideal.pdf
+python plot_ideal_dashboard.py $specphot_ideal green "Ideal, Perfectly Known calibration"
+cp "${specphot_ideal%_mcmc}.dashboard.pdf" ../tex/figures/ideal.pdf
 #fig 3
-python plot_dashboard.py $speconly_cal blue
-cp "${speconly_cal%_mcmc}_dashboard.pdf" ../tex/figures/speconly_calibrated.pdf
+python plot_dashboard.py $speconly_cal blue "Spectroscopy Only, Calibrated data"
+cp "${speconly_cal%_mcmc}.dashboard.pdf" ../tex/figures/speconly_calibrated.pdf
 #fig 4
-python plot_dashboard.py $speconly_uncal blue
-cp "${speconly_uncal%_mcmc}_dashboard.pdf" ../tex/figures/speconly_uncalibrated.pdf
[…]

### 2015-07-04 code/plot_dashboard.py

@@ -82,7 +82,10 @@ if __name__ == "__main__":
     haxes = np.array([pl.subplot(gs2[i, j]) for i in [2,3] for j in [0,1]])
 
     # Calibration figure
-    rescale=1e18
+    if norm < 1e10:
+        rescale = 1
+    else:
+        rescale = 1e18
     cfig, cax = calfig(mwave, calvec, specvecs, norm=norm, rescale=rescale,
                        fax=(None, cax), caltype='full', basecolor=bcolor)
     cax = format_calax(cax, norm, rescale=rescale)

### 2015-07-04 code/plot_ideal_dashboard.py

@@ -12,14 +12,8 @@ from bsfh.gp import ExpSquared
 from plotting import *
 matplotlib.colors.cnames.update(newcolors)
 
-
 sps = sps_basis.StellarPopBasis()
-import george
-kernel = (george.kernels.WhiteKernel(0.0) +
-          0.0 * george.kernels.ExpSquaredKernel(0.0))
-#gp = george.GP(kernel)#, solver=george.HODLRSolver)
 gp = ExpSquared(None, None)
-
 
 param_name_map = {'tage':'Age (Gyr)',
                   'mass': '$M_*$ $(M_\odot)$',
@@ -31,15 +25,23 @@ param_name_map = {'tage':'Age (Gyr)',
 
 pnmap = param_name_map
 
-
 if __name__ == "__main__":
 
+    basecolor = 'green'
+    suptitle = 'Ideal, Perfectly Known Calibration'
     if len(sys.argv) > 1:
         resfile=sys.argv[1]
+        try:
+            basecolor = sys.argv[2]
+        except:
+            pass
+        try:
+            suptitle = sys.argv[3]
+        except:
+            pass
     else:
         resfile = 'results/ggc_mock_ideal.c0.t9.0_z0.0_a0.5_1430261146_mcmc'
     model_file = resfile.replace('_mcmc','_model')
-    basecolor = 'green'
     pointcolor='orange'
     nsample = 10
 
@@ -87,5 +89,5 @@ if __name__ == "__main__":
     haxes[0].legend(loc=0, prop={'size':8})
 
     # Save
-    fig.suptitle('Ideal Case')
+    fig.suptitle(suptitle)
     fig.savefig(resfile.replace('_mcmc','.dashboard.pdf'))

### 2015-07-04 code/plot_joint_posterior.py

@@ -1,13 +1,29 @@
-import sys, pickle
+import sys, pickle, matplotlib
 import numpy as np
 import matplotlib.pyplot as pl
 from matplotlib import gridspec
 
 from bsfh import read_results as bread
 from plotting import *
+nc = newcolors.copy()
+#nc.pop('magenta')
+matplotlib.colors.cnames.update(nc)
+
+param_name_map = {'tage':'Age (Gyr)',
+                  'mass': '$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':'$A_V$ (mag)',
+                  'zmet': '$\log Z/Z_\odot$',
+                  'sigma_smooth': '$\sigma_{{LSF}}$',
+                  'zred': '${\it z}$',
+                  }
+pnmap = param_name_map
 
 def joint_pdf(res, p1, p2, **kwargs):
     trace, pars = hist_samples(res, res['model'], [p1, p2], **kwargs)
+    if p1 == 'mass':
+        trace[:,1] /= 1e5
+    if p2 == 'mass':
+        trace[:,0] /= 1e5
     trace = trace.copy().T
     xbins, ybins, sigma = compute_sigma_level(trace[0], trace[1])
     return xbins, ybins, sigma.T
@@ -38,14 +54,14 @@ def compute_sigma_level(trace1, trace2, nbins=30):
 if __name__ == "__main__":
     photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
     speconly = 'results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc'
-    specphot = 'results/ggc_mock_specphot.u0.t9.0_z0.0_a0.5_1430380402_mcmc'
+    specphot = 'results/ggc_mock_specphot_linear.u0.t9.0_z0.0_a0.5_5280432_1431898211_mcmc'
     resfiles = [photonly, speconly, specphot]
     clr = ['red','blue', 'magenta']
     results = [bread.read_pickles(rfile, model_file=rfile.replace('mcmc','model'))[0]
                for rfile in resfiles]
     obsdat = results[0]['obs']
     showpars = np.array(['mass', 'tage', 'zmet', 'dust2'])
-    parlims = np.array([[0.4e5, 4e5],
+    parlims = np.array([[0.4, 4],
                         [None, None],
                         [-1.0, 0.19],
                         [0, 1.5]])
[…]

### 2015-07-04 code/plot_photonly_dashboard.py

@@ -1,4 +1,4 @@
-import sys, pickle
+import sys, pickle, matplotlib
 import numpy as np
 import matplotlib.pyplot as pl
 from matplotlib import gridspec
@@ -8,23 +8,37 @@ from bsfh import sps_basis
 from bsfh.gp import ExpSquared
 
 from plotting import *
+matplotlib.colors.cnames.update(newcolors)
 
 sps = sps_basis.StellarPopBasis()
-import george
-kernel = (george.kernels.WhiteKernel(0.0) +
-          0.0 * george.kernels.ExpSquaredKernel(0.0))
-#gp = george.GP(kernel, solver=george.HODLRSolver)
 gp = ExpSquared(None, None)
 
+param_name_map = {'tage':'Age (Gyr)',
+                  'mass': '$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':'$A_V$ (mag)',
+                  'zmet': '$\log Z/Z_\odot$',
+                  'sigma_smooth': '$\sigma_{{LSF}}$',
+                  'zred': '${\it z}$',
+                  }
+pnmap = param_name_map
 
 if __name__ == "__main__":
 
+    basecolor = 'red'
+    suptitle = "Photometry Only"
     if len(sys.argv) > 1:
         resfile=sys.argv[1]
+        try:
+            basecolor = sys.argv[2]
+        except:
+            pass
+        try:
+            suptitle = sys.argv[3]
+        except:
+            pass
     else:
         resfile = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
     model_file = resfile.replace('_mcmc','_model')
-    basecolor = 'red'
     pointcolor='orange'
     nsample = 10
     
@@ -55,18 +69,15 @@ if __name__ == "__main__":
                        norm=1/obsdat['normalization_guess'], fax=(None,sax),
                        peraa=True, basecolor=basecolor, pointcolor=pointcolor)
     sax.plot(twave, tspec, color='black', label='True spectrum', alpha = 0.75)
-
-    sax.set_xscale('log')
-    sax.set_xlim(2.5e3, 1.6e4)
-    sax.legend(loc=0, prop={'size':12})
+    sax = format_sedax(sax)
     
     # Posterior parameter histograms
     pnames = ['mass', 'tage', 'dust2', 'zmet']
     samples, pnames_ord = hist_samples(res, mod, pnames, start=0.75, thin=10)
[…]

### 2015-07-04 code/plot_real_dashboard.py

@@ -1,4 +1,4 @@
-import sys, pickle
+import sys, pickle, matplotlib
 import numpy as np
 import matplotlib.pyplot as pl
 from matplotlib import gridspec
@@ -8,6 +8,7 @@ from bsfh import sps_basis
 from bsfh.gp import ExpSquared
 
 from plotting import *
+matplotlib.colors.cnames.update(newcolors)
 
 sps = sps_basis.StellarPopBasis()
 gp = ExpSquared(None, None)
@@ -64,14 +65,15 @@ if __name__ == "__main__":
         
     ### Build Figure ###
     fig = pl.figure(figsize=(10,8))
-    # Set up left hand side
-    gs1 = gridspec.GridSpec(3, 1)
-    gs1.update(left=0.05, right=0.48, wspace=0.05)
-    oax = pl.subplot(gs1[0,0])
-    cax = pl.subplot(gs1[1:,0])    
     # Set up right hand side
+    gs1 = gridspec.GridSpec(3, 1)
+    gs1.update(left=0.55, right=0.98, wspace=0.05, hspace=0.01)
+    oax = pl.subplot(gs1[0,0])
+    cax = pl.subplot(gs1[1:,0])
+
+    # Set up left hand side
     gs2 = gridspec.GridSpec(4, 2)
-    gs2.update(left=0.55, right=0.98, hspace=0.5)
+    gs2.update(left=0.05, right=0.45, hspace=0.5)
     sax = pl.subplot(gs2[0:2,:])
     haxes = np.array([pl.subplot(gs2[i, j]) for i in [2,3] for j in [0,1]])
 
@@ -91,8 +93,10 @@ if __name__ == "__main__":
     # Residual Figure    
     ofig, oax = residualfig(mwave, mospec, specvecs, unc=mounc,
                             basecolor=bcolor,fax=(None,oax), chi=True)
-    oax.set_ylabel(r'$\chi$')
+    oax.set_ylabel(r'$\chi$', fontsize=12)
     oax.legend(loc=0, prop={'size':8})
+    oax.tick_params(axis='both', which='major', labelsize=8)
+    oax.set_xticklabels([''])
     oax.set_ylim(-3,3)
 
     # Posterior parameter histograms

### 2015-07-04 code/plotting.py

@@ -2,17 +2,17 @@ import numpy as np
 import matplotlib.pyplot as pl
 import bsfh.read_results as bread
 from copy import deepcopy
-import matplotlib
 
 newcolors = {'blue':u'#5DA5DA',
              'orange': u'#FAA43A',
              'green': u'#60BD68',
              'red': u'#F15854',
-             'magenta':u'#FF70B1', #actually pink
+#             'magenta':u'#FF70B1', #actually pink
              'cyan': u'#39CCCC', #actually teal
              'yellow': u'#FFDC00',
              'maroon': u'#85144B',
             }
+import matplotlib
 matplotlib.colors.cnames.update(newcolors)
 
 def comp_samples(thetas, model, obs, sps=None, gp=None):
@@ -257,7 +257,7 @@ def hist_samples(res, model, showpars, start=0, thin=1,
     parnames = np.array(model.theta_labels())
     start_index = np.floor(start * (niter-1)).astype(int)
     flatchain = res['chain'][:,start_index::thin,:]
-    dims = flatchain.shape[0], flatchain.shape[1], flatchain.shape[2]
+    dims = flatchain.shape
     flatchain = flatchain.reshape(dims[0]*dims[1], dims[2])
     ind_show = np.array([p in showpars for p in parnames], dtype= bool)
     flatchain = flatchain[:, ind_show]
@@ -414,5 +414,5 @@ def format_calax(cax, norm, rescale=1):
     cax.set_xlabel('$\lambda (\AA)$', fontsize=12)
     cax.tick_params(axis='both', which='major', labelsize=8)
     cax.set_ylabel(cax.get_ylabel(), fontsize=12)
-    cax.legend(loc=0, prop={'size':12})
+    cax.legend(loc='lower right', prop={'size':12})
     return cax

### 2015-07-06 tex/figures.tex
plotting for n_phot trials, more plot prettification

@@
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/components.pdf}
-\caption{Components of the spectroscopic calibration.  
-Top Left: Posterior samples of the smooth component of the calibration
-vector, the exponential of a polynomial.  The input true calibration
-vector is shown in {\it black}.
-Bottom Left: The Gaussian Process prediction conditioned on the residual
-between the data and posterior samples of the mean model including the
-smooth calibration component.
-Top Right: Posterior samples of the sum of the smooth calibration
-component and the Gaussian Process prediction, compared to the input
-true calibration vector ({\it black}).
-Bottom Right: Ratio of the sum of the smooth calibration component and
-the Gaussian Process prediction to the input
-calibration vector ({\it black}).
-\label{fig:components}}
-\end{figure*}
-
-\begin{figure*}[h!]
 \includegraphics[width=0.5 \textwidth]{figures/photonly.pdf}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
+\includegraphics[width=\textwidth]{figures/components.pdf}
+\caption{Components of the spectroscopic calibration.  
+Top Left: Posterior samples of the smooth component of the calibration
+vector, the exponential of a polynomial.  The input true calibration
+vector is shown in {\it black}.
+Bottom Left: The Gaussian Process prediction conditioned on the residual
+between the data and posterior samples of the mean model including the
+smooth calibration component.
+Top Right: Posterior samples of the sum of the smooth calibration
+component and the Gaussian Process prediction, compared to the input
+true calibration vector ({\it black}).
+Bottom Right: Ratio of the sum of the smooth calibration component and
+the Gaussian Process prediction to the input
+calibration vector ({\it black}).
+\label{fig:components}}
+\end{figure*}
+
+\begin{figure*}[h!]
+%\includegraphics[width=\textwidth]{figures/calibration_posterior.pdf}
 \caption{Joint Posterior PDFs for the calibration parameters inferred
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
+\includegraphics[width=\textwidth]{figures/vary_nphot.pdf}
 \caption{The value of more photometry. Marginalized posterior PDFs
@@
 
-\begin{figure*}[h!]
+%\begin{figure*}[h!]
 %\includegraphics[width=\textwidth]{figures/inferred_calibration.pdf}
-\caption{Left: Ratio of the calibration vector inferred from the
-  real uncalibrated spectrum to that inferred from the real calibrated
-  spectrum ({\it green}). Taking the ratio reduces the effects of model
-  imperfections and shows how well we are able to infer the
-  calibration vector of \citet{schiavon05} ({\it black}).  
-Right: Joint posterior PDFs for the inferred calibration parameters.
-\label{fig:real_calibration_ratio}}
-\end{figure*}
+%\caption{Left: Ratio of the calibration vector inferred from the
+%  real uncalibrated spectrum to that inferred from the real calibrated
+%  spectrum ({\it green}). Taking the ratio reduces the effects of model
+%  imperfections and shows how well we are able to infer the
+%  calibration vector of \citet{schiavon05} ({\it black}).  
+%Right: Joint posterior PDFs for the inferred calibration parameters.
+%\label{fig:real_calibration_ratio}}
+%\end{figure*}
 

### 2015-07-06 code/plot_phys_summary.py

@@ -1,4 +1,4 @@
-import sys, pickle
+import sys, pickle, matplotlib
 import numpy as np
 import matplotlib.pyplot as pl
 from matplotlib import gridspec
@@ -8,6 +8,7 @@ from matplotlib import rcParams
         
 from bsfh import read_results as bread
 from plotting import *
+matplotlib.colors.cnames.update(newcolors)
 
 pnames = ['mass','tage','zmet','dust2']
 pmap = {'mass': lambda x: np.log10(x),
@@ -48,11 +49,12 @@ if __name__ == "__main__":
              ]
     aruns = ['results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a0.0_5313557_1432675536_mcmc',
              'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a0.5_5313542_1432675345_mcmc',
-             'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a1.0_5313614_1432675422_mcmc'
+             'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a1.0_5313614_1432675422_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a2.0_5391265_1434182123_mcmc'
              ]
-    zruns = ['results/ggc_mock_specphot_linear.u0.t12.0_z-1.5_a2.0_5354872_1433350381_mcmc',
-             'results/ggc_mock_specphot_linear.u0.t12.0_z-1.0_a2.0_5354866_1433350364_mcmc',
-             'results/ggc_mock_specphot_linear.u0.t12.0_z-0.5_a2.0_5354863_1433350639_mcmc',
+    zruns = ['results/ggc_mock_specphot_linear.u0.t12.0_z-1.5_a0.5_5391259_1434126258_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t12.0_z-1.0_a0.5_5391258_1434122880_mcmc',
+             'results/ggc_mock_specphot_linear.u0.t12.0_z-0.5_a0.5_5391256_1434100928_mcmc',
              'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a0.5_5313542_1432675345_mcmc'
              ]
         

### 2015-07-06 code/plot_real_joint_posterior.py

@@ -1,0 +1,129 @@
+import sys, pickle, matplotlib
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib import gridspec
+
+from bsfh import read_results as bread
+from plotting import *
+nc = newcolors.copy()
+#nc.pop('magenta')
+matplotlib.colors.cnames.update(nc)
+
+param_name_map = {'tage':'Age (Gyr)',
+                  'mass': '$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':'$A_V$ (mag)',
+                  'zmet': '$\log Z/Z_\odot$',
+                  'sigma_smooth': '$\sigma_{{LSF}}$',
+                  'zred': '${\it z}$',
+                  }
+pnmap = param_name_map
+
+def joint_pdf(res, p1, p2, **kwargs):
+    trace, pars = hist_samples(res, res['model'], [p1, p2], **kwargs)
+    if p1 == 'mass':
+        trace[:,1] /= 1e5
+    if p2 == 'mass':
+        trace[:,0] /= 1e5
+    trace = trace.copy().T
+    xbins, ybins, sigma = compute_sigma_level(trace[0], trace[1])
+    return xbins, ybins, sigma.T
+
+
+def compute_sigma_level(trace1, trace2, nbins=30):
+    """From a set of traces, bin by number of standard deviations"""
+    L, xbins, ybins = np.histogram2d(trace1, trace2, nbins)
+    L[L == 0] = 1E-16
+    logL = np.log(L)
+
+    shape = L.shape
+    L = L.ravel()
+
+    # obtain the indices to sort and unsort the flattened array
+    i_sort = np.argsort(L)[::-1]
+    i_unsort = np.argsort(i_sort)
+
+    L_cumsum = L[i_sort].cumsum()
+    L_cumsum /= L_cumsum[-1]
+    
+    xbins = 0.5 * (xbins[1:] + xbins[:-1])
+    ybins = 0.5 * (ybins[1:] + ybins[:-1])
+
+    return xbins, ybins, L_cumsum[i_unsort].reshape(shape)
+
+
+if __name__ == "__main__":
+    photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
+    speconly = 'results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc'
[…]

### 2015-07-06 code/plotting.py

@@ -365,13 +365,16 @@ def deltafig_vspar(results, models, pname, pvary, pmap={},
         if verbose:
             print(pname, ir)
         truths[ir] = res['obs']['mock_params'][pname][0]
-        vary_param[ir] = res['obs']['mock_params'][pvary][0]
+        if type(pvary) is str:
+            vary_param[ir] = res['obs']['mock_params'][pvary][0]
         pct[ir,:] = np.percentile(samples, ptile)
         # Transform the values if pmap supplied for this param
         pct[ir,:] = pmap.get(pname, identity)(pct[ir,:])
         truths[ir] = pmap.get(pname, identity)(truths[ir])
         
     delta = (pct - truths[:, None])
+    if type(pvary) is not str:
+        vary_param = pvary
     if fractional:
         delta /= truths[:, None]
         #title += '$/$Truth'

### 2015-07-08 tex/ms.tex
more figure code

@@
 
-THIS SECTION NEEDS WORK; THIS IS JUST AN EQUATION DUMP.
-
-HOGG: A model is a parameterized likelihood function, with prior PDFs
-on the nuisance parameters (at least)...  There is a likelihood for
+A model is a parameterized likelihood function, with prior PDFs
+on the nuisance parameters (at least).  There is a likelihood for
 the photometry and for the spectroscopy...  Each of these penalizes
 the difference between a column vector of data and a column vector of
-model expectation value...
+model expectation value.
 
@@
 non-parameteric model of the calibration.  We do this using a Gaussian
-Process: BDJ: prior over functions, analytically marginalizable,
-covariant fractional uncertainties the same as multiplying by a
-function (covariant uncertainties the same as adding a function.)
+Process: 
+BDJ: prior over functions, analytically marginalizable, covariant
+fractional uncertainties the same as multiplying by a function
+(covariant absolute uncertainties the same as adding a function.)
 Using a polynomial can result in degeneracies between model and
-polynomial parameters, whereas GP is only for things that {\it can't}
-be fit by model.
+polynomial parameters, whereas GP only reduces the penalty for
+residuals that {\it can't} be fit by the mean model.
 
@@
 \\
-C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} \, \mu)^2]\,\delta_{nn'} +
- K_\alpha(\lambda_n - \lambda_{n'}) \ast \mu \, \transpose{\mu}
+C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} \, \mu_n)^2]\,\delta_{nn'} +
+ K_\alpha(\lambda_n - \lambda_{n'}) 
 \quad ,
@@
 and each $\lambda_n$ is the wavelength of spectral pixel $n$.
-The multiplication of $\hat{s}$ and $K_\alpha$ by $\mu$ and
-$\mu\,\transpose{\mu}$ respectively in the construction of $C_{nn'}$
-signifies that they are defined in \emph{fractional} terms.
 The calibration vector $f(\alpha)$ is going to take care of the
@@
 \\
-K_\alpha(\lambda_n - \lambda_{n'}) &=& a^2\,\exp\left(-\frac{[\lambda_n - \lambda_{n'}]^2}{2\,\ell^2}\right)
+K_\alpha(\lambda_n - \lambda_{n'}) &=& \mu_n\,\mu_{n'}\, a^2\,\exp\left(-\frac{[\lambda_n - \lambda_{n'}]^2}{2\,\ell^2}\right)
 \\
@@
 issues, while $a^2$ and $\ell^2$ set the variance and correlation
-length of the remaining covariant calibration noise.
+length of the remaining covariant calibration noise. The
+multiplication by $\mu_n\, \mu_{n'}$ in the kernel function signifies
+signifies that it is defined in \emph{fractional} terms.
 
-\section{Data and Experiments}
+\section{Data and Experimental Setup}
 
@@
 our methodology is applicable any spectral model: stars, galaxies or
-ISM emission.
+ISM emission or any object which can be modeled.
 
@@
 
-Optical photometry is available from \citep{vanderbeke14} based on
+Optical photometry is available from \citet{vanderbeke14} based on
 SDSS for objects in the northern hemisphere and on data from CTIO for
 southern hemisphere objects.  Briefly, total fluxes within the half-light radii
-of the clusters \citet{harris98} were calculated, with small
+of the clusters \citep{harris96} were calculated, with small
 corrections for stars unlikely to be cluster members based on their
@@
 Near-Infrared photometry is available from \citet{cohen07}, who fit
-King profiles \citet{king65} to 2MASS data in the $J$, $H$, and $K_s$
+King profiles \citet{king62} to 2MASS data in the $J$, $H$, and $K_s$
 bands.  To produce NIR photometry consistent with the optical we
@@
 Flexible Stellar Population Synthesis code \citep[FSPS][]{fsps}.  We
-use the Padova 2007 isochrones \citep{girardi00, bertilli94, marigo07}
+use the Padova 2007 isochrones \citep{girardi00, bertelli94, marigo07}
 and the MILES stellar spectral library \citep{miles_I, miles_II,
@@
 
+\bibitem[Cohen et al.(2007)]{cohen07} Cohen, J.~G., Hsieh, S., 
+Metchev, S., Djorgovski, S.~G., \& Malkan, M.\ 2007, \aj, 133, 99
+
 \bibitem[Conroy \etal(2009)]{fsps} 
@@
 
-\bibitem[Lee et al.(2011)]{xray_calunc} Lee, H., Kashyap, V.~L., 
+\bibitem[Harris(1996)]{harris96} Harris, W.~E.\ 1996, \aj, 112, 
+1487
+
+\bibitem[King(1962)]{king62} King, I.\ 1962, \aj, 67, 471
+
+\bibitem[Koleva et al.(2009)]{koleva09} Koleva, M., 
+Prugniel, P., Bouchard, A., \& Wu, Y.\ 2009, \aap, 501, 1269
+
+\bibitem[Lee et al.(2011)]{lee11} Lee, H., Kashyap, V.~L., 
 van Dyk, D.~A., et al.\ 2011, \apj, 731, 126
@@
 
+\bibitem[Vanderbeke et al.(2014)]{vanderbeke14} Vanderbeke, J., 
+West, M.~J., De Propris, R., et al.\ 2014, \mnras, 437, 1725
+
 \bibitem[Walker et al.(2015)]{walker15} Walker, M.~G., 

### 2015-07-08 code/plot_cal_posterior.py

@@ -15,6 +15,12 @@ param_name_map = {'tage':'Age (Gyr)',
                   'zmet': '$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',
+                  'gp_jitter': '${\it s}$',
+                  'gp_amplitude': '${\it a}$',
+                  'gp_length' : '$\ell (\AA)$',
+                  'spec_norm': '${\it c}_{0}$',
+                  'poly_coeffs_1': '${\it c}_{1}$',
+                  'poly_coeffs_2': '${\it c}_{2}$' 
                   }
 pnmap = param_name_map
 
@@ -54,23 +60,26 @@ def compute_sigma_level(trace1, trace2, nbins=30):
 
 
 if __name__ == "__main__":
-    truths = None # {'mass':, 'tage':, 'dust2':}
-    
-    real_cal="results/ggc_ngc1851_1432787257_mcmc"
-    real_uncal="results/ggc_ngc1851_uncal_tightprior_1433448554_mcmc"
-    resfiles = [real_cal, real_uncal]
-    clr = ['green', 'orange']
+    photonly = 'results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5_1430274922_mcmc'
+    speconly = 'results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc'
+    specphot = 'results/ggc_mock_specphot_linear.u0.t9.0_z0.0_a0.5_5280432_1431898211_mcmc'
+    resfiles = [specphot]
+    clr = ['maroon']
     results = [bread.read_pickles(rfile, model_file=rfile.replace('mcmc','model'))[0]
                for rfile in resfiles]
     obsdat = results[0]['obs']
-    showpars = np.array(['mass', 'tage', 'zmet', 'dust2'])
-    parlims = np.array([[0.4, 4],
+    showpars = np.array(['dust2', 'gp_jitter', 'gp_length', 'gp_amplitude',
+                         'spec_norm', 'poly_coeffs_1', 'poly_coeffs_2'])
+    parlims = np.array([[0.0, 1.5],
                         [None, None],
-                        [-2.0, 0.19],
-                        [0, 1.5]])
+                        [100, 1000],
+                        [0, 0.5],
+                        [-1, 1],
+                        [-10, 10],
+                        [-10, 10]])
     npar = len(showpars)
 
[…]

### 2015-07-08 code/plot_joint_posterior.py

@@ -25,6 +25,8 @@ def joint_pdf(res, p1, p2, **kwargs):
     if p2 == 'mass':
         trace[:,0] /= 1e5
     trace = trace.copy().T
+    if pars[0] == p1:
+        trace = trace[::-1, :]
     xbins, ybins, sigma = compute_sigma_level(trace[0], trace[1])
     return xbins, ybins, sigma.T
 
@@ -78,13 +80,14 @@ if __name__ == "__main__":
                 trace /= 1e5
             dax.hist(trace, bins = 30, color=clr[n], normed=True,
                      alpha=0.5, histtype='stepfilled')
+            dax.tick_params(axis='both', which='major', labelsize=8)
         # Axis label foo
 #        if i == 0:
 #            dax.set_ylabel(pnmap.get(p1, p1))
 #        else:
         dax.set_yticklabels('')
         if i == (npar-1):
-            dax.set_xlabel(pnmap.get(p2, p2))
+            dax.set_xlabel(pnmap.get(p2, p2), fontsize=12)
         else:
             dax.set_xticklabels('')
         for j, p2 in enumerate(showpars[(i+1):]):
@@ -97,11 +100,11 @@ if __name__ == "__main__":
                 
             # Axis label foo
             if i == 0:
-                ax.set_ylabel(pnmap.get(p2, p2))
+                ax.set_ylabel(pnmap.get(p2, p2), fontsize=12)
             else:
                 ax.set_yticklabels('')
             if k == (npar-1):
-                ax.set_xlabel(pnmap.get(p1,p1))
+                ax.set_xlabel(pnmap.get(p1,p1), fontsize=12)
                 dax.set_xlim(ax.get_xlim())
             else:
                 ax.set_xticklabels('')

### 2015-07-08 tex/figures.tex
more figure code
tweak text in S2, and elsewhere, switch from A_v to tau_V

@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/calibration_posterior.pdf}
+\includegraphics[width=\textwidth]{figures/calibration_post.pdf}
 \caption{Joint Posterior PDFs for the calibration parameters inferred
@@
 \includegraphics[width=\textwidth]{figures/vary_nphot.pdf}
-\caption{The value of more photometry. Marginalized posterior PDFs
-obtained from mock spectra and photometry, for different numbers of
-photometric bands.  The pdfs $g$-band only ({\it red}), $g$- and $i-$
-band ({\it blue}), and the combined SDSS $griz$ and 2MASS $JHK_s$ set of
-bands ({\it orange}).
+\caption{The value of more photometry in combination with optical
+spectroscopy. Marginalized posterior PDFs obtained from mock spectra
+and photometry, for different numbers of photometric bands. The
+medians of the posterior PDFs are shown as connected black circles,
+the 16th and 84th percentile of the posteriors are indicated by the
+gray shaded region.
 \label{fig:vary_phot}}
@@
 \begin{figure*}[h!]
-%\includegraphics[width=\textwidth]{figures/real_phys_posterior.png}
+\includegraphics[width=\textwidth]{figures/real_post.pdf}
 \caption{Inferred parameters for \excluster.  We show the inference from the
-  calibrated spectrum ({\it red}), from the uncalibrated spectrum
-  ({\it blue}), and from the CMD ({\it black}).
+  calibrated spectrum ({\it green}), from the uncalibrated spectrum
+  ({\it orange}), and from the CMD ({\it black}).
 \label{fig:real_parameters}}

### 2015-07-08 tex/ms.tex
tweak text in S2, and elsewhere, switch from A_v to tau_V

@@
 on the nuisance parameters (at least).  There is a likelihood for
-the photometry and for the spectroscopy...  Each of these penalizes
+the photometry and for the spectroscopy.  Each of these penalizes
 the difference between a column vector of data and a column vector of
@@
 This modification shows the necessity of including the log-variance
-term.
+term.  Large $s$ reduces the penalty for individual large residuals,
+but also reduces the reward for well-fit data.
 This---equation~(\ref{eq:photometricLF})---is in fact the
@@
 s/\mu(\theta)$ is a nuisance noise-model parameter representing
-additonal fractional uncertainty in the flux.  The Gaussian Process
-will be a generalization of this modification.
+additonal fractional uncertainty in the flux.
 
@@
 spectrophotometric calibration in our likelihood function.  We take
-this calibration-vector that modifies the mean spectroscopic model to
+the calibration-vector that modifies the mean spectroscopic model to
 produce the observed spectrum to be multiplicative with respect to the
@@
 may be unknown.  It is therefore desirable to introduce a
-non-parameteric model of the calibration.  We do this using a Gaussian
-Process: 
-BDJ: prior over functions, analytically marginalizable, covariant
-fractional uncertainties the same as multiplying by a function
-(covariant absolute uncertainties the same as adding a function.)
-Using a polynomial can result in degeneracies between model and
-polynomial parameters, whereas GP only reduces the penalty for
-residuals that {\it can't} be fit by the mean model.
+`non-parameteric' model of the calibration.  We do this using a
+Gaussian Process in the likelihood function.  The Gaussian Process is
+a generalization of the modified log-likelihood introduced in
+Equation \label{eq:photometricLF} that allows for correlated noise in
+the residuals, as would be introduced by inaccurate calibration.
+
+%BDJ: prior over functions, analytically marginalizable, covariant
+%fractional uncertainties the same as multiplying by a function
+%(covariant absolute uncertainties the same as adding a function.)
 
@@
 large-scale calibration residual; the Gaussian Process is going to
-pick up smaller-scale residuals away from \emph{that}.
-The flexibility of the Gaussian Process specified by $C$ will obviate
-the need for numerous high order polynomial terms in $f(\alpha)$ and
-thus reduce the number of free parameters required in the model.  The
-prior over functions implied by $C$ is analytically conditioned on the
-residuals $\Delta$.
+pick up smaller-scale residuals away from \emph{that}.  The
+flexibility of the Gaussian Process specified by $C$ will obviate the
+need for numerous high order polynomial terms in $f(\alpha)$ and thus
+reduce the number of free parameters required in the model.
 This---equation~(\ref{eq:spectroscopicLF})---is the log-likelihood we
@@
 scaled by a fiducial wavelength $\lambda_0$.  The exponentiation of
-the polynomial in ensures that $f(\alpha)$ is everywhere positive.
+the polynomial ensures that $f(\alpha)$ is everywhere positive.
 Nuisance parameters $c_m$ set the shape of the large-scale calibration
 issues, while $a^2$ and $\ell^2$ set the variance and correlation
-length of the remaining covariant calibration noise. The
-multiplication by $\mu_n\, \mu_{n'}$ in the kernel function signifies
-signifies that it is defined in \emph{fractional} terms.
+length of the remaining covariant calibration noise. Structure in the
+residuals on the scale of $\ell$ and with amplitude $a$ will not be
+strongly penalized, but the determinant of $C$ becomes larger for
+larger $a$ and smaller $\ell$. The multiplication by $\mu_n\,
+\mu_{n'}$ in the kernel function signifies that it is defined in
+\emph{fractional} terms.  Using a high-order polynomial can result in
+strong degeneracies between model and polynomial parameters, whereas
+the GP {\color{blue} BDJ make this more precise and correct} only
+reduces the likelihood penalty for residuals on the scale of $\ell$
+with amplitude $a$ that {\it can't} be fit by the mean model.
 
@@
 f_{\theta_s}(\lambda_o) & = &
-L(\sigma_s, z) ,\, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
+L(\sigma_s, z) \, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
 \nonumber \\ 
@@
 
-\item Mock uncalibrated data:  vary the photometric bands to see how
-  much it changes the recovery of the parameters.
+\item \sout{Mock uncalibrated data:  vary the photometric bands to see how
+  much it changes the recovery of the parameters.}
 
@@
 where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
-logarithmic residual between the data and the model \citep{RW}.  For the
-perfectly calibrated spectrum the true calibration vector (shown in
-black) is one everywhere.  The spread of the inferred calibration
-vectors approximately indicates our uncertainty in the spectrophotometric
-calibration when no additional calibration information is available
-and only a single photometric point is available.
+residual between the data and the model \citep{RW},
+defined here as 
+\begin{eqnarray} \label{eq:calibration}
+\tilde{\Delta} & = & K \, C^{-1} \, \Delta
+\end{eqnarray}.  
+For the perfectly calibrated spectrum the true calibration vector
+(shown in black) is one everywhere.  The spread of the inferred
+calibration vectors approximately indicates our uncertainty in the
+spectrophotometric calibration when no additional calibration
+information is available and only a single photometric point is
+available.
 
@@
 inference on an \emph{uncalibrated} mock spectrum.  The results are
-similar to the case of the \emph{calibrated} spectrum.
+similar to the case of the \emph{calibrated} spectrum. An important
+difference is that the inferred calibration vector now contains numerous small scale wiggles,
+similar to the actual calibration vector.  The overall shape of the
+spectrum is still unconstrained, leading to large degeneracies between
+the polynomial terms and the dust attenuation.
 
@@
 or approximately remove gross features that are difficult to model
-parametrically or via a Gaussian Process.  {\color{blue} Discuss more
-complicated covariance kernels, multiple kernels, combining fractional
-and absolute covariance amplitudes.}
+parametrically or via a Gaussian Process. A Guassian Process can be
+used to model covaraint noise resulting from errors in an initial
+calibration (of an amplitude $a$) thus propogating calibration
+uncertainty into the model parameters $\theta$. 
+{\color{blue} Discuss more complicated covariance kernels, multiple
+kernels, combining fractional and absolute covariance amplitudes.}
 
@@
 care must be taken to avoid absorbing interesting model deficiencies
-into the calibration model. For example, in the model we have
-described, it is possible that broad shallow features (for example due
-to molecular bands or absorption line complexes) will be absorbed into
-the Gaussian Process if not properly included in the mean model. The
-Gaussian process will also absorb incorrectly modeled attenuation
-curve shapes. Third, we have made the assumption that the spectroscopy
+into the calibration model, or interpreting features in the
+calibration vector as features of the mean model. For example, in the
+model we have described, it is possible that broad shallow features
+(for example due to molecular bands or absorption line complexes) will
+be absorbed into the Gaussian Process if not properly included in the
+mean model. The Gaussian process will also absorb incorrectly modeled
+attenuation curve shapes. On the other hand, the higher likelihood at
+zero residual means that calibration features that \emph{can} be
+mimicked by the mean model may influence the mean model
+parameters. Third, we have made the assumption that the spectroscopy
 and the photometry are sampling the same populations.  In practice,
@@
 spectral models of astrophysical objects, then there is often no
-reason not to use those objects themselves as calibrators,
-especially if you expect your calibration to be spatially or 
-temporally variable, or to change with the brightness or other
-properties of the object.
+reason not to use those objects themselves as calibrators, especially
+if you expect your calibration to be spatially or temporally variable,
+or to change with the brightness or other properties of the object.
 

### 2015-07-08 code/plot_dashboard.py

@@ -15,7 +15,7 @@ gp = ExpSquared(None, None)
 
 param_name_map = {'tage':'Age (Gyr)',
                   'mass': '$M_*$ $(M_\odot/10^{5})$',
-                  'dust2':'$A_V$ (mag)',
+                  'dust2':'$\tau_V$',
                   'zmet': '$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',

### 2015-07-08 code/plot_ideal_dashboard.py

@@ -17,7 +17,7 @@ gp = ExpSquared(None, None)
 
 param_name_map = {'tage':'Age (Gyr)',
                   'mass': '$M_*$ $(M_\odot)$',
-                  'dust2':'$A_V$ (mag)',
+                  'dust2':'$\tau_V$',
                   'zmet': '$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',

### 2015-07-08 code/plot_joint_posterior.py

@@ -11,7 +11,7 @@ matplotlib.colors.cnames.update(nc)
 
 param_name_map = {'tage':'Age (Gyr)',
                   'mass': '$M_*$ $(M_\odot/10^{5})$',
-                  'dust2':'$A_V$ (mag)',
+                  'dust2':'$\tau_V$',
                   'zmet': '$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',

### 2015-07-08 code/plot_nphot.py

@@ -13,12 +13,12 @@ pmap = {'mass': lambda x: np.log10(x),
 plabel_map = {'mass':r'log M$_*$',
               'tage': 'log Age',
               'zmet': r'log $Z/Z_\odot$',
-              'dust2':r'A$_V$'
+              'dust2':r'$\tau_V$'
               }
 pvlabel_map = {'mass':r'M$_*$',
               'tage': 'Age (Gyr)',
               'zmet': r'log $Z/Z_\odot$',
-              'dust2':r'A$_V$'
+              'dust2':r'$\tau_V$'
               }
 
 sfraction = 0.90

### 2015-07-08 code/jobscripts/runjob_mac.sh
start reorganizing for consistent runs and mocks, switching to linear fitting, fix strings for some plots

@@ -1,32 +1,25 @@
 #!/bin/bash
 
-#python make_ggc_mock --tage=1.0 --zmet=0.0 --dust2=0.5 --add_noise=False --apply_cal=True
-
-#speconly_ideal
+# speconly_ideal
 mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_ideal.py \
        --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl \
        --outfile=$PROJECTS/speccal/code/results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5 \
-       --nwalkers=126 --niter=1024 --do_powell=False 
+       --nwalkers=126 --niter=1024 --do_powell=False \
+       --noisefactor=10.0
 
 # speconly_calibrated, lo S/N
-mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_losn.py \
+mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_linear.py \
   --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl \
   --outfile=$PROJECTS/speccal/code/results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5 \
-  --nwalkers=126 --niter=1024 --do_powell=False
+  --nwalkers=126 --niter=1024 --do_powell=False \
+  --noisefactor=10.0
 
-#speconly_uncalibrated, lo S/N
-mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_losn.py \
+# speconly_uncalibrated, lo S/N
+mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_speconly_linear.py \
        --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl \
        --outfile=$PROJECTS/speccal/code/results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5 \
-       --nwalkers=254 --niter=6144 --do_powell=False
-
-#specphot
[…]

### 2015-07-08 code/make_paper.sh

@@ -1,14 +1,19 @@
 #!bin/sh
 
+# define a version
+version="v1.0"
+
 # First we make the mocks with fiducial parameters
 ft="9.0"
 fz="0.0"
 fa="0.5"
 fall="t${ft}_z${fz}_a${fa}"
-#python make_ggc_mocks #$ft $fz $fa
+#python make_ggc_mocks #$version $ft $fz $fa
 
-### Then we fit the mocks and assign output names to variables
+### Then we build jobsripts and fit the mocks 
 #./runjobs.sh
+
+# and assign output names to variables
 specphot_ideal="results/ggc_mock_ideal.c0.t9.0_z0.0_a0.5_1430261146_mcmc"
 speconly_cal="results/ggc_mock_speconly.c0.t9.0_z0.0_a0.5_1430808300_mcmc"
 speconly_uncal="results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc"

### 2015-07-08 code/paramfiles/mock_speconly_ideal.py

@@ -14,7 +14,7 @@ run_params = {'verbose':True,
               'nburn':[16, 32, 32, 64, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
-              'logify_spectrum':True,
+              'logify_spectrum':False,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,

### 2015-07-08 code/paramfiles/mock_speconly_linear.py

@@ -14,7 +14,7 @@ run_params = {'verbose':True,
               'nburn':[64, 64, 128, 128, 256], 'niter':512,
               'initial_disp':0.1,
               'debug':False,
-              'logify_spectrum':True,
+              'logify_spectrum':False,
               'normalize_spectrum':True,
               'norm_band_name':'sdss_g0',
               'rescale':True,

### 2015-07-08 code/paramfiles/mock_specphot.py

@@ -1,212 +1,0 @@
-import numpy as np
-import pickle, os
-from bsfh import priors, sedmodel
-from sedpy import attenuation
-
-#The speccal directory
-sdir = os.path.join(os.environ['PROJECTS'], 'speccal')
-
-run_params = {'verbose':True,
-              'outfile':'results/ggc_mock_specphot_u0_t9.0_z0.0_a0.5',
-              'do_powell': False,
-              'ftol':0.5e-4, 'maxfev':5000,
-              'nwalkers':64, 
-              'nburn':[64, 64, 128, 128, 256], 'niter':512,
-              'initial_disp':0.1,
-              'debug':False,
-              'logify_spectrum':True,
-              'normalize_spectrum':True,
-              'norm_band_name':'sdss_g0',
-              'rescale':True,
-              'filename':os.path.join(sdir, 'data/ggclib/mocks/miles/ggc_mock.u0.t9.0_z0.0_a0.5.pkl'),
-              'wlo':3350.,
-              'whi':6500.,
-              'noisefactor':10
-              }
-
-##### OBSERVATIONAL DATA ######
-
-def load_obs(filename=None, noisefactor=1.0, **extras):
-    with open(filename) as f:
-        obs = pickle.load(f)
-    #obs['phot_mask'] = np.array(['sdss_g' in filt.name for filt in obs['filters']])
-    obs['unc'] *= noisefactor
-    obs['noisefactor'] = noisefactor
-    return obs
-
-obs = load_obs(**run_params)
-
-###### MODEL ###########
-model_type = sedmodel.SedModel
-
-model_params = []
-
-###### Distance ##########
-model_params.append({'name': 'lumdist', 'N': 1,
-                     'isfree': False,
-                     'init': 0.01,
-                     'units': 'Mpc',
-                     'prior_function': None,
-                     'prior_args': None})
-
-###### SFH ################
-
-model_params.append({'name': 'mass', 'N': 1,
-                     'isfree': True,
-                     'init': 2e5,
-                     'units': r'M$_\odot$',
-                     'prior_function': priors.tophat,
-                     'prior_args': {'mini':1e4, 'maxi': 1e6}})
-
-model_params.append({'name': 'tage', 'N': 1,
-                        'isfree': True,
-                        'init': 5.0,
-                        'units': 'Gyr',
-                        'prior_function': priors.tophat,
-                        'prior_args':{'mini':0.1, 'maxi':15.0}})
-
[…]

### 2015-07-08 code/plot_cal_posterior.py

@@ -10,9 +10,9 @@ nc = newcolors.copy()
 matplotlib.colors.cnames.update(nc)
 
 param_name_map = {'tage':'Age (Gyr)',
-                  'mass': '$M_*$ $(M_\odot/10^{5})$',
-                  'dust2':'$\tau_V$',
-                  'zmet': '$\log Z/Z_\odot$',
+                  'mass': r'$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':r'$\tau_V$',
+                  'zmet': r'$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',
                   'gp_jitter': '${\it s}$',

### 2015-07-08 code/plot_joint_posterior.py

@@ -10,9 +10,9 @@ nc = newcolors.copy()
 matplotlib.colors.cnames.update(nc)
 
 param_name_map = {'tage':'Age (Gyr)',
-                  'mass': '$M_*$ $(M_\odot/10^{5})$',
-                  'dust2':'$\tau_V$',
-                  'zmet': '$\log Z/Z_\odot$',
+                  'mass': r'$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':r'$\tau_V$',
+                  'zmet': r'$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',
                   }

### 2015-07-08 code/plot_nphot.py

@@ -10,15 +10,15 @@ pnames = ['mass','tage','zmet','dust2']
 pmap = {'mass': lambda x: np.log10(x),
         'tage': lambda x: np.log10(x)
         }
-plabel_map = {'mass':r'log M$_*$',
+plabel_map = {'mass':'log M$_*$',
               'tage': 'log Age',
-              'zmet': r'log $Z/Z_\odot$',
-              'dust2':r'$\tau_V$'
+              'zmet': 'log $Z/Z_\odot$',
+              'dust2':'$\tau_V$'
               }
-pvlabel_map = {'mass':r'M$_*$',
+pvlabel_map = {'mass':'M$_*$',
               'tage': 'Age (Gyr)',
-              'zmet': r'log $Z/Z_\odot$',
-              'dust2':r'$\tau_V$'
+              'zmet': 'log $Z/Z_\odot$',
+              'dust2':'$\tau_V$'
               }
 
 sfraction = 0.90
@@ -43,12 +43,13 @@ if __name__ == "__main__":
     as_hist = False
     
     runs = ['results/ggc_mock_speconly.u0.t9.0_z0.0_a0.5_1431313829_mcmc', #g
+            'results/ggc_mock_gi_spec_linear.u0.t12.0_z0.0_a0.5_5486144_1436374818_mcmc', #gi
             'results/ggc_mock_griz_spec_linear.u0.t12.0_z0.0_a0.5_5429625_1435022619_mcmc', #griz
             #'results/ggc_mock_specphot_linear.u0.t9.0_z0.0_a0.5_5280432_1431898211_mcmc', #grizJHK
             'results/ggc_mock_specphot_linear.u0.t12.0_z0.0_a0.5_5313542_1432675345_mcmc', #grizJHK 
             ]
-    runlabel = ['$g$','$griz$', '$griz$\n$JHK_s$']
-    pvary = [1, 2, 3]
+    runlabel = ['$g$','$gi$','$griz$', '$griz$\n$JHK_s$']
+    pvary = [1, 2, 3, 4]
     nreal = len(runs)
     results, models = read_results(runs)
     ytitle=r'$\Delta$'
@@ -59,12 +60,12 @@ if __name__ == "__main__":
         dfig, dax = deltafig_vspar(results, models, pname, pvary,
                                    sfraction=sfraction, thin=thin,
                                    fax=(None, dax), pmap=pmap,
-                                   xlims=(0, 4),
+                                   xlims=(min(pvary)-0.5, max(pvary)+0.5),
[…]

### 2015-07-08 code/plot_real_joint_posterior.py

@@ -9,10 +9,10 @@ nc = newcolors.copy()
 #nc.pop('magenta')
 matplotlib.colors.cnames.update(nc)
 
-param_name_map = {'tage':'Age (Gyr)',
-                  'mass': '$M_*$ $(M_\odot/10^{5})$',
-                  'dust2':'$\tau_V$',
-                  'zmet': '$\log Z/Z_\odot$',
+param_name_map = {'tage':r'Age (Gyr)',
+                  'mass': r'$M_*$ $(M_\odot/10^{5})$',
+                  'dust2':r'$\tau_V$',
+                  'zmet': r'$\log Z/Z_\odot$',
                   'sigma_smooth': '$\sigma_{{LSF}}$',
                   'zred': '${\it z}$',
                   }
@@ -105,7 +105,7 @@ if __name__ == "__main__":
             else:
                 ax.set_yticklabels('')
             if k == (npar-1):
-                ax.set_xlabel(pnmap.get(p1,p1))
+                ax.set_xlabel(pnmap.get(p1,p1), fontsize=12)
                 dax.set_xlim(ax.get_xlim())
             else:
                 ax.set_xticklabels('')

### 2015-07-12 tex/ms.tex
start reorganizing for consistent runs and mocks, switching to linear fitting, fix strings for some plots
changes to mock generation script for ease of use, consistency

@@
 photometry.
-This amounts to propogating the uncertainties in the
+This amounts to propagating the uncertainties in the
 spectrophotometric calibration (or alternatively in the continuum
@@
 If you don't believe the reported data noise variances $\sigma_n^2$,
-it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
+it often makes sense to add in quadrature a ``jitter'' variance $b^2$.
 This is a simple modification of the chi-squared log-likelihood:
 \begin{eqnarray}\label{eq:photometricLF}
-\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N
+\ln p(d\given\theta,b^2) &=& -\frac{1}{2}\,\sum_{n=1}^N
                              \left[\frac{[d_n - \mu_n(\theta)]^2}
-                             {[\sigma_n^2 + s^2]} + 
-                             \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
+                             {[\sigma_n^2 + b^2]} + 
+                             \ln(2\pi\,[\sigma_n^2 + b^2]) \right]
 \quad .
@@
 This modification shows the necessity of including the log-variance
-term.  Large $s$ reduces the penalty for individual large residuals,
+term.  Large $b$ reduces the penalty for individual large residuals,
 but also reduces the reward for well-fit data.
@@
 measurements in what follows.  For photometric data this ``jitter'' is
-often best described as a fractional error, $s^2 \equiv
-\hat{s}^2\mu(\theta)^2$, corresponding for example to an additional
+often best described as a fractional error, $b^2 \equiv
+\hat{b}^2\mu(\theta)^2$, corresponding for example to an additional
 magnitude zero-point uncertainty.  In this formulation, if $\theta$
-are the parameters of interest, the jitter variance $\hat{s} =
-s/\mu(\theta)$ is a nuisance noise-model parameter representing
+are the parameters of interest, the jitter variance $\hat{b} =
+b/\mu(\theta)$ is a nuisance noise-model parameter representing
 additonal fractional uncertainty in the flux.
@@
 a generalization of the modified log-likelihood introduced in
-Equation \label{eq:photometricLF} that allows for correlated noise in
+equation~\label{eq:photometricLF} that allows for correlated noise in
 the residuals, as would be introduced by inaccurate calibration.
@@
 strong degeneracies between model and polynomial parameters, whereas
-the GP {\color{blue} BDJ make this more precise and correct} only
-reduces the likelihood penalty for residuals on the scale of $\ell$
-with amplitude $a$ that {\it can't} be fit by the mean model.
+the Gaussian Process {\color{blue} BDJ make this more precise and
+correct} likelihood only reduces the penalty for residuals on the
+scale of $\ell$ with amplitude $a$ that {\it can't} be fit by the mean
+model.
+
+The two log-likelihoods, for photometry and spectroscopy, are combined
+into a single likelihood function,
+\begin{eqnarray}\displaystyle ln p(d_s, d_p\given \theta, \alpha, b) =
+ln p_{spec}(d_s\given \theta, alpha) + ln p_{phot}(d_p\given \theta,
+b) \quad .
+\end{eqnarray} where now $d_s$ is the spectroscopic data and $d_p$ is
+the photometric data.  The spectroscipc likelihood $p_{spec}$ is given
+by equation~(\ref{eq:spectroscopicLF}) and $p_{phot}$ is given by
+equation~(\ref{eq:photometricLF}).
 
@@
 \tilde{\Delta} & = & K \, C^{-1} \, \Delta
-\end{eqnarray}.  
+\quad .
+\end{eqnarray}
 For the perfectly calibrated spectrum the true calibration vector
@@
 
-When the spectrophotometric calibration is assumed to be unknown,
-the posterior PDFs for stellar mass and especially $A_v$ become
-extremely large.  There is now no information about the overall shape
-of the SED (and hence the dust attenuation), and the overall
-normalization is constrained entirely by the single photometric point.
-The uncertainty in the stellar mass is somewhat broader than the
-uncertainty on the $g$-band flux because of the variation in
-mass-to-light ratio due to uncertainties in dust and, to a lesser
+When the spectrophotometric calibration is assumed to be unknown and
+is explicitly modeled, as in Figure \ref{fig:speconly_calibrated}, the
+posterior PDFs for stellar mass and especially $A_v$ become extremely
+large.  There is now no information about the overall shape of the SED
+(and hence the dust attenuation), and the overall normalization is
+constrained entirely by the single photometric point.  The fractional
+uncertainty in the stellar mass is somewhat broader than the
+fractional uncertainty on the $g$-band flux because of the variation
+in mass-to-light ratio due to uncertainties in dust and, to a lesser
 extent, age.
@@
 similar to the case of the \emph{calibrated} spectrum. An important
-difference is that the inferred calibration vector now contains numerous small scale wiggles,
-similar to the actual calibration vector.  The overall shape of the
-spectrum is still unconstrained, leading to large degeneracies between
-the polynomial terms and the dust attenuation.
+difference is that the inferred calibration vector now contains
+numerous small scale wiggles, similar to the actual calibration vector
+used to generate the mock.  The overall shape of the spectrum is still
+unconstrained, leading to large degeneracies between the polynomial
+terms and the dust attenuation, and a poor constraint on the dust
+attenuation and stellar mass.
 
@@
 
-\bibitem[Bertelli et al.(1994)]{bertelli94} Bertelli, G., Bressan, A., Chiosi, C., Fagotto, F., \& Nasi, E.\ 1994, \aaps, 106, 275
+\bibitem[Bertelli et al.(1994)]{bertelli94} Bertelli, G., Bressan, A., 
+Chiosi, C., Fagotto, F., \& Nasi, E.\ 1994, \aaps, 106, 275
 
@@
 
-\bibitem[Sch{\"o}nrich 
-\& Bergemann(2014)]{schonrich14} Sch{\"o}nrich, R., \& Bergemann, M.\ 2014, \mnras, 443, 698
+\bibitem[Sch{\"o}nrich \& Bergemann(2014)]{schonrich14} Sch{\"o}nrich,
+  R., \& Bergemann, M.\ 2014, \mnras, 443, 698
 

### 2015-07-12 code/make_ggc_mocks.py

@@ -194,55 +194,83 @@ model_params.append({'name': 'phot_jitter', 'N':1,
                         'prior_args': {'mini':0.0, 'maxi':0.1}})
 
 
-if __name__ == "__main__":
+def main(versiondir='', do_vary=False, do_noise=False,
+         zmet=0.0, tage=12.0, dust2=0.5, **kwargs):
 
-     
+        
+    fiducial_params = {'tage':float(tage), 'zmet':float(zmet), 'dust2':float(dust2)}
+    vary_params = {'tage': [0.3, 1.1, 3.0, 6.0, 9.0, 12.0],
+                   'zmet': [-1.5, -1.0, -0.5, 0.0, 0.15],
+                   'dust2': [0, 0.5, 1.0, 2.0]}
+        
     info = {'objname': 'NGC1851',
             'datadir': os.path.join(sdir, 'data/ggclib/spectra/'),
             'outdir': os.path.join(sdir, 'data/ggclib/mocks/'),
             'apply_cal': True,
             'add_noise': False,
-            'mask': True
-            }
+            'mask': True,
+            'phot_snr':10}
+        
+    info.update(kwargs)
     caltype = ['c', 'u']
     noisetype = ['0','1']
     name_template = os.path.join(info['outdir'], lib,
                                  'ggc_mock.{0}{1}.t{2:3.1f}_z{3:3.1f}_a{4:3.1f}.pkl')
-    vary_params = {'tage': [0.3, 1.1, 3.0, 6.0, 9.0, 12.0],
-                   'zmet': [-1.5, -1.0, -0.5, 0.0, 0.15],
-                   'dust2': [0, 0.5, 1.0, 2.0]
-                   }
-    #vary_params = {'tage':[10.0]}
-    #theta_default = np.array([1.0, 0.0, 0.5])
     model = sedmodel.SedModel(model_params)
+    for k, v in fiducial_params.iteritems():
+        model.params[k] = np.atleast_1d(np.array(v))
     theta_default = model.initial_theta.copy()
 
-    #make mocks with varied parameters
-    for p, vals in vary_params.iteritems():
-        ind = model.theta_labels().index(p)
+    # Make calibrated mock
+    info['apply_cal'] = False
+    theta = theta_default.copy()
+    mock = ggcdata.ggc_mock(model, theta, sps, **info)
+    filename = name_template.format(caltype[info['apply_cal']], 0, *theta)
+    print('writing to {0}'.format(filename))
[…]

### 2015-07-14 code/jobscripts/make_jobscripts.py
algorithmically generate sbatch jobscripts, change to fiducial paremeters in make mocks

@@ -1,0 +1,46 @@
+import os
+import numpy as np
+
+sdir = os.path.join(os.environ.get('PROJECTS'), 'speccal')
+datadir= "$PROJECTS/speccal/data/ggclib/mocks/miles/"
+jobscriptdir = os.path.join(sdir, 'code','jobscripts')
+accounts = {'PHAT': 'TG-AST130057'}
+
+def make_stampede_mock_job(ncpu=16, niter=1024, do_powell=True,
+                           paramfile='mock_specphot_linear',
+                           params='u0.t12.z0.0.a0.5',
+                           partition='normal',
+                           walltime=5.0,
+                           jobscriptdir=jobscriptdir,
+                           account='TG-AST130057',
+                           noisefactor=10.0):
+
+    nwalkers = (ncpu - 1) * 2
+    wt = '{0:02.0f}:{1:02.0f}:00'.format(walltime, np.mod(walltime, 1) * 60)
+    jobname = '{0}.{1}'.format(paramfile, params)
+    scriptname = os.path.join(jobscriptdir, '{0}.sh'.format(jobname))
+    out = open(scriptname, 'w')
+    out.write("#!/bin/bash\n\n")
+    out.write("###partition\n"
+              "#SBATCH -p {}\n\n".format(partition))
+    out.write("### Requested number of nodes\n"
+              "#SBATCH -n {0}\n\n".format(ncpu))
+    out.write("### Requested computing time\n"
+              "#SBATCH -t {0}\n\n".format(wt))
+    out.write("### Account\n"
+              "#{0}\n\n".format(account))
+    out.write("### Job name\n"
+              "#SBATCH -J '{0}'\n\n".format(jobname))
+    out.write("### output and error logs\n"
+              "#SBATCH -o {0}_%j.out\n"
+              "#SBATCH -e {0}_%j.err\n\n".format(jobname))
+    out.write("\n ibrun python-mpi $PROJECTS/speccal/code/prospectr.py \\\n")
+    out.write(" --param_file=$PROJECTS/speccal/code/paramfiles/{0}.py \\\n".format(paramfile))
+    out.write(" --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.{0}.pkl \\\n".format(params))
+    out.write(" --outfile=$PROJECTS/speccal/code/results/{0}_$SLURM_JOB_ID \\\n".format(jobname))
+    out.write(" --nwalkers={0}"
+              " --niter={1}"
[…]

### 2015-07-14 code/make_paper.sh

@@ -1,17 +1,56 @@
 #!bin/sh
 
 # define a version
-version="v1.0"
+version=""
 
 # First we make the mocks with fiducial parameters
-ft="9.0"
-fz="0.0"
-fa="0.5"
-fall="t${ft}_z${fz}_a${fa}"
-#python make_ggc_mocks #$version $ft $fz $fa
-ft, fa, fz = make_ggc_mocks.main(tage=ft, zmet=fz, dust2=fa, do_noise=True, do_vary=True)
+fiducial_params = {'tage':12.0, 'zmet':0.0, 'dust2':0.5}
+fall = "t{tage:3.1f}_z{zmet:3.1f}_a{dust2:3.1f}".format(**fiducial_params)
 
-### Then we build jobsripts and fit the mocks 
+ft, fa, fz = make_ggc_mocks.main(fiducial_params=fiducial+params,
+				 do_noise=True, do_vary=True,
+				 version=version)
+
+### Then we build jobsripts
+import make_jobscripts
+make_job = make_jobscripts.make_stampede_mock_job
+
+# speconly_ideal
+jobn, ideal_script = make_job(ncpu=64, niter=1024,
+  			      paramfile='mock_speconly_ideal',
+			      params='c0.{0}'.format(fall),
+			      do_powell=False, noisefactor=10)
+
+# speconly_calibrated, lo S/N
+jobn, sonlycal_script = make_job(ncpu=128, niter=6144,
+  			         param_file='mock_speconly_linear',
+			         params='c0.{0}'.format(fall),
+			         do_powell=False, noisefactor=10)
+
+# speconly_uncalibrated, lo S/N
+jobn, sonlycal_script = make_job(ncpu=128, niter=6144,
+  			         param_file='mock_speconly_linear',
+			         params='u0.{0}'.format(fall),
+			         do_powell=False, noisefactor=10)
+
+# photonly
+jobn, photonly_script = make_job(ncpu=128, niter=1024,
+  			         param_file='mock_photonly',
+			         params='c0.{0}'.format(fall),
+			         do_powell=False, noisefactor=10)
+
+# specphot uncalibrated
+jobn, specphot_script = make_job(ncpu=128, niter=2048,
+  			         param_file='mock_specphot_linear',
+			         params='c0.{0}'.format(fall),
+			         do_powell=False, noisefactor=10)
+# noise_runs
+
[…]

### 2015-07-21 tex/ms.tex
support for mocks with differnt run parameters, add CMD based values to joint real posterior plot

@@
 The calibration-vector and Gaussian-Process modified log-likelihood is
-\begin{eqnarray}\label{eq:spectroscopicLF_v2}
+\begin{eqnarray}
+\label{eq:spectroscopicLF}
 \ln p(d\given\theta,\alpha) &=&
@@
 into a single likelihood function,
-\begin{eqnarray}\displaystyle ln p(d_s, d_p\given \theta, \alpha, b) =
-ln p_{spec}(d_s\given \theta, alpha) + ln p_{phot}(d_p\given \theta,
-b) \quad .
+\begin{eqnarray}\displaystyle 
+\ln p(d_s, d_p\given \theta, \alpha, b) =
+\ln p_{spec}(d_s\given \theta, \alpha) + \ln p_{phot}(d_p\given\theta, b) 
+\quad .
 \end{eqnarray} where now $d_s$ is the spectroscopic data and $d_p$ is
-the photometric data.  The spectroscipc likelihood $p_{spec}$ is given
+the photometric data.  The spectroscopic likelihood $p_{spec}$ is given
 by equation~(\ref{eq:spectroscopicLF}) and $p_{phot}$ is given by
@@
   good as we could get given the data and its uncertainties.} 
+ Make sure this is run for the linear model.
 
@@
 
-\item Compare the physical parameters inferred from from the real
-  calibrated and uncalibrated spectrum with each other and with CMD
+\item \sout{Compare the physical parameters inferred from from the real
+  calibrated and uncalibrated spectrum with each other} and with CMD
   based parameters.
@@
 uncertainty into the model parameters $\theta$.
+
 {\color{blue} Discuss more complicated covariance kernels, multiple
 kernels, combining fractional and absolute covariance amplitudes.}
+In the present study we have used a single, relatively simple kernel
+function to construct the covariance matrix.  It is possible to
+include multiple kernels by simply adding the resulting covariance
+kernels.  For example, one could add an additional kernel with a small
+amplitude and wavelength scale to account for model imperfections
+\citep[e.g.,][]{czekala15} or include covariance structure expected
+from the data reduction process \citep[e.g., ][]{bolton10} which
+would absolute (i.e. not a fraction of the mean model.)
 
@@
 in principle add information.  This would occur if models with very
-similar spectra in the observed range had differing SEDs outside that
-range.
+similar spectra in the observed range had widely differing SEDs
+outside that range.
 
@@
 
+\bibitem[Bolton \& Schlegel(2010)]{bolton10} Bolton, A.~S., \& 
+Schlegel, D.~J.\ 2010, \pasp, 122, 248
+
 \bibitem[Cardelli \etal(1989)]{CCM89} 

### 2015-07-21 code/jobscripts/runjob_mac.sh

@@ -25,7 +25,7 @@ mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/
 mpirun -np 5 python prospectr.py --param_file=$PROJECTS/speccal/code/paramfiles/mock_photonly.py \
   --filename=$PROJECTS/speccal/data/ggclib/mocks/miles/ggc_mock.c0.t9.0_z0.0_a0.5.pkl \
   --outfile=$PROJECTS/speccal/code/results/ggc_mock_photonly.c0.t9.0_z0.0_a0.5 \
-  --nwalkers=126 --niter=2048 --do_powell=False 
+  --nwalkers=64 --niter=2048 --do_powell=False 
 
 # somephot linear
 mpirun -np 5 python prospectr.py \

### 2015-07-21 code/make_ggc_mocks.py

@@ -198,7 +198,6 @@ fd = {'tage':12.0, 'zmet':0.0, 'dust2':0.5}
 def main(versiondir='', do_vary=False, do_noise=False,
          fiducial_params=fd, **kwargs):
 
-        
     
     vary_params = {'tage': [0.3, 1.1, 3.0, 6.0, 9.0, 12.0],
                    'zmet': [-1.5, -1.0, -0.5, 0.0, 0.15],
@@ -211,12 +210,15 @@ def main(versiondir='', do_vary=False, do_noise=False,
             'add_noise': False,
             'mask': True,
             'phot_snr':10}
-        
+
+    extras='.'
+    for k, v in kwargs.iteritems():
+        extras += '{}{}.'.format(k, v)
     info.update(kwargs)
     caltype = ['c', 'u']
     noisetype = ['0','1']
     name_template = os.path.join(info['outdir'], lib,
-                                 'ggc_mock.{0}{1}.t{2:3.1f}_z{3:3.1f}_a{4:3.1f}.pkl')
+                                 'ggc_mock.{1}{2}.t{3:3.1f}_z{4:3.1f}_a{5:3.1f}{0}pkl')
     model = sedmodel.SedModel(model_params)
     for k, v in fiducial_params.iteritems():
         model.params[k] = np.atleast_1d(np.array(v))
@@ -226,7 +228,7 @@ def main(versiondir='', do_vary=False, do_noise=False,
     info['apply_cal'] = False
     theta = theta_default.copy()
     mock = ggcdata.ggc_mock(model, theta, sps, **info)
-    filename = name_template.format(caltype[info['apply_cal']], 0, *theta)
+    filename = name_template.format(extras, caltype[info['apply_cal']], 0, *theta)
     print('writing to {0}'.format(filename))
     with open(filename, 'w') as f:
         pickle.dump(mock, f)
@@ -235,7 +237,7 @@ def main(versiondir='', do_vary=False, do_noise=False,
     info['apply_cal'] = True
     theta = theta_default.copy()
     mock = ggcdata.ggc_mock(model, theta, sps, **info)
-    filename = name_template.format(caltype[info['apply_cal']], 0, *theta)
+    filename = name_template.format(extras, caltype[info['apply_cal']], 0, *theta)
     print('writing to {0}'.format(filename))
     with open(filename, 'w') as f:
         pickle.dump(mock, f)
[…]

### 2015-07-21 code/make_paper.sh

@@ -4,12 +4,16 @@
 version=""
 
 # First we make the mocks with fiducial parameters
+import make_ggc_mocks
 fiducial_params = {'tage':12.0, 'zmet':0.0, 'dust2':0.5}
 fall = "t{tage:3.1f}_z{zmet:3.1f}_a{dust2:3.1f}".format(**fiducial_params)
 
-ft, fa, fz = make_ggc_mocks.main(fiducial_params=fiducial+params,
+ft, fa, fz = make_ggc_mocks.main(fiducial_params=fiducial_params,
 				 do_noise=True, do_vary=True,
-				 version=version)
+				 versiondir=version)
+ft, fa, fz = make_ggc_mocks.main(fiducial_params=fiducial_params,
+				 do_noise=False, do_vary=False,
+				 versiondir=version, phot_snr=20)
 
 ### Then we build jobsripts
 import make_jobscripts
@@ -23,17 +27,18 @@ jobn, ideal_script = make_job(ncpu=128, niter=1024,
 			      do_powell=False, noisefactor=10)
 
 # speconly_calibrated, lo S/N
-jobn, sonlycal_script = make_job(ncpu=128, niter=6144,
-				 walltime=5.0,
+jobn, sonlycal_script = make_job(ncpu=256, niter=6144,
+				 walltime=8.0,
   			         paramfile='mock_speconly_linear',
 			         params='c0.{0}'.format(fall),
 			         do_powell=False, noisefactor=10)
 
 # speconly_uncalibrated, lo S/N
-jobn, sonlycal_script = make_job(ncpu=128, niter=6144,
-  			         paramfile='mock_speconly_linear',
-			         params='u0.{0}'.format(fall),
-			         do_powell=False, noisefactor=10)
+jobn, sonlyuncal_script = make_job(ncpu=128, niter=6144,
+	  			   walltime=6.0,
+  			           paramfile='mock_speconly_linear',
+			           params='u0.{0}'.format(fall),
+			           do_powell=False, noisefactor=10)
 
 # photonly
 jobn, photonly_script = make_job(ncpu=64, niter=1024,
@@ -45,7 +50,7 @@ jobn, photonly_script = make_job(ncpu=64, niter=1024,
 # specphot uncalibrated
[…]

### 2015-07-21 code/plot_real_joint_posterior.py

@@ -54,8 +54,11 @@ def compute_sigma_level(trace1, trace2, nbins=30):
 
 
 if __name__ == "__main__":
-    truths = None # {'mass':, 'tage':, 'dust2':}
     
+    truths = {'mass':1e5, 'zmet':-1.25, 'tage':10.0, 'dust2':0.12}
+    truth_references = {'zmet': ["Yong et al. (2015)", "Gratton et al. 2012"],
+                        'tage': ["Cassisi et al. (2008)"],
+                        'dust2': ["Cassisi et al. (2008)"]}
     real_cal="results/ggc_ngc1851_1432787257_mcmc"
     real_uncal="results/ggc_ngc1851_uncal_tightprior_1433448554_mcmc"
     resfiles = [real_cal, real_uncal]

### 2015-07-21 code/plotting.py

@@ -200,13 +200,11 @@ def residualfig(wave, obsvec, specvecs, unc=None, chi=False,
             x, y, e = wave, obsvec, unc
             rax.fill_between(x, -e, e, facecolor='grey', alpha=0.3)
     # Plot posterior samples of the observed spectrum as a residual
-    for i, specs in enumerate(specvecs):
-        if i==0:
-            label = 'Posterior samples'
-        else:
-            label = None
+    label = 'Posterior samples'
+    for specs in specvecs:
         rax.plot(wave, (specs[3] - obsvec) / chi_unc, linewidth=0.5,
                  color=basecolor, alpha=0.3, label=label)
+        label = ''
     rax.axhline(0.0, linestyle=':', color='k')
     return rfig, rax
                 
